---
title: "Model Comparison Report: igt - luc"
subtitle: "10_models_15eaa99c"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: hide
    df_print: paged
params:
  results_file: "../data/model_comparison_results.rds"
  task: "igt"
  cohort: "luc"
  session: "00"
  comparison_name: "10_models_15eaa99c"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 10, fig.height = 6, dpi = 300)

# Load required libraries
suppressPackageStartupMessages({
  library(dplyr)
  library(ggplot2)
  library(knitr)
  library(DT)
  library(plotly)
  library(here)
})

# Load results
results <- readRDS(params$results_file)
comparison_data <- results$comparison_data
analysis_results <- results$analysis_results
models_by_type <- results$models_by_type
config <- results$config

# Load helper functions
source(file.path(here::here(), "scripts", "model_comparison", "helpers", "model_comparison_helpers.R"))
source(file.path(here::here(), "scripts", "model_comparison", "visualization", "comparison_plots.R"))
source(file.path(here::here(), "scripts", "ppc", "helpers", "task_config.R"))
```

# Executive Summary

## Key Findings

```{r executive-summary}
# Create executive summary table
summary_table <- data.frame(
  Criterion = character(),
  Best_Model = character(), 
  Performance = character(),
  Notes = character(),
  stringsAsFactors = FALSE
)

# Information Criteria Winner
if ("ic" %in% names(analysis_results) && nrow(analysis_results$ic$overall_ranking) > 0) {
  best_ic_model <- analysis_results$ic$overall_ranking$model[1]
  ic_method <- analysis_results$ic$metadata$ic_method
  delta_col <- grep("^delta_", names(analysis_results$ic$overall_ranking), value = TRUE)[1]
  best_delta <- analysis_results$ic$overall_ranking[[delta_col]][1]
  
  summary_table <- rbind(summary_table, data.frame(
    Criterion = paste("Information Criteria (", toupper(ic_method), ")", sep = ""),
    Best_Model = best_ic_model,
    Performance = sprintf("Δ%s = %.2f", toupper(ic_method), best_delta),
    Notes = analysis_results$ic$overall_ranking$performance_tier[1]
  ))
}

# Parameter Recovery Winner
if ("recovery" %in% names(analysis_results) && nrow(analysis_results$recovery$model_summary) > 0) {
  best_recovery_model <- analysis_results$recovery$model_summary$model[1]
  best_recovery_score <- analysis_results$recovery$model_summary$mean_correlation[1]
  
  summary_table <- rbind(summary_table, data.frame(
    Criterion = "Parameter Recovery",
    Best_Model = best_recovery_model,
    Performance = sprintf("r = %.3f", best_recovery_score),
    Notes = analysis_results$recovery$model_summary$recovery_quality[1]
  ))
}

# PPC Winner
if ("ppc" %in% names(analysis_results) && nrow(analysis_results$ppc$model_summary) > 0) {
  best_ppc_model <- analysis_results$ppc$model_summary$model[1]
  best_ppc_score <- analysis_results$ppc$model_summary$overall_proportion_extreme[1]
  
  summary_table <- rbind(summary_table, data.frame(
    Criterion = "Posterior Predictive Checks",
    Best_Model = best_ppc_model,
    Performance = sprintf("%.1f%% extreme", best_ppc_score * 100),
    Notes = analysis_results$ppc$model_summary$model_quality[1]
  ))
}

kable(summary_table, caption = "Model Comparison Summary") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
```

## Models Analyzed

```{r models-analyzed}
models_table <- data.frame(
  Model = names(comparison_data),
  Type = sapply(names(comparison_data), classify_model_type),
  Has_Recovery = sapply(comparison_data, function(x) !is.null(x$recovery)),
  Has_PPC = sapply(comparison_data, function(x) !is.null(x$ppc)),
  Has_IC = sapply(comparison_data, function(x) !is.null(x$ic)),
  stringsAsFactors = FALSE
)

models_table$Complete <- models_table$Has_Recovery & models_table$Has_PPC & models_table$Has_IC

kable(models_table, caption = "Available Data by Model") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
  kableExtra::column_spec(6, background = ifelse(models_table$Complete, "#d4edda", "#f8d7da"))
```

# Information Criteria Analysis

## Information Criteria Rankings

```{r ic-ranking-table}
if ("ic" %in% names(analysis_results) && nrow(analysis_results$ic$overall_ranking) > 0) {
  ic_ranking <- analysis_results$ic$overall_ranking
  ic_method <- analysis_results$ic$metadata$ic_method
  
  # Display main ranking table
  display_cols <- c("rank", "model", "model_type")
  display_cols <- c(display_cols, grep("estimate$|^delta_|_se$|model_weight|performance_tier", 
                                      names(ic_ranking), value = TRUE))
  
  ranking_table <- ic_ranking[display_cols] %>%
    mutate(across(where(is.numeric), ~round(.x, 3)))
  
  DT::datatable(ranking_table, 
                caption = paste("Model Ranking by", toupper(ic_method)),
                options = list(pageLength = 15, scrollX = TRUE)) %>%
    DT::formatStyle("performance_tier",
                    backgroundColor = DT::styleEqual(
                      c("top_tier", "competitive", "considerable_difference", "strong_difference", "decisive_difference"),
                      c("#d4edda", "#fff3cd", "#ffeaa7", "#fdcb6e", "#e17055")
                    ))
} else {
  cat("No information criteria results available.")
}
```

## Model Selection Evidence

```{r ic-evidence}
if ("ic" %in% names(analysis_results) && nrow(analysis_results$ic$overall_ranking) > 0) {
  ic_ranking <- analysis_results$ic$overall_ranking
  
  # Create evidence strength summary
  evidence_summary <- ic_ranking %>%
    mutate(
      evidence_against_best = case_when(
        performance_tier == "top_tier" ~ "Negligible difference",
        performance_tier == "competitive" ~ "Weak evidence against",
        performance_tier == "considerable_difference" ~ "Moderate evidence against", 
        performance_tier == "strong_difference" ~ "Strong evidence against",
        performance_tier == "decisive_difference" ~ "Decisive evidence against",
        TRUE ~ "Unknown"
      )
    ) %>%
    count(evidence_against_best, model_type) %>%
    pivot_wider(names_from = model_type, values_from = n, values_fill = 0)
  
  kable(evidence_summary, caption = "Evidence Strength Summary") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
}
```

## Information Criteria Plots

```{r ic-plots, fig.height=8}
if ("ic" %in% names(analysis_results)) {
  # Create IC plots
  ic_plots <- create_ic_plots(analysis_results$ic, models_by_type)
  
  # Display ranking plot
  if (!is.null(ic_plots$ranking_plot)) {
    print(ic_plots$ranking_plot)
  }
  
  # Display weights plot
  if (!is.null(ic_plots$weights_plot)) {
    print(ic_plots$weights_plot)
  }
  
  # Display complexity plot if available
  if (!is.null(ic_plots$complexity_plot)) {
    print(ic_plots$complexity_plot)
  }
}
```

## Model Complexity Analysis

```{r complexity-analysis}
if ("ic" %in% names(analysis_results) && nrow(analysis_results$ic$complexity_analysis) > 0) {
  complexity_table <- analysis_results$ic$complexity_analysis %>%
    select(model, model_type, p_eff, complexity_category) %>%
    arrange(desc(p_eff))
  
  kable(complexity_table, caption = "Model Complexity Analysis") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
}
```

# Parameter Recovery Analysis

## Parameter Recovery by Construct Groups

```{r recovery-group-summary}
if ("recovery" %in% names(analysis_results) && nrow(analysis_results$recovery$group_summary) > 0) {
  recovery_summary <- analysis_results$recovery$group_summary %>%
    arrange(desc(mean_correlation)) %>%
    mutate(across(where(is.numeric), ~round(.x, 3)))
  
  DT::datatable(recovery_summary, 
                caption = "Parameter Recovery Quality by Construct Group",
                options = list(pageLength = 10, scrollX = TRUE)) %>%
    DT::formatStyle("recovery_quality",
                    backgroundColor = DT::styleEqual(
                      c("excellent", "good", "acceptable", "poor"),
                      c("#d4edda", "#d1ecf1", "#fff3cd", "#f8d7da")
                    ))
} else {
  cat("No parameter recovery results available.")
}
```

## Recovery Performance by Model

```{r recovery-model-summary}
if ("recovery" %in% names(analysis_results) && nrow(analysis_results$recovery$model_summary) > 0) {
  model_recovery <- analysis_results$recovery$model_summary %>%
    arrange(desc(mean_correlation)) %>%
    mutate(across(where(is.numeric), ~round(.x, 3)))
  
  DT::datatable(model_recovery, 
                caption = "Parameter Recovery Quality by Model",
                options = list(pageLength = 15, scrollX = TRUE)) %>%
    DT::formatStyle("recovery_quality",
                    backgroundColor = DT::styleEqual(
                      c("excellent", "good", "acceptable", "poor"),
                      c("#d4edda", "#d1ecf1", "#fff3cd", "#f8d7da")
                    ))
}
```

## Parameter Recovery Visualizations

```{r recovery-plots, fig.height=10}
if ("recovery" %in% names(analysis_results)) {
  # Create recovery plots
  recovery_plots <- generate_all_recovery_plots(analysis_results$recovery, models_by_type)
  
  # Display group heatmap
  if (!is.null(recovery_plots$heatmap)) {
    print(recovery_plots$heatmap)
  }
  
  # Display model comparison
  if (!is.null(recovery_plots$comparison)) {
    print(recovery_plots$comparison)
  }
  
  # Display type comparison
  if (!is.null(recovery_plots$by_type)) {
    print(recovery_plots$by_type)
  }
}
```

## Best and Worst Performing Groups

```{r recovery-best-worst}
if ("recovery" %in% names(analysis_results) && 
    "best_worst_groups" %in% names(analysis_results$recovery)) {
  
  best_worst <- analysis_results$recovery$best_worst_groups
  
  # Best groups
  if (nrow(best_worst$best_groups) > 0) {
    cat("### Best Recovered Parameter Groupsnn")
    best_table <- best_worst$best_groups %>%
      select(group, mean_correlation, recovery_quality, n_models) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    kable(best_table, caption = "Top Parameter Groups by Recovery Quality") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    cat("nn")
  }
  
  # Worst groups
  if (nrow(best_worst$worst_groups) > 0) {
    cat("### Most Challenging Parameter Groupsnn")
    worst_table <- best_worst$worst_groups %>%
      select(group, mean_correlation, recovery_quality, n_models) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    kable(worst_table, caption = "Most Challenging Parameter Groups") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    cat("nn")
  }
  
  # Poor recovery groups
  if (nrow(best_worst$poor_groups) > 0) {
    cat("### Parameter Groups with Poor Recoverynn")
    poor_table <- best_worst$poor_groups %>%
      select(group, mean_correlation, recovery_quality, n_models) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    kable(poor_table, caption = "Groups with Poor Recovery (r < 0.4)") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    cat("nn")
  }
}
```

## Cross-Model Type Comparison

```{r recovery-cross-model}
if ("recovery" %in% names(analysis_results) && nrow(analysis_results$recovery$cross_model_comparison) > 0) {
  cross_comparison <- analysis_results$recovery$cross_model_comparison %>%
    arrange(model_type, desc(mean_correlation)) %>%
    mutate(across(where(is.numeric), ~round(.x, 3)))
  
  DT::datatable(cross_comparison, 
                caption = "Parameter Recovery by Model Type and Group",
                options = list(pageLength = 15, scrollX = TRUE)) %>%
    DT::formatStyle("recovery_quality",
                    backgroundColor = DT::styleEqual(
                      c("excellent", "good", "acceptable", "poor"),
                      c("#d4edda", "#d1ecf1", "#fff3cd", "#f8d7da")
                    ))
}
```

## Parameter Recovery Insights

```{r recovery-insights}
if ("recovery" %in% names(analysis_results)) {
  cat("### Key Findingsnn")
  
  # Overall insights
  if (nrow(analysis_results$recovery$group_summary) > 0) {
    best_group <- analysis_results$recovery$group_summary$group[1]
    best_corr <- analysis_results$recovery$group_summary$mean_correlation[1]
    worst_group <- tail(analysis_results$recovery$group_summary$group, 1)
    worst_corr <- tail(analysis_results$recovery$group_summary$mean_correlation, 1)
    
    cat("- **Best recovered construct:** ", best_group, " (r = ", round(best_corr, 3), ")n")
    cat("- **Most challenging construct:** ", worst_group, " (r = ", round(worst_corr, 3), ")nn")
  }
  
  # Model insights
  if (nrow(analysis_results$recovery$model_summary) > 0) {
    best_model <- analysis_results$recovery$model_summary$model[1]
    best_model_corr <- analysis_results$recovery$model_summary$mean_correlation[1]
    
    cat("- **Best overall recovery:** ", best_model, " (mean r = ", round(best_model_corr, 3), ")nn")
  }
  
  # Type insights
  if (nrow(analysis_results$recovery$cross_model_comparison) > 0) {
    type_summary <- analysis_results$recovery$cross_model_comparison %>%
      group_by(model_type) %>%
      summarise(mean_recovery = mean(mean_correlation, na.rm = TRUE), .groups = "drop") %>%
      arrange(desc(mean_recovery))
    
    if (nrow(type_summary) > 1) {
      best_type <- type_summary$model_type[1]
      best_type_corr <- type_summary$mean_recovery[1]
      cat("- **Best model type for recovery:** ", best_type, " (mean r = ", round(best_type_corr, 3), ")nn")
    }
  }
}
```

# Posterior Predictive Checks

## PPC Performance by Behavioral Domain

```{r ppc-domain-summary}
if ("ppc" %in% names(analysis_results) && nrow(analysis_results$ppc$domain_summary) > 0) {
  domain_summary <- analysis_results$ppc$domain_summary %>%
    arrange(proportion_extreme) %>%
    mutate(across(where(is.numeric), ~round(.x, 3)))
  
  DT::datatable(domain_summary, 
                caption = "PPC Performance by Behavioral Domain",
                options = list(pageLength = 10, scrollX = TRUE)) %>%
    DT::formatStyle("domain_quality",
                    backgroundColor = DT::styleEqual(
                      c("excellent", "good", "acceptable", "concerning", "poor"),
                      c("#d4edda", "#d1ecf1", "#fff3cd", "#ffeaa7", "#f8d7da")
                    ))
} else {
  cat("No PPC domain results available.")
}
```

## PPC Performance by Model

```{r ppc-model-summary}
if ("ppc" %in% names(analysis_results) && nrow(analysis_results$ppc$model_summary) > 0) {
  model_ppc <- analysis_results$ppc$model_summary %>%
    arrange(overall_proportion_extreme) %>%
    mutate(across(where(is.numeric), ~round(.x, 3)))
  
  DT::datatable(model_ppc, 
                caption = "PPC Performance by Model",
                options = list(pageLength = 15, scrollX = TRUE)) %>%
    DT::formatStyle("model_quality",
                    backgroundColor = DT::styleEqual(
                      c("excellent", "good", "acceptable", "concerning", "poor"),
                      c("#d4edda", "#d1ecf1", "#fff3cd", "#ffeaa7", "#f8d7da")
                    ))
}
```

## PPC Visualizations

```{r ppc-plots, fig.height=10}
if ("ppc" %in% names(analysis_results)) {
  # Create PPC plots
  ppc_plots <- generate_all_ppc_plots(analysis_results$ppc, models_by_type, params$task)
  
  # Display domain heatmap
  if (!is.null(ppc_plots$domain_heatmap)) {
    print(ppc_plots$domain_heatmap)
  }
  
  # Display extreme failures
  if (!is.null(ppc_plots$failure_summary)) {
    print(ppc_plots$failure_summary)
  }
  
  # Display behavioral patterns
  if (!is.null(ppc_plots$domain_difficulty)) {
    print(ppc_plots$domain_difficulty)
  }
}
```

## Extreme PPC Failures

```{r ppc-extreme-failures}
if ("ppc" %in% names(analysis_results) && nrow(analysis_results$ppc$extreme_failures) > 0) {
  # Summarize extreme failures
  failure_summary <- analysis_results$ppc$extreme_failures %>%
    count(model, model_type, failure_severity, name = "n_failures") %>%
    pivot_wider(names_from = failure_severity, values_from = n_failures, values_fill = 0) %>%
    arrange(desc(severe), desc(moderate), desc(mild))
  
  DT::datatable(failure_summary, 
                caption = "Extreme PPC Failures by Model and Severity",
                options = list(pageLength = 15, scrollX = TRUE))
  
  # Most problematic statistics
  cat("nn### Most Problematic Statisticsnn")
  
  problem_stats <- analysis_results$ppc$extreme_failures %>%
    count(statistic, failure_severity) %>%
    pivot_wider(names_from = failure_severity, values_from = n, values_fill = 0) %>%
    mutate(total_failures = severe + moderate + mild) %>%
    arrange(desc(total_failures)) %>%
    head(10)
  
  kable(problem_stats, caption = "Statistics with Most Extreme PPP Failures") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  
} else {
  cat("No extreme PPC failures detected across all models.")
}
```

## Behavioral Pattern Analysis

```{r ppc-behavioral-patterns}
if ("ppc" %in% names(analysis_results) && "behavioral_patterns" %in% names(analysis_results$ppc)) {
  patterns <- analysis_results$ppc$behavioral_patterns
  
  # Difficult domains
  if ("difficult_domains" %in% names(patterns) && nrow(patterns$difficult_domains) > 0) {
    cat("### Most Challenging Behavioral Domainsnn")
    
    difficult_table <- patterns$difficult_domains %>%
      arrange(desc(mean_proportion_extreme)) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    kable(difficult_table, caption = "Challenging Domains by Model Type") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    cat("nn")
  }
  
  # RT performance by type (if available)
  if ("rt_performance_by_type" %in% names(patterns) && nrow(patterns$rt_performance_by_type) > 0) {
    cat("### RT Performance by Model Typenn")
    
    rt_table <- patterns$rt_performance_by_type %>%
      arrange(mean_proportion_extreme) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    kable(rt_table, caption = "RT Pattern Reproduction by Model Type") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    cat("nn")
  }
  
  # Learning performance by type (if available)
  if ("learning_performance_by_type" %in% names(patterns) && nrow(patterns$learning_performance_by_type) > 0) {
    cat("### Learning Dynamics Performance by Model Typenn")
    
    learning_table <- patterns$learning_performance_by_type %>%
      arrange(mean_proportion_extreme) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    kable(learning_table, caption = "Learning Pattern Reproduction by Model Type") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    cat("nn")
  }
  
  # Best/worst models by domain
  if ("model_performance_by_domain" %in% names(patterns) && nrow(patterns$model_performance_by_domain) > 0) {
    cat("### Best and Worst Models by Domainnn")
    
    domain_table <- patterns$model_performance_by_domain %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    kable(domain_table, caption = "Model Performance Range by Behavioral Domain") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }
}
```

## Task-Specific PPC Analysis

```{r ppc-task-specific}
if ("ppc" %in% names(analysis_results) && "task_specific_analysis" %in% names(analysis_results$ppc)) {
  task_analysis <- analysis_results$ppc$task_specific_analysis
  
  if (params$task == "igt_mod") {
    # mIGT-specific analysis
    if ("play_pass_analysis" %in% names(task_analysis) && nrow(task_analysis$play_pass_analysis) > 0) {
      cat("### Play/Pass Decision Patternsnn")
      
      play_pass_table <- task_analysis$play_pass_analysis %>%
        mutate(across(where(is.numeric), ~round(.x, 3))) %>%
        arrange(model, statistic)
      
      kable(play_pass_table, caption = "Play/Pass PPC Performance by Model") %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
      cat("nn")
    }
    
    if ("deck_preference_analysis" %in% names(task_analysis) && nrow(task_analysis$deck_preference_analysis) > 0) {
      cat("### Deck Preference Patternsnn")
      
      deck_table <- task_analysis$deck_preference_analysis %>%
        mutate(across(where(is.numeric), ~round(.x, 3))) %>%
        arrange(model, deck)
      
      kable(deck_table, caption = "Deck-Specific PPC Performance") %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    }
    
  } else if (params$task == "igt") {
    # IGT-specific analysis
    if ("deck_selection_analysis" %in% names(task_analysis) && nrow(task_analysis$deck_selection_analysis) > 0) {
      cat("### Deck Selection Patternsnn")
      
      deck_table <- task_analysis$deck_selection_analysis %>%
        mutate(across(where(is.numeric), ~round(.x, 3))) %>%
        arrange(model, statistic)
      
      kable(deck_table, caption = "Deck Selection PPC Performance") %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
      cat("nn")
    }
    
    if ("strategy_analysis" %in% names(task_analysis) && nrow(task_analysis$strategy_analysis) > 0) {
      cat("### Strategy Pattern Analysisnn")
      
      strategy_table <- task_analysis$strategy_analysis %>%
        mutate(across(where(is.numeric), ~round(.x, 3))) %>%
        arrange(model, statistic)
      
      kable(strategy_table, caption = "Strategy-Related PPC Performance") %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    }
  }
}
```

## PPC Insights Summary

```{r ppc-insights}
if ("ppc" %in% names(analysis_results)) {
  cat("### Key PPC Findingsnn")
  
  # Best performing models
  if (nrow(analysis_results$ppc$model_summary) > 0) {
    best_ppc_model <- analysis_results$ppc$model_summary$model[1]
    best_ppc_score <- analysis_results$ppc$model_summary$overall_proportion_extreme[1]
    
    cat("- **Best overall PPC performance:** ", best_ppc_model, " (", round(best_ppc_score * 100, 1), "% extreme PPP)n")
  }
  
  # Most challenging domains
  if (nrow(analysis_results$ppc$domain_summary) > 0) {
    difficult_domains <- analysis_results$ppc$domain_summary %>%
      arrange(desc(proportion_extreme)) %>%
      head(3) %>%
      pull(domain)
    
    cat("- **Most challenging behavioral domains:** ", paste(difficult_domains, collapse = ", "), "n")
  }
  
  # Overall failure rate
  if (nrow(analysis_results$ppc$extreme_failures) > 0) {
    total_statistics <- sum(analysis_results$ppc$model_summary$total_statistics, na.rm = TRUE)
    total_failures <- nrow(analysis_results$ppc$extreme_failures)
    failure_rate <- round((total_failures / total_statistics) * 100, 1)
    
    cat("- **Overall extreme failure rate:** ", failure_rate, "% of all statisticsn")
  }
  
  cat("n")
}
```

# Model Type Comparisons

```{r model-type-setup}
# Calculate cross-type performance metrics
type_summary <- data.frame()

if (length(models_by_type) > 1) {
  for (type_name in names(models_by_type)) {
    type_models <- models_by_type[[type_name]]
    
    if (length(type_models) == 0) next
    
    type_row <- data.frame(
      model_type = type_name,
      n_models = length(type_models),
      stringsAsFactors = FALSE
    )
    
    # IC performance
    if ("ic" %in% names(analysis_results) && nrow(analysis_results$ic$overall_ranking) > 0) {
      type_ic <- analysis_results$ic$overall_ranking %>%
        filter(model %in% type_models)
      
      if (nrow(type_ic) > 0) {
        # Get the delta column name dynamically
        delta_col <- grep("^delta_", names(type_ic), value = TRUE)[1]
        type_row$mean_delta_ic <- mean(type_ic[[delta_col]], na.rm = TRUE)
        type_row$best_ic_rank <- min(type_ic$rank, na.rm = TRUE)
        type_row$top_tier_models <- sum(type_ic$performance_tier == "top_tier", na.rm = TRUE)
      }
    }
    
    # Recovery performance
    if ("recovery" %in% names(analysis_results) && nrow(analysis_results$recovery$model_summary) > 0) {
      type_recovery <- analysis_results$recovery$model_summary %>%
        filter(model %in% type_models)
      
      if (nrow(type_recovery) > 0) {
        type_row$mean_recovery_correlation <- mean(type_recovery$mean_correlation, na.rm = TRUE)
        type_row$excellent_recovery_groups <- sum(type_recovery$recovery_quality == "excellent", na.rm = TRUE)
      }
    }
    
    # PPC performance
    if ("ppc" %in% names(analysis_results) && nrow(analysis_results$ppc$model_summary) > 0) {
      type_ppc <- analysis_results$ppc$model_summary %>%
        filter(model %in% type_models)
      
      if (nrow(type_ppc) > 0) {
        type_row$mean_ppc_extreme <- mean(type_ppc$overall_proportion_extreme, na.rm = TRUE)
        type_row$excellent_ppc_models <- sum(type_ppc$model_quality == "excellent", na.rm = TRUE)
      }
    }
    
    type_summary <- rbind(type_summary, type_row)
  }
}
```

## Performance Overview by Model Type

```{r model-type-overview}
if (nrow(type_summary) > 0) {
  display_summary <- type_summary %>%
    mutate(across(where(is.numeric), ~round(.x, 3))) %>%
    arrange(mean_delta_ic %||% 999)  # Sort by IC performance if available
  
  DT::datatable(display_summary, 
                caption = "Model Type Performance Summary",
                options = list(pageLength = 10, scrollX = TRUE)) %>%
    DT::formatRound(columns = which(sapply(display_summary, is.numeric)), digits = 3)
} else {
  cat("Only one model type available for comparison.")
}
```

## Information Criteria by Model Type

```{r ic-by-type}
if ("ic" %in% names(analysis_results) && length(analysis_results$ic$by_type_ranking) > 0) {
  
  # Create combined ranking plot
  combined_rankings <- bind_rows(analysis_results$ic$by_type_ranking, .id = "model_type_group")
  
  if (nrow(combined_rankings) > 0) {
    # Get delta column name
    delta_col <- grep("^delta_", names(combined_rankings), value = TRUE)[1]
    
    # Create plot
    type_ic_plot <- combined_rankings %>%
      ggplot(aes(x = !!sym(delta_col), y = reorder(model, !!sym(delta_col)), color = model_type_group)) +
      geom_point(size = 3) +
      geom_vline(xintercept = c(2, 4, 7, 10), linetype = "dashed", alpha = 0.5) +
      facet_wrap(~model_type_group, scales = "free_y", ncol = 1) +
      scale_color_viridis_d(option = "viridis") +
      labs(
        title = "Information Criteria Performance by Model Type",
        x = paste("Δ", toupper(gsub("delta_", "", delta_col))),
        y = "Model",
        color = "Model Type"
      ) +
      theme_minimal() +
      theme(legend.position = "none")
    
    print(type_ic_plot)
  }
  
  # Summary table by type
  ic_type_summary <- combined_rankings %>%
    group_by(model_type_group) %>%
    summarise(
      n_models = n(),
      best_rank = min(rank, na.rm = TRUE),
      mean_delta_ic = mean(!!sym(delta_col), na.rm = TRUE),
      top_tier_count = sum(performance_tier == "top_tier", na.rm = TRUE),
      competitive_count = sum(performance_tier %in% c("top_tier", "competitive"), na.rm = TRUE),
      .groups = "drop"
    ) %>%
    arrange(mean_delta_ic)
  
  kable(ic_type_summary, 
        caption = "Information Criteria Summary by Model Type",
        digits = 3) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
}
```

## Parameter Recovery by Model Type

```{r recovery-by-type}
if ("recovery" %in% names(analysis_results) && nrow(analysis_results$recovery$cross_model_comparison) > 0) {
  
  # Recovery performance by type and group
  recovery_type_plot <- analysis_results$recovery$cross_model_comparison %>%
    ggplot(aes(x = group, y = mean_correlation, fill = model_type)) +
    geom_col(position = position_dodge(width = 0.8), alpha = 0.8) +
    geom_errorbar(aes(ymin = mean_correlation - sd_correlation, 
                      ymax = mean_correlation + sd_correlation),
                  position = position_dodge(width = 0.8), width = 0.3) +
    scale_fill_viridis_d(name = "Model Type", option = "viridis") +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
    labs(
      title = "Parameter Recovery by Model Type and Construct Group",
      x = "Parameter Group",
      y = "Mean Recovery Correlation",
      caption = "Error bars show ±1 SD across models"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "bottom"
    )
  
  print(recovery_type_plot)
  
  # Summary statistics
  recovery_type_summary <- analysis_results$recovery$cross_model_comparison %>%
    group_by(model_type) %>%
    summarise(
      n_groups = n_distinct(group),
      n_models = first(n_models),
      overall_mean_correlation = mean(mean_correlation, na.rm = TRUE),
      excellent_groups = sum(recovery_quality == "excellent", na.rm = TRUE),
      good_or_better_groups = sum(recovery_quality %in% c("excellent", "good"), na.rm = TRUE),
      .groups = "drop"
    ) %>%
    arrange(desc(overall_mean_correlation))
  
  kable(recovery_type_summary, 
        caption = "Parameter Recovery Summary by Model Type",
        digits = 3) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
}
```

## PPC Performance by Model Type

```{r ppc-by-type}
if ("ppc" %in% names(analysis_results) && "behavioral_patterns" %in% names(analysis_results$ppc) &&
    "difficult_domains" %in% names(analysis_results$ppc$behavioral_patterns)) {
  
  difficult_domains <- analysis_results$ppc$behavioral_patterns$difficult_domains
  
  if (nrow(difficult_domains) > 0) {
    # PPC performance by type and domain
    ppc_type_plot <- difficult_domains %>%
      ggplot(aes(x = domain, y = mean_proportion_extreme, fill = model_type)) +
      geom_col(position = position_dodge(width = 0.8), alpha = 0.8) +
      scale_fill_viridis_d(name = "Model Type", option = "viridis") +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(
        title = "PPC Extreme Failure Rate by Model Type and Domain",
        x = "Behavioral Domain",
        y = "Mean Proportion Extreme PPP",
        caption = "Lower values indicate better performance"
      ) +
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom"
      )
    
    print(ppc_type_plot)
  }
  
  # Summary by type
  if (nrow(analysis_results$ppc$model_summary) > 0) {
    ppc_type_summary <- analysis_results$ppc$model_summary %>%
      group_by(model_type) %>%
      summarise(
        n_models = n(),
        mean_proportion_extreme = mean(overall_proportion_extreme, na.rm = TRUE),
        excellent_models = sum(model_quality == "excellent", na.rm = TRUE),
        good_or_better_models = sum(model_quality %in% c("excellent", "good"), na.rm = TRUE),
        .groups = "drop"
      ) %>%
      arrange(mean_proportion_extreme)
    
    kable(ppc_type_summary, 
          caption = "PPC Performance Summary by Model Type",
          digits = 3) %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }
}
```

## Model Type Capabilities and Recommendations

### Specialized Capabilities by Model Type

```{r specialized-capabilities, results='asis'}
if (nrow(type_summary) > 0) {
  for (i in 1:nrow(type_summary)) {
    type_name <- type_summary$model_type[i]
    cat("#### ", toupper(type_name), " Modelsnn")
    
    # Describe capabilities
    if (type_name == "RL") {
      cat("**Specialized for:** Choice patterns, learning dynamics, strategy analysisnn")
      cat("**Strengths:**n")
      cat("- Model learning and decision-making processesn")
      cat("- Capture individual differences in learning parametersn")
      cat("- Predict choice sequences and strategiesnn")
      cat("**Limitations:**n")
      cat("- Cannot model response time distributionsn")
      cat("- May miss speed-accuracy tradeoffsnn")
      
    } else if (type_name == "SSM") {
      cat("**Specialized for:** Response time patterns, decision dynamicsnn")
      cat("**Strengths:**n")
      cat("- Model complete response time distributionsn")
      cat("- Capture speed-accuracy tradeoffsn")
      cat("- Provide insights into decision processesnn")
      cat("**Limitations:**n")
      cat("- Limited learning mechanismsn")
      cat("- May not capture complex choice strategiesnn")
      
    } else if (type_name == "hybrid") {
      cat("**Specialized for:** Integrated choice and RT modelingnn")
      cat("**Strengths:**n")
      cat("- Model both choices and response timesn")
      cat("- Capture learning and decision dynamicsn")
      cat("- Most comprehensive behavioral accountnn")
      cat("**Limitations:**n")
      cat("- Higher complexity and parameter countn")
      cat("- Potentially more difficult parameter recoverynn")
    }
    
    # Performance summary
    if (!is.na(type_summary$mean_delta_ic[i])) {
      cat("**IC Performance:** Mean Δ", analysis_results$ic$metadata$ic_method %||% "IC", " = ", round(type_summary$mean_delta_ic[i], 2), "n")
    }
    
    if (!is.na(type_summary$mean_recovery_correlation[i])) {
      cat("**Recovery Performance:** Mean correlation = ", round(type_summary$mean_recovery_correlation[i], 3), "n")
    }
    
    if (!is.na(type_summary$mean_ppc_extreme[i])) {
      cat("**PPC Performance:** ", round(type_summary$mean_ppc_extreme[i] * 100, 1), "% extreme failuresn")
    }
    
    cat("n---nn")
  }
}
```

### Cross-Type Model Comparison

```{r cross-type-comparison, results='asis'}
if (nrow(type_summary) > 1) {
  cat("### Winner by Analysis Typenn")
  
  winners <- list()
  
  # IC winner
  if ("mean_delta_ic" %in% names(type_summary)) {
    ic_winner <- type_summary %>%
      filter(!is.na(mean_delta_ic)) %>%
      arrange(mean_delta_ic) %>%
      slice(1) %>%
      pull(model_type)
    
    if (length(ic_winner) > 0) {
      winners$ic <- paste("**Information Criteria:**", ic_winner)
    }
  }
  
  # Recovery winner
  if ("mean_recovery_correlation" %in% names(type_summary)) {
    recovery_winner <- type_summary %>%
      filter(!is.na(mean_recovery_correlation)) %>%
      arrange(desc(mean_recovery_correlation)) %>%
      slice(1) %>%
      pull(model_type)
    
    if (length(recovery_winner) > 0) {
      winners$recovery <- paste("**Parameter Recovery:**", recovery_winner)
    }
  }
  
  # PPC winner
  if ("mean_ppc_extreme" %in% names(type_summary)) {
    ppc_winner <- type_summary %>%
      filter(!is.na(mean_ppc_extreme)) %>%
      arrange(mean_ppc_extreme) %>%
      slice(1) %>%
      pull(model_type)
    
    if (length(ppc_winner) > 0) {
      winners$ppc <- paste("**PPC Performance:**", ppc_winner)
    }
  }
  
  for (winner in winners) {
    cat(winner, "nn")
  }
  
  # Overall assessment
  cat("### Model Type Recommendationsnn")
  
  cat("**For choice-only analysis:** Use RL models for computational efficiency and interpretabilitynn")
  cat("**For RT analysis:** Hybrid models provide the most complete accountnn")
  cat("**For parameter recovery studies:** Check type-specific recovery quality abovenn")
  cat("**For model comparison studies:** Include multiple types to assess different aspects of behaviornn")
}
```

# Task-Specific Analysis

```{r task-specific-setup}
# Task-specific analysis based on the task type
task_config <- get_task_config(params$task)
```

## Task Overview: {{TASK}}

```{r task-overview, results='asis'}
if (params$task == "igt_mod") {
  cat("### Modified Iowa Gambling Task (mIGT)nn")
  cat("The mIGT is a variant of the classic IGT where participants make **play/pass decisions** ")
  cat("when shown individual cards from different decks, rather than directly selecting decks.nn")
  
  cat("**Key Behavioral Measures:**n")
  cat("- Play/pass rates overall and by deck typen")
  cat("- Good deck (3,4) vs bad deck (1,2) play ratesn")
  cat("- Learning trajectories across blocksn")
  cat("- Response time patterns for different decisionsnn")
  
} else if (params$task == "igt") {
  cat("### Iowa Gambling Task (IGT)nn")
  cat("The IGT is a classic decision-making task where participants ")
  cat("**select from four decks** with different reward/punishment contingencies.nn")
  
  cat("**Key Behavioral Measures:**n")
  cat("- Deck selection frequenciesn")
  cat("- Good deck (3,4) vs bad deck (1,2) preferencesn")
  cat("- Win-stay/lose-shift strategiesn")
  cat("- Learning curves and strategy developmentnn")
}

cat("**Deck Contingencies:**n")
cat("- **Deck 1 & 2:** High immediate rewards, larger long-term losses (disadvantageous)n")
cat("- **Deck 3 & 4:** Lower immediate rewards, smaller long-term losses (advantageous)nn")
```

## Task-Specific Model Performance

### mIGT-Specific Analysis {.tabset .tabset-pills}

```{r migt-analysis-check}
show_migt <- params$task == "igt_mod" && 
            "ppc" %in% names(analysis_results) && 
            "task_specific_analysis" %in% names(analysis_results$ppc)
```

#### Play/Pass Decision Modeling

```{r migt-play-pass, eval=show_migt}
if (show_migt) {
  task_analysis <- analysis_results$ppc$task_specific_analysis
  
  if ("play_pass_analysis" %in% names(task_analysis) && nrow(task_analysis$play_pass_analysis) > 0) {
    play_pass_summary <- task_analysis$play_pass_analysis %>%
      group_by(model) %>%
      summarise(
        mean_ppp_play = mean(mean_ppp[statistic == "play_ratio"], na.rm = TRUE),
        mean_ppp_good_play = mean(mean_ppp[statistic == "good_play_ratio"], na.rm = TRUE),
        mean_ppp_bad_play = mean(mean_ppp[statistic == "bad_play_ratio"], na.rm = TRUE),
        avg_extreme_rate = mean(proportion_extreme, na.rm = TRUE),
        .groups = "drop"
      ) %>%
      arrange(avg_extreme_rate) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    DT::datatable(play_pass_summary, 
                  caption = "Play/Pass Pattern Reproduction by Model",
                  options = list(pageLength = 10))
  } else {
    cat("No play/pass analysis data available.")
  }
}
```

#### Deck Preference Patterns

```{r migt-deck-preference, eval=show_migt}
if (show_migt) {
  task_analysis <- analysis_results$ppc$task_specific_analysis
  
  if ("deck_preference_analysis" %in% names(task_analysis) && nrow(task_analysis$deck_preference_analysis) > 0) {
    # Deck preference summary
    deck_summary <- task_analysis$deck_preference_analysis %>%
      group_by(model, deck_type) %>%
      summarise(
        mean_ppp = mean(mean_ppp, na.rm = TRUE),
        mean_extreme_rate = mean(proportion_extreme, na.rm = TRUE),
        .groups = "drop"
      ) %>%
      pivot_wider(names_from = deck_type, values_from = c(mean_ppp, mean_extreme_rate), 
                  names_sep = "_") %>%
      arrange(mean_extreme_rate_good + mean_extreme_rate_bad) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    kable(deck_summary, caption = "Deck Preference Modeling Performance") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    
    # Best models for each deck type
    best_good_deck <- task_analysis$deck_preference_analysis %>%
      filter(deck_type == "good") %>%
      group_by(model) %>%
      summarise(avg_extreme = mean(proportion_extreme, na.rm = TRUE), .groups = "drop") %>%
      arrange(avg_extreme) %>%
      slice(1) %>%
      pull(model)
    
    best_bad_deck <- task_analysis$deck_preference_analysis %>%
      filter(deck_type == "bad") %>%
      group_by(model) %>%
      summarise(avg_extreme = mean(proportion_extreme, na.rm = TRUE), .groups = "drop") %>%
      arrange(avg_extreme) %>%
      slice(1) %>%
      pull(model)
    
    cat("nn**Best models for deck preferences:**n")
    cat("- Good deck patterns:", best_good_deck, "n")
    cat("- Bad deck patterns:", best_bad_deck, "n")
    
  } else {
    cat("No deck preference analysis data available.")
  }
}
```

### IGT-Specific Analysis {.tabset .tabset-pills}

```{r igt-analysis-check}
show_igt <- params$task == "igt" && 
           "ppc" %in% names(analysis_results) && 
           "task_specific_analysis" %in% names(analysis_results$ppc)
```

#### Deck Selection Modeling

```{r igt-deck-selection, eval=show_igt}
if (show_igt) {
  task_analysis <- analysis_results$ppc$task_specific_analysis
  
  if ("deck_selection_analysis" %in% names(task_analysis) && nrow(task_analysis$deck_selection_analysis) > 0) {
    deck_selection_summary <- task_analysis$deck_selection_analysis %>%
      group_by(model) %>%
      summarise(
        mean_ppp_individual = mean(mean_ppp[grepl("deck[1-4]_freq", statistic)], na.rm = TRUE),
        mean_ppp_good_bad = mean(mean_ppp[statistic %in% c("good_deck_freq", "bad_deck_freq")], na.rm = TRUE),
        avg_extreme_rate = mean(proportion_extreme, na.rm = TRUE),
        .groups = "drop"
      ) %>%
      arrange(avg_extreme_rate) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    DT::datatable(deck_selection_summary, 
                  caption = "Deck Selection Pattern Reproduction by Model",
                  options = list(pageLength = 10))
  } else {
    cat("No deck selection analysis data available.")
  }
}
```

#### Strategy Pattern Modeling

```{r igt-strategy, eval=show_igt}
if (show_igt) {
  task_analysis <- analysis_results$ppc$task_specific_analysis
  
  if ("strategy_analysis" %in% names(task_analysis) && nrow(task_analysis$strategy_analysis) > 0) {
    strategy_summary <- task_analysis$strategy_analysis %>%
      group_by(model) %>%
      summarise(
        mean_ppp_wsls = mean(mean_ppp[statistic %in% c("win_stay", "lose_shift")], na.rm = TRUE),
        mean_ppp_perseveration = mean(mean_ppp[statistic == "perseveration"], na.rm = TRUE),
        avg_extreme_rate = mean(proportion_extreme, na.rm = TRUE),
        .groups = "drop"
      ) %>%
      arrange(avg_extreme_rate) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    kable(strategy_summary, caption = "Strategy Pattern Reproduction by Model") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    
    # Best strategy model
    best_strategy_model <- strategy_summary$model[1]
    cat("nn**Best model for strategy patterns:**", best_strategy_model)
    
  } else {
    cat("No strategy analysis data available.")
  }
}
```

## Learning Dynamics Analysis

```{r learning-dynamics}
# Analyze block-level performance (learning curves)
if ("ppc" %in% names(analysis_results) && nrow(analysis_results$ppc$by_domain_and_model) > 0) {
  learning_domain_data <- analysis_results$ppc$by_domain_and_model %>%
    filter(domain == "learning_dynamics")
  
  if (nrow(learning_domain_data) > 0) {
    learning_summary <- learning_domain_data %>%
      arrange(proportion_extreme) %>%
      select(model, model_type, mean_ppp, proportion_extreme, domain_quality) %>%
      mutate(across(where(is.numeric), ~round(.x, 3)))
    
    kable(learning_summary, caption = "Learning Dynamics Modeling Performance") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    
    best_learning_model <- learning_summary$model[1]
    
    # Learning performance by model type
    if (length(unique(learning_summary$model_type)) > 1) {
      learning_by_type <- learning_summary %>%
        group_by(model_type) %>%
        summarise(
          n_models = n(),
          mean_proportion_extreme = mean(proportion_extreme, na.rm = TRUE),
          .groups = "drop"
        ) %>%
        arrange(mean_proportion_extreme)
      
      cat("nn### Learning Performance by Model Typenn")
      kable(learning_by_type, caption = "Learning Dynamics by Model Type") %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    }
    
    cat("nn**Best model for learning dynamics:**", best_learning_model)
  }
} else {
  cat("No learning dynamics analysis available.")
}
```

## Response Time Analysis

```{r rt-analysis, results='asis'}
# RT analysis for SSM and hybrid models
rt_capable_models <- names(comparison_data)[sapply(names(comparison_data), function(m) {
  classify_model_type(m) %in% c("SSM", "hybrid")
})]

if (length(rt_capable_models) > 0) {
  cat("### Response Time Modelingnn")
  cat("Models capable of RT prediction:", paste(rt_capable_models, collapse = ", "), "nn")
  
  # RT domain performance
  if ("ppc" %in% names(analysis_results) && nrow(analysis_results$ppc$by_domain_and_model) > 0) {
    rt_domain_data <- analysis_results$ppc$by_domain_and_model %>%
      filter(domain == "rt_patterns", model %in% rt_capable_models)
    
    if (nrow(rt_domain_data) > 0) {
      rt_summary <- rt_domain_data %>%
        arrange(proportion_extreme) %>%
        select(model, model_type, mean_ppp, proportion_extreme, domain_quality) %>%
        mutate(across(where(is.numeric), ~round(.x, 3)))
      
      kable(rt_summary, caption = "Response Time Pattern Reproduction") %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
      
      best_rt_model <- rt_summary$model[1]
      cat("n**Best model for RT patterns:**", best_rt_model, "nn")
      
      # RT performance insights
      if (params$task == "igt_mod") {
        cat("#### mIGT RT Insightsnn")
        cat("- RT patterns include overall distributions and play/pass differencesn")
        cat("- Good models should capture different RT distributions for different decision typesn")
        cat("- Hybrid models can link choice preferences to decision confidence (via RT)nn")
      }
    } else {
      cat("No RT domain data available for RT-capable models.nn")
    }
  }
} else {
  cat("### Response Time AnalysisnnNo RT-capable models (SSM or hybrid) included in this comparison.nn")
}
```

## Task-Specific Insights and Recommendations

```{r task-insights, results='asis'}
cat("### Key Task-Specific Findingsnn")

# Generate insights based on task type and available results
insights <- list()

if (params$task == "igt_mod") {
  insights$task_nature <- "**mIGT Modeling Challenges:** The play/pass decision structure requires models to capture binary choice processes with deck-specific value learning."
  
  if ("ppc" %in% names(analysis_results)) {
    # Find models that do well on play/pass vs deck preferences
    domain_performance <- analysis_results$ppc$by_domain_and_model %>%
      filter(domain %in% c("choice_patterns", "performance")) %>%
      group_by(model) %>%
      summarise(avg_performance = mean(proportion_extreme, na.rm = TRUE), .groups = "drop") %>%
      arrange(avg_performance)
    
    if (nrow(domain_performance) > 0) {
      best_choice_model <- domain_performance$model[1]
      insights$choice_modeling <- paste("**Best choice pattern model:**", best_choice_model, "- excels at capturing play/pass and deck preference patterns")
    }
  }
  
} else if (params$task == "igt") {
  insights$task_nature <- "**IGT Modeling Challenges:** Direct deck selection requires models to capture sequential choice patterns and strategy development over time."
  
  if ("ppc" %in% names(analysis_results)) {
    # Find models that balance deck selection and strategy patterns
    strategy_performance <- analysis_results$ppc$by_domain_and_model %>%
      filter(domain %in% c("choice_patterns", "strategies")) %>%
      group_by(model) %>%
      summarise(avg_performance = mean(proportion_extreme, na.rm = TRUE), .groups = "drop") %>%
      arrange(avg_performance)
    
    if (nrow(strategy_performance) > 0) {
      best_strategy_model <- strategy_performance$model[1]
      insights$strategy_modeling <- paste("**Best strategy model:**", best_strategy_model, "- captures both deck preferences and strategic patterns")
    }
  }
}

# Model type recommendations for this task
if (length(rt_capable_models) > 0 && length(rt_capable_models) < length(names(comparison_data))) {
  insights$model_type_rec <- "**Model Type Recommendation:** Consider hybrid models if RT data is available and important for your research questions, otherwise RL models provide efficient choice modeling."
} else if (length(rt_capable_models) == 0) {
  insights$model_type_rec <- "**Model Type Recommendation:** RL models are most appropriate for choice-only analysis of this task."
} else {
  insights$model_type_rec <- "**Model Type Recommendation:** All models in this comparison can handle RT data - choose based on other performance criteria."
}

# Recovery recommendations
if ("recovery" %in% names(analysis_results) && nrow(analysis_results$recovery$group_summary) > 0) {
  best_recovery_groups <- head(analysis_results$recovery$group_summary$group, 2)
  worst_recovery_groups <- tail(analysis_results$recovery$group_summary$group, 2)
  
  insights$recovery_rec <- paste("**Parameter Recovery:** Focus on", paste(best_recovery_groups, collapse = " and "), 
                                "parameters as they show excellent recovery. Be cautious interpreting", 
                                paste(worst_recovery_groups, collapse = " and "), "parameters due to poor recovery.")
}

# Print all insights
for (i in seq_along(insights)) {
  cat(insights[[i]], "nn")
}
```

## Task-Specific Visualization

```{r task-visualization, fig.height=8}
# Create task-specific summary plot
if ("ppc" %in% names(analysis_results)) {
  
  if (params$task == "igt_mod") {
    # mIGT: Focus on play/pass and deck preferences
    key_domains <- c("choice_patterns", "performance")
    domain_title <- "mIGT: Choice Patterns and Performance"
    
  } else if (params$task == "igt") {
    # IGT: Focus on deck selection and strategies  
    key_domains <- c("choice_patterns", "strategies")
    domain_title <- "IGT: Deck Selection and Strategies"
  }
  
  task_viz_data <- analysis_results$ppc$by_domain_and_model %>%
    filter(domain %in% key_domains)
  
  if (nrow(task_viz_data) > 0) {
    task_plot <- task_viz_data %>%
      ggplot(aes(x = model, y = proportion_extreme, fill = domain)) +
      geom_col(position = position_dodge(width = 0.8), alpha = 0.8) +
      scale_fill_viridis_d(name = "Behavioral Domain", option = "viridis") +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(
        title = paste("Task-Specific Performance:", domain_title),
        x = "Model",
        y = "Proportion Extreme PPP",
        caption = "Lower values indicate better model fit"
      ) +
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom"
      )
    
    print(task_plot)
  }
}
```

# Detailed Model Profiles

```{r model-profiles}
# Create detailed profile for each model
model_names <- names(comparison_data)

for (model_name in model_names) {
  cat('
## Model:', model_name, '

')
  
  # Model metadata
  model_type <- classify_model_type(model_name)
  cat('**Type:** ', model_type, '

')
  
  # IC performance
  if ('ic' %in% names(analysis_results) && nrow(analysis_results$ic$overall_ranking) > 0) {
    ic_info <- analysis_results$ic$overall_ranking %>% filter(model == model_name)
    if (nrow(ic_info) > 0) {
      cat('**Information Criteria:**
')
      cat('- Rank:', ic_info$rank, '
')
      cat('- Performance Tier:', ic_info$performance_tier, '
')
      cat('- Model Weight:', round(ic_info$model_weight, 3), '

')
    }
  }
  
  # Recovery performance
  if ('recovery' %in% names(analysis_results) && nrow(analysis_results$recovery$model_summary) > 0) {
    recovery_info <- analysis_results$recovery$model_summary %>% filter(model == model_name)
    if (nrow(recovery_info) > 0) {
      cat('**Parameter Recovery:**
')
      cat('- Mean Correlation:', round(recovery_info$mean_correlation, 3), '
')
      cat('- Recovery Quality:', recovery_info$recovery_quality, '

')
    }
  }
  
  # PPC performance
  if ('ppc' %in% names(analysis_results) && nrow(analysis_results$ppc$model_summary) > 0) {
    ppc_info <- analysis_results$ppc$model_summary %>% filter(model == model_name)
    if (nrow(ppc_info) > 0) {
      cat('**PPC Performance:**
')
      cat('- Mean PPP:', round(ppc_info$overall_mean_ppp, 3), '
')
      cat('- Proportion Extreme:', round(ppc_info$overall_proportion_extreme, 3), '
')
      cat('- PPC Quality:', ppc_info$model_quality, '
')
      cat('- Best Domain:', ppc_info$best_domain, '
')
      cat('- Worst Domain:', ppc_info$worst_domain, '

')
    }
  }
  
  cat('---
')
}
```

# Conclusions and Recommendations

## Overall Model Ranking

```{r overall-ranking}
if ("integrated_ranking" %in% names(analysis_results)) {
  # Use integrated ranking if available
  integrated_ranking <- analysis_results$integrated_ranking$consensus_ranking %>%
    select(consensus_rank, model, model_type, overall_quality, 
           ic_score, recovery_score, ppc_score, rank_stability) %>%
    mutate(across(c(ic_score, recovery_score, ppc_score, rank_stability), ~round(.x, 3)))
  
  DT::datatable(integrated_ranking, 
                caption = "Integrated Model Ranking (Consensus across all metrics)",
                options = list(pageLength = 15, scrollX = TRUE)) %>%
    DT::formatStyle("overall_quality",
                    backgroundColor = DT::styleEqual(
                      c("excellent_all_around", "strong_overall", "good_balanced", 
                        "strong_but_uneven", "adequate_performance", "needs_improvement"),
                      c("#d4edda", "#d1ecf1", "#fff3cd", "#ffeaa7", "#fdcb6e", "#f8d7da")
                    ))
  
  cat("\n\n### Methodology\n\n")
  cat("This integrated ranking combines:
")
  cat("- **Information Criteria (IC):** Model fit with complexity penalty\n")
  cat("- **Parameter Recovery:** Ability to recover true parameter values\n")
  cat("- **Posterior Predictive Checks (PPC):** Reproduction of behavioral patterns\n\n")
  
  cat("**Weighting schemes used:**\n")
  cat("- Equal: 33% each metric\n")
  cat("- IC-weighted: 50% IC, 25% recovery, 25% PPC\n")
  cat("- Balanced: 40% IC, 30% recovery, 30% PPC\n\n")
  
  cat("**Consensus rank:** Median rank across all weighting schemes\n")
  cat("**Rank stability:** Lower values indicate more consistent ranking across schemes\n\n")
  
} else if ("ic" %in% names(analysis_results) && nrow(analysis_results$ic$overall_ranking) > 0) {
  # Fall back to IC ranking only if integrated ranking not available
  ranking_display <- analysis_results$ic$overall_ranking %>%
    select(rank, model, model_type, matches("estimate$"), matches("^delta_"), 
           model_weight, performance_tier) %>%
    mutate(across(where(is.numeric), ~round(.x, 3)))
  
  DT::datatable(ranking_display, 
                caption = "Model Ranking (Information Criteria Only)",
                options = list(pageLength = 15, scrollX = TRUE)) %>%
    DT::formatStyle("performance_tier",
                    backgroundColor = DT::styleEqual(
                      c("top_tier", "competitive", "considerable_difference", "strong_difference", "decisive_difference"),
                      c("#d4edda", "#fff3cd", "#ffeaa7", "#fdcb6e", "#e17055")
                    ))
  
  cat("\n\n**Note:** This ranking is based on Information Criteria only. ",
      "For comprehensive evaluation, include parameter recovery and PPC analysis.\n\n")
  
} else {
  cat("No ranking data available.")
}
```

## Key Insights

```{r insights}
insights <- list()

# Integrated ranking insights (preferred)
if ("integrated_ranking" %in% names(analysis_results)) {
  consensus_ranking <- analysis_results$integrated_ranking$consensus_ranking
  best_model <- consensus_ranking$model[1]
  best_quality <- consensus_ranking$overall_quality[1]
  
  insights$integrated <- paste("**Best overall model (integrated ranking):**", best_model, 
                              "with", gsub("_", " ", best_quality), "performance")
  
  # Top tier models (consensus rank <= 3 or top 25%)
  top_threshold <- max(3, round(nrow(consensus_ranking) * 0.25))
  top_models <- consensus_ranking$model[consensus_ranking$consensus_rank <= top_threshold]
  
  if (length(top_models) > 1) {
    insights$top_models <- paste("**Top-performing models:**", paste(top_models, collapse = ", "))
  }
  
  # Stability insights
  stable_models <- consensus_ranking %>%
    filter(rank_stability <= quantile(rank_stability, 0.25, na.rm = TRUE)) %>%
    pull(model)
  
  if (length(stable_models) > 0) {
    insights$stability <- paste("**Most stable rankings:**", paste(head(stable_models, 3), collapse = ", "),
                               "- consistent performance across weighting schemes")
  }
  
  # Quality distribution
  quality_summary <- table(consensus_ranking$overall_quality)
  excellent_count <- sum(quality_summary[grepl("excellent|strong", names(quality_summary))], na.rm = TRUE)
  
  if (excellent_count > 0) {
    insights$quality_dist <- paste("**High-quality models:**", excellent_count, "out of", 
                                  nrow(consensus_ranking), "models show excellent or strong overall performance")
  }
}

# IC insights (fallback or additional)
if ("ic" %in% names(analysis_results)) {
  ic_ranking <- analysis_results$ic$overall_ranking
  top_tier_models <- ic_ranking %>%
    filter(performance_tier == "top_tier") %>%
    pull(model)
  
  if (length(top_tier_models) == 1) {
    insights$ic <- paste("**Clear IC winner:**", top_tier_models[1])
  } else if (length(top_tier_models) > 1) {
    insights$ic <- paste("**Multiple competitive models (IC):**", paste(top_tier_models, collapse = ", "))
  }
}

# Recovery insights
if ("recovery" %in% names(analysis_results)) {
  best_groups <- head(analysis_results$recovery$group_summary$group, 3)
  worst_groups <- tail(analysis_results$recovery$group_summary$group, 3)
  
  insights$recovery <- paste("**Parameter Recovery:** Best recovered groups:", paste(best_groups, collapse = ", "),
                           ". Most challenging:", paste(worst_groups, collapse = ", "))
}

# PPC insights
if ("ppc" %in% names(analysis_results)) {
  difficult_domains <- analysis_results$ppc$domain_summary %>%
    arrange(desc(proportion_extreme)) %>%
    head(2) %>%
    pull(domain)
  
  insights$ppc <- paste("**PPC Performance:** Most challenging behavioral domains:", paste(difficult_domains, collapse = ", "))
}

for (i in seq_along(insights)) {
  cat("**", names(insights)[i], "**: ", insights[[i]], "\n\n")
}
```

## Recommendations

Based on the comprehensive analysis:

```{r recommendations}
# Generate data-driven recommendations
recommendations <- list()

if ("ic" %in% names(analysis_results)) {
  ic_ranking <- analysis_results$ic$overall_ranking
  
  # Top recommendation
  best_model <- ic_ranking$model[1]
  best_tier <- ic_ranking$performance_tier[1]
  
  if (best_tier == "top_tier") {
    recommendations$primary <- paste("**Primary recommendation:** Use", best_model, "as it shows the best overall fit to the data.")
  } else {
    recommendations$primary <- paste("**Primary recommendation:** Consider", best_model, "but note that model selection is less decisive.")
  }
  
  # Alternative recommendations
  competitive_models <- ic_ranking %>%
    filter(performance_tier %in% c("top_tier", "competitive")) %>%
    filter(row_number() > 1) %>%
    pull(model)
  
  if (length(competitive_models) > 0) {
    recommendations$alternatives <- paste("**Alternative options:** Consider", paste(competitive_models, collapse = ", "), "as competitive alternatives.")
  }
}

# Type-specific recommendations
if (length(models_by_type) > 1) {
  type_winners <- sapply(names(models_by_type), function(type) {
    type_models <- models_by_type[[type]]
    if ("ic" %in% names(analysis_results)) {
      type_ranking <- analysis_results$ic$overall_ranking %>%
        filter(model %in% type_models) %>%
        arrange(rank)
      if (nrow(type_ranking) > 0) {
        return(type_ranking$model[1])
      }
    }
    return(NA)
  })
  
  type_winners <- type_winners[!is.na(type_winners)]
  
  if (length(type_winners) > 0) {
    type_text <- paste(names(type_winners), ":", type_winners, collapse = "; ")
    recommendations$by_type <- paste("**Best by model type:** ", type_text)
  }
}

for (rec in recommendations) {
  cat(rec, "\n\n")
}
```

---

*Report generated on `r Sys.time()` using the model comparison pipeline.*

*Analysis included 10 models with data from parameter recovery, posterior predictive checks, and information criteria.*
