---
title: "Posterior Predictive Check Analysis: igt_mod - ddm - batch_001"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
suppressPackageStartupMessages({
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  library(knitr)
  library(kableExtra)
  library(reshape2)  # For melting matrices
  library(corrplot)
  library(viridis)
  library(igraph)
})

# Define input files
subject_file <- "/Users/icd/Library/CloudStorage/Dropbox/Projects/modeling_mIGT/Data/sim/ppc/ppc_subject_summary_task-igt_mod_model-ddm_group-batch_001.csv"
model_file <- "/Users/icd/Library/CloudStorage/Dropbox/Projects/modeling_mIGT/Data/sim/ppc/ppc_model_summary_task-igt_mod_model-ddm_group-batch_001.csv"
block_file <- "/Users/icd/Library/CloudStorage/Dropbox/Projects/modeling_mIGT/Data/sim/ppc/ppc_block_stats_task-igt_mod_model-ddm_group-batch_001.csv"

# Load data
subject_data <- read.csv(subject_file)
model_summary <- read.csv(model_file)

#' Parse BIDS-inspired filename to extract components
#' @param filename The filename to parse
#' @return List of extracted components (task, model, group, plus any additional tags)
parse_bids_filename <- function(filename) {
  # Extract the relevant part of the filename
  base_name <- basename(filename)
  
  # Use regex to extract each key-value pair
  task_match <- regexec("task-([^_]+(?:_[^_]+)*?)(?:_model-|$)", base_name)
  model_match <- regexec("model-([^_]+(?:_[^_]+)*?)(?:_group-|$)", base_name)
  group_match <- regexec("group-([^_]+(?:_[^_]+)*?)(?:\\.|$)", base_name)
  
  # Extract the matched values
  result <- list()
  
  # Extract task
  if (task_match[[1]][1] > 0) {
    result$task <- substr(base_name, 
                         task_match[[1]][2], 
                         task_match[[1]][2] + attr(task_match[[1]], "match.length")[2] - 1)
  }
  
  # Extract model
  if (model_match[[1]][1] > 0) {
    result$model <- substr(base_name, 
                          model_match[[1]][2], 
                          model_match[[1]][2] + attr(model_match[[1]], "match.length")[2] - 1)
  }
  
  # Extract group
  if (group_match[[1]][1] > 0) {
    result$group <- substr(base_name, 
                          group_match[[1]][2], 
                          group_match[[1]][2] + attr(group_match[[1]], "match.length")[2] - 1)
  }
  
  return(result)
}

components <- parse_bids_filename(basename(subject_file))
task <- components$task
model <- components$model
group <- components$group

# Construct recovery file path
recovery_dir <- gsub("sim/ppc", "sim/recovery", dirname(subject_file))
recovery_csv <- file.path(recovery_dir, 
           paste0("recovery_", task, "_", model, "_", group, ".csv"))

cat("Extracted components from filename:\n")
cat(paste("Task:", task, "\n"))
cat(paste("Model:", model, "\n"))
cat(paste("Group:", group, "\n"))

# Create helper function for correlation plots
create_corr_plot <- function(corr_matrix, title, mar = c(1,1,2,1)) {
  if(ncol(corr_matrix) > 1 && nrow(corr_matrix) > 0) {
    if (nrow(corr_matrix) == ncol(corr_matrix)){
    corrplot(corr_matrix, 
             method = "circle", 
             type = "upper", 
             tl.col = "black",
             tl.srt = 45,
             addCoef.col = "black",
             number.cex = 0.7,
             mar = mar,
             title = title,
             diag = FALSE)
    } else{
      corrplot(corr_matrix, 
             method = "circle", 
             type = "full", 
             tl.col = "black",
             tl.srt = 45,
             addCoef.col = "black",
             number.cex = 0.7,
             mar = mar,
             title = title)
    }
    return(TRUE)
  } else {
    cat("Insufficient data for correlation matrix:", title, "\n")
    return(FALSE)
  }
}

# Format parameter and statistic names for display
format_names <- function(names) {
  names %>% 
    gsub("_", " ", .) %>%
    gsub("ssm ", "", .) %>%
    gsub("rl ", "", .) %>%
    tools::toTitleCase(.)
}

# Create function to find top correlations
get_top_correlations <- function(cor_matrix, n = 10) {
  cors_long <- as.data.frame(as.table(cor_matrix)) %>%
    rename(Parameter = Var1, Statistic = Var2, Correlation = Freq) %>%
    mutate(
      Parameter = as.character(Parameter),
      Statistic = as.character(Statistic),
      Abs_Correlation = abs(Correlation)
    ) %>%
    arrange(desc(Abs_Correlation))
  
  # Return top N correlations
  return(head(cors_long, n))
}

# Load recovery data if file exists
if (file.exists(recovery_csv)) {
  recovery_data <- read.csv(recovery_csv)
  cat("Recovery data loaded successfully from:", recovery_csv, "\n")
} else {
  cat("Recovery data file not found at:", recovery_csv, "\n")
  cat("Attempting to search for recovery data...\n")
  
  # Try to find recovery file by searching in expected directory
  recovery_files <- list.files(path = recovery_dir, 
                              pattern = paste0("recovery_", task, "_", model, ".*\\.csv$"), 
                              full.names = TRUE)
  
  if (length(recovery_files) > 0) {
    recovery_csv <- recovery_files[1]
    recovery_data <- read.csv(recovery_csv)
    cat("Found and loaded alternative recovery file:", recovery_csv, "\n")
  } else {
    cat("No suitable recovery data found. Correlation analysis will be skipped.\n")
    recovery_data <- NULL
  }
}

if (sum(grepl("*has_rt_data*", model_summary$statistic)) > 0){
  subject_data <- subject_data %>% 
    select(-contains("has_rt_data"))
  subject_data <- subject_data %>% 
    filter(!grepl("has_rt_data", statistic))
  
  model_summary <- model_summary %>% 
    select(-contains("has_rt_data"))
  model_summary <- model_summary %>% 
    filter(!grepl("has_rt_data", statistic))
}

# Check if block stats exist
has_block_stats <- file.exists(block_file)
if (has_block_stats) {
  block_stats <- read.csv(block_file)
}

# Calculate additional statistics
extreme_ppp_count <- sum(subject_data$ppp_extreme, na.rm = TRUE)
total_ppp_count <- nrow(subject_data)
extreme_ppp_ratio <- extreme_ppp_count / total_ppp_count
```

## Overview

This document presents posterior predictive check (PPC) analysis for the **ddm** model (SSM type) applied to the **igt_mod** task with group type **batch_001**.

Posterior predictive checks compare statistics from observed data with statistics from data simulated using posterior parameter samples. These checks help validate whether the model can reproduce key behavioral patterns in the data.

## Summary Statistics

### PPC Quality Overview

```{r summary, echo=FALSE}
summary_df <- data.frame(
  Statistic = c("Total Statistics Checked", "Extreme PPP Values (p < 0.05 or p > 0.95)", 
                "Proportion Extreme"),
  Value = c(total_ppp_count, extreme_ppp_count, sprintf("%.2f%%", extreme_ppp_ratio * 100))
)

kable(summary_df, caption = "Summary of PPC Results") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Model-Level Statistics

```{r model_stats, echo=FALSE}
# Display model-level statistics
kable(model_summary, caption = "Model-Level PPC Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## PPP Value Distribution

PPP values should ideally be distributed uniformly between 0 and 1 if the model fits well. Extreme values (< 0.05 or > 0.95) indicate statistics that the model struggles to reproduce.

```{r ppp_dist, echo=FALSE, fig.width=10, fig.height=6}
ggplot(subject_data, aes(x = statistic, y = ppp_value)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, height = 0, alpha = 0.5) +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dashed", color = "red") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Distribution of PPP Values Across Subjects",
       subtitle = "Red lines indicate thresholds for extreme values (p < 0.05 or p > 0.95)",
       x = "Statistic", y = "Posterior Predictive p-value")

# Show extreme statistics
extreme_stats <- subject_data %>%
  filter(ppp_extreme) %>%
  group_by(statistic) %>%
  summarize(
    count = n(),
    proportion = n() / length(unique(subject_data$subject_id)),
    avg_ppp = mean(ppp_value),
    .groups = "drop"
  ) %>%
  arrange(abs(0.5 - avg_ppp))

if(nrow(extreme_stats) > 0) {
  kable(extreme_stats, caption = "Statistics with Extreme PPP Values") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}

# Reshape the data from wide to long format
extreme_stats_long <- extreme_stats %>% 
  arrange(proportion) %>%
  pivot_longer(cols = c(proportion),
               names_to = "metric",
               values_to = "value")

# Create the heatmap
ggplot(extreme_stats_long, aes(x = metric, y = statistic, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 3)), color = "black", size = 3) +
  scale_fill_viridis(option = "plasma") +
  labs(title = "Statistics Heatmap",
       x = "Metric",
       y = "Statistic",
       fill = "Value") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
```

## Subject-Level Statistics

The plots below compare observed statistics (red) with model predictions (blue with 95% CI). Good model fit is indicated by observed values falling within the prediction intervals.

```{r subject_level, echo=FALSE, fig.width=10, fig.height=8}
# Select a sample of subjects and key statistics for visualization
subjects_to_plot <- sample(unique(subject_data$subject_id), min(6, length(unique(subject_data$subject_id))))
key_stats <- c("good_deck_ratio", "win_stay_ratio", "lose_shift_ratio", "skip_ratio", "rt_play_mean", "rt_skip_mean", "choice_prob")
key_stats <- key_stats[key_stats %in% unique(subject_data$statistic)]

subject_sample <- subject_data %>%
  filter(subject_id %in% subjects_to_plot & statistic %in% key_stats)

if(nrow(subject_sample) > 0) {
  p1 = ggplot(subject_sample, aes(x = statistic, y = predicted_mean)) +
    geom_point() +
    geom_errorbar(aes(ymin = predicted_q025, ymax = predicted_q975), width = 0.2) +
    geom_point(aes(y = observed), color = "red", size = 3, shape = 4) +
    facet_wrap(~subject_id) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Key Statistics: Observed vs. Predicted", 
         subtitle = "Red X = Observed, Blue points with error bars = Predicted with 95% CI",
         x = "", y = "Value")
  knitr::knit_print(p1)
}
```

## Directionality of Model Misfit

This section examines not only whether the model fits the data, but also the direction of misfit (whether the model systematically over- or under-predicts observed statistics).

```{r misfit_analysis, echo=FALSE, fig.width=10, fig.height=8}
# Calculate misfit measures
misfit_data <- subject_data %>%
  mutate(
    misfit = observed - predicted_mean,
    misfit_standardized = misfit / (predicted_q975 - predicted_q025) * 2,
    misfit_direction = case_when(
      misfit > 0 & ppp_extreme ~ "Model Underpredicts",
      misfit < 0 & ppp_extreme ~ "Model Overpredicts",
      TRUE ~ "Good Fit"
    )
  )

# Plot standardized misfit by statistic
ggplot(misfit_data, aes(x = statistic, y = misfit_standardized, fill = misfit_direction)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = c(-1, 1), linetype = "dotted", color = "red") +
  scale_fill_manual(values = c("Good Fit" = "gray", 
                             "Model Underpredicts" = "blue", 
                             "Model Overpredicts" = "red")) +
  coord_flip() +
  theme_minimal() +
  labs(title = "Standardized Misfit by Statistic",
       subtitle = "Misfit = (Observed - Predicted) / Width of 95% CI",
       x = "", y = "Standardized Misfit",
       fill = "Direction")

# Create misfit summary table
misfit_summary <- misfit_data %>%
  group_by(statistic) %>%
  summarize(
    mean_misfit = mean(misfit, na.rm = TRUE),
    mean_std_misfit = mean(misfit_standardized, na.rm = TRUE),
    prop_underpredict = mean(misfit_direction == "Model Underpredicts", na.rm = TRUE),
    prop_overpredict = mean(misfit_direction == "Model Overpredicts", na.rm = TRUE),
    mean_abs_misfit = mean(abs(misfit_standardized), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(mean_abs_misfit))

kable(misfit_summary, caption = "Summary of Model Misfit Direction and Magnitude") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```


## SSM-Specific Analyses

#### Response Time Distributions

The plots below compare observed response time (RT) distributions (red) with model predictions (blue with 95% CI).

```{r rt_distributions, echo=FALSE, fig.width=10, fig.height=6}
# Extract RT quantile data
rt_quantile_data <- subject_data %>%
  filter(grepl("rt_.*_quantiles", statistic) | grepl("rt_.*_q", statistic))
if(nrow(rt_quantile_data) > 0) {
  # Properly extract quantile and rt_type from the statistic column 
  # Fix the regex patterns - the double backslashes were causing issues
  rt_quantile_data <- rt_quantile_data %>%
    mutate(
      quantile = as.numeric(sub(".*_quantiles_(\\d+).*", "\\1", statistic)),
      rt_type = sub("rt_(.*)_quantiles.*", "\\1", statistic)
    ) %>%
    # Filter out rows where quantile extraction failed (would be NA)
    filter(!is.na(quantile))
  
  # Aggregate across subjects
  rt_quantile_agg <- rt_quantile_data %>%
    group_by(quantile, rt_type) %>%
    summarize(
      predicted_mean = mean(predicted_mean, na.rm = TRUE),
      predicted_q025 = mean(predicted_q025, na.rm = TRUE),
      predicted_q975 = mean(predicted_q975, na.rm = TRUE),
      observed = mean(observed, na.rm = TRUE),
      .groups = 'drop'
    )
  
  # Convert quantile to factor for proper ordering on x-axis
  rt_quantile_agg$quantile <- factor(rt_quantile_agg$quantile, levels = sort(unique(rt_quantile_agg$quantile)))
  
  # Plot aggregated RT quantiles
  ggplot(rt_quantile_agg, aes(x = quantile, group = rt_type, color = rt_type)) +
    # Predicted lines and points
    geom_line(aes(y = predicted_mean), size = 1) +
    geom_point(aes(y = predicted_mean), size = 3) +
    geom_errorbar(aes(ymin = predicted_q025, ymax = predicted_q975), width = 0.1, alpha = 0.7) +
    # Observed lines and points
    geom_line(aes(y = observed), linetype = "dashed", size = 1) +
    geom_point(aes(y = observed), shape = 4, size = 3)  +
    facet_wrap(~ rt_type, scales = "free_y") +
    # Theme and labels
    theme_minimal(base_size = 14) +
    labs(title = "Aggregate RT Quantiles",
         subtitle = "Solid = Predicted (with 95% CI), Dashed = Observed",
         x = "Quantile", y = "Response Time (s)",
         color = "RT Type") +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank(),
      panel.border = element_rect(fill = NA, color = "gray80"),
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
}
```

```{r}
# Extract RT mean and median data
rt_mean_data <- subject_data %>%
  filter(grepl("rt_.*_mean|rt_.*_median", statistic))

if(nrow(rt_mean_data) > 0) {
  # Aggregate across subjects
  rt_mean_agg <- rt_mean_data %>%
    group_by(statistic) %>%
    summarize(
      predicted_mean = mean(predicted_mean, na.rm = TRUE),
      predicted_q025 = mean(predicted_q025, na.rm = TRUE),
      predicted_q975 = mean(predicted_q975, na.rm = TRUE),
      observed = mean(observed, na.rm = TRUE),
      .groups = 'drop'
    )
  
  # Create factor for ordering
  rt_mean_agg$statistic <- factor(rt_mean_agg$statistic, 
                                levels = sort(unique(rt_mean_agg$statistic)))
  
  # Plot aggregated RT means and medians
  ggplot(rt_mean_agg, aes(x = statistic, y = predicted_mean)) +
    geom_point(size = 3, color = "blue") +
    geom_errorbar(aes(ymin = predicted_q025, ymax = predicted_q975), 
                 width = 0.2, color = "blue", alpha = 0.7) +
    geom_point(aes(y = observed), color = "red", size = 3, shape = 4) +
    theme_minimal(base_size = 14) +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      panel.grid.minor = element_blank(),
      panel.border = element_rect(fill = NA, color = "gray80")
    ) +
    labs(title = "Aggregate RT Means and Medians", 
         subtitle = "Red X = Observed, Blue points with error bars = Predicted (95% CI)",
         x = "", y = "Response Time (s)")
}
```

#### Choice Probabilities

```{r choice_probs, echo=FALSE, fig.width=10, fig.height=6}
# Extract choice probability data
choice_prob_data <- subject_data %>%
  filter(grepl("choice_prob", statistic) | grepl("selection_ratio", statistic))

if(nrow(choice_prob_data) > 0) {
  # Aggregate across subjects
  choice_prob_agg <- choice_prob_data %>%
    group_by(statistic) %>%
    summarize(
      predicted_mean = mean(predicted_mean, na.rm = TRUE),
      predicted_q025 = mean(predicted_q025, na.rm = TRUE),
      predicted_q975 = mean(predicted_q975, na.rm = TRUE),
      observed = mean(observed, na.rm = TRUE),
      .groups = 'drop'
    )
  
  # Create factor for ordering
  choice_prob_agg$statistic <- factor(choice_prob_agg$statistic, 
                                     levels = sort(unique(choice_prob_agg$statistic)))
  
  # Plot aggregated choice probabilities
  ggplot(choice_prob_agg, aes(x = statistic, y = predicted_mean)) +
    geom_point(size = 3, color = "blue") +
    geom_errorbar(aes(ymin = predicted_q025, ymax = predicted_q975), 
                 width = 0.2, color = "blue", alpha = 0.7) +
    geom_point(aes(y = observed), color = "red", size = 3, shape = 4) +
    theme_minimal(base_size = 14) +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      panel.grid.minor = element_blank(),
      panel.border = element_rect(fill = NA, color = "gray80")
    ) +
    labs(title = "Aggregate Choice Probabilities", 
         subtitle = "Red X = Observed, Blue points with error bars = Predicted (95% CI)",
         x = "", y = "Probability")
}
```

#### Quantile-Probability Plot

This plot shows the relationship between response time quantiles and accuracy/choice probability, similar to Fig. 4 in Wagenmakers et al. (2008).

```{r quantile_probability, echo=FALSE, fig.width=10, fig.height=8}
# Extract necessary data
rt_quantile_data <- subject_data %>%
  filter(grepl("rt_.*_quantiles.*", statistic))

choice_prob_data <- subject_data %>%
  filter(grepl("choice_prob|accuracy", statistic))

if(nrow(rt_quantile_data) > 0 && nrow(choice_prob_data) > 0) {
  # Process RT quantile data
  rt_quantile_data <- rt_quantile_data %>%
    mutate(
      quantile = as.numeric(sub(".*_quantiles_(\\d+).*", "\\1", statistic)) / 100,
      rt_type = sub("rt_(.*)_quantiles_.*", "\\1", statistic)
    )
  
  # Process choice probability data
  choice_prob_data <- choice_prob_data %>%
    mutate(
      choice_type = sub("(.*)_prob", "\1", statistic)
    )
  
  # Try to link RT quantiles with corresponding choice probabilities
  # This is an approximation and may need customization based on your data structure
  combined_data <- rt_quantile_data %>%
    left_join(
      choice_prob_data,
      by = c("subject_id", "rt_type" = "choice_type")
    )
  
  # If join was successful, create the quantile-probability plot
  if(!all(is.na(combined_data$observed.y))) {
    ggplot(combined_data, aes(x = observed.y * 100, y = observed.x, group = quantile)) +
      geom_line() +
      geom_point(size = 2, color = "black", fill = "black") +
      geom_line(aes(x = predicted_mean.y * 100, y = predicted_mean.x), linetype = "dashed") +
      geom_point(aes(x = predicted_mean.y * 100, y = predicted_mean.x), 
                shape = 21, size = 2, fill = "white") +
      geom_errorbar(aes(ymin = predicted_q025.x, ymax = predicted_q975.x), width = 0, alpha = 0.3) +
      facet_wrap(~rt_type) +
      scale_y_continuous(name = "RT Quantiles", 
                        breaks = function(x) pretty(x, n = 10)) +
      scale_x_continuous(name = "Accuracy/Choice Probability (%)", 
                        breaks = function(x) pretty(x, n = 10)) +
      theme_minimal() +
      labs(title = "Quantile-Probability Plot", 
           subtitle = "Solid line/filled points = Observed, Dashed line/open points = Predicted")
  } else {
    # Alternative implementation if join fails
    # Create separate panels for each quantile with accuracy on x-axis
    
    # First get aggregate quantiles across subjects
    agg_quantiles <- rt_quantile_data %>%
      group_by(rt_type, quantile) %>%
      summarize(
        obs_mean = mean(observed, na.rm = TRUE),
        obs_se = sd(observed, na.rm = TRUE)/sqrt(n()),
        pred_mean = mean(predicted_mean, na.rm = TRUE),
        pred_lower = mean(predicted_q025, na.rm = TRUE),
        pred_upper = mean(predicted_q975, na.rm = TRUE),
        .groups = "drop"
      )
    
    # Then get aggregate choice probs
    agg_choice_probs <- choice_prob_data %>%
      group_by(choice_type) %>%
      summarize(
        obs_prob = mean(observed, na.rm = TRUE),
        pred_prob = mean(predicted_mean, na.rm = TRUE),
        .groups = "drop"
      )
    
    # Create the plot with quantiles only
    ggplot(agg_quantiles, aes(x = as.factor(quantile), y = obs_mean, group = 1)) +
      geom_line() +
      geom_point(size = 3) +
      geom_errorbar(aes(ymin = obs_mean - obs_se, ymax = obs_mean + obs_se), width = 0.1) +
      geom_line(aes(y = pred_mean), linetype = "dashed") +
      geom_point(aes(y = pred_mean), shape = 21, size = 3, fill = "white") +
      geom_ribbon(aes(ymin = pred_lower, ymax = pred_upper), alpha = 0.2) +
      facet_wrap(~rt_type) +
      theme_minimal() +
      labs(title = "RT Quantile Plot by Response Type", 
           subtitle = "Solid line/filled points = Observed, Dashed line/open points = Predicted",
           x = "Quantile", y = "Response Time (s)")
  }
}
```

#### Play vs. Pass RT Comparison

```{r play_pass_rt, echo=FALSE, fig.width=10, fig.height=6}
# Extract play vs skip RT data
rt_play_skip <- subject_data %>%
  filter(grepl("rt_play|rt_skip", statistic) & !grepl("hist|quantiles", statistic))

if(nrow(rt_play_skip) > 0) {
  # Clean up statistic names for better display
  rt_play_skip <- rt_play_skip %>%
    mutate(
      rt_type = case_when(
        grepl("play", statistic) ~ "Play",
        grepl("skip", statistic) ~ "Skip/Pass",
        TRUE ~ "Other"
      ),
      metric_type = case_when(
        grepl("mean", statistic) ~ "Mean",
        grepl("median", statistic) ~ "Median",
        grepl("_q[0-9]", statistic) ~ sub(".*_q([0-9]+).*", "Q\1", statistic),
        TRUE ~ "Other"
      )
    )
  
  # Aggregate across subjects
  rt_agg <- rt_play_skip %>%
    group_by(rt_type, metric_type) %>%
    summarize(
      obs_mean = mean(observed, na.rm = TRUE),
      obs_se = sd(observed, na.rm = TRUE)/sqrt(n()),
      pred_mean = mean(predicted_mean, na.rm = TRUE),
      pred_lower = mean(predicted_q025, na.rm = TRUE),
      pred_upper = mean(predicted_q975, na.rm = TRUE),
      .groups = "drop"
    )
  
  # Plot aggregated RT for play vs skip
  p1 = ggplot(rt_agg, aes(x = metric_type, y = obs_mean, color = rt_type, group = rt_type)) +
    geom_line() +
    geom_point(size = 3, shape = 16) +
    geom_errorbar(aes(ymin = obs_mean - obs_se, ymax = obs_mean + obs_se), width = 0.1) +
    geom_line(aes(y = pred_mean), linetype = "dashed") +
    geom_point(aes(y = pred_mean), shape = 1, size = 3) +
    geom_ribbon(aes(ymin = pred_lower, ymax = pred_upper, fill = rt_type), 
               alpha = 0.2, color = NA) +
    theme_minimal() +
    labs(title = "Play vs. Pass Response Times", 
         subtitle = "Solid = Observed (with SE), Dashed = Predicted (with 95% CI)",
         x = "RT Metric", y = "Response Time (s)",
         color = "Response Type", fill = "Response Type")
  
  # Calculate play-pass RT difference
  rt_diff <- rt_agg %>%
    select(metric_type, rt_type, obs_mean, pred_mean) %>%
    pivot_wider(
      names_from = rt_type,
      values_from = c(obs_mean, pred_mean)
    ) %>%
    mutate(
      obs_diff = obs_mean_Play - `obs_mean_Skip/Pass`,
      pred_diff = pred_mean_Play - `pred_mean_Skip/Pass`,
      diff_error = obs_diff - pred_diff
    )
  
  # Plot the play-pass RT difference
  p2 = ggplot(rt_diff, aes(x = metric_type, y = obs_diff)) +
    geom_bar(stat = "identity", fill = "darkred", alpha = 0.7) +
    geom_point(aes(y = pred_diff), size = 3, color = "blue") +
    geom_line(aes(y = pred_diff, group = 1), color = "blue") +
    geom_hline(yintercept = 0, linetype = "dashed") +
    theme_minimal() +
    labs(title = "Play - Pass RT Difference", 
         subtitle = "Red bars = Observed difference, Blue line/points = Predicted difference",
         x = "RT Metric", y = "Difference (s)")
  knitr::knit_print(p1)
  knitr::knit_print(p2)
}
```

## Parameter/Data Correlations
```{r ssm_param_correlation_analysis, fig.width=10, fig.height=8, results='asis'}
if (!is.null(recovery_data)) {
  # Extract SSM parameters from recovery data
  ssm_params <- recovery_data %>%
    filter(parameter_type %in% c("individual", "group", "single")) %>%
    # Filter to include only SSM-specific parameters
    filter(grepl("ndt|boundary|threshold|drift|tau|beta", parameter, ignore.case = TRUE)) %>%
    select(subject_id, parameter, true_value, recovered_value) %>%
    # We'll use recovered values for correlations (since these are what the model "thinks" it has)
    select(subject_id, parameter, recovered_value) %>%
    pivot_wider(names_from = parameter, values_from = recovered_value)
  
  # Extract SSM metrics from PPC data
  ssm_ppc_stats <- subject_data %>%
    filter(component == "SSM" | grepl("rt|choice", statistic, ignore.case = TRUE)) %>%
    select(subject_id, statistic, observed) %>%
    pivot_wider(names_from = statistic, values_from = observed)
  
  # Only proceed if we have enough data
  if (ncol(ssm_params) > 1 && ncol(ssm_ppc_stats) > 1) {
    # Join datasets by subject_id
    ssm_params$subject_id = ssm_ppc_stats$subject_id
    ssm_combined <- inner_join(ssm_params, ssm_ppc_stats, by = "subject_id")
    
    # Select only numeric columns for correlation
    ssm_numeric <- ssm_combined %>% select_if(is.numeric)
    
    # Separate parameters and statistics for clearer presentation
    ssm_param_cols <- setdiff(names(ssm_params), "subject_id")
    ssm_stat_cols <- setdiff(names(ssm_ppc_stats), "subject_id")
    
    # Group SSM stats into meaningful categories
    general_metrics <- c("mean_rt", "median_rt", "min_rt", "max_rt", "choice_prob")
    general_stats <- intersect(general_metrics, ssm_stat_cols)
    
    play_rt_stats <- grep("rt_play", ssm_stat_cols, value = TRUE)
    skip_rt_stats <- grep("rt_skip", ssm_stat_cols, value = TRUE)
    
    # Initialize data frame for storing all correlations
    all_ssm_cors <- data.frame()
    
    # 1. SSM parameters vs general metrics
    if (length(general_stats) > 0) {
      general_matrix <- cor(ssm_numeric[ssm_param_cols], ssm_numeric[general_stats], 
                         use = "pairwise.complete.obs")
      
      success_general <- create_corr_plot(general_matrix, "SSM Parameters vs. General Metrics")
      
      if (success_general) {
        general_cors <- get_top_correlations(general_matrix, n = 10) %>% 
          mutate(Category = "General")
        all_ssm_cors <- rbind(all_ssm_cors, general_cors)
      }
    }
    
    # 2. SSM parameters vs Play RT metrics
    if (length(play_rt_stats) > 0) {
      play_matrix <- cor(ssm_numeric[ssm_param_cols], ssm_numeric[play_rt_stats], 
                       use = "pairwise.complete.obs")
      
      success_play <- create_corr_plot(play_matrix, "SSM Parameters vs. Play RT Metrics")
      
      if (success_play) {
        play_cors <- get_top_correlations(play_matrix, n = 10) %>% 
          mutate(Category = "Play RT")
        all_ssm_cors <- rbind(all_ssm_cors, play_cors)
      }
    }
    
    # 3. SSM parameters vs Skip RT metrics
    if (length(skip_rt_stats) > 0) {
      skip_matrix <- cor(ssm_numeric[ssm_param_cols], ssm_numeric[skip_rt_stats], 
                       use = "pairwise.complete.obs")
      
      success_skip <- create_corr_plot(skip_matrix, "SSM Parameters vs. Skip RT Metrics")
      
      if (success_skip) {
        skip_cors <- get_top_correlations(skip_matrix, n = 10) %>% 
          mutate(Category = "Skip RT")
        all_ssm_cors <- rbind(all_ssm_cors, skip_cors)
      }
    }
    
    # If we have correlations, continue with analysis
    if (nrow(all_ssm_cors) > 0) {
      # Create a table of strongest correlations across all categories
      all_ssm_cors %>%
        mutate(
          Parameter = format_names(Parameter),
          Statistic = format_names(Statistic)
        ) %>%
        arrange(desc(Abs_Correlation)) %>%
        head(15) %>%
        kable(caption = "Top 15 Parameter-Behavior Correlations (All Categories)", digits = 3) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                      full_width = FALSE) %>%
        knitr::knit_print()
      
      # Create category-specific correlation tables
      for (category in unique(all_ssm_cors$Category)) {
        all_ssm_cors %>%
          filter(Category == category) %>%
          mutate(
            Parameter = format_names(Parameter),
            Statistic = format_names(Statistic)
          ) %>%
          arrange(desc(Abs_Correlation)) %>%
          head(8) %>%
          select(-Category) %>%
          kable(caption = paste0("Top Correlations - ", category, " Metrics"), digits = 3) %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                       full_width = FALSE) %>%
          knitr::knit_print()
      }
      
      # Create parameter-parameter correlation matrix
      param_cor <- cor(ssm_numeric[ssm_param_cols], use = "pairwise.complete.obs")
      create_corr_plot(param_cor, "Parameter-Parameter Correlations")
      
      # Identify high-impact parameters
      param_impact <- all_ssm_cors %>%
        group_by(Parameter, Category) %>%
        summarize(
          Mean_Abs_Correlation = mean(Abs_Correlation, na.rm = TRUE),
          Max_Correlation = max(Correlation, na.rm = TRUE),
          Min_Correlation = min(Correlation, na.rm = TRUE),
          Impact_Score = sum(Abs_Correlation, na.rm = TRUE),
          Num_Strong_Correlations = sum(Abs_Correlation > 0.4, na.rm = TRUE),
          .groups = "drop"
        ) %>%
        arrange(desc(Impact_Score))
      
      # Calculate overall parameter impact
      overall_impact <- param_impact %>%
        group_by(Parameter) %>%
        summarize(
          Mean_Abs_Correlation = mean(Mean_Abs_Correlation, na.rm = TRUE),
          Max_Correlation = max(Max_Correlation, na.rm = TRUE),
          Min_Correlation = min(Min_Correlation, na.rm = TRUE),
          Impact_Score = sum(Impact_Score, na.rm = TRUE),
          .groups = "drop"
        ) %>%
        arrange(desc(Impact_Score))
      
      # Show parameter impact table
      overall_impact %>%
        mutate(Parameter = format_names(Parameter)) %>%
        head(10) %>%
        kable(caption = "Parameter Impact Rankings", digits = 3) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                      full_width = FALSE) %>%
        knitr::knit_print()
      
      # Create detailed impact breakdown by category
      param_impact %>%
        mutate(Parameter = format_names(Parameter)) %>%
        pivot_wider(
          id_cols = Parameter,
          names_from = Category,
          values_from = Impact_Score,
          values_fill = 0
        ) %>%
        mutate(Total_Impact = rowSums(across(where(is.numeric)))) %>%
        arrange(desc(Total_Impact)) %>%
        head(10) %>%
        kable(caption = "Parameter Impact by Category", digits = 3) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                     full_width = FALSE) %>%
        knitr::knit_print()
      
      # Visualize top parameter impacts
      if (nrow(overall_impact) >= 3) {
        top_params <- head(overall_impact, 5)$Parameter
        
        # Extract correlations for top parameters
        top_cors <- all_ssm_cors %>%
          filter(Parameter %in% top_params) %>%
          mutate(
            Parameter = factor(Parameter, levels = rev(top_params)),
            Statistic = gsub("_", " ", Statistic)
          )
        
        # Create a horizontal bar plot
        ggplot(top_cors, aes(x = reorder(Statistic, Abs_Correlation), 
                              y = Correlation, fill = Parameter)) +
          geom_col(position = "dodge") +
          coord_flip() +
          scale_fill_brewer(palette = "Set2") +
          theme_minimal() +
          labs(title = "Top Parameters' Influence on Response Metrics",
               x = "",
               y = "Correlation Strength") +
          theme(legend.title = element_blank())
        
        # Create a heatmap visualization
        if (length(top_params) >= 3 && nrow(top_cors) >= 10) {
          # Only include metrics that have strong correlations with at least one parameter
          top_metrics <- top_cors %>%
            group_by(Statistic) %>%
            summarize(max_abs_corr = max(abs(Correlation)), .groups = "drop") %>%
            filter(max_abs_corr > 0.3) %>%
            arrange(desc(max_abs_corr)) %>%
            head(12) %>%
            pull(Statistic)
          
          # Filter correlations to top parameters and top metrics
          heatmap_data <- top_cors %>%
            filter(Statistic %in% top_metrics)
          
          if (nrow(heatmap_data) > 0) {
            ggplot(heatmap_data, aes(x = Parameter, y = Statistic, fill = Correlation)) +
              geom_tile() +
              scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                                  midpoint = 0, limit = c(-1,1)) +
              theme_minimal() +
              theme(axis.text.x = element_text(angle = 45, hjust = 1),
                    axis.text.y = element_text(size = 8)) +
              labs(title = "Parameter-Metric Correlation Heatmap",
                   subtitle = "Key parameters and their influence on behavioral metrics")
          }
        }
        
        # Create category-based impact visualization
        impact_by_category <- param_impact %>%
          filter(Parameter %in% top_params) %>%
          mutate(Parameter = factor(Parameter, levels = top_params))
        
        ggplot(impact_by_category, aes(x = Parameter, y = Impact_Score, fill = Category)) +
          geom_col() +
          scale_fill_brewer(palette = "Set1") +
          theme_minimal() +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          labs(title = "Parameter Impact by Category",
               x = "Parameter", 
               y = "Impact Score",
               fill = "Metric Category")
      }
    } else {
      message("Insufficient correlation data for SSM analysis.")
    }
  } else {
    message("Insufficient parameter or PPC data for correlation analysis.")
  }
} else {
  message("Recovery data not available for correlation analysis.")
}
```


```{r}
# Define correlation threshold as a variable
cor_threshold <- 0.1  # Minimum correlation magnitude to consider 

# Get number of observations (subjects)
n_subjects <- nrow(ssm_combined)

# Calculate significance and filter
significant_cors <- all_ssm_cors %>%
  mutate(
    # Calculate p-value using t-distribution
    p_value = 2 * pt(abs(Correlation) * sqrt(n_subjects - 2) / sqrt(1 - Correlation^2), 
                    df = n_subjects - 2, lower.tail = FALSE),
    # Flag for significance
    is_significant = p_value < 0.05
  ) %>%
  filter(is_significant & Abs_Correlation > cor_threshold) %>%
  arrange(desc(Abs_Correlation)) %>%
  head(30)  # Take top 30 by correlation magnitude AFTER filtering for significance

if (nrow(significant_cors) > 5) {
  # Create graph
  g <- graph_from_data_frame(significant_cors[, c("Parameter", "Statistic", "Correlation")], directed = TRUE)
  
  # Add node attributes
  V(g)$type <- ifelse(V(g)$name %in% significant_cors$Parameter, "Parameter", "Statistic")
  V(g)$category <- "Unknown"
  
  # Assign categories to statistics
  for (cat in unique(significant_cors$Category)) {
    cat_stats <- significant_cors$Statistic[significant_cors$Category == cat]
    V(g)$category[V(g)$type == "Statistic" & V(g)$name %in% cat_stats] <- cat
  }
  
  # Set edge width based on correlation strength
  E(g)$width <- 1 + 4 * abs(E(g)$Correlation)
  
  # Set edge color based on positive/negative correlation
  E(g)$color <- ifelse(E(g)$Correlation > 0, "#4DAF4A", "#E41A1C")
  
  # Set node color based on type and category
  V(g)$color <- ifelse(V(g)$type == "Parameter", "#377EB8", 
                      ifelse(V(g)$category == "General", "#4DAF4A",
                            ifelse(V(g)$category == "Play RT", "#FF7F00",
                                  ifelse(V(g)$category == "Skip RT", "#984EA3", "#999999"))))
  
  # Set node shape based on type (parameters are circles, statistics are squares)
  V(g)$shape <- ifelse(V(g)$type == "Parameter", "circle", "square")
  
  # Create layout
  l <- layout_with_fr(g)
  
  # Plot the network
  par(mar = c(0,0,2,0))
  plot(g, layout = l,
       vertex.size = 15,
       vertex.label.cex = 0.7,
       vertex.label.color = "black",
       vertex.frame.color = NA,
       edge.curved = 0.3,
       main = paste0("Significant SSM Parameter-Behavior Correlations (p<.05, r>", cor_threshold, ")"))
  
  legend("bottomright", 
         legend = c("Parameter (latent)", "General Metric (observed)", 
                   "Play RT Metric (observed)", "Skip RT Metric (observed)", 
                   "Positive Correlation", "Negative Correlation"),
         pch = c(16, 15, 15, 15, NA, NA),
         col = c("#377EB8", "#4DAF4A", "#FF7F00", "#984EA3", "#4DAF4A", "#E41A1C"),
         lty = c(NA, NA, NA, NA, 1, 1),
         pt.cex = 2,
         cex = 0.7,
         bty = "n")
  
  # Add a table with correlation values and CIs
  significant_cors %>%
    mutate(
      # Calculate Fisher's z transformation for CI
      z = 0.5 * log((1 + Correlation) / (1 - Correlation)),
      se_z = 1 / sqrt(n_subjects - 3),
      ci_lower_z = z - 1.96 * se_z,
      ci_upper_z = z + 1.96 * se_z,
      # Transform back to correlation scale
      ci_lower = (exp(2 * ci_lower_z) - 1) / (exp(2 * ci_lower_z) + 1),
      ci_upper = (exp(2 * ci_upper_z) - 1) / (exp(2 * ci_upper_z) + 1)
    ) %>%
    select(Category, Parameter, Statistic, Correlation, ci_lower, ci_upper, p_value) %>%
    mutate(
      Parameter = format_names(Parameter),
      Statistic = format_names(Statistic),
      CI = sprintf("[%.2f, %.2f]", ci_lower, ci_upper)
    ) %>%
    select(Category, Parameter, Statistic, Correlation, CI, p_value) %>%
    arrange(Category, desc(abs(Correlation))) %>%
    kable(caption = "Significant SSM Correlations with 95% CIs by Category", 
          digits = c(NA, NA, NA, 2, NA, 3)) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  full_width = FALSE) %>%
    knitr::knit_print()
} else {
  message("Insufficient significant correlations for network visualization.")
}
```


## Conclusion

This analysis examines how well the ddm model can reproduce key behavioral patterns observed in the igt_mod task. The model's fit quality is evaluated through posterior predictive checks, comparing observed statistics to those generated from model simulations.

PPP values near 0 or 1 suggest systematic discrepancies between the model and observed data. These may indicate aspects of behavior that the model struggles to capture. Good model fit is indicated by PPP values distributed uniformly between 0 and 1, with observed statistics falling within the model's predicted range.
