## RL Component Analysis

This section examines reinforcement learning behavioral metrics across participants.

```{r rl_setup, include=FALSE}
# Load task config for RL-specific analysis
source(file.path(here::here(), "scripts", "ppc", "helpers", "task_config.R"))
task_config <- get_task_config(task)
```

### Choice Statistics Visualization

```{r rl_choice_stats, echo=FALSE, fig.width=10, fig.height=8}
# Create choice statistics plots
choice_plots <- plot_choice_statistics(ppc_summary)

# Display each group of plots
for (plot_name in names(choice_plots)) {
  knitr::knit_print(choice_plots[[plot_name]])
}
```

### Block-Level Curves

```{r choice_block_curves, echo=FALSE, fig.width=10, fig.height=6}

# Task-specific variables to plot
if (task_config$type == "deck_selection") {
  # IGT block curves - no play/pass stuff
  variables_to_plot = c("good_deck_freq", "bad_deck_freq", "net_score", "total_earnings", 
                       "deck1_freq", "deck2_freq", "deck3_freq", "deck4_freq")
} else if (task_config$type == "play_pass") {
  # mIGT block curves
  variables_to_plot = c("good_play_ratio", "bad_play_ratio", "net_score", "total_earnings", "play_ratio", 
                       "play_ratio_deck1", "play_ratio_deck2", "play_ratio_deck3", "play_ratio_deck4")
}

for (plot_stat in variables_to_plot){
  if (any(ppc_summary$statistic == plot_stat & grepl("block_", ppc_summary$session))) {
    tryCatch({
      plot <- plot_block_curve(ppc_summary, statistic = plot_stat)
      knitr::knit_print(plot)
    }, error = function(e) {
      cat("Could not create block curve for", plot_stat, ":", e$message, "\n")
    })
  }
}

```

### Win-Stay/Lose-Shift Behavior

```{r rl_wsls, echo=FALSE, fig.width=8, fig.height=5}
# Task-specific WSLS analysis
if (task_config$type == "deck_selection") {
  # IGT: WSLS makes sense and uses "win_stay", "lose_shift" names
  wsls_stats <- c("win_stay", "lose_shift")
  wsls_data <- ppc_summary %>%
    filter(category == "choice" & session == "session" & 
           statistic %in% wsls_stats)
  
  if(nrow(wsls_data) > 0) {
    # Aggregate across subjects for cleaner visualization
    wsls_agg <- wsls_data %>%
      group_by(statistic) %>%
      summarize(
        obs_mean = mean(observed, na.rm = TRUE),
        obs_se = sd(observed, na.rm = TRUE)/sqrt(n()),
        pred_mean = quantile(unlist(list(simulated_mean)), 0.5, na.rm = TRUE),
        pred_lower = quantile(unlist(list(simulated_mean)), 0.025, na.rm = TRUE),
        pred_upper = quantile(unlist(list(simulated_mean)), 0.975, na.rm = TRUE),
        misfit = obs_mean - pred_mean,
        misfit_standardized = misfit / (pred_upper - pred_lower) * 2,
        .groups = "drop"
      )
    
    # Plot aggregated WSLS data
    p1 = ggplot(wsls_agg, aes(x = statistic)) +
      geom_pointrange(aes(y = pred_mean, ymin = pred_lower, ymax = pred_upper), 
                     color = "blue", size = 1, position = position_dodge(width = 0.5)) +
      geom_pointrange(aes(y = obs_mean, ymin = obs_mean - obs_se, ymax = obs_mean + obs_se), 
                     color = "red", shape = 4, size = 1, position = position_dodge(width = 0.5)) +
      ylim(0, 1) +
      theme_minimal() +
      labs(title = "Win-Stay/Lose-Shift Behavior (IGT)", 
           subtitle = "Red X = Observed (with SE), Blue dots = Predicted (with 95% CI)",
           x = "", y = "Ratio")
    
    # Create summary table
    kable(wsls_agg %>% select(statistic, obs_mean, pred_mean, misfit, misfit_standardized),
          caption = "Win-Stay/Lose-Shift: Observed vs. Predicted", digits = 3) %>%
      kable_styling(bootstrap_options = c("striped", "hover"))
    
    knitr::knit_print(p1)
  } else {
    cat("No Win-Stay/Lose-Shift data found in the statistics for IGT.\n")
  }
  
} else if (task_config$type == "play_pass") {
  # mIGT: WSLS doesn't make sense for play/pass decisions
  cat("Win-Stay/Lose-Shift behavior is not applicable to the modified IGT (play/pass decisions).\n")
  cat("This behavioral pattern requires a choice outcome followed by the same choice option,\n")
  cat("which is not meaningful when participants choose whether to play or pass on different decks.\n")
}
```

### Deck Selection Stats

```{r deck_selection_ratio, echo=FALSE, fig.width=8, fig.height=6}
# Task-specific deck selection analysis
if (task_config$type == "deck_selection") {
  # IGT: Look for deck frequency data
  deck_ratio_data <- ppc_summary %>%
    filter(category == "choice" & session == "session" & 
           grepl("deck[1-4]_freq|good_deck_freq|bad_deck_freq", statistic))
  
  plot_title <- "IGT Deck Selection Frequencies"
  subtitle_text <- "Direct deck selection from 4 decks"
  
} else if (task_config$type == "play_pass") {
  # mIGT: Look for play ratio data
  deck_ratio_data <- ppc_summary %>%
    filter(category == "choice" & session == "session" & 
           grepl("play_ratio_deck|good_play_ratio|bad_play_ratio", statistic))
  
  plot_title <- "mIGT Play Ratios by Deck"  
  subtitle_text <- "Play/pass decisions for offered decks"
}

if(nrow(deck_ratio_data) > 0) {
  # Aggregate across subjects
  ratio_agg <- deck_ratio_data %>%
    group_by(statistic) %>%
    summarize(
      obs_mean = mean(observed, na.rm = TRUE),
      obs_se = sd(observed, na.rm = TRUE)/sqrt(n()),
      pred_mean = mean(simulated_mean, na.rm = TRUE),
      pred_lower = mean(p_2.5, na.rm = TRUE),
      pred_upper = mean(p_97.5, na.rm = TRUE),
      misfit = obs_mean - pred_mean,
      misfit_standardized = misfit / (pred_upper - pred_lower) * 2,
      .groups = "drop"
    )
  
  # Plot deck selection ratios
  p1 = ggplot(ratio_agg, aes(x = statistic)) +
    geom_pointrange(aes(y = pred_mean, ymin = pred_lower, ymax = pred_upper), 
                   color = "blue", size = 1, position = position_dodge(width = 0.5)) +
    geom_pointrange(aes(y = obs_mean, ymin = obs_mean - obs_se, ymax = obs_mean + obs_se), 
                   color = "red", shape = 4, size = 1, position = position_dodge(width = 0.5)) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = plot_title, 
         subtitle = paste(subtitle_text, "- Red X = Observed (with SE), Blue dots = Predicted (with 95% CI)"),
         x = "", y = "Frequency/Ratio")
  
  # Plot directionality of misfit
  p2 = ggplot(ratio_agg, aes(x = statistic, y = misfit, fill = abs(misfit_standardized) > 1)) +
    geom_col() +
    geom_hline(yintercept = 0, linetype = "dashed") +
    scale_fill_manual(values = c("TRUE" = "red", "FALSE" = "gray"), 
                     labels = c("FALSE" = "Not Significant", "TRUE" = "Significant"),
                     name = "Misfit") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Misfit Direction for Deck Selection Metrics",
         subtitle = "Positive = Model Underpredicts, Negative = Model Overpredicts",
         x = "", y = "Observed - Predicted")
  
  knitr::knit_print(p1)
  knitr::knit_print(p2)
} else {
  cat("No deck selection/play ratio data found in the statistics.\n")
}
```

### Earnings Performance

```{r earnings_performance, echo=FALSE, fig.width=10, fig.height=6}
# Extract earnings/money data
earnings_data <- ppc_summary %>%
  filter(category == "choice" & session == "session" & 
         grepl("earnings|net_score", statistic))

if(nrow(earnings_data) > 0) {
  # Aggregate across subjects
  earnings_agg <- earnings_data %>%
    group_by(statistic) %>%
    summarize(
      obs_mean = mean(observed, na.rm = TRUE),
      obs_se = sd(observed, na.rm = TRUE)/sqrt(n()),
      pred_mean = mean(simulated_mean, na.rm = TRUE),
      pred_lower = mean(p_2.5, na.rm = TRUE),
      pred_upper = mean(p_97.5, na.rm = TRUE),
      misfit = obs_mean - pred_mean,
      misfit_pct = (obs_mean - pred_mean) / pred_mean * 100,
      .groups = "drop"
    )
  
  # Prepare data for plot with facets
  earnings_agg$y_max <- pmax(earnings_agg$obs_mean + earnings_agg$obs_se, 
                           earnings_agg$pred_upper, na.rm = TRUE)
  earnings_agg$text_y <- earnings_agg$y_max * 1.15
  
  # Plot earnings metrics
  ggplot(earnings_agg, aes(x = statistic)) +
    geom_pointrange(aes(y = pred_mean, ymin = pred_lower, ymax = pred_upper), 
                   color = "blue", size = 1) +
    geom_pointrange(aes(y = obs_mean, ymin = obs_mean - obs_se, ymax = obs_mean + obs_se), 
                   color = "red", shape = 4, size = 1) +
    geom_text(aes(y = text_y, label = sprintf("Δ: %.1f%%", misfit_pct)),
              size = 4, fontface = "bold") +
    facet_wrap(~statistic, scales = "free_y") +
    scale_x_discrete(labels = NULL) +
    theme_minimal() +
    theme(
      strip.text = element_text(size = 14, face = "bold"),
      axis.text.y = element_text(size = 10),
      axis.ticks.x = element_blank(),
      axis.text.x = element_blank(),
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      panel.grid.major.x = element_blank(),
      panel.grid.minor = element_blank()
    ) +
    labs(
      title = "Earnings Performance Metrics",
      subtitle = "Red X = Observed (with SE), Blue dots = Predicted (with 95% CI)",
      x = "", y = "Value"
    )
  
  # Create summary table
  kable(earnings_agg %>% select(statistic, obs_mean, pred_mean, misfit_pct),
        caption = "Earnings Metrics Summary", digits = 2) %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("No earnings data found in the statistics.\n")
}
```

## Subject-Level Statistics

The plots below compare observed statistics (red) with model predictions (blue with 95% CI). Good model fit is indicated by observed values falling within the prediction intervals.

```{r subject_level_overall, echo=FALSE, fig.width=10, fig.height=8}
# Select a sample of subjects for visualization
subjects_to_plot <- sample(unique(ppc_summary$subject_id), 
                           min(6, length(unique(ppc_summary$subject_id))))

for (subject_id in subjects_to_plot) {
  # Generate plots for this subject
  tryCatch({
    subject_plots <- generate_subject_plots(ppc_summary, subject_id, save_plots = FALSE)
    
    # Print key plots
    if (!is.null(subject_plots$choice)) {
      if (is.list(subject_plots$choice)) {
        for (plot_name in names(subject_plots$choice)) {
          print(subject_plots$choice[[plot_name]])
        }
      } else {
        print(subject_plots$choice)
      }
    }
  }, error = function(e) {
    cat("Could not generate subject plots for", subject_id, ":", e$message, "\n")
  })
}
```
