---
title: "Posterior Predictive Check Analysis: igt_mod - ev - batch_001"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressPackageStartupMessages({
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  library(knitr)
  library(kableExtra)
  library(reshape2)
  library(corrplot)
  library(viridis)
  library(igraph)
})

# Source helper functions - use existing functions rather than duplicating
script_dir <- file.path(here::here(), "scripts")
source(file.path(script_dir, "parameter_recovery", "helper_functions_PR.R"))
source(file.path(script_dir, "helper_functions_cmdSR.R"))
source(file.path(script_dir, "ppc", "visualization_functions.R"))

# The only file we actually need is the summary file
ppc_summary_file <- "/Users/icd/Library/CloudStorage/Dropbox/Projects/modeling_mIGT/Data/ppc/stats/ppc_summary_task-igt_mod_model-ev_group-batch_001.csv"     # ppc_summary_{task}_{model}_{group}.csv

# Extract components from the summary filename using helper function
components <- parse_bids_filename(basename(ppc_summary_file))
task <- components$task
model <- components$model
group <- components$group

# Create model_type tag based on model name
model_type <- if(model == "ddm") {
  "SSM"  # Pure Sequential Sampling Model
} else if(grepl("ddm", model)) {
  "RL_SSM"  # Combined RL and Sequential Sampling Model
} else {
  "RL"  # Pure Reinforcement Learning Model
}

# Load the summary data from CSV file
message("Loading PPC statistics...")

# Load the primary data source
if (file.exists(ppc_summary_file)) {
  message("Loading summary file: ", ppc_summary_file)
  ppc_summary <- read.csv(ppc_summary_file)
  
  # Ensure proper column naming for compatibility with visualization functions
  if (!"subject_id" %in% names(ppc_summary) && "sid" %in% names(ppc_summary)) {
    ppc_summary <- ppc_summary %>% rename(subject_id = sid)
  }
} else {
  stop("Summary file not found: ", ppc_summary_file)
}

# Construct recovery file path - model parameter recovery analysis if available
recovery_dir <- gsub("ppc", "recovery", dirname(ppc_summary_file))
recovery_csv <- file.path(recovery_dir, 
           paste0("recovery_", task, "_", model, "_", group, ".csv"))

# Format parameter and statistic names for display
format_names <- function(names) {
  names %>% 
    gsub("_", " ", .) %>%
    gsub("ssm ", "", .) %>%
    gsub("rl ", "", .) %>%
    tools::toTitleCase(.)
}

# Create function to find top correlations
get_top_correlations <- function(cor_matrix, n = 10) {
  cors_long <- as.data.frame(as.table(cor_matrix)) %>%
    rename(Parameter = Var1, Statistic = Var2, Correlation = Freq) %>%
    mutate(
      Parameter = as.character(Parameter),
      Statistic = as.character(Statistic),
      Abs_Correlation = abs(Correlation)
    ) %>%
    arrange(desc(Abs_Correlation))
  
  # Return top N correlations
  return(head(cors_long, n))
}

# Helper function for correlation plots
create_corr_plot <- function(corr_matrix, title, mar = c(1,1,2,1)) {
  if(ncol(corr_matrix) > 1 && nrow(corr_matrix) > 0) {
    if (nrow(corr_matrix) == ncol(corr_matrix)){
    corrplot(corr_matrix, 
             method = "circle", 
             type = "upper", 
             tl.col = "black",
             tl.srt = 45,
             addCoef.col = "black",
             number.cex = 0.7,
             mar = mar,
             title = title,
             diag = FALSE)
    } else{
      corrplot(corr_matrix, 
             method = "circle", 
             type = "full", 
             tl.col = "black",
             tl.srt = 45,
             addCoef.col = "black",
             number.cex = 0.7,
             mar = mar,
             title = title)
    }
    return(TRUE)
  } else {
    cat("Insufficient data for correlation matrix:", title, "\n")
    return(FALSE)
  }
}

# Calculate extreme PPP metrics directly from ppc_summary
# Only count session-level data (not block-level) for summary statistics
if ("extreme_ppp" %in% names(ppc_summary)) {
  session_data <- ppc_summary[!grepl("block_", ppc_summary$session),] %>%
    filter(!grepl("lose_shift", statistic), !grepl("win_stay", statistic))
  extreme_ppp_count <- sum(session_data$extreme_ppp, na.rm = TRUE)
  total_ppp_count <- nrow(session_data)
  extreme_ppp_ratio <- extreme_ppp_count / total_ppp_count
} else {
  extreme_ppp_count <- 0
  total_ppp_count <- 0
  extreme_ppp_ratio <- 0
  message("Could not find PPP extreme values data")
}
```

## Overview

This document presents posterior predictive check (PPC) analysis for the **ev** model (**`r model_type`** type) applied to the **igt_mod** task with group type **batch_001**.

Posterior predictive checks compare statistics from observed data with statistics from data simulated using posterior parameter samples. These checks help validate whether the model can reproduce key behavioral patterns in the data.

## Summary Statistics

### PPC Quality Overview

```{r summary, echo=FALSE}
summary_df <- data.frame(
  Statistic = c("Total Statistics Checked", "Extreme PPP Values (p < 0.05 or p > 0.95)", 
                "Proportion Extreme"),
  Value = c(total_ppp_count, extreme_ppp_count, sprintf("%.2f%%", extreme_ppp_ratio * 100))
)

kable(summary_df, caption = "Summary of All Individual PPC Results") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Model-Level Statistics

```{r model_stats, echo=FALSE}
# Create an aggregate summary for display
model_stats <- ppc_summary %>%
  filter(!grepl("block_", session)) %>%
  group_by(category, statistic) %>%
  summarize(
    observed = mean(observed, na.rm = TRUE),
    simulated_mean = mean(simulated_mean, na.rm = TRUE),
    ppp = mean(ppp, na.rm = TRUE),
    extreme_rate = mean(extreme_ppp, na.rm = TRUE),
    .groups = "drop"
  )

# Select most relevant columns for display
priority_cols <- c("category", "statistic", "observed", "simulated_mean", "ppp", "extreme_rate")
display_cols <- intersect(priority_cols, names(model_stats))

# Limit number of rows displayed for readability
if (nrow(model_stats) > 15) {
  display_rows <- 15
  note <- "Showing top 15 rows. See full statistics in the data file."
} else {
  display_rows <- nrow(model_stats)
  note <- NULL
}

# Create display table
model_display <- model_stats[1:display_rows, display_cols]

# Display the table
kable(model_display, caption = "Model-Level PPC Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

if (!is.null(note)) {
  cat(note)
}
```

## PPP Value Distribution

PPP values should ideally be distributed uniformly between 0 and 1 if the model fits well. Extreme values (< 0.05 or > 0.95) indicate statistics that the model struggles to reproduce.

```{r ppp_dist, echo=FALSE, fig.width=10, fig.height=6}
# Create PPP summary plots for each category
if (any(ppc_summary$category == "choice")) {
  choice_ppp <- plot_ppp_summary(ppc_summary, category = "choice")
  print(choice_ppp)
}

if (any(ppc_summary$category == "rt")) {
  rt_ppp <- plot_ppp_summary(ppc_summary, category = "rt")
  print(rt_ppp)
}

# Add PPP heatmap for more detailed view
if (exists("plot_ppp_heatmap", mode = "function") && any(ppc_summary$category == "choice")) {
  ppp_heatmap <- plot_ppp_heatmap(ppc_summary, category = "choice")
  print(ppp_heatmap)
}
```

## Directionality of Model Misfit

This section examines not only whether the model fits the data, but also the direction of misfit (whether the model systematically over- or under-predicts observed statistics).

```{r misfit_analysis, echo=FALSE, fig.width=10, fig.height=8}
# Calculate misfit for session data
session_data <- ppc_summary %>% filter(session == "session")

# Calculate misfit
misfit_data <- session_data %>%
  mutate(
    misfit = observed - simulated_mean,
    misfit_standardized = misfit / (p_97.5 - p_2.5) * 2,
    misfit_direction = case_when(
      misfit > 0 & extreme_ppp ~ "Model Underpredicts",
      misfit < 0 & extreme_ppp ~ "Model Overpredicts",
      TRUE ~ "Good Fit"
    )
  )

# Plot standardized misfit by category and statistic
misfit_data %>%
  filter(category == "choice") %>%
ggplot(., aes(x = statistic, y = misfit_standardized, fill = misfit_direction)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = c(-1, 1), linetype = "dotted", color = "red") +
  scale_fill_manual(values = c("Good Fit" = "gray", 
                            "Model Underpredicts" = "blue", 
                            "Model Overpredicts" = "red")) +
  facet_wrap(~category, scales = "free_x") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Standardized Misfit by Statistic",
       subtitle = "Misfit = (Observed - Predicted) / Width of 95% CI",
       x = "", y = "Standardized Misfit",
       fill = "Direction")

if (any(ppc_summary$category == "rt")) {
  misfit_data %>%
    filter(category == "rt") %>%
  ggplot(., aes(x = statistic, y = misfit_standardized, fill = misfit_direction)) +
    geom_boxplot() +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = c(-1, 1), linetype = "dotted", color = "red") +
    scale_fill_manual(values = c("Good Fit" = "gray", 
                              "Model Underpredicts" = "blue", 
                              "Model Overpredicts" = "red")) +
    facet_wrap(~category, scales = "free_x") +
    coord_flip() +
    theme_minimal() +
    labs(title = "Standardized Misfit by Statistic",
         subtitle = "Misfit = (Observed - Predicted) / Width of 95% CI",
         x = "", y = "Standardized Misfit",
         fill = "Direction")
  
  # Create misfit summary table
  misfit_summary <- misfit_data %>%
    group_by(category, statistic) %>%
    summarize(
      mean_misfit = mean(misfit, na.rm = TRUE),
      mean_std_misfit = mean(misfit_standardized, na.rm = TRUE),
      prop_underpredict = mean(misfit_direction == "Model Underpredicts", na.rm = TRUE),
      prop_overpredict = mean(misfit_direction == "Model Overpredicts", na.rm = TRUE),
      mean_abs_misfit = mean(abs(misfit_standardized), na.rm = TRUE),
      .groups = "drop"
    ) %>%
    arrange(category, desc(mean_abs_misfit))
  
  kable(misfit_summary, caption = "Summary of Model Misfit Direction and Magnitude") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

## RL Component Analysis

This section examines reinforcement learning behavioral metrics across participants.

### Choice Statistics Visualization

```{r rl_choice_stats, echo=FALSE, fig.width=10, fig.height=8}
# Create choice statistics plots
choice_plots <- plot_choice_statistics(ppc_summary)

# Display each group of plots
for (plot_name in names(choice_plots)) {
  knitr::knit_print(choice_plots[[plot_name]])
}
```

### Block-Level Curves

```{r choice_block_curves, echo=FALSE, fig.width=10, fig.height=6}

variables_to_plot = c("good_play_ratio", "net_score", "total_earnings", "pass_ratio", "play_ratio_deck1", "play_ratio_deck2", "play_ratio_deck3", "play_ratio_deck4", "bad_play_ratio")

for (plot_stat in variables_to_plot){
  plot <- plot_block_curve(ppc_summary, statistic = plot_stat)
  knitr::knit_print(plot)
}

```

### Win-Stay/Lose-Shift Behavior

```{r rl_wsls, echo=FALSE, fig.width=8, fig.height=5}
# Extract WSLS data
wsls_stats <- c("win_stay_ratio", "lose_shift_ratio")
wsls_data <- ppc_summary %>%
  filter(category == "choice" & session == "session" & 
         statistic %in% wsls_stats)

if(nrow(wsls_data) > 0) {
  # Aggregate across subjects for cleaner visualization
  wsls_agg <- wsls_data %>%
    group_by(statistic) %>%
    summarize(
      obs_mean = mean(observed, na.rm = TRUE),
      obs_se = sd(observed, na.rm = TRUE)/sqrt(n()),
      pred_mean = mean(simulated_mean, na.rm = TRUE),
      pred_lower = mean(p_2.5, na.rm = TRUE),
      pred_upper = mean(p_97.5, na.rm = TRUE),
      misfit = obs_mean - pred_mean,
      misfit_standardized = misfit / (pred_upper - pred_lower) * 2,
      .groups = "drop"
    )
  
  # Plot aggregated WSLS data
  p1 = ggplot(wsls_agg, aes(x = statistic)) +
    geom_pointrange(aes(y = pred_mean, ymin = pred_lower, ymax = pred_upper), 
                   color = "blue", size = 1, position = position_dodge(width = 0.5)) +
    geom_pointrange(aes(y = obs_mean, ymin = obs_mean - obs_se, ymax = obs_mean + obs_se), 
                   color = "red", shape = 4, size = 1, position = position_dodge(width = 0.5)) +
    ylim(0, 1) +
    theme_minimal() +
    labs(title = "Win-Stay/Lose-Shift Behavior", 
         subtitle = "Red X = Observed (with SE), Blue dots = Predicted (with 95% CI)",
         x = "", y = "Ratio")
  
  # Create summary table
  kable(wsls_agg %>% select(statistic, obs_mean, pred_mean, misfit, misfit_standardized),
        caption = "Win-Stay/Lose-Shift: Observed vs. Predicted", digits = 3) %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
  
  knitr::knit_print(p1)
} else {
  cat("No Win-Stay/Lose-Shift data found in the statistics.n")
}
```

### Deck Selection Stats

```{r deck_selection_ratio, echo=FALSE, fig.width=8, fig.height=6}
# Extract deck ratio data
deck_ratio_data <- ppc_summary %>%
  filter(category == "choice" & session == "session" & 
         grepl("play_ratio_deck|good_play_ratio|bad_play_ratio", statistic))

if(nrow(deck_ratio_data) > 0) {
  # Aggregate across subjects
  ratio_agg <- deck_ratio_data %>%
    group_by(statistic) %>%
    summarize(
      obs_mean = mean(observed, na.rm = TRUE),
      obs_se = sd(observed, na.rm = TRUE)/sqrt(n()),
      pred_mean = mean(simulated_mean, na.rm = TRUE),
      pred_lower = mean(p_2.5, na.rm = TRUE),
      pred_upper = mean(p_97.5, na.rm = TRUE),
      misfit = obs_mean - pred_mean,
      misfit_standardized = misfit / (pred_upper - pred_lower) * 2,
      .groups = "drop"
    )
  
  # Plot deck selection ratios
  p1 = ggplot(ratio_agg, aes(x = statistic)) +
    geom_pointrange(aes(y = pred_mean, ymin = pred_lower, ymax = pred_upper), 
                   color = "blue", size = 1, position = position_dodge(width = 0.5)) +
    geom_pointrange(aes(y = obs_mean, ymin = obs_mean - obs_se, ymax = obs_mean + obs_se), 
                   color = "red", shape = 4, size = 1, position = position_dodge(width = 0.5)) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Deck Selection Performance", 
         subtitle = "Red X = Observed (with SE), Blue dots = Predicted (with 95% CI)",
         x = "", y = "Ratio")
  
  # Plot directionality of misfit
  p2 = ggplot(ratio_agg, aes(x = statistic, y = misfit, fill = abs(misfit_standardized) > 1)) +
    geom_col() +
    geom_hline(yintercept = 0, linetype = "dashed") +
    scale_fill_manual(values = c("TRUE" = "red", "FALSE" = "gray"), 
                     labels = c("FALSE" = "Not Significant", "TRUE" = "Significant"),
                     name = "Misfit") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Misfit Direction for Deck Selection Metrics",
         subtitle = "Positive = Model Underpredicts, Negative = Model Overpredicts",
         x = "", y = "Observed - Predicted")
  
  knitr::knit_print(p1)
  knitr::knit_print(p2)
} else {
  cat("No deck selection ratio data found in the statistics.n")
}
```

### Earnings Performance

```{r earnings_performance, echo=FALSE, fig.width=10, fig.height=6}
# Extract earnings/money data
earnings_data <- ppc_summary %>%
  filter(category == "choice" & session == "session" & 
         grepl("earnings|net_score", statistic))

if(nrow(earnings_data) > 0) {
  # Aggregate across subjects
  earnings_agg <- earnings_data %>%
    group_by(statistic) %>%
    summarize(
      obs_mean = mean(observed, na.rm = TRUE),
      obs_se = sd(observed, na.rm = TRUE)/sqrt(n()),
      pred_mean = mean(simulated_mean, na.rm = TRUE),
      pred_lower = mean(p_2.5, na.rm = TRUE),
      pred_upper = mean(p_97.5, na.rm = TRUE),
      misfit = obs_mean - pred_mean,
      misfit_pct = (obs_mean - pred_mean) / pred_mean * 100,
      .groups = "drop"
    )
  
  # Prepare data for plot with facets
  earnings_agg$y_max <- pmax(earnings_agg$obs_mean + earnings_agg$obs_se, 
                           earnings_agg$pred_upper, na.rm = TRUE)
  earnings_agg$text_y <- earnings_agg$y_max * 1.15
  
  # Plot earnings metrics
  ggplot(earnings_agg, aes(x = statistic)) +
    geom_pointrange(aes(y = pred_mean, ymin = pred_lower, ymax = pred_upper), 
                   color = "blue", size = 1) +
    geom_pointrange(aes(y = obs_mean, ymin = obs_mean - obs_se, ymax = obs_mean + obs_se), 
                   color = "red", shape = 4, size = 1) +
    geom_text(aes(y = text_y, label = sprintf("Δ: %.1f%%", misfit_pct)),
              size = 4, fontface = "bold") +
    facet_wrap(~statistic, scales = "free_y") +
    scale_x_discrete(labels = NULL) +
    theme_minimal() +
    theme(
      strip.text = element_text(size = 14, face = "bold"),
      axis.text.y = element_text(size = 10),
      axis.ticks.x = element_blank(),
      axis.text.x = element_blank(),
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      panel.grid.major.x = element_blank(),
      panel.grid.minor = element_blank()
    ) +
    labs(
      title = "Earnings Performance Metrics",
      subtitle = "Red X = Observed (with SE), Blue dots = Predicted (with 95% CI)",
      x = "", y = "Value"
    )
  
  # Create summary table
  kable(earnings_agg %>% select(statistic, obs_mean, pred_mean, misfit_pct),
        caption = "Earnings Metrics Summary", digits = 2) %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("No earnings data found in the statistics.n")
}
```

## Subject-Level Statistics

The plots below compare observed statistics (red) with model predictions (blue with 95% CI). Good model fit is indicated by observed values falling within the prediction intervals.

```{r subject_level_overall, echo=FALSE, fig.width=10, fig.height=8}
# Select a sample of subjects for visualization
subjects_to_plot <- sample(unique(ppc_summary$subject_id), 
                           min(6, length(unique(ppc_summary$subject_id))))

for (subject_id in subjects_to_plot) {
  # Generate plots for this subject
  subject_plots <- generate_subject_plots(ppc_summary, subject_id, save_plots = FALSE)
  
  # Print key plots
  if (!is.null(subject_plots$choice)) {
    if (is.list(subject_plots$choice)) {
      for (plot_name in names(subject_plots$choice)) {
        print(subject_plots$choice[[plot_name]])
      }
    } else {
      print(subject_plots$choice)
    }
  }
}
```

## Conclusion

This analysis examines how well the ev model can reproduce key behavioral patterns observed in the igt_mod task. The model's fit quality is evaluated through posterior predictive checks, comparing observed statistics to those generated from model simulations.

PPP values near 0 or 1 suggest systematic discrepancies between the model and observed data. These may indicate aspects of behavior that the model struggles to capture. Good model fit is indicated by PPP values distributed uniformly between 0 and 1, with observed statistics falling within the model's predicted range.
