---
title: "Modified Iowa Gambling Task: Cleaned Data Analysis"
date: "2025-03-08"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(viridis)
library(scales)
library(foreign)  # For reading SPSS files
library(gridExtra)
library(psych)    # For descriptive statistics
```

# Data Loading and Initial Preparation

```{r load-data}
# Define the path to the SPSS file - replace with actual path
PROJ_DIR <- here::here()
DATA_DIR <- file.path(PROJ_DIR, "Data")
SAFE_DATA_DIR <- file.path(DATA_DIR, "AHRB")
wave1.sav.file <- file.path(SAFE_DATA_DIR, "modigt_data_Wave1.sav")

# Load the data
wave1.raw <- read.spss(wave1.sav.file, to.data.frame = TRUE)

# Filter for the first 500 participants
participant_ids <- unique(wave1.raw$sid)#[1:500]
data <- wave1.raw[wave1.raw$sid %in% participant_ids, ]

# Create initial trial-level dataset
trial_data <- data %>%
  mutate(
    # Convert variables to appropriate types
    play_choice = v_response == 2,  # TRUE if played, FALSE if passed
    good_deck = v_targetdeck %in% c(3, 4),  # Decks C & D are advantageous
    rt = latency / 1000,  # Convert RT to seconds
    
    # Create deck labels
    deck_label = case_when(
      v_targetdeck == 1 ~ "A",
      v_targetdeck == 2 ~ "B",
      v_targetdeck == 3 ~ "C",
      v_targetdeck == 4 ~ "D"
    ),
    
    # Identify training block
    is_training = count_igtblocks == 1
  )

# Print basic data summary
cat("Initial data summary:\n")
cat("Total number of trials:", nrow(trial_data), "\n")
cat("Number of participants:", length(unique(trial_data$sid)), "\n")
cat("Play choices:", sum(trial_data$play_choice), "(", round(mean(trial_data$play_choice)*100, 1), "%)\n")
cat("Pass choices:", sum(!trial_data$play_choice), "(", round(mean(!trial_data$play_choice)*100, 1), "%)\n")
cat("Training trials:", sum(trial_data$is_training), "(", round(mean(trial_data$is_training)*100, 1), "%)\n")
```

# Data Cleaning

## RT-Based Trial Removal

We'll remove trials with RT < 50ms (likely anticipatory responses) and RT ≥ 4s (timeout trials).

```{r rt-cleaning}
# Identify RT thresholds
min_rt <- 0.1  # 100ms
max_rt <- 2.6   # 2.6 seconds

# Check trials outside RT bounds
low_rt_trials <- trial_data$rt < min_rt
high_rt_trials <- trial_data$rt >= max_rt

# Generate RT cleaning statistics
cat("RT-based trial removal:\n")
cat("Trials with RT <", min_rt, "seconds:", sum(low_rt_trials), 
    "(", round(mean(low_rt_trials)*100, 2), "%)\n")
cat("Trials with RT ≥", max_rt, "seconds:", sum(high_rt_trials), 
    "(", round(mean(high_rt_trials)*100, 2), "%)\n")

# Break down by play/pass
cat("\nBreakdown by response type:\n")
cat("Low RT & Play:", sum(low_rt_trials & trial_data$play_choice), "\n")
cat("Low RT & Pass:", sum(low_rt_trials & !trial_data$play_choice), "\n")
cat("High RT & Play:", sum(high_rt_trials & trial_data$play_choice), "\n")
cat("High RT & Pass:", sum(high_rt_trials & !trial_data$play_choice), "\n")

# Apply RT filtering
valid_rt_data <- trial_data %>%
  filter(rt >= min_rt, rt < max_rt)

# Calculate per-participant removal stats
participant_rt_stats <- trial_data %>%
  group_by(sid) %>%
  summarize(
    total_trials = n(),
    low_rt_trials = sum(rt < min_rt),
    high_rt_trials = sum(rt >= max_rt),
    valid_rt_trials = sum(rt >= min_rt & rt < max_rt),
    pct_removed = 100 * (1 - valid_rt_trials / total_trials),
    .groups = "drop"
  )

# Display distribution of removed trials per participant
ggplot(participant_rt_stats, aes(x = pct_removed)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(title = "Percentage of Trials Removed per Participant Due to RT Thresholds",
       x = "Percentage of Trials Removed", y = "Count")

# Summary of per-participant removal stats
rt_removal_summary <- participant_rt_stats %>%
  summarize(
    min_removed = min(pct_removed),
    q25_removed = quantile(pct_removed, 0.25),
    median_removed = median(pct_removed),
    mean_removed = mean(pct_removed),
    q75_removed = quantile(pct_removed, 0.75),
    max_removed = max(pct_removed),
    .groups = "drop"
  )

kable(rt_removal_summary, 
      caption = "Summary of Percentage of Trials Removed per Participant (RT Thresholds)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

## RT Distributions (All Data)

```{r rt-distributions_pre_clean}
# Calculate overall RT statistics
rt_stats <- trial_data %>%
  select(rt) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max) %>%
  round(3)

rt_stats = rbind(rt_stats, trial_data %>%
  filter(v_response == 2) %>%
  select(rt) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max) %>%
  round(3)
)

rt_stats = rbind(rt_stats, trial_data %>%
  filter(!v_response == 2) %>%
  select(rt) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max) %>%
  round(3)
)

rownames(rt_stats) = c("all", "play", "pass")

sid_rt_stats = trial_data %>%
  group_by(sid) %>%
  summarize(
    # RT-related metrics
    mean_rt = mean(rt, na.rm = TRUE),
    median_rt = median(rt, na.rm = TRUE),
    mean_play_rt = mean(rt[play_choice], na.rm = TRUE),
    median_play_rt = median(rt[play_choice], na.rm = TRUE),
    mean_pass_rt = mean(rt[!play_choice], na.rm = TRUE),
    median_pass_rt = median(rt[!play_choice], na.rm = TRUE),
    
    # Add RT quantiles when we have sufficient data
    # Overall RT quantiles
    rt_q10 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.1, na.rm = TRUE) else NA,
    rt_q30 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.3, na.rm = TRUE) else NA,
    rt_q50 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.5, na.rm = TRUE) else NA,
    rt_q70 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.7, na.rm = TRUE) else NA,
    rt_q90 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.9, na.rm = TRUE) else NA,
    
    # Play RT quantiles
    play_rt_q10 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.1, na.rm = TRUE) else NA,
    play_rt_q30 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.3, na.rm = TRUE) else NA,
    play_rt_q50 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.5, na.rm = TRUE) else NA,
    play_rt_q70 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.7, na.rm = TRUE) else NA,
    play_rt_q90 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.9, na.rm = TRUE) else NA,
    
    # Pass RT quantiles
    pass_rt_q10 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.1, na.rm = TRUE) else NA,
    pass_rt_q30 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.3, na.rm = TRUE) else NA,
    pass_rt_q50 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.5, na.rm = TRUE) else NA,
    pass_rt_q70 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.7, na.rm = TRUE) else NA,
    pass_rt_q90 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.9, na.rm = TRUE) else NA,
    
    .groups = "drop"
  )

# Display RT statistics table
kable(rt_stats, 
      caption = "Descriptive Statistics for Reaction Times (seconds)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Prepare data for RT density plots
rt_long <- trial_data %>%
  mutate(response_type = if_else(v_response == 2, "Play", "Pass")) %>%
  select(sid, rt, response_type)

# Create density plot for overall RTs by response type
ggplot(rt_long, aes(x = rt, fill = response_type)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("Play" = "blue", "Pass" = "red")) +
  theme_minimal() +
  xlim(0, 3.5) +  # Limit to reasonable RT range below max_rt
  labs(title = "RT Distributions by Response Type",
       x = "Reaction Time (seconds)", y = "Density",
       fill = "Response Type")

# Calculate RT quantiles statistics
rt_quantiles <- sid_rt_stats %>%
  select(contains("rt_q")) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max) %>%
  round(3)

# Display RT quantiles table
kable(rt_quantiles, 
      caption = "Descriptive Statistics for RT Quantiles (seconds)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create data frame for RT quantile plots
quantile_names <- c("10%", "30%", "50%", "70%", "90%")
quantile_values <- list(
  "Overall" = colMeans(sid_rt_stats[, c("rt_q10", "rt_q30", "rt_q50", "rt_q70", "rt_q90")], na.rm = TRUE),
  "Play" = colMeans(sid_rt_stats[, c("play_rt_q10", "play_rt_q30", "play_rt_q50", "play_rt_q70", "play_rt_q90")], na.rm = TRUE),
  "Pass" = colMeans(sid_rt_stats[, c("pass_rt_q10", "pass_rt_q30", "pass_rt_q50", "pass_rt_q70", "pass_rt_q90")], na.rm = TRUE)
)

quantile_df <- data.frame(
  Quantile = rep(quantile_names, 3),
  RT = c(unlist(quantile_values$Overall), unlist(quantile_values$Play), unlist(quantile_values$Pass)),
  Response_Type = factor(rep(c("Overall", "Play", "Pass"), each = 5), 
                         levels = c("Overall", "Play", "Pass"))
)

# Plot RT quantiles
ggplot(quantile_df, aes(x = Quantile, y = RT, group = Response_Type, color = Response_Type)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  theme_minimal() +
  scale_color_manual(values = c("Overall" = "purple", "Play" = "blue", "Pass" = "red")) +
  labs(title = "RT Quantiles by Response Type",
       x = "Quantile", y = "Reaction Time (seconds)",
       color = "Response Type")
```

### RT Distributions (Clean Data)
```{r rt-distributions_clean}
# Calculate overall RT statistics
rt_stats <- valid_rt_data %>%
  select(rt) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max) %>%
  round(3)

rt_stats = rbind(rt_stats, valid_rt_data %>%
  filter(v_response == 2) %>%
  select(rt) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max) %>%
  round(3)
)

rt_stats = rbind(rt_stats, valid_rt_data %>%
  filter(!v_response == 2) %>%
  select(rt) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max) %>%
  round(3)
)

rownames(rt_stats) = c("all", "play", "pass")

sid_rt_stats = valid_rt_data %>%
  group_by(sid) %>%
  summarize(
    # RT-related metrics
    mean_rt = mean(rt, na.rm = TRUE),
    median_rt = median(rt, na.rm = TRUE),
    mean_play_rt = mean(rt[play_choice], na.rm = TRUE),
    median_play_rt = median(rt[play_choice], na.rm = TRUE),
    mean_pass_rt = mean(rt[!play_choice], na.rm = TRUE),
    median_pass_rt = median(rt[!play_choice], na.rm = TRUE),
    
    # Add RT quantiles when we have sufficient data
    # Overall RT quantiles
    rt_q10 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.1, na.rm = TRUE) else NA,
    rt_q30 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.3, na.rm = TRUE) else NA,
    rt_q50 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.5, na.rm = TRUE) else NA,
    rt_q70 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.7, na.rm = TRUE) else NA,
    rt_q90 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.9, na.rm = TRUE) else NA,
    
    # Play RT quantiles
    play_rt_q10 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.1, na.rm = TRUE) else NA,
    play_rt_q30 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.3, na.rm = TRUE) else NA,
    play_rt_q50 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.5, na.rm = TRUE) else NA,
    play_rt_q70 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.7, na.rm = TRUE) else NA,
    play_rt_q90 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.9, na.rm = TRUE) else NA,
    
    # Pass RT quantiles
    pass_rt_q10 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.1, na.rm = TRUE) else NA,
    pass_rt_q30 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.3, na.rm = TRUE) else NA,
    pass_rt_q50 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.5, na.rm = TRUE) else NA,
    pass_rt_q70 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.7, na.rm = TRUE) else NA,
    pass_rt_q90 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.9, na.rm = TRUE) else NA,
    
    .groups = "drop"
  )

# Display RT statistics table
kable(rt_stats, 
      caption = "Descriptive Statistics for Reaction Times (seconds)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Prepare data for RT density plots
rt_long <- valid_rt_data %>%
  mutate(response_type = if_else(v_response == 2, "Play", "Pass")) %>%
  select(sid, rt, response_type)

# Create density plot for overall RTs by response type
ggplot(rt_long, aes(x = rt, fill = response_type)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("Play" = "blue", "Pass" = "red")) +
  theme_minimal() +
  xlim(0, 3.5) +  # Limit to reasonable RT range below max_rt
  labs(title = "RT Distributions by Response Type",
       x = "Reaction Time (seconds)", y = "Density",
       fill = "Response Type")

# Calculate RT quantiles statistics
rt_quantiles <- sid_rt_stats %>%
  select(contains("rt_q")) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max) %>%
  round(3)

# Display RT quantiles table
kable(rt_quantiles, 
      caption = "Descriptive Statistics for RT Quantiles (seconds)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create data frame for RT quantile plots
quantile_names <- c("10%", "30%", "50%", "70%", "90%")
quantile_values <- list(
  "Overall" = colMeans(sid_rt_stats[, c("rt_q10", "rt_q30", "rt_q50", "rt_q70", "rt_q90")], na.rm = TRUE),
  "Play" = colMeans(sid_rt_stats[, c("play_rt_q10", "play_rt_q30", "play_rt_q50", "play_rt_q70", "play_rt_q90")], na.rm = TRUE),
  "Pass" = colMeans(sid_rt_stats[, c("pass_rt_q10", "pass_rt_q30", "pass_rt_q50", "pass_rt_q70", "pass_rt_q90")], na.rm = TRUE)
)

quantile_df <- data.frame(
  Quantile = rep(quantile_names, 3),
  RT = c(unlist(quantile_values$Overall), unlist(quantile_values$Play), unlist(quantile_values$Pass)),
  Response_Type = factor(rep(c("Overall", "Play", "Pass"), each = 5), 
                         levels = c("Overall", "Play", "Pass"))
)

# Plot RT quantiles
ggplot(quantile_df, aes(x = Quantile, y = RT, group = Response_Type, color = Response_Type)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  theme_minimal() +
  scale_color_manual(values = c("Overall" = "purple", "Play" = "blue", "Pass" = "red")) +
  labs(title = "RT Quantiles by Response Type",
       x = "Quantile", y = "Reaction Time (seconds)",
       color = "Response Type")
```

## Play/Pass Ratio Analysis

We'll identify participants with extreme play/pass ratios.

```{r play-pass-ratio}
# Calculate play ratio per participant
participant_play_ratio <- valid_rt_data %>%
  group_by(sid) %>%
  summarize(
    total_trials = n(),
    play_trials = sum(play_choice),
    pass_trials = sum(!play_choice),
    play_ratio = play_trials / total_trials,
    pass_ratio = pass_trials / total_trials,
    .groups = "drop"
  )

# Display distribution of play ratios
ggplot(participant_play_ratio, aes(x = play_ratio)) +
  geom_histogram(binwidth = 0.05, fill = "salmon", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(title = "Distribution of Play Ratios Across Participants",
       x = "Play Ratio", y = "Count")

# Identify extreme play/pass ratio participants
min_play_ratio <- quantile(participant_play_ratio$play_ratio, 0.025)  # Exclude if less than 20% play choices
max_play_ratio <- quantile(participant_play_ratio$play_ratio, 0.975)  # Exclude if more than 95% play choices

extreme_ratio_participants <- participant_play_ratio %>%
  filter(play_ratio < min_play_ratio | play_ratio > max_play_ratio) %>%
  mutate(
    exclusion_reason = case_when(
      play_ratio < min_play_ratio ~ "Too few play choices",
      play_ratio > max_play_ratio ~ "Too few pass choices"
    )
  )

# Display extreme ratio participants
cat("Participants with extreme play/pass ratios:\n")
cat("Too few play choices (<", min_play_ratio, "):", 
    sum(participant_play_ratio$play_ratio < min_play_ratio), "\n")
cat("Too few pass choices (>", max_play_ratio, "):", 
    sum(participant_play_ratio$play_ratio > max_play_ratio), "\n")
cat("Total extreme ratio participants:", nrow(extreme_ratio_participants), 
    "(", round(nrow(extreme_ratio_participants)/nrow(participant_play_ratio)*100, 1), "%)\n")

# Display table of extreme ratio participants
if(nrow(extreme_ratio_participants) > 0) {
  kable(extreme_ratio_participants, 
        caption = "Participants with Extreme Play/Pass Ratios") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
}
```

## Trial Count Analysis

We'll identify participants with insufficient valid trials after RT cleaning.

```{r trial-count}
# Define minimum required trials
min_trials <- 110

# Identify participants with insufficient trials
insufficient_trial_participants <- participant_play_ratio %>%
  filter(total_trials < min_trials) %>%
  mutate(exclusion_reason = "Insufficient valid trials")

# Display insufficient trial participants
cat("Participants with insufficient valid trials:\n")
cat("Less than", min_trials, "valid trials:", nrow(insufficient_trial_participants),
    "(", round(nrow(insufficient_trial_participants)/nrow(participant_play_ratio)*100, 1), "%)\n")

# Display table of insufficient trial participants
if(nrow(insufficient_trial_participants) > 0) {
  kable(insufficient_trial_participants, 
        caption = "Participants with Insufficient Valid Trials") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
}

# Distribution of valid trials per participant
ggplot(participant_play_ratio, aes(x = total_trials)) +
  geom_histogram(binwidth = 5, fill = "lightgreen", color = "black", alpha = 0.7) +
  geom_vline(xintercept = min_trials, color = "red", linetype = "dashed") +
  theme_minimal() +
  labs(title = "Distribution of Valid Trials per Participant",
       subtitle = paste("Red line indicates minimum requirement of", min_trials, "trials"),
       x = "Number of Valid Trials", y = "Count")
```

## Combined Exclusion Criteria

We'll now combine all exclusion criteria to identify participants to remove.

```{r combined-exclusions}
rt_excludes = participant_rt_stats$sid[participant_rt_stats$valid_rt_trials < min_trials]
# Combine exclusion lists
exclude_sids <- unique(c(
  extreme_ratio_participants$sid,
  insufficient_trial_participants$sid,
  rt_excludes
))

# Create comprehensive exclusion summary
all_participant_stats <- participant_play_ratio %>%
  left_join(participant_rt_stats %>% select(sid, low_rt_trials, high_rt_trials, pct_removed), by = "sid") %>%
  mutate(
    exclude = sid %in% exclude_sids,
    exclusion_reason = case_when(
      sid %in% extreme_ratio_participants$sid & play_ratio < min_play_ratio ~ "Too few play choices",
      sid %in% extreme_ratio_participants$sid & play_ratio > max_play_ratio ~ "Too few pass choices",
      sid %in% insufficient_trial_participants$sid ~ "Insufficient valid trials",
      sid %in% rt_excludes ~ "Too few trials after RT bournds",
      TRUE ~ "Included"
    )
  )

# Display summary of exclusions
excluded_summary <- all_participant_stats %>%
  group_by(exclusion_reason) %>%
  summarize(
    count = n(),
    percentage = 100 * n() / nrow(all_participant_stats),
    .groups = "drop"
  )

kable(excluded_summary, 
      caption = "Summary of Participant Exclusions") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create clean dataset with excluded participants removed
clean_trial_data <- valid_rt_data %>%
  filter(!sid %in% exclude_sids)

# Summarize final clean dataset
cat("Clean dataset summary:\n")
cat("Original participants:", length(unique(trial_data$sid)), "\n")
cat("Excluded participants:", length(exclude_sids), 
    "(", round(length(exclude_sids)/length(unique(trial_data$sid))*100, 1), "%)\n")
cat("Remaining participants:", length(unique(clean_trial_data$sid)), "\n")
cat("Original trials:", nrow(trial_data), "\n")
cat("Clean trials:", nrow(clean_trial_data), 
    "(", round(nrow(clean_trial_data)/nrow(trial_data)*100, 1), "%)\n")
```

# Clean Data Analysis

## Participant-Level Summary Dataset

```{r participant-summary}
# Create participant-level summary with clean data
participant_summary <- clean_trial_data %>%
  group_by(sid) %>%
  summarize(
    # RL-related metrics
    total_money = sum(v_netchange, na.rm = TRUE),
    good_deck_ratio = sum(good_deck & play_choice, na.rm = TRUE) / sum(play_choice, na.rm = TRUE),
    skip_ratio = mean(!play_choice, na.rm = TRUE),
    total_plays = sum(play_choice, na.rm = TRUE),
    total_trials = n(),
    
    # RT-related metrics
    mean_rt = mean(rt, na.rm = TRUE),
    median_rt = median(rt, na.rm = TRUE),
    mean_play_rt = mean(rt[play_choice], na.rm = TRUE),
    median_play_rt = median(rt[play_choice], na.rm = TRUE),
    mean_pass_rt = mean(rt[!play_choice], na.rm = TRUE),
    median_pass_rt = median(rt[!play_choice], na.rm = TRUE),
    
    # Add RT quantiles when we have sufficient data
    # Overall RT quantiles
    rt_q10 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.1, na.rm = TRUE) else NA,
    rt_q30 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.3, na.rm = TRUE) else NA,
    rt_q50 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.5, na.rm = TRUE) else NA,
    rt_q70 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.7, na.rm = TRUE) else NA,
    rt_q90 = if(sum(!is.na(rt)) >= 10) quantile(rt, 0.9, na.rm = TRUE) else NA,
    
    # Play RT quantiles
    play_rt_q10 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.1, na.rm = TRUE) else NA,
    play_rt_q30 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.3, na.rm = TRUE) else NA,
    play_rt_q50 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.5, na.rm = TRUE) else NA,
    play_rt_q70 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.7, na.rm = TRUE) else NA,
    play_rt_q90 = if(sum(play_choice) >= 10) quantile(rt[play_choice], 0.9, na.rm = TRUE) else NA,
    
    # Pass RT quantiles
    pass_rt_q10 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.1, na.rm = TRUE) else NA,
    pass_rt_q30 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.3, na.rm = TRUE) else NA,
    pass_rt_q50 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.5, na.rm = TRUE) else NA,
    pass_rt_q70 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.7, na.rm = TRUE) else NA,
    pass_rt_q90 = if(sum(!play_choice) >= 10) quantile(rt[!play_choice], 0.9, na.rm = TRUE) else NA,
    
    .groups = "drop"
  )
```

## Block-Level and Deck-Specific Datasets

```{r specialized-datasets}
# Create block-level dataset
block_data <- clean_trial_data %>%
  group_by(sid, count_igtblocks) %>%
  summarize(
    block_money = sum(v_netchange, na.rm = TRUE),
    block_good_deck_ratio = sum(good_deck & play_choice, na.rm = TRUE) / sum(play_choice, na.rm = TRUE),
    block_skip_ratio = mean(!play_choice, na.rm = TRUE),
    block_mean_rt = mean(rt, na.rm = TRUE),
    block_mean_play_rt = mean(rt[play_choice], na.rm = TRUE),
    block_mean_pass_rt = mean(rt[!play_choice], na.rm = TRUE),
    total_trials = n(),
    is_training = all(is_training),
    .groups = "drop"
  )

# Create deck-specific dataset
deck_data <- clean_trial_data %>%
  group_by(sid, deck_label) %>%
  summarize(
    total_shown = n(),
    total_selected = sum(play_choice),
    selection_ratio = total_selected / total_shown,
    avg_gain = mean(v_gain[play_choice], na.rm = TRUE),
    avg_loss = mean(v_loss[play_choice], na.rm = TRUE),
    avg_net = mean(v_netchange[play_choice], na.rm = TRUE),
    mean_rt_when_shown = mean(rt, na.rm = TRUE),
    mean_rt_when_selected = mean(rt[play_choice], na.rm = TRUE),
    mean_rt_when_skipped = mean(rt[!play_choice], na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    is_good_deck = deck_label %in% c("C", "D")
  )

# Create a deck-by-block dataset
deck_block_data <- clean_trial_data %>%
  group_by(sid, count_igtblocks, deck_label) %>%
  summarize(
    times_shown = n(),
    times_selected = sum(play_choice),
    selection_ratio = if(times_shown > 0) times_selected / times_shown else NA,
    avg_gain = mean(v_gain[play_choice], na.rm = TRUE),
    avg_loss = mean(v_loss[play_choice], na.rm = TRUE),
    avg_net = mean(v_netchange[play_choice], na.rm = TRUE),
    is_training = all(is_training),
    .groups = "drop"
  ) %>%
  mutate(
    is_good_deck = deck_label %in% c("C", "D")
  )
```

# Task Performance Analysis

## Overall Performance Metrics

```{r overall-performance}
# Calculate descriptive statistics for key metrics
performance_stats <- participant_summary %>%
  select(total_money, good_deck_ratio, skip_ratio) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max, skew, kurtosis) %>%
  round(2)

# Display the statistics table
kable(performance_stats, 
      caption = "Descriptive Statistics for Key Performance Metrics (Clean Data)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Histogram of total money
p1 <- ggplot(participant_summary, aes(x = total_money)) +
  geom_histogram(binwidth = 100, fill = "skyblue", color = "black", alpha = 0.7) +
  geom_vline(aes(xintercept = mean(total_money)), color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  labs(title = "Distribution of Total Money Won",
       x = "Total Money", y = "Count")

# Histogram of good deck ratio
p2 <- ggplot(participant_summary, aes(x = good_deck_ratio)) +
  geom_histogram(binwidth = 0.05, fill = "lightgreen", color = "black", alpha = 0.7) +
  geom_vline(aes(xintercept = mean(good_deck_ratio, na.rm = TRUE)), 
             color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  labs(title = "Distribution of Good Deck Selection Ratio",
       x = "Good Deck Selection Ratio", y = "Count")

# Histogram of skip ratio
p3 <- ggplot(participant_summary, aes(x = skip_ratio)) +
  geom_histogram(binwidth = 0.05, fill = "salmon", color = "black", alpha = 0.7) +
  geom_vline(aes(xintercept = mean(skip_ratio)), color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  labs(title = "Distribution of Skip Ratio",
       x = "Skip Ratio", y = "Count")

# Combine plots
p1 / p2 / p3
```

## Training vs. Test Block Performance

```{r training-test-comparison}
# Calculate mean values per block type across participants
block_type_summary <- block_data %>%
  group_by(is_training) %>%
  summarize(
    mean_money = mean(block_money, na.rm = TRUE),
    sd_money = sd(block_money, na.rm = TRUE),
    mean_good_deck = mean(block_good_deck_ratio, na.rm = TRUE),
    sd_good_deck = sd(block_good_deck_ratio, na.rm = TRUE),
    mean_skip = mean(block_skip_ratio, na.rm = TRUE),
    sd_skip = sd(block_skip_ratio, na.rm = TRUE),
    mean_rt = mean(block_mean_rt, na.rm = TRUE),
    sd_rt = sd(block_mean_rt, na.rm = TRUE),
    .groups = "drop"
  )

# Display training vs. test comparison
kable(block_type_summary, 
      caption = "Training vs. Test Block Performance") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create a training vs. test plot for key metrics
block_type_long <- block_type_summary %>%
  pivot_longer(
    cols = starts_with("mean_"),
    names_to = "metric",
    values_to = "value"
  ) %>%
  mutate(
    metric = case_when(
      metric == "mean_money" ~ "Money Won",
      metric == "mean_good_deck" ~ "Good Deck Ratio",
      metric == "mean_skip" ~ "Skip Ratio",
      metric == "mean_rt" ~ "Mean RT (s)"
    ),
    block_type = if_else(is_training, "Training", "Test")
  )

ggplot(block_type_long, aes(x = block_type, y = value, fill = block_type)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ metric, scales = "free_y") +
  theme_minimal() +
  scale_fill_manual(values = c("Training" = "orange", "Test" = "skyblue")) +
  labs(title = "Comparison of Training vs. Test Blocks",
       x = "", y = "Value",
       fill = "Block Type")
```

## Learning Across Test Blocks

```{r block-learning}
# Filter for test blocks only
test_block_data <- block_data %>%
  filter(!is_training)

# Calculate mean values per block across participants
block_summary <- test_block_data %>%
  group_by(count_igtblocks) %>%
  summarize(
    mean_money = mean(block_money, na.rm = TRUE),
    lower_money = mean_money - 1.96 * sd(block_money, na.rm = TRUE) / sqrt(n()),
    upper_money = mean_money + 1.96 * sd(block_money, na.rm = TRUE) / sqrt(n()),
    
    mean_good_deck = mean(block_good_deck_ratio, na.rm = TRUE),
    lower_good_deck = mean_good_deck - 1.96 * sd(block_good_deck_ratio, na.rm = TRUE) / sqrt(n()),
    upper_good_deck = mean_good_deck + 1.96 * sd(block_good_deck_ratio, na.rm = TRUE) / sqrt(n()),
    
    mean_skip = mean(block_skip_ratio, na.rm = TRUE),
    lower_skip = mean_skip - 1.96 * sd(block_skip_ratio, na.rm = TRUE) / sqrt(n()),
    upper_skip = mean_skip + 1.96 * sd(block_skip_ratio, na.rm = TRUE) / sqrt(n()),
    
    .groups = "drop"
  )

# Display the block summary table
kable(block_summary, 
      caption = "Test Block Performance (with 95% CIs)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Plot learning curves for good deck selection
p1 <- ggplot(block_summary, aes(x = count_igtblocks, y = mean_good_deck)) +
  geom_line(size = 1, color = "darkgreen") +
  geom_point(size = 3, color = "darkgreen") +
  geom_ribbon(aes(ymin = lower_good_deck, ymax = upper_good_deck), alpha = 0.2, fill = "green") +
  theme_minimal() +
  scale_x_continuous(breaks = 2:6) +
  ylim(0, 1) +
  labs(title = "Learning Curve: Good Deck Selection (Test Blocks Only)",
       subtitle = "Mean with 95% confidence interval",
       x = "Block", y = "Good Deck Selection Ratio")

# Plot learning curves for money earned
p2 <- ggplot(block_summary, aes(x = count_igtblocks, y = mean_money)) +
  geom_line(size = 1, color = "blue") +
  geom_point(size = 3, color = "blue") +
  geom_ribbon(aes(ymin = lower_money, ymax = upper_money), alpha = 0.2, fill = "skyblue") +
  theme_minimal() +
  scale_x_continuous(breaks = 2:6) +
  labs(title = "Money Earned per Test Block",
       subtitle = "Mean with 95% confidence interval",
       x = "Block", y = "Money Earned")

# Plot learning curves for skip ratio
p3 <- ggplot(block_summary, aes(x = count_igtblocks, y = mean_skip)) +
  geom_line(size = 1, color = "darkred") +
  geom_point(size = 3, color = "darkred") +
  geom_ribbon(aes(ymin = lower_skip, ymax = upper_skip), alpha = 0.2, fill = "salmon") +
  theme_minimal() +
  scale_x_continuous(breaks = 2:6) +
  ylim(0, 1) +
  labs(title = "Skip Ratio by Test Block",
       subtitle = "Mean with 95% confidence interval",
       x = "Block", y = "Skip Ratio")

# Display plots
p1 / p2 / p3

# Calculate cumulative money earned (test blocks only)
cumulative_money <- test_block_data %>%
  arrange(sid, count_igtblocks) %>%
  group_by(sid) %>%
  mutate(cumulative_money = cumsum(block_money)) %>%
  ungroup()

# Calculate mean cumulative money by block
cum_money_summary <- cumulative_money %>%
  group_by(count_igtblocks) %>%
  summarize(
    mean_cum_money = mean(cumulative_money, na.rm = TRUE),
    lower_cum_money = mean_cum_money - 1.96 * sd(cumulative_money, na.rm = TRUE) / sqrt(n()),
    upper_cum_money = mean_cum_money + 1.96 * sd(cumulative_money, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

# Plot cumulative money earned
ggplot(cum_money_summary, aes(x = count_igtblocks, y = mean_cum_money)) +
  geom_line(size = 1, color = "purple") +
  geom_point(size = 3, color = "purple") +
  geom_ribbon(aes(ymin = lower_cum_money, ymax = upper_cum_money), alpha = 0.2, fill = "plum") +
  theme_minimal() +
  scale_x_continuous(breaks = 2:6) +
  labs(title = "Cumulative Money Earned (Test Blocks Only)",
       subtitle = "Mean with 95% confidence interval",
       x = "Block", y = "Cumulative Money")
```

## Deck-Specific Analysis

```{r deck-analysis}
# Calculate average statistics by deck across participants
deck_summary <- deck_data %>%
  group_by(deck_label, is_good_deck) %>%
  summarize(
    mean_selection_ratio = mean(selection_ratio, na.rm = TRUE),
    sd_selection_ratio = sd(selection_ratio, na.rm = TRUE),
    mean_avg_gain = mean(avg_gain, na.rm = TRUE),
    mean_avg_loss = mean(avg_loss, na.rm = TRUE),
    mean_avg_net = mean(avg_net, na.rm = TRUE),
    mean_rt_selected = mean(mean_rt_when_selected, na.rm = TRUE),
    mean_rt_skipped = mean(mean_rt_when_skipped, na.rm = TRUE),
    .groups = "drop"
  )

# Display deck summary table
kable(deck_summary, 
      caption = "Average Performance by Deck") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Plot selection ratio by deck
ggplot(deck_summary, aes(x = deck_label, y = mean_selection_ratio, fill = is_good_deck)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = mean_selection_ratio - sd_selection_ratio,
                   ymax = mean_selection_ratio + sd_selection_ratio),
               width = 0.2) +
  scale_fill_manual(values = c("FALSE" = "tomato", "TRUE" = "lightgreen"),
                    labels = c("Bad Deck", "Good Deck")) +
  theme_minimal() +
  ylim(0, 1) +
  labs(title = "Selection Ratio by Deck",
       subtitle = "Error bars show ±1 SD",
       x = "Deck", y = "Selection Ratio",
       fill = "Deck Type")

# Plot average net outcome by deck
ggplot(deck_summary, aes(x = deck_label, y = mean_avg_net, fill = is_good_deck)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("FALSE" = "tomato", "TRUE" = "lightgreen"),
                   labels = c("Bad Deck", "Good Deck")) +
  theme_minimal() +
  labs(title = "Average Net Outcome by Deck",
       x = "Deck", y = "Average Net Outcome",
       fill = "Deck Type")

# Plot mean RT by deck and response type
deck_rt_long <- deck_summary %>%
  select(deck_label, is_good_deck, mean_rt_selected, mean_rt_skipped) %>%
  pivot_longer(
    cols = c(mean_rt_selected, mean_rt_skipped),
    names_to = "response_type",
    values_to = "mean_rt"
  ) %>%
  mutate(
    response_type = if_else(response_type == "mean_rt_selected", "Play", "Pass")
  )

ggplot(deck_rt_long, aes(x = deck_label, y = mean_rt, fill = response_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("Play" = "blue", "Pass" = "red")) +
  theme_minimal() +
  labs(title = "Mean RT by Deck and Response Type",
       x = "Deck", y = "Mean RT (seconds)",
       fill = "Response Type")

# Plot deck selection over blocks
deck_block_summary <- deck_block_data %>%
  filter(!is_training) %>%  # Exclude training block
  group_by(count_igtblocks, deck_label, is_good_deck) %>%
  summarize(
    mean_selection_ratio = mean(selection_ratio, na.rm = TRUE),
    .groups = "drop"
  )

ggplot(deck_block_summary, aes(x = count_igtblocks, y = mean_selection_ratio, 
                               color = deck_label, linetype = is_good_deck)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_color_brewer(palette = "Set1") +
  scale_linetype_manual(values = c("FALSE" = "dashed", "TRUE" = "solid"),
                        labels = c("Bad Deck", "Good Deck")) +
  theme_minimal() +
  scale_x_continuous(breaks = 2:6) +
  labs(title = "Deck Selection Ratio Across Test Blocks",
       x = "Block", y = "Mean Selection Ratio",
       color = "Deck", linetype = "Deck Type")
```

# Reaction Time Analysis

## RT Distributions

```{r rt-distributions}
# Calculate overall RT statistics
rt_stats <- participant_summary %>%
  select(mean_rt, median_rt, mean_play_rt, median_play_rt, mean_pass_rt, median_pass_rt) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max) %>%
  round(3)

# Display RT statistics table
kable(rt_stats, 
      caption = "Descriptive Statistics for Reaction Times (seconds)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Prepare data for RT density plots
rt_long <- clean_trial_data %>%
  mutate(response_type = if_else(play_choice, "Play", "Pass")) %>%
  select(sid, rt, response_type)

# Create density plot for overall RTs by response type
ggplot(rt_long, aes(x = rt, fill = response_type)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("Play" = "blue", "Pass" = "red")) +
  theme_minimal() +
  xlim(0, 3.5) +  # Limit to reasonable RT range below max_rt
  labs(title = "RT Distributions by Response Type",
       x = "Reaction Time (seconds)", y = "Density",
       fill = "Response Type")

# Calculate RT quantiles statistics
rt_quantiles <- participant_summary %>%
  select(contains("rt_q")) %>%
  psych::describe() %>%
  as.data.frame() %>%
  select(mean, sd, median, min, max) %>%
  round(3)

# Display RT quantiles table
kable(rt_quantiles, 
      caption = "Descriptive Statistics for RT Quantiles (seconds)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create data frame for RT quantile plots
quantile_names <- c("10%", "30%", "50%", "70%", "90%")
quantile_values <- list(
  "Overall" = colMeans(participant_summary[, c("rt_q10", "rt_q30", "rt_q50", "rt_q70", "rt_q90")], na.rm = TRUE),
  "Play" = colMeans(participant_summary[, c("play_rt_q10", "play_rt_q30", "play_rt_q50", "play_rt_q70", "play_rt_q90")], na.rm = TRUE),
  "Pass" = colMeans(participant_summary[, c("pass_rt_q10", "pass_rt_q30", "pass_rt_q50", "pass_rt_q70", "pass_rt_q90")], na.rm = TRUE)
)

quantile_df <- data.frame(
  Quantile = rep(quantile_names, 3),
  RT = c(unlist(quantile_values$Overall), unlist(quantile_values$Play), unlist(quantile_values$Pass)),
  Response_Type = factor(rep(c("Overall", "Play", "Pass"), each = 5), 
                         levels = c("Overall", "Play", "Pass"))
)

# Plot RT quantiles
ggplot(quantile_df, aes(x = Quantile, y = RT, group = Response_Type, color = Response_Type)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  theme_minimal() +
  scale_color_manual(values = c("Overall" = "purple", "Play" = "blue", "Pass" = "red")) +
  labs(title = "RT Quantiles by Response Type",
       x = "Quantile", y = "Reaction Time (seconds)",
       color = "Response Type")
```

## RT Changes Across Blocks

```{r rt-block-changes}
# Calculate mean RT values per block across participants
rt_block_summary <- test_block_data %>%  # Using only test blocks
  group_by(count_igtblocks) %>%
  summarize(
    mean_rt = mean(block_mean_rt, na.rm = TRUE),
    lower_rt = mean_rt - 1.96 * sd(block_mean_rt, na.rm = TRUE) / sqrt(n()),
    upper_rt = mean_rt + 1.96 * sd(block_mean_rt, na.rm = TRUE) / sqrt(n()),
    
    mean_play_rt = mean(block_mean_play_rt, na.rm = TRUE),
    lower_play_rt = mean_play_rt - 1.96 * sd(block_mean_play_rt, na.rm = TRUE) / sqrt(n()),
    upper_play_rt = mean_play_rt + 1.96 * sd(block_mean_play_rt, na.rm = TRUE) / sqrt(n()),
    
    mean_pass_rt = mean(block_mean_pass_rt, na.rm = TRUE),
    lower_pass_rt = mean_pass_rt - 1.96 * sd(block_mean_pass_rt, na.rm = TRUE) / sqrt(n()),
    upper_pass_rt = mean_pass_rt + 1.96 * sd(block_mean_pass_rt, na.rm = TRUE) / sqrt(n()),
    
    .groups = "drop"
  )

# Display the RT block summary table
kable(rt_block_summary %>% select(count_igtblocks, mean_rt, mean_play_rt, mean_pass_rt), 
      caption = "Mean RTs by Test Block (seconds)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Prepare data for RT by block plot
rt_block_long <- rt_block_summary %>%
  pivot_longer(
    cols = c(mean_rt, mean_play_rt, mean_pass_rt),
    names_to = "response_type",
    values_to = "rt"
  ) %>%
  pivot_longer(
    cols = c(lower_rt, lower_play_rt, lower_pass_rt),
    names_to = "lower_type",
    values_to = "lower"
  ) %>%
  pivot_longer(
    cols = c(upper_rt, upper_play_rt, upper_pass_rt),
    names_to = "upper_type",
    values_to = "upper"
  ) %>%
  filter(
    (response_type == "mean_rt" & lower_type == "lower_rt" & upper_type == "upper_rt") |
    (response_type == "mean_play_rt" & lower_type == "lower_play_rt" & upper_type == "upper_play_rt") |
    (response_type == "mean_pass_rt" & lower_type == "lower_pass_rt" & upper_type == "upper_pass_rt")
  ) %>%
  mutate(response_type = case_when(
    response_type == "mean_rt" ~ "Overall",
    response_type == "mean_play_rt" ~ "Play",
    response_type == "mean_pass_rt" ~ "Pass"
  ))

# Plot RT changes by block
ggplot(rt_block_long, aes(x = count_igtblocks, y = rt, color = response_type, fill = response_type)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, color = NA) +
  theme_minimal() +
  scale_x_continuous(breaks = 2:6) +
  scale_color_manual(values = c("Overall" = "purple", "Play" = "blue", "Pass" = "red")) +
  scale_fill_manual(values = c("Overall" = "purple", "Play" = "blue", "Pass" = "red")) +
  labs(title = "RT Changes Across Test Blocks",
       subtitle = "Mean with 95% confidence interval",
       x = "Block", y = "Reaction Time (seconds)",
       color = "Response Type", fill = "Response Type")
```

# Individual Differences

## Distribution of Key Metrics

```{r metric-distributions}
# Calculate correlations between key measures
# First check which variables exist and have non-NA values
valid_vars <- sapply(participant_summary, function(x) sum(!is.na(x)) > 0)
potential_corr_vars <- c("total_money", "good_deck_ratio", "skip_ratio", "mean_rt", "mean_play_rt", "mean_pass_rt")
corr_vars <- intersect(potential_corr_vars, names(participant_summary)[valid_vars])

# Check if we have at least 2 variables for correlation
if(length(corr_vars) >= 2) {
  # Compute correlation matrix
  corr_matrix <- cor(participant_summary[, corr_vars], use = "pairwise.complete.obs")
  
  # Display correlation matrix
  kable(round(corr_matrix, 2), 
        caption = "Correlations Between Key Behavioral Measures") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
  
  # Create correlation plot if package available
  if(requireNamespace("corrplot", quietly = TRUE)) {
    corrplot::corrplot(corr_matrix, method = "circle", type = "upper", tl.col = "black",
           addCoef.col = "black", number.cex = 0.7,
           title = "Correlation Matrix of Key Behavioral Measures")
  }
}

# Create boxplots for key metrics to examine individual differences
metrics_long <- participant_summary %>%
  select(good_deck_ratio, skip_ratio, mean_play_rt, mean_pass_rt) %>%
  pivot_longer(cols = everything(), 
               names_to = "metric", 
               values_to = "value")

# Create faceted boxplot
ggplot(metrics_long, aes(x = metric, y = value)) +
  geom_boxplot(fill = "lightblue", color = "blue") +
  geom_jitter(width = 0.2, alpha = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Distribution of Key Behavioral Metrics Across Participants",
       x = "", y = "Value")
```

## Strategy Classification

```{r strategy-classification}
# Create a scatter plot of good deck ratio vs. skip ratio to visualize potential strategies
# Remove NAs from plotting data
plot_data <- participant_summary %>%
  filter(!is.na(good_deck_ratio), !is.na(skip_ratio))

if(nrow(plot_data) > 0) {
  # Create scatter plot
  ggplot(plot_data, aes(x = good_deck_ratio, y = skip_ratio, color = total_money)) +
    geom_point(alpha = 0.7) +
    scale_color_viridis_c() +
    theme_minimal() +
    labs(title = "Relationship Between Good Deck Selection and Skip Ratio",
         subtitle = "Color indicates total money won",
         x = "Good Deck Ratio", y = "Skip Ratio",
         color = "Total Money")
  
  # Define strategy groups
  strategies <- participant_summary %>%
    filter(!is.na(good_deck_ratio), !is.na(skip_ratio)) %>%
    mutate(
      strategy_group = case_when(
        good_deck_ratio > 0.7 & skip_ratio < 0.3 ~ "Good deck preferrers",
        good_deck_ratio < 0.3 & skip_ratio < 0.3 ~ "Bad deck preferrers",
        skip_ratio > 0.7 ~ "Frequent skippers",
        TRUE ~ "Mixed strategy"
      )
    )
  
  # Calculate the proportion of each strategy
  strategy_counts <- strategies %>%
    group_by(strategy_group) %>%
    summarize(
      count = n(),
      proportion = n() / nrow(strategies),
      mean_money = mean(total_money, na.rm = TRUE),
      .groups = "drop"
    )
  
  # Display strategy statistics
  kable(strategy_counts, 
        caption = "Distribution of Strategy Groups") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
  
  # Create a bar plot of strategy distribution
  ggplot(strategy_counts, aes(x = strategy_group, y = proportion, fill = mean_money)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = sprintf("%.1f%%", proportion * 100)), vjust = -0.5) +
    scale_fill_viridis_c() +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Distribution of Strategy Groups",
         subtitle = "Color indicates mean money won",
         x = "", y = "Proportion",
         fill = "Mean Money")
}
```

# Individual Learning Rates

```{r learning-rates}
# Calculate individual learning rates for good deck selection
learning_rates <- block_data %>%
  filter(!is_training) %>%  # Exclude training block
  group_by(sid) %>%
  do({
    model <- lm(block_good_deck_ratio ~ count_igtblocks, data = .)
    data.frame(
      learning_slope = coef(model)[2],
      learning_intercept = coef(model)[1],
      r_squared = summary(model)$r.squared
    )
  }) %>%
  ungroup()

# Display learning rate statistics
learning_rate_stats <- learning_rates %>%
  summarize(
    mean_slope = mean(learning_slope, na.rm = TRUE),
    sd_slope = sd(learning_slope, na.rm = TRUE),
    median_slope = median(learning_slope, na.rm = TRUE),
    min_slope = min(learning_slope, na.rm = TRUE),
    max_slope = max(learning_slope, na.rm = TRUE),
    pct_positive = mean(learning_slope > 0, na.rm = TRUE) * 100,
    mean_r_squared = mean(r_squared, na.rm = TRUE)
  )

kable(learning_rate_stats, 
      caption = "Individual Learning Rate Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Distribution of learning slopes
ggplot(learning_rates, aes(x = learning_slope)) +
  geom_histogram(binwidth = 0.01, fill = "lightblue", color = "black", alpha = 0.7) +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed") +
  theme_minimal() +
  labs(title = "Distribution of Individual Learning Slopes",
       subtitle = "Positive values indicate improvement in good deck selection over blocks",
       x = "Learning Slope", y = "Count")

# Relationship between learning slope and total money
ggplot(left_join(learning_rates, participant_summary, by = "sid"), 
       aes(x = learning_slope, y = total_money)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", color = "blue") +
  theme_minimal() +
  labs(title = "Relationship Between Learning Rate and Total Money Won",
       x = "Learning Slope", y = "Total Money Won")
```

# Summary Statistics for PPC Comparison

This section provides concise summary statistics for all key metrics that are used in posterior predictive checks (PPC).

```{r ppc-stats}
# Create summary tables for key RL metrics
rl_metrics_summary <- participant_summary %>%
  select(total_money, good_deck_ratio, skip_ratio) %>%
  pivot_longer(cols = everything(), names_to = "metric", values_to = "value") %>%
  group_by(metric) %>%
  summarize(
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    q025 = quantile(value, 0.025, na.rm = TRUE),
    q25 = quantile(value, 0.25, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    q75 = quantile(value, 0.75, na.rm = TRUE),
    q975 = quantile(value, 0.975, na.rm = TRUE),
    .groups = "drop"
  )

# Create summary tables for key RT metrics
rt_metrics_summary <- participant_summary %>%
  select(mean_rt, median_rt, mean_play_rt, median_play_rt, mean_pass_rt, median_pass_rt) %>%
  pivot_longer(cols = everything(), names_to = "metric", values_to = "value") %>%
  group_by(metric) %>%
  summarize(
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    q025 = quantile(value, 0.025, na.rm = TRUE),
    q25 = quantile(value, 0.25, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    q75 = quantile(value, 0.75, na.rm = TRUE),
    q975 = quantile(value, 0.975, na.rm = TRUE),
    .groups = "drop"
  )

# Create summary tables for RT quantiles
rt_quantiles_summary <- participant_summary %>%
  select(contains("_q")) %>%
  pivot_longer(cols = everything(), names_to = "metric", values_to = "value") %>%
  group_by(metric) %>%
  summarize(
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    q025 = quantile(value, 0.025, na.rm = TRUE),
    q25 = quantile(value, 0.25, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    q75 = quantile(value, 0.75, na.rm = TRUE),
    q975 = quantile(value, 0.975, na.rm = TRUE),
    .groups = "drop"
  )

# Display all summary tables
kable(rl_metrics_summary, 
      caption = "Summary Statistics for RL Metrics (for PPC Comparison)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

kable(rt_metrics_summary, 
      caption = "Summary Statistics for RT Metrics (for PPC Comparison)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

kable(rt_quantiles_summary, 
      caption = "Summary Statistics for RT Quantiles (for PPC Comparison)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create a comprehensive table for block-level metrics (test blocks only)
block_level_metrics <- test_block_data %>%
  group_by(count_igtblocks) %>%
  summarize(
    block_good_deck_ratio_mean = mean(block_good_deck_ratio, na.rm = TRUE),
    block_good_deck_ratio_sd = sd(block_good_deck_ratio, na.rm = TRUE),
    block_skip_ratio_mean = mean(block_skip_ratio, na.rm = TRUE),
    block_skip_ratio_sd = sd(block_skip_ratio, na.rm = TRUE),
    block_money_mean = mean(block_money, na.rm = TRUE),
    block_money_sd = sd(block_money, na.rm = TRUE),
    block_rt_mean = mean(block_mean_rt, na.rm = TRUE),
    block_rt_sd = sd(block_mean_rt, na.rm = TRUE),
    block_play_rt_mean = mean(block_mean_play_rt, na.rm = TRUE),
    block_play_rt_sd = sd(block_mean_play_rt, na.rm = TRUE),
    block_pass_rt_mean = mean(block_mean_pass_rt, na.rm = TRUE),
    block_pass_rt_sd = sd(block_mean_pass_rt, na.rm = TRUE),
    .groups = "drop"
  )

# Display block-level metrics for PPC
kable(block_level_metrics, 
      caption = "Block-Level Metrics for PPC Comparison (Test Blocks Only)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create deck-specific metrics for PPC
deck_ppc_metrics <- clean_trial_data %>%
  filter(!is_training) %>%  # Exclude training block
  group_by(deck_label) %>%
  summarize(
    selection_ratio_mean = mean(play_choice, na.rm = TRUE),
    selection_ratio_sd = sd(play_choice, na.rm = TRUE),
    rt_mean = mean(rt, na.rm = TRUE),
    rt_sd = sd(rt, na.rm = TRUE),
    rt_play_mean = mean(rt[play_choice], na.rm = TRUE),
    rt_play_sd = sd(rt[play_choice], na.rm = TRUE),
    rt_pass_mean = mean(rt[!play_choice], na.rm = TRUE),
    rt_pass_sd = sd(rt[!play_choice], na.rm = TRUE),
    .groups = "drop"
  )

# Display deck-specific metrics for PPC
kable(deck_ppc_metrics, 
      caption = "Deck-Specific Metrics for PPC Comparison (Test Blocks Only)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# The summary statistics can be saved to an RDS file for use in PPC analysis
# saveRDS(list(
#   rl_metrics = rl_metrics_summary,
#   rt_metrics = rt_metrics_summary,
#   rt_quantiles = rt_quantiles_summary,
#   block_metrics = block_level_metrics,
#   deck_metrics = deck_ppc_metrics
# ), "migt_clean_metrics_for_ppc.rds")
```

```{r}

```

