---
title: "Adolescent Risk Behaviors: Combining RL and Evidence Accumulation Models"
author: "Felix Pichardo"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE,
  fig.width = 10, 
  fig.height = 6,
  out.width = "100%"
)
```

# Introduction

This analysis investigates the relationship between computational decision-making parameters from the Iowa Gambling Task (IGT) and adolescent risk behaviors. We use both reinforcement learning (RL) models and evidence accumulation models (EAMs) in a combined framework to better characterize the mechanisms that may underlie adolescent risk-taking.

## Research Questions

1. Are computational model parameters more predictive of risk behaviors than raw behavioral performance?
2. Do gender differences exist in the relationship between decision processes and risk behaviors?
3. How do developmental factors (age/grade, pubertal timing) relate to decision processes?

# Setup and Data Preparation

```{r load-packages}
suppressPackageStartupMessages({
  library(here)
  library(foreign)
  library(dplyr) 
  library(tidyr)
  library(plyr)   
  library(ggplot2)
  library(gridExtra)
  library(grid)   
  library(kableExtra) 
  library(caret)
  library(MplusAutomation)
  library(tidyverse)
  library(psych)
  library(car)
  library(corrplot)
  library(lme4)
  library(lmerTest)  
  library(sjPlot)    # For model visualization
  library(MuMIn)     # For R-squared in mixed models
})

# Directories
PROJ_DIR            = file.path(here::here())
DATA_DIR            = file.path(PROJ_DIR, "Data")
SAFE_DATA_DIR       = file.path(DATA_DIR, "AHRB")
MODELS_DIR          = file.path(PROJ_DIR, "models")
MODELS_RDS_DIR      = file.path(MODELS_DIR, "rds")
MODELS_RDS_FIT_DIR  = file.path(MODELS_RDS_DIR, "fit")
MODELS_RDS_PoPC_DIR = file.path(MODELS_RDS_DIR, "postpc")

# Source helper functions
source(file.path(PROJ_DIR, "scripts", "helper_functions_cmdSR.R"))

model_defaults = get_model_defaults()
```

## Load Data

```{r load-data}
# Trial-level data with v_groupnumber
wave1.sav.file = file.path(SAFE_DATA_DIR, "modigt_data_Wave1.sav")
wave1.raw      = read.spss(wave1.sav.file, to.data.frame = TRUE)

# Extract v_groupnumber for later use in nested random effects
groupnumber_df = wave1.raw %>% 
  group_by(sid) %>% 
  dplyr::summarise(v_groupnumber = first(v_groupnumber)) %>%
  ungroup()

# Risk data
risk.file = file.path(SAFE_DATA_DIR, "AHRB.P1W1_v11_AW_v2.sav")
risk.data = read.spss(risk.file, to.data.frame = TRUE)

# Excluded subs
exclude_file = file.path(DATA_DIR, "txt/subs/subject_ids_excludes.txt")
excluded_sids = unlist(unname(read.csv(exclude_file, header = F)))

# Set model info
main_model_name = "pvlboth"
task <- "igt_mod" 
group_type <- "batch_001"

# Set full model name
if (grepl("batch", group_type)){
  fit_model_name = paste(task, group_type, main_model_name, sep="_")
  full_model_name = paste(task, "sing", main_model_name, sep="_")
} else {
  fit_model_name = paste(task, group_type, main_model_name, sep="_")
  full_model_name = paste(task, group_type, main_model_name, sep="_")
}

# Load model fit output
model.fit.path = file.path(MODELS_RDS_FIT_DIR, paste0(fit_model_name, "_fit.rds"))
fit_output_file = sub('/models/', '/Data/', paste0(tools::file_path_sans_ext(model.fit.path), "_output.rds"))
model_fit_obj = readRDS(file = fit_output_file)

# Also load the hybrid model
hybrid_model_name <- paste0(main_model_name, "_ddm")
if (grepl("batch", group_type)){
  hybrid_fit_model_name = paste(task, group_type, hybrid_model_name, sep="_")
  hybrid_full_model_name = paste(task, "sing", hybrid_model_name, sep="_")
} else {
  hybrid_fit_model_name = paste(task, group_type, hybrid_model_name, sep="_")
  hybrid_full_model_name = paste(task, group_type, hybrid_model_name, sep="_")
}

hybrid_model.fit.path = file.path(MODELS_RDS_FIT_DIR, paste0(hybrid_fit_model_name, "_fit.rds"))
hybrid_fit_output_file = sub('/models/', '/Data/', paste0(tools::file_path_sans_ext(hybrid_model.fit.path), "_output.rds"))
hybrid_model_fit_obj = readRDS(file = hybrid_fit_output_file)
```

## Extract Behavioral Measures and Parameters

```{r extract-data}
risk.data$sid = as.character(risk.data$sid)

# Extract behavioral data
sids = unname(unlist(lapply(model_fit_obj, function(x) x$subid)))
sids = sids[!unlist(lapply(sids, function(x) x %in% as.character(excluded_sids)))]

behav_data = wave1.raw %>% group_by(sid) %>%
  dplyr::summarise(
    good_play_ratio = last(v_number_goodplay)/last(v_total_gooddeck),
    bad_play_ratio = last(v_number_badplay)/last(v_total_baddeck),
    good_bad_ratio = good_play_ratio/bad_play_ratio,
    money = last(v_currenttotal)
    ) %>% 
  ungroup() %>%
  filter(sid %in% sids)

# Extract RL parameters
rl_param_df <- data.frame(sid = sids)

for (param in model_defaults[[full_model_name]]$params){
  rl_param_df[[param]] <- numeric(length(sids))
}

for (sid_idx in 1:length(sids)) {
  for (param in model_defaults[[full_model_name]]$params) {
      rl_param_df[[param]][sid_idx] <- model_fit_obj[[sid_idx]]$summary_stats$mean[which(model_fit_obj[[sid_idx]]$all_params == param)]
  }
}

# Extract hybrid model parameters
hybrid_sids = unname(unlist(lapply(hybrid_model_fit_obj, function(x) x$subid)))
hybrid_param_df <- data.frame(sid = hybrid_sids)

for (param in model_defaults[[hybrid_full_model_name]]$params){
  hybrid_param_df[[param]] <- numeric(length(hybrid_sids))
}

for (sid_idx in 1:length(hybrid_sids)) {
  for (param in model_defaults[[hybrid_full_model_name]]$params) {
      hybrid_param_df[[param]][sid_idx] <- hybrid_model_fit_obj[[sid_idx]]$summary_stats$median[which(hybrid_model_fit_obj[[sid_idx]]$all_params == param)]
  }
}

# Define variable names for risk data
variable_names = tolower(c("BISB", "BSSS_ES", "BSSS_BS", "BSSS_TS", "BSSS_SD", 
                           "ysr_attentionproblems", "ysr_maggressive_t", "ysr_mconduct_t", "age", "pubertyage", "pubertaltiming", "pubertaltiming_num",
                           "SID"))

# Convert pubertal timing to numeric
risk.data$pubertaltiming <- factor(risk.data$pubertaltiming, 
                                   levels = c("much earlier", "earlier", 
                                              "at the same time", "later", 
                                              "much later"), 
                                   ordered = TRUE)
risk.data$pubertaltiming_num = as.numeric(risk.data$pubertaltiming)

# Create final datasets by merging
# 1. Behavioral measures
behav_final_df <- behav_data %>%
  inner_join(risk.data[c(variable_names, "bsss8", "male", "race_ethnicity", "grade10", "parent_edu6")], by = "sid") %>%
  inner_join(wave1.raw %>% group_by(sid) %>% select(grpid) %>% ungroup() %>% unique(), by = "sid") %>%
  inner_join(groupnumber_df, by = "sid")

# 2. RL model parameters
rl_final_df <- rl_param_df %>%
  inner_join(risk.data[c(variable_names, "bsss8", "male", "race_ethnicity", "grade10", "parent_edu6")], by = "sid") %>%
  inner_join(wave1.raw %>% group_by(sid) %>% select(grpid) %>% ungroup() %>% unique(), by = "sid") %>%
  inner_join(groupnumber_df, by = "sid")

# 3. Hybrid model parameters
hybrid_final_df <- hybrid_param_df %>%
  inner_join(risk.data[c(variable_names, "bsss8", "male", "race_ethnicity", "grade10", "parent_edu6")], by = "sid") %>%
  inner_join(wave1.raw %>% group_by(sid) %>% select(grpid) %>% ungroup() %>% unique(), by = "sid") %>%
  inner_join(groupnumber_df, by = "sid")

# Create Asian Non-Hispanic indicator for controls
behav_final_df$race_ethnicity_ANH = as.numeric(behav_final_df$race_ethnicity == "asian non hispanic")
rl_final_df$race_ethnicity_ANH = as.numeric(rl_final_df$race_ethnicity == "asian non hispanic")
hybrid_final_df$race_ethnicity_ANH = as.numeric(hybrid_final_df$race_ethnicity == "asian non hispanic")

# Fix good/bad ratio
# if (sum(is.infinite(behav_data$good_bad_ratio)) > 0){
#   temp_vals = behav_data$good_bad_ratio[!is.infinite(behav_data$good_bad_ratio)]
#   ratio_sd = sd(temp_vals)
#   behav_data$good_bad_ratio[is.infinite(behav_data$good_bad_ratio)] = max(temp_vals) + ratio_sd
# }



```

### Fix puberty issue
```{r}
# Convert pubertyage to numeric
convert_pubertyage <- function(puberty_cat) {
  # Convert categorical pubertyage to numeric values
  # Using midpoints or conservative estimates for ranges
  case_when(
    puberty_cat == "=/< 10" ~ 10,    # Using upper bound of 10
    puberty_cat == "11" ~ 11,
    puberty_cat == "12" ~ 12,
    puberty_cat == "13" ~ 13,
    puberty_cat == "14" ~ 14,
    puberty_cat == "15" ~ 15,
    puberty_cat == "16" ~ 16,
    puberty_cat == "=/> 17" ~ 17,    # Using lower bound of 17
    TRUE ~ NA_real_                  # Handle any other cases
  )
}

# Apply conversion and calculate time since puberty
create_puberty_metrics <- function(df) {
  df %>%
    mutate(
      pubertyage_num = convert_pubertyage(pubertyage),
      time_since_puberty = age - pubertyage_num
    )
}

# Apply to the dataframes
behav_final_df <- behav_final_df %>% create_puberty_metrics()
rl_final_df <- rl_final_df %>% create_puberty_metrics()
hybrid_final_df <- hybrid_final_df %>% create_puberty_metrics()
```


# Preliminary Data Exploration

## Correlation Analysis

```{r correlation-analysis}
# Define risk outcomes of interest
risk_outcomes <- c("bsss_sd", "ysr_attentionproblems", "ysr_maggressive_t", "ysr_mconduct_t")

# Examine correlations for behavioral measures
behav_corr_vars <- c("good_play_ratio", "money", "bad_play_ratio", "good_bad_ratio", risk_outcomes)
behav_corr <- cor(behav_final_df[behav_corr_vars], use = "complete.obs")

# Examine correlations for RL parameters
rl_params <- model_defaults[[full_model_name]]$params
rl_corr_vars <- c(rl_params, risk_outcomes)
rl_corr <- cor(rl_final_df[rl_corr_vars], use = "complete.obs")

# Examine correlations for hybrid parameters
hybrid_params <- model_defaults[[hybrid_full_model_name]]$params
hybrid_corr_vars <- c(hybrid_params, risk_outcomes)
hybrid_corr <- cor(hybrid_final_df[hybrid_corr_vars], use = "complete.obs")

# Plot correlations
corrplot(behav_corr, method = "color", type = "upper", diag = FALSE, 
         title = "Behavioral Measures", mar = c(0,0,1,0))
corrplot(rl_corr, method = "color", type = "upper", diag = FALSE, 
         title = "RL Parameters", mar = c(0,0,1,0))
corrplot(hybrid_corr, method = "color", type = "upper", diag = FALSE, 
         title = "Hybrid Parameters", mar = c(0,0,1,0))
```

## Age and Pubertal Timing Distribution

```{r development-distribution}
# Examine age distribution
ggplot(risk.data, aes(x = age)) +
  geom_histogram(binwidth = 0.25, fill = "skyblue", color = "black") +
  geom_vline(xintercept = mean(risk.data$age, na.rm = TRUE), color = "red", linetype = "dashed") +
  labs(title = "Age Distribution", x = "Age (years)", y = "Count")

# Examine pubertal timing distribution
ggplot(risk.data, aes(x = pubertaltiming)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Pubertal Timing Distribution", x = "Pubertal Timing", y = "Count")

# Examine age by grade
ggplot(risk.data, aes(x = factor(grade10, labels = c("12th Grade", "10th Grade")), y = age)) +
  geom_boxplot(fill = "skyblue") +
  labs(title = "Age Distribution by Grade", x = "Grade", y = "Age (years)")
```

# Model Comparison Analysis

## Function to Compare Model Types

```{r define-comparison-function}
# Function to compare different model types for predicting risk behaviors
compare_models <- function(outcome, df_behav, df_rl, df_hybrid) {
  # Prepare empty results dataframe
  results <- data.frame(
    outcome = character(),
    model_type = character(),
    AIC = numeric(),
    BIC = numeric(),
    r2m = numeric(),
    r2c = numeric(),
    stringsAsFactors = FALSE
  )
  
  # Raw behavioral model
  behav_formula <- as.formula(paste(outcome, "~ good_bad_ratio + money + (1|grpid/v_groupnumber)"))
  behav_model <- lmer(behav_formula, data = df_behav)
  behav_r2 <- r.squaredGLMM(behav_model)
  
  results <- rbind(results, data.frame(
    outcome = outcome,
    model_type = "Raw Behavioral",
    AIC = AIC(behav_model),
    BIC = BIC(behav_model),
    r2m = behav_r2[1],
    r2c = behav_r2[2]
  ))
  
  # Motivational parameters - RL model
  motiv_params_rl <- c("gain", "loss")
  motiv_formula_rl <- as.formula(paste(outcome, "~", paste(motiv_params_rl, collapse = " + "), 
                                     "+ (1|grpid/v_groupnumber)"))
  motiv_model_rl <- lmer(motiv_formula_rl, data = df_rl)
  motiv_r2_rl <- r.squaredGLMM(motiv_model_rl)
  
  results <- rbind(results, data.frame(
    outcome = outcome,
    model_type = "Motivational (RL)",
    AIC = AIC(motiv_model_rl),
    BIC = BIC(motiv_model_rl),
    r2m = motiv_r2_rl[1],
    r2c = motiv_r2_rl[2]
  ))
  
  # Motivational parameters - Hybrid model
  motiv_formula_hybrid <- as.formula(paste(outcome, "~", paste(motiv_params_rl, collapse = " + "), 
                                         "+ (1|grpid/v_groupnumber)"))
  motiv_model_hybrid <- lmer(motiv_formula_hybrid, data = df_hybrid)
  motiv_r2_hybrid <- r.squaredGLMM(motiv_model_hybrid)
  
  results <- rbind(results, data.frame(
    outcome = outcome,
    model_type = "Motivational (Hybrid)",
    AIC = AIC(motiv_model_hybrid),
    BIC = BIC(motiv_model_hybrid),
    r2m = motiv_r2_hybrid[1],
    r2c = motiv_r2_hybrid[2]
  ))
  
  # Cognitive parameters - RL model
  cognitive_params <- c("update", "decay")
  if(all(cognitive_params %in% colnames(df_rl))) {
    cog_formula_rl <- as.formula(paste(outcome, "~", paste(cognitive_params, collapse = " + "), 
                                      "+ (1|grpid/v_groupnumber)"))
    cog_model_rl <- lmer(cog_formula_rl, data = df_rl)
    cog_r2_rl <- r.squaredGLMM(cog_model_rl)
    
    results <- rbind(results, data.frame(
      outcome = outcome,
      model_type = "Cognitive (RL)",
      AIC = AIC(cog_model_rl),
      BIC = BIC(cog_model_rl),
      r2m = cog_r2_rl[1],
      r2c = cog_r2_rl[2]
    ))
  }
  
  # Cognitive parameters - Hybrid model
  if(all(cognitive_params %in% colnames(df_hybrid))) {
    cog_formula_hybrid <- as.formula(paste(outcome, "~", paste(cognitive_params, collapse = " + "), 
                                         "+ (1|grpid/v_groupnumber)"))
    cog_model_hybrid <- lmer(cog_formula_hybrid, data = df_hybrid)
    cog_r2_hybrid <- r.squaredGLMM(cog_model_hybrid)
    
    results <- rbind(results, data.frame(
      outcome = outcome,
      model_type = "Cognitive (Hybrid)",
      AIC = AIC(cog_model_hybrid),
      BIC = BIC(cog_model_hybrid),
      r2m = cog_r2_hybrid[1],
      r2c = cog_r2_hybrid[2]
    ))
  }
  
  # DDM parameters
  ddm_params <- c("boundary", "tau", "beta")
  available_ddm <- ddm_params[ddm_params %in% colnames(df_hybrid)]
  
  if(length(available_ddm) > 0) {
    ddm_formula <- as.formula(paste(outcome, "~", paste(available_ddm, collapse = " + "), 
                                  "+ (1|grpid/v_groupnumber)"))
    ddm_model <- lmer(ddm_formula, data = df_hybrid)
    ddm_r2 <- r.squaredGLMM(ddm_model)
    
    results <- rbind(results, data.frame(
      outcome = outcome,
      model_type = "DDM Parameters",
      AIC = AIC(ddm_model),
      BIC = BIC(ddm_model),
      r2m = ddm_r2[1],
      r2c = ddm_r2[2]
    ))
  }
  
  # Combined motivational and cognitive - RL model
  combined_params_rl <- c(motiv_params_rl, cognitive_params)
  available_combined_rl <- combined_params_rl[combined_params_rl %in% colnames(df_rl)]
  
  if(length(available_combined_rl) > 0) {
    combined_formula_rl <- as.formula(paste(outcome, "~", paste(available_combined_rl, collapse = " + "), 
                                          "+ (1|grpid/v_groupnumber)"))
    combined_model_rl <- lmer(combined_formula_rl, data = df_rl)
    combined_r2_rl <- r.squaredGLMM(combined_model_rl)
    
    results <- rbind(results, data.frame(
      outcome = outcome,
      model_type = "Motiv+Cognitive (RL)",
      AIC = AIC(combined_model_rl),
      BIC = BIC(combined_model_rl),
      r2m = combined_r2_rl[1],
      r2c = combined_r2_rl[2]
    ))
  }
  
  # Combined motivational and cognitive - Hybrid model
  combined_params_hybrid <- c(motiv_params_rl, cognitive_params)
  available_combined_hybrid <- combined_params_hybrid[combined_params_hybrid %in% colnames(df_hybrid)]
  
  if(length(available_combined_hybrid) > 0) {
    combined_formula_hybrid <- as.formula(paste(outcome, "~", paste(available_combined_hybrid, collapse = " + "), 
                                              "+ (1|grpid/v_groupnumber)"))
    combined_model_hybrid <- lmer(combined_formula_hybrid, data = df_hybrid)
    combined_r2_hybrid <- r.squaredGLMM(combined_model_hybrid)
    
    results <- rbind(results, data.frame(
      outcome = outcome,
      model_type = "Motiv+Cognitive (Hybrid)",
      AIC = AIC(combined_model_hybrid),
      BIC = BIC(combined_model_hybrid),
      r2m = combined_r2_hybrid[1],
      r2c = combined_r2_hybrid[2]
    ))
  }
  
  return(results)
}
```

## Compare Models for Each Risk Outcome

```{r model-comparison}
# Run comparison for each risk outcome
all_comparisons <- data.frame()

for (outcome in risk_outcomes) {
  comparison <- compare_models(outcome, behav_final_df, rl_final_df, hybrid_final_df)
  all_comparisons <- rbind(all_comparisons, comparison)
}

# Display comparison results
kable(all_comparisons, caption = "Model Comparison Results") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize comparison
ggplot(all_comparisons, aes(x = model_type, y = r2m, fill = model_type)) +
  geom_bar(stat = "identity") +
  facet_wrap(~outcome, scales = "free_y") +
  labs(title = "Variance Explained by Different Model Types",
       x = "Model Type", y = "Marginal R²") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Gender Differences Analysis

## Parameter Group Analysis by Gender

```{r parameter-groups}
# Define parameter groups for conceptual organization
evidence_params <- c("boundary", "drift_con")
response_params <- c("tau", "beta")
reward_params <- c("gain", "loss")
update_params <- c("update", "decay")

# Function to analyze gender differences for parameter groups
analyze_gender_differences <- function(outcome, df) {
  # Evidence accumulation parameters
  if (all(evidence_params %in% colnames(df))) {
    evidence_formula <- as.formula(paste(outcome, "~", 
                                       paste(paste0(evidence_params, "*male"), collapse = " + "), 
                                       "+ (1|grpid/v_groupnumber)"))
    evidence_model <- lmer(evidence_formula, data = df)
    evidence_summary <- summary(evidence_model)
  } else {
    evidence_summary <- NULL
  }
  
  # Response caution parameters
  if (all(response_params %in% colnames(df))) {
    response_formula <- as.formula(paste(outcome, "~", 
                                       paste(paste0(response_params, "*male"), collapse = " + "), 
                                       "+ (1|grpid/v_groupnumber)"))
    response_model <- lmer(response_formula, data = df)
    response_summary <- summary(response_model)
  } else {
    response_summary <- NULL
  }
  
  # Reward learning parameters
  if (all(reward_params %in% colnames(df))) {
    reward_formula <- as.formula(paste(outcome, "~", 
                                      paste(paste0(reward_params, "*male"), collapse = " + "), 
                                      "+ (1|grpid/v_groupnumber)"))
    reward_model <- lmer(reward_formula, data = df)
    reward_summary <- summary(reward_model)
  } else {
    reward_summary <- NULL
  }
  
  # Experience updating parameters
  if (all(update_params %in% colnames(df))) {
    update_formula <- as.formula(paste(outcome, "~", 
                                      paste(paste0(update_params, "*male"), collapse = " + "), 
                                      "+ (1|grpid/v_groupnumber)"))
    update_model <- lmer(update_formula, data = df)
    update_summary <- summary(update_model)
  } else {
    update_summary <- NULL
  }
  
  return(list(
    outcome = outcome,
    evidence_model = if(exists("evidence_model")) evidence_model else NULL,
    response_model = if(exists("response_model")) response_model else NULL,
    reward_model = if(exists("reward_model")) reward_model else NULL,
    update_model = if(exists("update_model")) update_model else NULL
  ))
}
```

## Run Gender Difference Analysis

```{r gender-analysis}
# Analyze gender differences for each risk outcome
gender_results <- list()

for (outcome in risk_outcomes) {
  gender_results[[outcome]] <- analyze_gender_differences(outcome, hybrid_final_df)
}

# Extract significant gender interactions
extract_significant_interactions <- function(model_results, interaction_term = "male") {
  if (is.null(model_results)) return(NULL)
  
  coefs <- summary(model_results)$coefficients
  interaction_rows <- grep(paste0(":", interaction_term), rownames(coefs))
  
  if (length(interaction_rows) == 0) return(NULL)
  
  significant_interactions <- data.frame(
    parameter = gsub(paste0(":", interaction_term), "", rownames(coefs)[interaction_rows]),
    estimate = coefs[interaction_rows, "Estimate"],
    std_error = coefs[interaction_rows, "Std. Error"],
    t_value = coefs[interaction_rows, "t value"],
    p_value = coefs[interaction_rows, "Pr(>|t|)"],
    significant = coefs[interaction_rows, "Pr(>|t|)"] < 0.05
  )
  
  return(significant_interactions)
}

# Collect significant interactions for each outcome and parameter group
significant_gender_interactions <- data.frame()

for (outcome in risk_outcomes) {
  result <- gender_results[[outcome]]
  
  # Evidence accumulation parameters
  if (!is.null(result$evidence_model)) {
    evidence_interactions <- extract_significant_interactions(result$evidence_model)
    if (!is.null(evidence_interactions)) {
      evidence_interactions$outcome <- outcome
      evidence_interactions$parameter_group <- "Evidence Accumulation"
      significant_gender_interactions <- rbind(significant_gender_interactions, evidence_interactions)
    }
  }
  
  # Response caution parameters
  if (!is.null(result$response_model)) {
    response_interactions <- extract_significant_interactions(result$response_model)
    if (!is.null(response_interactions)) {
      response_interactions$outcome <- outcome
      response_interactions$parameter_group <- "Response Caution"
      significant_gender_interactions <- rbind(significant_gender_interactions, response_interactions)
    }
  }
  
  # Reward learning parameters
  if (!is.null(result$reward_model)) {
    reward_interactions <- extract_significant_interactions(result$reward_model)
    if (!is.null(reward_interactions)) {
      reward_interactions$outcome <- outcome
      reward_interactions$parameter_group <- "Reward Learning"
      significant_gender_interactions <- rbind(significant_gender_interactions, reward_interactions)
    }
  }
  
  # Experience updating parameters
  if (!is.null(result$update_model)) {
    update_interactions <- extract_significant_interactions(result$update_model)
    if (!is.null(update_interactions)) {
      update_interactions$outcome <- outcome
      update_interactions$parameter_group <- "Experience Updating"
      significant_gender_interactions <- rbind(significant_gender_interactions, update_interactions)
    }
  }
}

# Display significant gender interactions
if (nrow(significant_gender_interactions) > 0) {
  kable(significant_gender_interactions, caption = "Significant Gender Interactions") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
  
  # Visualize significant gender interactions
  ggplot(significant_gender_interactions, 
         aes(x = parameter, y = estimate, fill = outcome)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error), 
                  position = position_dodge(width = 0.9), width = 0.25) +
    facet_wrap(~parameter_group, scales = "free_x") +
    labs(title = "Gender Differences in Decision-Making Parameters",
         subtitle = "Parameter × Male Interactions",
         x = "Parameter", 
         y = "Effect Size") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
} else {
  cat("No significant gender interactions found.")
}
```

# Developmental Analysis

## Grade and Pubertal Timing Effects on Parameters
```{r developmental-effects-behav}
# Function to analyze developmental effects on parameters
analyze_developmental_effects <- function(param, df) {
  # Grade effect
  grade_formula <- as.formula(paste(param, "~ grade10 + (1|grpid/v_groupnumber)"))
  grade_model <- lmer(grade_formula, data = df)
  
  # Pubertal timing effect
  puberty_formula <- as.formula(paste(param, "~ time_since_puberty + (1|grpid/v_groupnumber)"))
  puberty_model <- lmer(puberty_formula, data = df)
  
  # Combined model
  combined_formula <- as.formula(paste(param, "~ grade10 + time_since_puberty + (1|grpid/v_groupnumber)"))
  combined_model <- lmer(combined_formula, data = df)
  
  # Return results
  return(list(
    parameter = param,
    grade_model = grade_model,
    puberty_model = puberty_model,
    combined_model = combined_model
  ))
}

# Run analysis for hybrid model parameters
dev_results <- list()
for (param in c("good_play_ratio", "money", "bad_play_ratio", "good_bad_ratio")) {
  dev_results[[param]] <- analyze_developmental_effects(param, behav_final_df)
}

# Extract significant developmental effects
extract_developmental_effects <- function(model_list) {
  result_df <- data.frame(
    parameter = character(),
    grade_effect = numeric(),
    grade_p = numeric(),
    puberty_effect = numeric(),
    puberty_p = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (param in names(model_list)) {
    models <- model_list[[param]]
    
    # Extract grade effect
    grade_coef <- summary(models$grade_model)$coefficients["grade1010th grade", ]
    
    # Extract puberty effect
    puberty_coef <- summary(models$puberty_model)$coefficients["time_since_puberty", ]
    
    result_df <- rbind(result_df, data.frame(
      parameter = param,
      grade_effect = grade_coef["Estimate"],
      grade_p = grade_coef["Pr(>|t|)"],
      puberty_effect = puberty_coef["Estimate"],
      puberty_p = puberty_coef["Pr(>|t|)"],
      stringsAsFactors = FALSE
    ))
  }
  
  result_df$grade_sig <- result_df$grade_p < 0.05
  result_df$puberty_sig <- result_df$puberty_p < 0.05
  
  return(result_df)
}

developmental_effects <- extract_developmental_effects(dev_results)

# Display developmental effects
kable(developmental_effects, caption = "Developmental Effects on Behavioral Metrics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize significant developmental effects
dev_plot_data <- developmental_effects %>%
  pivot_longer(cols = c(grade_effect, puberty_effect), 
               names_to = "effect_type", 
               values_to = "effect_size") %>%
  mutate(significance = case_when(
    effect_type == "grade_effect" & grade_sig ~ "Significant",
    effect_type == "puberty_effect" & puberty_sig ~ "Significant",
    TRUE ~ "Non-significant"
  ),
  effect_type = case_when(
    effect_type == "grade_effect" ~ "Grade (10th vs 12th)",
    effect_type == "puberty_effect" ~ "Time Since Puberty Start",
    TRUE ~ effect_type
  ))

ggplot(dev_plot_data, aes(x = parameter, y = effect_size, fill = significance)) +
  geom_bar(stat = "identity") +
  facet_wrap(~effect_type, scales = "free") +
  labs(title = "Developmental Effects on Behavioral Metrics",
       x = "Parameter", 
       y = "Effect Size") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r developmental-effects-rl}
# Function to analyze developmental effects on parameters
analyze_developmental_effects <- function(param, df) {
  # Grade effect
  grade_formula <- as.formula(paste(param, "~ grade10 + (1|grpid/v_groupnumber)"))
  grade_model <- lmer(grade_formula, data = df)
  
  # Pubertal timing effect
  puberty_formula <- as.formula(paste(param, "~ time_since_puberty + (1|grpid/v_groupnumber)"))
  puberty_model <- lmer(puberty_formula, data = df)
  
  # Combined model
  combined_formula <- as.formula(paste(param, "~ grade10 + time_since_puberty + (1|grpid/v_groupnumber)"))
  combined_model <- lmer(combined_formula, data = df)
  
  # Return results
  return(list(
    parameter = param,
    grade_model = grade_model,
    puberty_model = puberty_model,
    combined_model = combined_model
  ))
}

# Run analysis for hybrid model parameters
dev_results <- list()
for (param in model_defaults[[full_model_name]]$params) {
  dev_results[[param]] <- analyze_developmental_effects(param, rl_final_df)
}

# Extract significant developmental effects
extract_developmental_effects <- function(model_list) {
  result_df <- data.frame(
    parameter = character(),
    grade_effect = numeric(),
    grade_p = numeric(),
    puberty_effect = numeric(),
    puberty_p = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (param in names(model_list)) {
    models <- model_list[[param]]
    
    # Extract grade effect
    grade_coef <- summary(models$grade_model)$coefficients["grade1010th grade", ]
    
    # Extract puberty effect
    puberty_coef <- summary(models$puberty_model)$coefficients["time_since_puberty", ]
    
    result_df <- rbind(result_df, data.frame(
      parameter = param,
      grade_effect = grade_coef["Estimate"],
      grade_p = grade_coef["Pr(>|t|)"],
      puberty_effect = puberty_coef["Estimate"],
      puberty_p = puberty_coef["Pr(>|t|)"],
      stringsAsFactors = FALSE
    ))
  }
  
  result_df$grade_sig <- result_df$grade_p < 0.05
  result_df$puberty_sig <- result_df$puberty_p < 0.05
  
  return(result_df)
}

developmental_effects <- extract_developmental_effects(dev_results)

# Display developmental effects
kable(developmental_effects, caption = "Developmental Effects on Decision Parameters") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize significant developmental effects
dev_plot_data <- developmental_effects %>%
  pivot_longer(cols = c(grade_effect, puberty_effect), 
               names_to = "effect_type", 
               values_to = "effect_size") %>%
  mutate(significance = case_when(
    effect_type == "grade_effect" & grade_sig ~ "Significant",
    effect_type == "puberty_effect" & puberty_sig ~ "Significant",
    TRUE ~ "Non-significant"
  ),
  effect_type = case_when(
    effect_type == "grade_effect" ~ "Grade (10th vs 12th)",
    effect_type == "puberty_effect" ~ "Time Since Puberty Start",
    TRUE ~ effect_type
  ))

ggplot(dev_plot_data, aes(x = parameter, y = effect_size, fill = significance)) +
  geom_bar(stat = "identity") +
  facet_wrap(~effect_type, scales = "free") +
  labs(title = "Developmental Effects on RL Decision Parameters",
       x = "Parameter", 
       y = "Effect Size") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r developmental-effects}
# Function to analyze developmental effects on parameters
analyze_developmental_effects <- function(param, df) {
  # Grade effect
  grade_formula <- as.formula(paste(param, "~ grade10 + (1|grpid/v_groupnumber)"))
  grade_model <- lmer(grade_formula, data = df)
  
  # Pubertal timing effect
  puberty_formula <- as.formula(paste(param, "~ time_since_puberty + (1|grpid/v_groupnumber)"))
  puberty_model <- lmer(puberty_formula, data = df)
  
  # Combined model
  combined_formula <- as.formula(paste(param, "~ grade10 + time_since_puberty + (1|grpid/v_groupnumber)"))
  combined_model <- lmer(combined_formula, data = df)
  
  # Return results
  return(list(
    parameter = param,
    grade_model = grade_model,
    puberty_model = puberty_model,
    combined_model = combined_model
  ))
}

# Run analysis for hybrid model parameters
dev_results <- list()
for (param in model_defaults[[hybrid_full_model_name]]$params) {
  dev_results[[param]] <- analyze_developmental_effects(param, hybrid_final_df)
}

# Extract significant developmental effects
extract_developmental_effects <- function(model_list) {
  result_df <- data.frame(
    parameter = character(),
    grade_effect = numeric(),
    grade_p = numeric(),
    puberty_effect = numeric(),
    puberty_p = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (param in names(model_list)) {
    models <- model_list[[param]]
    
    # Extract grade effect
    grade_coef <- summary(models$grade_model)$coefficients["grade1010th grade", ]
    
    # Extract puberty effect
    puberty_coef <- summary(models$puberty_model)$coefficients["time_since_puberty", ]
    
    result_df <- rbind(result_df, data.frame(
      parameter = param,
      grade_effect = grade_coef["Estimate"],
      grade_p = grade_coef["Pr(>|t|)"],
      puberty_effect = puberty_coef["Estimate"],
      puberty_p = puberty_coef["Pr(>|t|)"],
      stringsAsFactors = FALSE
    ))
  }
  
  result_df$grade_sig <- result_df$grade_p < 0.05
  result_df$puberty_sig <- result_df$puberty_p < 0.05
  
  return(result_df)
}

developmental_effects <- extract_developmental_effects(dev_results)

# Display developmental effects
kable(developmental_effects, caption = "Developmental Effects on Decision Parameters") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize significant developmental effects
dev_plot_data <- developmental_effects %>%
  pivot_longer(cols = c(grade_effect, puberty_effect), 
               names_to = "effect_type", 
               values_to = "effect_size") %>%
  mutate(significance = case_when(
    effect_type == "grade_effect" & grade_sig ~ "Significant",
    effect_type == "puberty_effect" & puberty_sig ~ "Significant",
    TRUE ~ "Non-significant"
  ),
  effect_type = case_when(
    effect_type == "grade_effect" ~ "Grade (10th vs 12th)",
    effect_type == "puberty_effect" ~ "Pubertal Timing",
    TRUE ~ effect_type
  ))

ggplot(dev_plot_data, aes(x = parameter, y = effect_size, fill = significance)) +
  geom_bar(stat = "identity") +
  facet_wrap(~effect_type, scales = "free") +
  labs(title = "Developmental Effects on Hybrid Decision Parameters",
       x = "Parameter", 
       y = "Effect Size") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Combined Model Analysis

## Identify Key Predictive Parameters

```{r key-parameters}
# Function to identify key predictive parameters for each risk outcome
identify_key_parameters <- function(outcome, df) {
  # Full model with all parameters
  all_params <- model_defaults[[hybrid_full_model_name]]$params
  full_formula <- as.formula(paste(outcome, "~", paste(all_params, collapse = " + "), 
                                  "+ (1|grpid/v_groupnumber)"))
  full_model <- lmer(full_formula, data = df)
  
  # Extract coefficients and p-values
  coefs <- summary(full_model)$coefficients
  param_rows <- match(all_params, rownames(coefs))
  param_rows <- param_rows[!is.na(param_rows)]
  
  # Identify significant parameters (p < 0.10)
  significant_params <- rownames(coefs)[param_rows[coefs[param_rows, "Pr(>|t|)"] < 0.10]]
  
  # Return results
  return(list(
    outcome = outcome,
    full_model = full_model,
    significant_params = significant_params,
    all_coefficients = coefs[param_rows, ]
  ))
}

# Identify key parameters for each risk outcome
key_params_results <- list()
for (outcome in risk_outcomes) {
  key_params_results[[outcome]] <- identify_key_parameters(outcome, hybrid_final_df)
}

# Create summary of key parameters
key_params_summary <- data.frame(
  outcome = character(),
  significant_parameters = character(),
  stringsAsFactors = FALSE
)

for (outcome in risk_outcomes) {
  key_params_summary <- rbind(key_params_summary, data.frame(
    outcome = outcome,
    significant_parameters = paste(key_params_results[[outcome]]$significant_params, collapse = ", "),
    stringsAsFactors = FALSE
  ))
}

# Display key parameters
kable(key_params_summary, caption = "Key Predictive Parameters by Risk Outcome") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

## Final Models with Gender and Developmental Factors

```{r final-models}
# Function to create focused model for each outcome
create_focused_model <- function(outcome, key_params, df) {
  # Base formula with key parameters
  base_formula <- paste(outcome, "~", paste(key_params, collapse = " + "))
  
  # Add gender effects for parameters with significant gender interactions
  gender_params <- c()
  for (param in key_params) {
    gender_interactions <- significant_gender_interactions[significant_gender_interactions$outcome == outcome & 
                                                          significant_gender_interactions$parameter == param,]
    if(nrow(gender_interactions) > 0) {
      gender_params <- c(gender_params, param)
    }
  }
  
  # Add gender interaction terms
  if(length(gender_params) > 0) {
    gender_formula <- paste(paste0(gender_params, "*male"), collapse = " + ")
    formula_str <- paste(base_formula, "+", gender_formula)
  } else {
    formula_str <- paste(base_formula, "+ male")
  }
  
  # Add developmental factors
  formula_str <- paste(formula_str, "+ grade10 + pubertaltiming_num")
  
  # Add random effects
  formula_str <- paste(formula_str, "+ (1|grpid/v_groupnumber)")
  
  # Fit model
  model <- lmer(as.formula(formula_str), data = df)
  
  return(list(
    outcome = outcome,
    formula = formula_str,
    model = model,
    summary = summary(model)
  ))
}

# Create focused models for each risk outcome
focused_models <- list()
for (outcome in risk_outcomes) {
  key_params <- key_params_results[[outcome]]$significant_params
  if(length(key_params) > 0) {
    focused_models[[outcome]] <- create_focused_model(outcome, key_params, hybrid_final_df)
  }
}

# Display model summaries
for (outcome in names(focused_models)) {
  cat("\n\n## Final Model for", outcome, "\n")
  cat("Formula:", focused_models[[outcome]]$formula, "\n\n")
  print(focused_models[[outcome]]$summary)
}

# Create table of significant predictors from focused models
extract_significant_predictors <- function(model_list) {
  result_df <- data.frame(
    outcome = character(),
    parameter = character(),
    estimate = numeric(),
    std_error = numeric(),
    t_value = numeric(),
    p_value = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (outcome in names(model_list)) {
    model_summary <- model_list[[outcome]]$summary
    coefs <- model_summary$coefficients
    
    # Get all rows except intercept
    pred_rows <- rownames(coefs)[-1]
    
    for (pred in pred_rows) {
      if (coefs[pred, "Pr(>|t|)"] < 0.05) {
        result_df <- rbind(result_df, data.frame(
          outcome = outcome,
          parameter = pred,
          estimate = coefs[pred, "Estimate"],
          std_error = coefs[pred, "Std. Error"],
          t_value = coefs[pred, "t value"],
          p_value = coefs[pred, "Pr(>|t|)"],
          stringsAsFactors = FALSE
        ))
      }
    }
  }
  
  return(result_df)
}

# Extract significant predictors
significant_predictors <- extract_significant_predictors(focused_models)

# Display significant predictors
if (nrow(significant_predictors) > 0) {
  kable(significant_predictors, caption = "Significant Predictors in Final Models") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
  
  # Visualize significant predictors
  ggplot(significant_predictors, aes(x = parameter, y = estimate, fill = outcome)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error), 
                  position = position_dodge(width = 0.9), width = 0.25) +
    labs(title = "Significant Predictors of Risk Behaviors",
         x = "Parameter", 
         y = "Effect Size") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
} else {
  cat("No significant predictors found in final models.")
}
```

# Parameter Interpretation

Before discussing the implications, let's clarify the interpretation of the model parameters:

```{r parameter-definitions, echo=FALSE}
parameter_definitions <- data.frame(
  Parameter = c("boundary", "tau", "beta", "drift_con", "gain", "loss", "update", "decay"),
  Type = c("DDM", "DDM", "DDM", "DDM", "RL", "RL", "RL", "RL"),
  Definition = c(
    "Decision threshold - higher values indicate more cautious decision-making requiring more evidence",
    "Non-decision time - cognitive processing time unrelated to the decision process",
    "Response bias - tendency to favor one response option over another",
    "Drift rate constant - baseline information processing efficiency",
    "Reward sensitivity - learning rate for positive outcomes",
    "Punishment sensitivity - learning rate for negative outcomes",
    "Value updating rate - how quickly expected values are updated based on new information",
    "Memory decay rate - how quickly prior information is forgotten"
  )
)

kable(parameter_definitions, caption = "Decision Model Parameter Definitions") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```
