---
title: "Adolescent Risk Behaviors: Combining RL and Evidence Accumulation Models - NNLdecay"
author: "Felix Pichardo"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE,
  fig.width = 10, 
  fig.height = 6,
  out.width = "100%"
)

# Set model info
main_model_name = "nnldelta"
task <- "igt_mod"
group_type <- "batch_001"
```

# Introduction

This analysis investigates the relationship between computational decision-making parameters from the Iowa Gambling Task (IGT) and adolescent risk behaviors. We use both reinforcement learning (RL) models and evidence accumulation models (EAMs) in a combined framework to better characterize the mechanisms that may underlie adolescent risk-taking.

## Research Questions

1. Are computational model parameters more predictive of risk behaviors than raw behavioral performance?
2. Do gender differences exist in the relationship between decision processes and risk behaviors?
3. How do developmental factors (age/grade, pubertal timing) relate to decision processes?
4. Do successful performance mechanisms vary by development stage or gender/sex?

# Setup and Data Preparation

```{r load-packages}
suppressPackageStartupMessages({
  library(here)
  library(foreign)
  library(dplyr) 
  library(tidyr)
  library(plyr)   
  library(ggplot2)
  library(gridExtra)
  library(grid)   
  library(kableExtra) 
  library(caret)
  library(MplusAutomation)
  library(tidyverse)
  library(psych)
  library(car)
  library(corrplot)
  library(lme4)
  library(lmerTest)  
  library(sjPlot)    # For model visualization
  library(MuMIn)     # For R-squared in mixed models
  library(qvalue)
})

# Directories
PROJ_DIR            = file.path(here::here())
DATA_DIR            = file.path(PROJ_DIR, "Data")
SAFE_DATA_DIR       = file.path(DATA_DIR, "AHRB")
MODELS_DIR          = file.path(PROJ_DIR, "models")
MODELS_RDS_DIR      = file.path(MODELS_DIR, "rds")
MODELS_RDS_FIT_DIR  = file.path(MODELS_RDS_DIR, "fit")
MODELS_RDS_PoPC_DIR = file.path(MODELS_RDS_DIR, "postpc")

# Source helper functions
source(file.path(PROJ_DIR, "scripts", "helpers", "helper_functions_cmdSR.R"))

model_defaults = get_model_defaults(task)
```

## Load Data

```{r load-data}
# Trial-level data with v_groupnumber
wave1.sav.file <- file.path(SAFE_DATA_DIR, "modigt_data_Wave1.sav")
wave1.raw <- read.spss(wave1.sav.file, to.data.frame = TRUE)

# Extract v_groupnumber for later use in nested random effects
groupnumber_df <- wave1.raw %>% 
  group_by(sid) %>% 
  dplyr::summarise(v_groupnumber = first(v_groupnumber)) %>%
  ungroup()

districtid_schoolid_df <- wave1.raw %>% 
     group_by(sid) %>% 
     slice_tail(n = 1) %>%
     dplyr::summarise(
         districtid = as.factor(districtid),
         schoolid = as.factor(schoolid)
     ) %>%
     ungroup()

# Risk data
risk.file <- file.path(SAFE_DATA_DIR, "AHRB.P1W1_v11_AW_v2.sav")
risk.data <- read.spss(risk.file, to.data.frame = TRUE)

# Excluded subs
exclude_file <- file.path(SAFE_DATA_DIR, "subs/subject_ids_excludes.txt")
excluded_sids <- unlist(unname(read.csv(exclude_file, header = F)))

# Set model names - Make sure to define main_model_name and group_type
# For example: main_model_name <- "pvldelta"
# For example: group_type <- "batch_001"

# Build full model names
if (grepl("batch", group_type)) {
  fit_model_name <- paste(task, group_type, main_model_name, sep="_")
  full_model_name <- paste(task, "sing", main_model_name, sep="_")
} else {
  fit_model_name <- paste(task, group_type, main_model_name, sep="_")
  full_model_name <- paste(task, group_type, main_model_name, sep="_")
}

# Load model fit output - updated paths
model_output_dir <- file.path(DATA_DIR, "igt_mod", "rds", "fit")
fit_output_file <- file.path(model_output_dir, paste0(fit_model_name, "_fit_output.rds"))
model_fit_obj <- readRDS(file = fit_output_file)

# Also load the hybrid model
hybrid_model_name <- paste0(main_model_name, "_ddm_b1b")
if (grepl("batch", group_type)) {
  hybrid_fit_model_name <- paste(task, group_type, hybrid_model_name, sep="_")
  hybrid_full_model_name <- paste(task, "sing", hybrid_model_name, sep="_")
} else {
  hybrid_fit_model_name <- paste(task, group_type, hybrid_model_name, sep="_")
  hybrid_full_model_name <- paste(task, group_type, hybrid_model_name, sep="_")
}

hybrid_fit_output_file <- file.path(model_output_dir, paste0(hybrid_fit_model_name, "_fit_output.rds"))
hybrid_model_fit_obj <- readRDS(file = hybrid_fit_output_file)
```

## Extract Behavioral Measures and Parameters

```{r extract-data}
risk.data$sid = as.character(risk.data$sid)

# Extract behavioral data
sids = unname(unlist(lapply(model_fit_obj, function(x) x$subid)))
sids = sids[!unlist(lapply(sids, function(x) x %in% as.character(excluded_sids)))]

behav_data = wave1.raw %>% group_by(sid) %>%
  dplyr::summarise(
    good_play_ratio = last(v_number_goodplay)/last(v_total_gooddeck),
    good_pass_ratio = 1 - good_play_ratio,
    bad_play_ratio = last(v_number_badplay)/last(v_total_baddeck),
    bad_pass_ratio = 1 - bad_play_ratio,
    good_bad_ratio = good_play_ratio/bad_play_ratio,
    good_choice_ratio = (good_play_ratio + bad_pass_ratio)/2,
    money = last(v_currenttotal)
    ) %>% 
  ungroup() %>%
  filter(sid %in% sids)

# Extract RL parameters
rl_param_df <- data.frame(sid = sids)

for (param in model_defaults[[full_model_name]]$params){
  rl_param_df[[param]] <- numeric(length(sids))
}

for (sid_idx in 1:length(sids)) {
  for (param in model_defaults[[full_model_name]]$params) {
      rl_param_df[[param]][sid_idx] <- model_fit_obj[[sid_idx]]$summary_stats$mean[which(model_fit_obj[[sid_idx]]$all_params == param)]
  }
}

# Extract hybrid model parameters
hybrid_sids = unname(unlist(lapply(hybrid_model_fit_obj, function(x) x$subid)))
hybrid_param_df <- data.frame(sid = hybrid_sids)

for (param in model_defaults[[hybrid_full_model_name]]$params){
  hybrid_param_df[[param]] <- numeric(length(hybrid_sids))
}

for (sid_idx in 1:length(hybrid_sids)) {
  for (param in model_defaults[[hybrid_full_model_name]]$params) {
      hybrid_param_df[[param]][sid_idx] <- hybrid_model_fit_obj[[sid_idx]]$summary_stats$median[which(hybrid_model_fit_obj[[sid_idx]]$all_params == param)]
  }
}

# Define variable names for risk data
variable_names = tolower(c("BISB", "BSSS_ES", "BSSS_BS", "BSSS_TS", "BSSS_SD", 
                           "ysr_attentionproblems", "ysr_rulebreak", "ysr_mrulebreak", "ysr_aggressive", "ysr_maggressive", "ysr_conduct", "ysr_mconduct", "ysr_external", "bisb", "ysr_somaticcomplaints", "ysr_internal", "ysr_ocd", "ysr_anxdep", "ysr_withdep", "age", "pubertyage", "pubertaltiming", "pubertaltiming_num",
                           "SID"))

# Convert pubertal timing to numeric
risk.data$pubertaltiming <- factor(risk.data$pubertaltiming, 
                                   levels = c("much earlier", "earlier", 
                                              "at the same time", "later", 
                                              "much later"), 
                                   ordered = TRUE)
risk.data$pubertaltiming_num = as.numeric(risk.data$pubertaltiming)

# Create final datasets by merging
# 1. Behavioral measures
behav_final_df <- behav_data %>%
  inner_join(risk.data[c(variable_names, "bsss8", "male", "race_ethnicity", "grade12", "parent_edu6")], by = "sid") %>%
  inner_join(wave1.raw %>% group_by(sid) %>% dplyr::select(grpid) %>% ungroup() %>% unique(), by = "sid") %>%
  inner_join(districtid_schoolid_df, by = "sid") %>%
  inner_join(groupnumber_df, by = "sid")

# 2. RL model parameters
rl_final_df <- rl_param_df %>%
  inner_join(risk.data[c(variable_names, "bsss8", "male", "race_ethnicity", "grade12", "parent_edu6")], by = "sid") %>%
  inner_join(wave1.raw %>% group_by(sid) %>% dplyr::select(grpid) %>% ungroup() %>% unique(), by = "sid") %>%
  inner_join(districtid_schoolid_df, by = "sid") %>%
  inner_join(groupnumber_df, by = "sid")

# 3. Hybrid model parameters
hybrid_final_df <- hybrid_param_df %>%
  inner_join(risk.data[c(variable_names, "bsss8", "male", "race_ethnicity", "grade12", "parent_edu6")], by = "sid") %>%
  inner_join(wave1.raw %>% group_by(sid) %>% dplyr::select(grpid) %>% ungroup() %>% unique(), by = "sid") %>%
  inner_join(districtid_schoolid_df, by = "sid") %>%
  inner_join(groupnumber_df, by = "sid")

# Create Asian Non-Hispanic indicator for controls
behav_final_df$race_ethnicity_ANH = as.numeric(behav_final_df$race_ethnicity == "asian non hispanic")
rl_final_df$race_ethnicity_ANH = as.numeric(rl_final_df$race_ethnicity == "asian non hispanic")
hybrid_final_df$race_ethnicity_ANH = as.numeric(hybrid_final_df$race_ethnicity == "asian non hispanic")
```

### Fix puberty issue
```{r}
# Convert pubertyage to numeric
convert_pubertyage <- function(puberty_cat) {
  # Convert categorical pubertyage to numeric values
  # Using midpoints or conservative estimates for ranges
  case_when(
    puberty_cat == "=/< 10" ~ 10,    # Using upper bound of 10
    puberty_cat == "11" ~ 11,
    puberty_cat == "12" ~ 12,
    puberty_cat == "13" ~ 13,
    puberty_cat == "14" ~ 14,
    puberty_cat == "15" ~ 15,
    puberty_cat == "16" ~ 16,
    puberty_cat == "=/> 17" ~ 17,    # Using lower bound of 17
    TRUE ~ NA_real_                  # Handle any other cases
  )
}

# Apply conversion and calculate time since puberty
create_puberty_metrics <- function(df) {
  df %>%
    mutate(
      pubertyage_num = convert_pubertyage(pubertyage),
      time_since_puberty = age - pubertyage_num
    )
}

# Apply to the dataframes
behav_final_df <- behav_final_df %>% create_puberty_metrics()
rl_final_df <- rl_final_df %>% create_puberty_metrics()
hybrid_final_df <- hybrid_final_df %>% create_puberty_metrics()
```

## Standardize Variables

```{r standardize-variables}
# Function to standardize all numeric variables in a dataframe
standardize_variables <- function(df) {
  # Identify numeric columns (excluding ID and categorical variables)
  numeric_cols <- sapply(df, is.numeric)
  
  # Exclude specific columns that shouldn't be standardized
  exclude_cols <- c("sid", "grpid", "v_groupnumber", "schoolid", "districtid")
  numeric_cols[names(df) %in% exclude_cols] <- FALSE
  
  # Standardize numeric columns
  df_std <- df
  for (col in names(df)[numeric_cols]) {
    df_std[[col]] <- scale(df[[col]])
  }
  
  return(df_std)
}

# Apply standardization to the dataframes
behav_final_df_std <- standardize_variables(behav_final_df)
rl_final_df_std <- standardize_variables(rl_final_df)
hybrid_final_df_std <- standardize_variables(hybrid_final_df)

# Use standardized dataframes for analyses
behav_final_df <- behav_final_df_std
rl_final_df <- rl_final_df_std
hybrid_final_df <- hybrid_final_df_std
```

## Helper Function for Model Fitting

```{r helper-function}
# Helper function to handle model fitting with fallbacks for singular fits
try_fit_model <- function(formula_str, data) {
  # Try with nested random effects
  formula <- as.formula(formula_str)
  model <- tryCatch(lmer(formula, data = data), error = function(e) NULL)
  
  # If model is NULL or singular, try with just districtid
  if (is.null(model) || isSingular(model)) {
    if (grepl("\\(1\\|districtid/schoolid\\)", formula_str)) {
      new_formula <- gsub("\\(1\\|districtid/schoolid\\)", "(1|districtid)", formula_str)
      model <- tryCatch(lmer(as.formula(new_formula), data = data), error = function(e) NULL)
      
      # If still NULL or singular, fall back to lm
      if (is.null(model) || isSingular(model)) {
        fixed_formula <- gsub("\\s*\\+\\s*\\([^)]+\\)", "", formula_str)
        model <- lm(as.formula(fixed_formula), data = data)
      }
    } else {
      # For any other random effects, fall back to lm
      fixed_formula <- gsub("\\s*\\+\\s*\\([^)]+\\)", "", formula_str)
      model <- lm(as.formula(fixed_formula), data = data)
    }
  }
  
  return(model)
}
```

# Preliminary Data Exploration

## Correlation Analysis

```{r correlation-analysis}
# Define risk outcomes of interest
risk_outcomes <- c("bsss_sd", "ysr_attentionproblems", "ysr_maggressive_t", "ysr_mconduct_t")

# Examine correlations for behavioral measures
behav_corr_vars <- c("good_play_ratio", "money", "bad_play_ratio", "good_bad_ratio", "bad_pass_ratio", "good_choice_ratio", risk_outcomes)
behav_corr <- cor(behav_final_df[behav_corr_vars], use = "complete.obs")

# Examine correlations for RL parameters
rl_params <- model_defaults[[full_model_name]]$params
rl_corr_vars <- c(rl_params, risk_outcomes)
rl_corr <- cor(rl_final_df[rl_corr_vars], use = "complete.obs")

# Examine correlations for hybrid parameters
hybrid_params <- model_defaults[[hybrid_full_model_name]]$params
hybrid_corr_vars <- c(hybrid_params, risk_outcomes)
hybrid_corr <- cor(hybrid_final_df[hybrid_corr_vars], use = "complete.obs")

# Plot correlations
corrplot(behav_corr, method = "color", type = "upper", diag = FALSE, 
         title = "Behavioral Measures", mar = c(0,0,1,0))
corrplot(rl_corr, method = "color", type = "upper", diag = FALSE, 
         title = "RL Parameters", mar = c(0,0,1,0))
corrplot(hybrid_corr, method = "color", type = "upper", diag = FALSE, 
         title = "Hybrid Parameters", mar = c(0,0,1,0))
```

## Age and Pubertal Timing Distribution

```{r development-distribution}
# Examine age distribution
ggplot(risk.data, aes(x = age)) +
  geom_histogram(binwidth = 0.25, fill = "skyblue", color = "black") +
  geom_vline(xintercept = mean(risk.data$age, na.rm = TRUE), color = "red", linetype = "dashed") +
  labs(title = "Age Distribution", x = "Age (years)", y = "Count")

# Examine pubertal timing distribution
ggplot(risk.data, aes(x = pubertaltiming)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Pubertal Timing Distribution", x = "Pubertal Timing", y = "Count")

risk.data %>% 
  create_puberty_metrics() %>%
  ggplot(aes(x = pubertyage_num)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Pubertal Age Distribution", x = "Pubertal Age", y = "Count")

# Examine age by grade
ggplot(risk.data, aes(x = factor(grade12, labels = c("10th Grade", "12th Grade")), y = age)) +
  geom_boxplot(fill = "skyblue") +
  labs(title = "Age Distribution by Grade", x = "Grade", y = "Age (years)")
```

# Model Comparison Analysis

## Function to Compare Model Types

```{r define-comparison-function}
# Function to compare different model types for predicting risk behaviors
compare_models <- function(outcome, df_behav, df_rl, df_hybrid) {
  # Prepare empty results dataframe
  results <- data.frame(
    outcome = character(),
    model_type = character(),
    AIC = numeric(),
    BIC = numeric(),
    r2m = numeric(),
    r2c = numeric(),
    stringsAsFactors = FALSE
  )
  
  # Raw behavioral model
  behav_formula <- paste(outcome, "~ good_bad_ratio + money + (1|schoolid)")
  behav_model <- try_fit_model(behav_formula, df_behav)
  
  # Calculate R2 with handling for lm vs lmer models
  if ("lmerModLmerTest" %in% class(behav_model)) {
    behav_r2 <- r.squaredGLMM(behav_model)
    behav_r2m <- behav_r2[1]
    behav_r2c <- behav_r2[2]
  } else {
    behav_r2m <- summary(behav_model)$r.squared
    behav_r2c <- behav_r2m
  }
  
  results <- rbind(results, data.frame(
    outcome = outcome,
    model_type = "Raw Behavioral",
    AIC = AIC(behav_model),
    BIC = BIC(behav_model),
    r2m = behav_r2m,
    r2c = behav_r2c
  ))
  
  # Motivational parameters - RL model
  motiv_params_rl <- c("gain", "loss")
  motiv_formula_rl <- paste(outcome, "~", paste(motiv_params_rl, collapse = " + "), 
                          "+ (1|schoolid)")
  motiv_model_rl <- try_fit_model(motiv_formula_rl, df_rl)
  
  # Calculate R2
  if ("lmerModLmerTest" %in% class(motiv_model_rl)) {
    motiv_r2_rl <- r.squaredGLMM(motiv_model_rl)
    motiv_r2m_rl <- motiv_r2_rl[1]
    motiv_r2c_rl <- motiv_r2_rl[2]
  } else {
    motiv_r2m_rl <- summary(motiv_model_rl)$r.squared
    motiv_r2c_rl <- motiv_r2m_rl
  }
  
  results <- rbind(results, data.frame(
    outcome = outcome,
    model_type = "Motivational (RL)",
    AIC = AIC(motiv_model_rl),
    BIC = BIC(motiv_model_rl),
    r2m = motiv_r2m_rl,
    r2c = motiv_r2c_rl
  ))
  
  # Motivational parameters - Hybrid model
  motiv_formula_hybrid <- paste(outcome, "~", paste(motiv_params_rl, collapse = " + "), 
                              "+ (1|schoolid)")
  motiv_model_hybrid <- try_fit_model(motiv_formula_hybrid, df_hybrid)
  
  # Calculate R2
  if ("lmerModLmerTest" %in% class(motiv_model_hybrid)) {
    motiv_r2_hybrid <- r.squaredGLMM(motiv_model_hybrid)
    motiv_r2m_hybrid <- motiv_r2_hybrid[1]
    motiv_r2c_hybrid <- motiv_r2_hybrid[2]
  } else {
    motiv_r2m_hybrid <- summary(motiv_model_hybrid)$r.squared
    motiv_r2c_hybrid <- motiv_r2m_hybrid
  }
  
  results <- rbind(results, data.frame(
    outcome = outcome,
    model_type = "Motivational (Hybrid)",
    AIC = AIC(motiv_model_hybrid),
    BIC = BIC(motiv_model_hybrid),
    r2m = motiv_r2m_hybrid,
    r2c = motiv_r2c_hybrid
  ))
  
  # Cognitive parameters - RL model
  cognitive_params <- c("update", ifelse("retend" %in% colnames(df_rl), "retend", "decay"))
  if(all(cognitive_params %in% colnames(df_rl))) {
    cog_formula_rl <- paste(outcome, "~", paste(cognitive_params, collapse = " + "), 
                          "+ (1|schoolid)")
    cog_model_rl <- try_fit_model(cog_formula_rl, df_rl)
    
    # Calculate R2
    if ("lmerModLmerTest" %in% class(cog_model_rl)) {
      cog_r2_rl <- r.squaredGLMM(cog_model_rl)
      cog_r2m_rl <- cog_r2_rl[1]
      cog_r2c_rl <- cog_r2_rl[2]
    } else {
      cog_r2m_rl <- summary(cog_model_rl)$r.squared
      cog_r2c_rl <- cog_r2m_rl
    }
    
    results <- rbind(results, data.frame(
      outcome = outcome,
      model_type = "Cognitive (RL)",
      AIC = AIC(cog_model_rl),
      BIC = BIC(cog_model_rl),
      r2m = cog_r2m_rl,
      r2c = cog_r2c_rl
    ))
  }
  
  # Cognitive parameters - Hybrid model
  if(all(cognitive_params %in% colnames(df_hybrid))) {
    cog_formula_hybrid <- paste(outcome, "~", paste(cognitive_params, collapse = " + "), 
                              "+ (1|schoolid)")
    cog_model_hybrid <- try_fit_model(cog_formula_hybrid, df_hybrid)
    
    # Calculate R2
    if ("lmerModLmerTest" %in% class(cog_model_hybrid)) {
      cog_r2_hybrid <- r.squaredGLMM(cog_model_hybrid)
      cog_r2m_hybrid <- cog_r2_hybrid[1]
      cog_r2c_hybrid <- cog_r2_hybrid[2]
    } else {
      cog_r2m_hybrid <- summary(cog_model_hybrid)$r.squared
      cog_r2c_hybrid <- cog_r2m_hybrid
    }
    
    results <- rbind(results, data.frame(
      outcome = outcome,
      model_type = "Cognitive (Hybrid)",
      AIC = AIC(cog_model_hybrid),
      BIC = BIC(cog_model_hybrid),
      r2m = cog_r2m_hybrid,
      r2c = cog_r2c_hybrid
    ))
  }
  
  # DDM parameters
  ddm_params <- c("boundary", "tau", "beta")
  available_ddm <- ddm_params[ddm_params %in% colnames(df_hybrid)]
  
  if(length(available_ddm) > 0) {
    ddm_formula <- paste(outcome, "~", paste(available_ddm, collapse = " + "), 
                       "+ (1|schoolid)")
    ddm_model <- try_fit_model(ddm_formula, df_hybrid)
    
    # Calculate R2
    if ("lmerModLmerTest" %in% class(ddm_model)) {
      ddm_r2 <- r.squaredGLMM(ddm_model)
      ddm_r2m <- ddm_r2[1]
      ddm_r2c <- ddm_r2[2]
    } else {
      ddm_r2m <- summary(ddm_model)$r.squared
      ddm_r2c <- ddm_r2m
    }
    
    results <- rbind(results, data.frame(
      outcome = outcome,
      model_type = "DDM Parameters",
      AIC = AIC(ddm_model),
      BIC = BIC(ddm_model),
      r2m = ddm_r2m,
      r2c = ddm_r2c
    ))
  }
  
  # Combined motivational and cognitive - RL model
  combined_params_rl <- c(motiv_params_rl, cognitive_params)
  available_combined_rl <- combined_params_rl[combined_params_rl %in% colnames(df_rl)]
  
  if(length(available_combined_rl) > 0) {
    combined_formula_rl <- paste(outcome, "~", paste(available_combined_rl, collapse = " + "), 
                               "+ (1|schoolid)")
    combined_model_rl <- try_fit_model(combined_formula_rl, df_rl)
    
    # Calculate R2
    if ("lmerModLmerTest" %in% class(combined_model_rl)) {
      combined_r2_rl <- r.squaredGLMM(combined_model_rl)
      combined_r2m_rl <- combined_r2_rl[1]
      combined_r2c_rl <- combined_r2_rl[2]
    } else {
      combined_r2m_rl <- summary(combined_model_rl)$r.squared
      combined_r2c_rl <- combined_r2m_rl
    }
    
    results <- rbind(results, data.frame(
      outcome = outcome,
      model_type = "Motiv+Cognitive (RL)",
      AIC = AIC(combined_model_rl),
      BIC = BIC(combined_model_rl),
      r2m = combined_r2m_rl,
      r2c = combined_r2c_rl
    ))
  }
  
  # Combined motivational and cognitive - Hybrid model
  combined_params_hybrid <- c(motiv_params_rl, cognitive_params)
  available_combined_hybrid <- combined_params_hybrid[combined_params_hybrid %in% colnames(df_hybrid)]
  
  if(length(available_combined_hybrid) > 0) {
    combined_formula_hybrid <- paste(outcome, "~", paste(available_combined_hybrid, collapse = " + "), 
                                   "+ (1|schoolid)")
    combined_model_hybrid <- try_fit_model(combined_formula_hybrid, df_hybrid)
    
    # Calculate R2
    if ("lmerModLmerTest" %in% class(combined_model_hybrid)) {
      combined_r2_hybrid <- r.squaredGLMM(combined_model_hybrid)
      combined_r2m_hybrid <- combined_r2_hybrid[1]
      combined_r2c_hybrid <- combined_r2_hybrid[2]
    } else {
      combined_r2m_hybrid <- summary(combined_model_hybrid)$r.squared
      combined_r2c_hybrid <- combined_r2m_hybrid
    }
    
    results <- rbind(results, data.frame(
      outcome = outcome,
      model_type = "Motiv+Cognitive (Hybrid)",
      AIC = AIC(combined_model_hybrid),
      BIC = BIC(combined_model_hybrid),
      r2m = combined_r2m_hybrid,
      r2c = combined_r2c_hybrid
    ))
  }
  
  return(results)
}
```

## Compare Models for Each Risk Outcome

```{r model-comparison}
# Run comparison for each risk outcome
all_comparisons <- data.frame()

for (outcome in risk_outcomes) {
  comparison <- compare_models(outcome, behav_final_df, rl_final_df, hybrid_final_df)
  all_comparisons <- rbind(all_comparisons, comparison)
}

# Display comparison results
kable(all_comparisons, caption = "Model Comparison Results") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize comparison
ggplot(all_comparisons, aes(x = model_type, y = r2m, fill = model_type)) +
  geom_bar(stat = "identity") +
  facet_wrap(~outcome, scales = "free_y") +
  labs(title = "Variance Explained by Different Model Types",
       x = "Model Type", y = "Marginal R²") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Gender Differences Analysis

## Parameter Group Analysis by Gender

```{r parameter-groups}
# Define parameter groups for conceptual organization
evidence_params <- c("drift_con", "con")
response_params <- c("tau", "beta", "boundary")
reward_params <- c("gain", "loss")
update_params <- c("update", ifelse("retend" %in% colnames(rl_final_df), "retend", "decay"))

# Function to analyze gender differences for parameter groups
analyze_gender_differences <- function(outcome, df) {
  # Evidence accumulation parameters
  if (all(evidence_params %in% colnames(df))) {
    evidence_formula <- paste(outcome, "~", 
                            paste(paste0(evidence_params, "*male"), collapse = " + "), 
                            "+ (1|schoolid)")
    evidence_model <- try_fit_model(evidence_formula, df)
  } else {
    evidence_model <- NULL
  }
  
  # Response caution parameters
  if (all(response_params %in% colnames(df))) {
    response_formula <- paste(outcome, "~", 
                            paste(paste0(response_params, "*male"), collapse = " + "), 
                            "+ (1|schoolid)")
    response_model <- try_fit_model(response_formula, df)
  } else {
    response_model <- NULL
  }
  
  # Reward learning parameters
  if (all(reward_params %in% colnames(df))) {
    reward_formula <- paste(outcome, "~", 
                          paste(paste0(reward_params, "*male"), collapse = " + "), 
                          "+ (1|schoolid)")
    reward_model <- try_fit_model(reward_formula, df)
  } else {
    reward_model <- NULL
  }
  
  # Experience updating parameters
  if (all(update_params %in% colnames(df))) {
    update_formula <- paste(outcome, "~", 
                          paste(paste0(update_params, "*male"), collapse = " + "), 
                          "+ (1|schoolid)")
    update_model <- try_fit_model(update_formula, df)
  } else {
    update_model <- NULL
  }
  
  return(list(
    outcome = outcome,
    evidence_model = if(exists("evidence_model")) evidence_model else NULL,
    response_model = if(exists("response_model")) response_model else NULL,
    reward_model = if(exists("reward_model")) reward_model else NULL,
    update_model = if(exists("update_model")) update_model else NULL
  ))
}
```

## Run Gender Difference Analysis

```{r gender-analysis}
# Analyze gender differences for each risk outcome
gender_results_behavioral <- list()
gender_results_rl <- list()
gender_results_hybrid <- list()

for (outcome in risk_outcomes) {
  gender_results_behavioral[[outcome]] <- analyze_gender_differences(outcome, behav_final_df)
  gender_results_rl[[outcome]] <- analyze_gender_differences(outcome, rl_final_df)
  gender_results_hybrid[[outcome]] <- analyze_gender_differences(outcome, hybrid_final_df)
}

# Extract significant gender interactions
extract_significant_interactions <- function(model_results, interaction_term = "male") {
  if (is.null(model_results)) return(NULL)
  
  if ("lmerModLmerTest" %in% class(model_results)) {
    coefs <- summary(model_results)$coefficients
  } else {
    coefs <- summary(model_results)$coefficients
    # For lm models, we need different handling
    if (!any(grepl(interaction_term, rownames(coefs)))) return(NULL)
  }
  
  interaction_rows <- grep(paste0(":", interaction_term), rownames(coefs))
  
  if (length(interaction_rows) == 0) return(NULL)
  
  significant_interactions <- data.frame(
    parameter = gsub(paste0(":", interaction_term), "", rownames(coefs)[interaction_rows]),
    estimate = coefs[interaction_rows, "Estimate"],
    std_error = coefs[interaction_rows, "Std. Error"],
    t_value = coefs[interaction_rows, "t value"],
    p_value = ifelse("lmerModLmerTest" %in% class(model_results), 
                     coefs[interaction_rows, "Pr(>|t|)"],
                     coefs[interaction_rows, ifelse("Pr(>|t|)" %in% colnames(coefs), "Pr(>|t|)", 4)]),
    significant = ifelse("lmerModLmerTest" %in% class(model_results), 
                         coefs[interaction_rows, "Pr(>|t|)"] < 0.05,
                         coefs[interaction_rows, ifelse("Pr(>|t|)" %in% colnames(coefs), "Pr(>|t|)", 4)] < 0.05)
  )
  
  return(significant_interactions)
}

# Function to collect significant interactions
collect_significant_interactions <- function(gender_results) {
  significant_gender_interactions <- data.frame()
  
  for (outcome in risk_outcomes) {
    result <- gender_results[[outcome]]
    
    # Reward learning parameters (since this applies to all model types)
    if (!is.null(result$reward_model)) {
      reward_interactions <- extract_significant_interactions(result$reward_model)
      if (!is.null(reward_interactions)) {
        reward_interactions$outcome <- outcome
        reward_interactions$parameter_group <- "Reward Learning"
        significant_gender_interactions <- rbind(significant_gender_interactions, reward_interactions)
      }
    }
    
    # Experience updating parameters
    if (!is.null(result$update_model)) {
      update_interactions <- extract_significant_interactions(result$update_model)
      if (!is.null(update_interactions)) {
        update_interactions$outcome <- outcome
        update_interactions$parameter_group <- "Experience Updating"
        significant_gender_interactions <- rbind(significant_gender_interactions, update_interactions)
      }
    }
    
    # Consistency parameters (Con parameters)
    if (!is.null(result$evidence_model)) {
      evidence_interactions <- extract_significant_interactions(result$evidence_model)
      if (!is.null(evidence_interactions)) {
        evidence_interactions$outcome <- outcome
        evidence_interactions$parameter_group <- "Evidence Consistency"
        significant_gender_interactions <- rbind(significant_gender_interactions, evidence_interactions)
      }
    }
    
    # Response caution parameters (hybrid model only)
    if (!is.null(result$response_model)) {
      response_interactions <- extract_significant_interactions(result$response_model)
      if (!is.null(response_interactions)) {
        response_interactions$outcome <- outcome
        response_interactions$parameter_group <- "Response Caution/Other"
        significant_gender_interactions <- rbind(significant_gender_interactions, response_interactions)
      }
    }
  }
  
  return(significant_gender_interactions)
}

# Collect significant interactions for each model type
significant_gender_interactions_rl <- collect_significant_interactions(gender_results_rl)
significant_gender_interactions_hybrid <- collect_significant_interactions(gender_results_hybrid)

# Analyze behavioral measures for gender differences
analyze_behav_gender_differences <- function(outcome, df) {
  behav_formula <- paste(outcome, "~", 
                        paste(paste0(c("good_play_ratio", "money", "bad_play_ratio", "good_bad_ratio", "bad_pass_ratio", "good_choice_ratio"), "*male"), collapse = " + "), 
                        "+ (1|schoolid)")
  behav_model <- try_fit_model(behav_formula, df)
  
  return(list(outcome = outcome, behav_model = behav_model))
}

# Collect behavioral gender differences
behav_gender_results <- list()
for (outcome in risk_outcomes) {
  behav_gender_results[[outcome]] <- analyze_behav_gender_differences(outcome, behav_final_df)
}

significant_gender_interactions_behav <- data.frame()
for (outcome in risk_outcomes) {
  result <- behav_gender_results[[outcome]]
  
  behav_interactions <- extract_significant_interactions(result$behav_model)
  if (!is.null(behav_interactions)) {
    behav_interactions$outcome <- outcome
    behav_interactions$parameter_group <- "Behavioral Measures"
    significant_gender_interactions_behav <- rbind(significant_gender_interactions_behav, behav_interactions)
  }
}

# Display significant gender interactions
cat("\n### Significant Gender Interactions for Behavioral Measures\n")
if (nrow(significant_gender_interactions_behav) > 0) {
  kable(significant_gender_interactions_behav, caption = "Significant Gender Interactions - Behavioral Measures") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
  
  # Visualize significant gender interactions
  ggplot(significant_gender_interactions_behav, 
         aes(x = parameter, y = estimate, fill = outcome)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error), 
                  position = position_dodge(width = 0.9), width = 0.25) +
    labs(title = "Gender Differences in Behavioral Measures",
         subtitle = "Parameter × Male Interactions",
         x = "Parameter", 
         y = "Effect Size") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
} else {
  cat("No significant gender interactions found for behavioral measures.\n")
}

cat("\n### Significant Gender Interactions for RL Parameters\n")
if (nrow(significant_gender_interactions_rl) > 0) {
  kable(significant_gender_interactions_rl, caption = "Significant Gender Interactions - RL Parameters") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
  
  # Visualize significant gender interactions
  ggplot(significant_gender_interactions_rl, 
         aes(x = parameter, y = estimate, fill = outcome)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error), 
                  position = position_dodge(width = 0.9), width = 0.25) +
    facet_wrap(~parameter_group, scales = "free_x") +
    labs(title = "Gender Differences in RL Parameters",
         subtitle = "Parameter × Male Interactions",
         x = "Parameter", 
         y = "Effect Size") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
} else {
  cat("No significant gender interactions found for RL parameters.\n")
}

cat("\n### Significant Gender Interactions for Hybrid Parameters\n")
if (nrow(significant_gender_interactions_hybrid) > 0) {
  kable(significant_gender_interactions_hybrid, caption = "Significant Gender Interactions - Hybrid Parameters") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
  
  # Visualize significant gender interactions
  ggplot(significant_gender_interactions_hybrid, 
         aes(x = parameter, y = estimate, fill = outcome)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error), 
                  position = position_dodge(width = 0.9), width = 0.25) +
    facet_wrap(~parameter_group, scales = "free_x") +
    labs(title = "Gender Differences in Hybrid Parameters",
         subtitle = "Parameter × Male Interactions",
         x = "Parameter", 
         y = "Effect Size") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
} else {
  cat("No significant gender interactions found for hybrid parameters.\n")
}
```

# Developmental Analysis

## Grade and Pubertal Timing Effects on Parameters

# Developmental Analysis section - consolidated approach
```{r developmental-effects-combined}
# Function to analyze developmental effects on parameters
analyze_developmental_effects <- function(param, df) {
  # Grade effect only
  grade_formula <- paste(param, "~ grade12 + (1|schoolid)")
  grade_model <- try_fit_model(grade_formula, df)
  
  # Pubertal timing effect only
  puberty_formula <- paste(param, "~ time_since_puberty + (1|schoolid)")
  puberty_model <- try_fit_model(puberty_formula, df)
  
  # Combined model with both factors
  combined_formula <- paste(param, "~ grade12 + time_since_puberty + (1|schoolid)")
  combined_model <- try_fit_model(combined_formula, df)
  
  # Return results
  return(list(
    parameter = param,
    grade_model = grade_model,
    puberty_model = puberty_model,
    combined_model = combined_model
  ))
}

# Extract significant developmental effects with combined model results
extract_developmental_effects <- function(model_list) {
  result_df <- data.frame(
    parameter = character(),
    grade_effect = numeric(),
    grade_p = numeric(),
    puberty_effect = numeric(),
    puberty_p = numeric(),
    combined_grade_effect = numeric(),
    combined_grade_p = numeric(),
    combined_puberty_effect = numeric(),
    combined_puberty_p = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (param in names(model_list)) {
    models <- model_list[[param]]
    
    # Extract grade effect from separate model
    if ("lmerMod" %in% class(models$grade_model)) {
      grade_coef <- summary(models$grade_model)$coefficients["grade1212th grade", ]
      grade_p_col <- "Pr(>|t|)"
    } else {
      grade_coef <- summary(models$grade_model)$coefficients["grade1212th grade", ]
      grade_p_col <- ifelse("Pr(>|t|)" %in% colnames(summary(models$grade_model)$coefficients), 
                           "Pr(>|t|)", 4)
    }
    
    # Extract puberty effect from separate model
    if ("lmerMod" %in% class(models$puberty_model)) {
      puberty_coef <- summary(models$puberty_model)$coefficients["time_since_puberty", ]
      puberty_p_col <- "Pr(>|t|)"
    } else {
      puberty_coef <- summary(models$puberty_model)$coefficients["time_since_puberty", ]
      puberty_p_col <- ifelse("Pr(>|t|)" %in% colnames(summary(models$puberty_model)$coefficients), 
                             "Pr(>|t|)", 4)
    }
    
    # Extract combined model effects
    if ("lmerMod" %in% class(models$combined_model)) {
      combined_coefs <- summary(models$combined_model)$coefficients
      combined_grade_coef <- combined_coefs["grade1212th grade", ]
      combined_puberty_coef <- combined_coefs["time_since_puberty", ]
      combined_p_col <- "Pr(>|t|)"
    } else {
      combined_coefs <- summary(models$combined_model)$coefficients
      combined_grade_coef <- combined_coefs["grade1212th grade", ]
      combined_puberty_coef <- combined_coefs["time_since_puberty", ]
      combined_p_col <- ifelse("Pr(>|t|)" %in% colnames(combined_coefs), 
                              "Pr(>|t|)", 4)
    }
    
    result_df <- rbind(result_df, data.frame(
      parameter = param,
      # Effects from separate models
      grade_effect = grade_coef["Estimate"],
      grade_p = grade_coef[grade_p_col],
      puberty_effect = puberty_coef["Estimate"],
      puberty_p = puberty_coef[puberty_p_col],
      # Effects from combined model
      combined_grade_effect = combined_grade_coef["Estimate"],
      combined_grade_p = combined_grade_coef[combined_p_col],
      combined_puberty_effect = combined_puberty_coef["Estimate"],
      combined_puberty_p = combined_puberty_coef[combined_p_col],
      stringsAsFactors = FALSE
    ))
  }
  
  # Add significance flags
  result_df$grade_sig <- result_df$grade_p < 0.05
  result_df$puberty_sig <- result_df$puberty_p < 0.05
  result_df$combined_grade_sig <- result_df$combined_grade_p < 0.05
  result_df$combined_puberty_sig <- result_df$combined_puberty_p < 0.05
  
  return(result_df)
}

# Run analysis for all three model types
# 1. Behavioral measures
dev_results_behav <- list()
for (param in c("good_play_ratio", "money", "bad_play_ratio", "good_choice_ratio", "bad_pass_ratio")) {
  dev_results_behav[[param]] <- analyze_developmental_effects(param, behav_final_df)
}
developmental_effects_behav <- extract_developmental_effects(dev_results_behav)

# 2. RL parameters
dev_results_rl <- list()
for (param in model_defaults[[full_model_name]]$params) {
  dev_results_rl[[param]] <- analyze_developmental_effects(param, rl_final_df)
}
developmental_effects_rl <- extract_developmental_effects(dev_results_rl)

# 3. Hybrid parameters
dev_results_hybrid <- list()
for (param in model_defaults[[hybrid_full_model_name]]$params) {
  dev_results_hybrid[[param]] <- analyze_developmental_effects(param, hybrid_final_df)
}
developmental_effects_hybrid <- extract_developmental_effects(dev_results_hybrid)

# Check for multicollinearity between grade and time since puberty
cat("\n### Assessing multicollinearity between developmental measures\n")
cor_dev <- cor(as.numeric(behav_final_df$grade12), behav_final_df$time_since_puberty, use="complete.obs")
print(cor_dev)

# Display results for combined models
cat("\n### Behavioral Metrics - Developmental Effects (Combined Model)\n")
kable(developmental_effects_behav %>% 
      select(parameter, combined_grade_effect, combined_grade_p, combined_grade_sig, 
             combined_puberty_effect, combined_puberty_p, combined_puberty_sig), 
      caption = "Developmental Effects on Behavioral Metrics (Controlling for Both Factors)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

cat("\n### RL Parameters - Developmental Effects (Combined Model)\n")
kable(developmental_effects_rl %>% 
      select(parameter, combined_grade_effect, combined_grade_p, combined_grade_sig, 
             combined_puberty_effect, combined_puberty_p, combined_puberty_sig), 
      caption = "Developmental Effects on RL Parameters (Controlling for Both Factors)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

cat("\n### Hybrid Parameters - Developmental Effects (Combined Model)\n")
kable(developmental_effects_hybrid %>% 
      select(parameter, combined_grade_effect, combined_grade_p, combined_grade_sig, 
             combined_puberty_effect, combined_puberty_p, combined_puberty_sig), 
      caption = "Developmental Effects on Hybrid Parameters (Controlling for Both Factors)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create a unified plot showing the unique contributions from the combined model
# Create parameter grouping for better organization
parameter_grouping <- function(param_name) {
  if (param_name %in% c("good_play_ratio", "money", "bad_play_ratio", "good_choice_ratio", "bad_pass_ratio")) {
    return("Behavioral Performance")
  } else if (param_name %in% c("boundary", "tau", "beta")) {
    return("DDM Parameters")
  } else if (param_name %in% c("gain", "loss")) {
    return("Motivation Parameters")
  } else if (param_name %in% c("update", ifelse("retend" %in% colnames(rl_final_df), "retend", "decay"))) {
    return("Cognitive Parameters")
  } else if (param_name %in% c("con", "drift_con")) {
    return("Consistency Parameters")
  } else {
    return("Other Parameters")
  }
}

# Define a parameter display order (for within-group sorting)
parameter_order <- c(
  # Behavioral
  "good_play_ratio", "good_choice_ratio", "bad_play_ratio", "money", "bad_pass_ratio",
  # DDM
  "boundary", "tau", "beta",
  # Motivation
  "gain", "loss",
  # Cognitive
  "update", ifelse("retend" %in% colnames(rl_final_df), "retend", "decay"),
  # Con
  "drift_con", "con"
)

# Create data for plotting individual models (non-combined)
dev_plot_data_individual <- bind_rows(
  developmental_effects_behav %>% 
    select(parameter, grade_effect, grade_sig, puberty_effect, puberty_sig) %>%
    mutate(model_type = "Behavioral"),
  developmental_effects_rl %>% 
    select(parameter, grade_effect, grade_sig, puberty_effect, puberty_sig) %>%
    mutate(model_type = "RL"),
  developmental_effects_hybrid %>% 
    select(parameter, grade_effect, grade_sig, puberty_effect, puberty_sig) %>%
    mutate(model_type = "Hybrid")
) %>%
  pivot_longer(cols = c(grade_effect, puberty_effect),
               names_to = "effect_type",
               values_to = "effect_size") %>%
  mutate(
    significance = case_when(
      effect_type == "grade_effect" & grade_sig ~ "Significant",
      effect_type == "puberty_effect" & puberty_sig ~ "Significant",
      TRUE ~ "Non-significant"
    ),
    effect_type = case_when(
      effect_type == "grade_effect" ~ "Grade (12th vs 10th)",
      effect_type == "puberty_effect" ~ "Time Since Puberty",
      TRUE ~ effect_type
    ),
    param_group = sapply(parameter, parameter_grouping),
    # Create an ordering for parameters within groups
    parameter = factor(parameter, levels = parameter_order)
  )

# Create data for plotting combined models
dev_plot_data_combined <- bind_rows(
  developmental_effects_behav %>% 
    select(parameter, combined_grade_effect, combined_grade_sig, combined_puberty_effect, combined_puberty_sig) %>%
    mutate(model_type = "Behavioral"),
  developmental_effects_rl %>% 
    select(parameter, combined_grade_effect, combined_grade_sig, combined_puberty_effect, combined_puberty_sig) %>%
    mutate(model_type = "RL"),
  developmental_effects_hybrid %>% 
    select(parameter, combined_grade_effect, combined_grade_sig, combined_puberty_effect, combined_puberty_sig) %>%
    mutate(model_type = "Hybrid")
) %>%
  pivot_longer(cols = c(combined_grade_effect, combined_puberty_effect),
               names_to = "effect_type",
               values_to = "effect_size") %>%
  mutate(
    significance = case_when(
      effect_type == "combined_grade_effect" & combined_grade_sig ~ "Significant",
      effect_type == "combined_puberty_effect" & combined_puberty_sig ~ "Significant",
      TRUE ~ "Non-significant"
    ),
    effect_type = case_when(
      effect_type == "combined_grade_effect" ~ "Grade (12th vs 10th)",
      effect_type == "combined_puberty_effect" ~ "Time Since Puberty",
      TRUE ~ effect_type
    ),
    param_group = sapply(parameter, parameter_grouping),
    # Create an ordering for parameters within groups
    parameter = factor(parameter, levels = parameter_order)
  )

# Define a consistent group order
param_group_order <- c("Behavioral Performance", "DDM Parameters", 
                       "Motivation Parameters", "Cognitive Parameters", "Consistency Parameters", "Other Parameters")

# Plot 1: Individual model effects (Grade and Time Since Puberty fit separately)
ggplot(dev_plot_data_individual, aes(x = parameter, y = effect_size, fill = significance)) +
  geom_bar(stat = "identity") +
  facet_grid(model_type ~ param_group + effect_type, scales = "free_x", space = "free_x",
             labeller = labeller(param_group = label_wrap_gen(width = 15))) +
  labs(title = "Developmental Effects on Parameters",
       subtitle = "Grade and Time Since Puberty in Separate Models",
       x = "Parameter", 
       y = "Effect Size (Standardized)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 9),
        panel.spacing = unit(0.5, "lines")) +
  scale_fill_manual(values = c("Significant" = "darkblue", "Non-significant" = "lightblue"))

# Plot 2: Combined model effects (controlling for other factor)
ggplot(dev_plot_data_combined, aes(x = parameter, y = effect_size, fill = significance)) +
  geom_bar(stat = "identity") +
  facet_grid(model_type ~ param_group + effect_type, scales = "free_x", space = "free_x",
             labeller = labeller(param_group = label_wrap_gen(width = 15))) +
  labs(title = "Developmental Effects on Parameters from Combined Models",
       subtitle = "Effects when Both Grade and Time Since Puberty are Included",
       x = "Parameter", 
       y = "Effect Size (Standardized)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 9),
        panel.spacing = unit(0.5, "lines")) +
  scale_fill_manual(values = c("Significant" = "darkblue", "Non-significant" = "lightblue"))
```

# Parameter-Performance Relationship Analysis

## Parameters Predicting Performance Metrics

```{r parameter-performance}
# Function to analyze how computational parameters predict behavioral performance
analyze_performance_predictors <- function(param_df, behav_df) {
  # Merge parameter and behavioral data
  combined_df <- param_df %>%
    inner_join(behav_df %>% select(sid, good_play_ratio, money, bad_play_ratio, good_bad_ratio, bad_pass_ratio, good_choice_ratio), by = "sid")
  
  # Define performance metrics
  performance_metrics <- c("good_play_ratio", "money", "bad_play_ratio", "good_bad_ratio", "bad_pass_ratio", "good_choice_ratio")
  
  # Define parameter groups
  rl_params <- model_defaults[[full_model_name]]$params
  hybrid_params <- model_defaults[[hybrid_full_model_name]]$params
  
  # Use whichever parameters are available
  available_params <- colnames(param_df)[colnames(param_df) %in% c(rl_params, hybrid_params)]
  
  results <- list()
  
  # For each performance metric, fit a model with all available parameters
  for (metric in performance_metrics) {
    formula_str <- paste(metric, "~", paste(available_params, collapse = " + "), "+ (1|schoolid)")
    model <- try_fit_model(formula_str, combined_df)
    
    # Store model
    results[[metric]] <- model
  }
  
  return(results)
}

# Analyze parameters predicting performance for RL and hybrid models
performance_predictors_rl <- analyze_performance_predictors(rl_final_df, behav_final_df)
performance_predictors_hybrid <- analyze_performance_predictors(hybrid_final_df, behav_final_df)

# Function to summarize significant predictors
summarize_performance_predictors <- function(model_list) {
  summary_df <- data.frame(
    performance_metric = character(),
    parameter = character(),
    estimate = numeric(),
    p_value = numeric(),
    significant = logical(),
    stringsAsFactors = FALSE
  )
  
  for (metric in names(model_list)) {
    model <- model_list[[metric]]
    
    if ("lmerMod" %in% class(model)) {
      coefs <- summary(model)$coefficients
      intercept_row <- which(rownames(coefs) == "(Intercept)")
      if (length(intercept_row) > 0) {
        param_rows <- (1:nrow(coefs))[-intercept_row]
        
        for (i in param_rows) {
          summary_df <- rbind(summary_df, data.frame(
            performance_metric = metric,
            parameter = rownames(coefs)[i],
            estimate = coefs[i, "Estimate"],
            p_value = coefs[i, "Pr(>|t|)"],
            significant = coefs[i, "Pr(>|t|)"] < 0.05,
            stringsAsFactors = FALSE
          ))
        }
      }
    } else {
      coefs <- summary(model)$coefficients
      intercept_row <- which(rownames(coefs) == "(Intercept)")
      if (length(intercept_row) > 0) {
        param_rows <- (1:nrow(coefs))[-intercept_row]
        p_col <- ifelse("Pr(>|t|)" %in% colnames(coefs), "Pr(>|t|)", 4)
        
        for (i in param_rows) {
          summary_df <- rbind(summary_df, data.frame(
            performance_metric = metric,
            parameter = rownames(coefs)[i],
            estimate = coefs[i, "Estimate"],
            p_value = coefs[i, p_col],
            significant = coefs[i, p_col] < 0.05,
            stringsAsFactors = FALSE
          ))
        }
      }
    }
  }
  
  return(summary_df)
}

# Summarize predictors
performance_summary_rl <- summarize_performance_predictors(performance_predictors_rl)
performance_summary_hybrid <- summarize_performance_predictors(performance_predictors_hybrid)

# Display significant predictors
cat("\n### RL Parameters Predicting Performance\n")
kable(performance_summary_rl %>% filter(significant), 
      caption = "Significant RL Parameters Predicting Performance") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

cat("\n### Hybrid Parameters Predicting Performance\n")
kable(performance_summary_hybrid %>% filter(significant), 
      caption = "Significant Hybrid Parameters Predicting Performance") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize significant predictors
ggplot(performance_summary_rl %>% filter(significant), 
       aes(x = parameter, y = estimate, fill = performance_metric)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = "How RL Parameters Predict Task Performance",
       x = "Parameter", 
       y = "Effect Size") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(performance_summary_hybrid %>% filter(significant), 
       aes(x = parameter, y = estimate, fill = performance_metric)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = "How Hybrid Parameters Predict Task Performance",
       x = "Parameter", 
       y = "Effect Size") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Developmental Differences in Parameter-Performance Relationship

```{r developmental-parameter-performance}
# Function to analyze developmental interactions in parameter-performance relationships
analyze_developmental_interactions <- function(param_df, behav_df, performance_summary_rl, performance_summary_hybrid) {
  # Merge parameter and behavioral data
  combined_df <- param_df %>%
    inner_join(behav_df %>% select(sid, good_play_ratio, money, bad_pass_ratio, good_choice_ratio, bad_play_ratio), by = "sid")
  
  # Define key performance metrics (limiting to reduce complexity)
  performance_metrics <- c("good_play_ratio", "money", "bad_pass_ratio", "good_choice_ratio", "bad_play_ratio")
  
  # Use parameters that were significant in previous analysis
  significant_params_rl <- performance_summary_rl %>% 
    filter(significant) %>% 
    pull(parameter) %>% 
    unique()
  
  significant_params_hybrid <- performance_summary_hybrid %>% 
    filter(significant) %>% 
    pull(parameter) %>% 
    unique()
  
  # Use whichever parameters are significant and available
  available_params <- colnames(param_df)[colnames(param_df) %in% c(significant_params_rl, significant_params_hybrid)]
  
  results <- list()
  
  # For each performance metric and significant parameter, test for developmental interactions
  for (metric in performance_metrics) {
    for (param in available_params) {
      # Grade interaction
      grade_formula <- paste(metric, "~", param, "*grade12 + (1|schoolid)")
      grade_model <- try_fit_model(grade_formula, combined_df)
      
      # Puberty interaction
      puberty_formula <- paste(metric, "~", param, "*time_since_puberty + (1|schoolid)")
      puberty_model <- try_fit_model(puberty_formula, combined_df)
      
      # Combined model with both developmental factors
      combined_formula <- paste(metric, "~", param, "*grade12 +", param, "*time_since_puberty + (1|schoolid)")
      combined_model <- try_fit_model(combined_formula, combined_df)
      
      # Store models
      results[[paste(metric, param, "grade", sep = "_")]] <- grade_model
      results[[paste(metric, param, "puberty", sep = "_")]] <- puberty_model
      results[[paste(metric, param, "combined", sep = "_")]] <- combined_model
    }
  }
  
  return(results)
}

# Function to extract significant developmental interactions
extract_developmental_interactions <- function(model_list) {
  summary_df <- data.frame(
    model_name = character(),
    interaction_term = character(),
    estimate = numeric(),
    p_value = numeric(),
    significant = logical(),
    stringsAsFactors = FALSE
  )
  
  for (model_name in names(model_list)) {
    model <- model_list[[model_name]]
    
    # Split model name to get components
    parts <- strsplit(model_name, "_")[[1]]
    metric <- parts[1]
    param <- parts[2]
    dev_factor <- parts[3]
    
    # Process based on dev_factor
    if (dev_factor == "grade") {
      interaction_term <- paste0(param, ":grade1212th grade")
      
      # Extract coefficient info
      if ("lmerModLmerTest" %in% class(model)) {
        coefs <- summary(model)$coefficients
        if (interaction_term %in% rownames(coefs)) {
          summary_df <- rbind(summary_df, data.frame(
            model_name = model_name,
            interaction_term = interaction_term,
            estimate = coefs[interaction_term, "Estimate"],
            p_value = coefs[interaction_term, "Pr(>|t|)"],
            significant = coefs[interaction_term, "Pr(>|t|)"] < 0.05,
            stringsAsFactors = FALSE
          ))
        }
      } else {
        coefs <- summary(model)$coefficients
        if (interaction_term %in% rownames(coefs)) {
          p_col <- ifelse("Pr(>|t|)" %in% colnames(coefs), "Pr(>|t|)", 4)
          
          summary_df <- rbind(summary_df, data.frame(
            model_name = model_name,
            interaction_term = interaction_term,
            estimate = coefs[interaction_term, "Estimate"],
            p_value = coefs[interaction_term, p_col],
            significant = coefs[interaction_term, p_col] < 0.05,
            stringsAsFactors = FALSE
          ))
        }
      }
      
    } else if (dev_factor == "puberty") {
      interaction_term <- paste0(param, ":time_since_puberty")
      
      # Extract coefficient info
      if ("lmerModLmerTest" %in% class(model)) {
        coefs <- summary(model)$coefficients
        if (interaction_term %in% rownames(coefs)) {
          summary_df <- rbind(summary_df, data.frame(
            model_name = model_name,
            interaction_term = interaction_term,
            estimate = coefs[interaction_term, "Estimate"],
            p_value = coefs[interaction_term, "Pr(>|t|)"],
            significant = coefs[interaction_term, "Pr(>|t|)"] < 0.05,
            stringsAsFactors = FALSE
          ))
        }
      } else {
        coefs <- summary(model)$coefficients
        if (interaction_term %in% rownames(coefs)) {
          p_col <- ifelse("Pr(>|t|)" %in% colnames(coefs), "Pr(>|t|)", 4)
          
          summary_df <- rbind(summary_df, data.frame(
            model_name = model_name,
            interaction_term = interaction_term,
            estimate = coefs[interaction_term, "Estimate"],
            p_value = coefs[interaction_term, p_col],
            significant = coefs[interaction_term, p_col] < 0.05,
            stringsAsFactors = FALSE
          ))
        }
      }
      
    } else if (dev_factor == "combined") {
      # For combined models, check both interactions
      grade_interaction <- paste0(param, ":grade1212th grade")
      puberty_interaction <- paste0(param, ":time_since_puberty")
      
      # Process both interactions
      if ("lmerModLmerTest" %in% class(model)) {
        coefs <- summary(model)$coefficients
        # Check grade interaction
        if (grade_interaction %in% rownames(coefs)) {
          summary_df <- rbind(summary_df, data.frame(
            model_name = model_name,
            interaction_term = grade_interaction,
            estimate = coefs[grade_interaction, "Estimate"],
            p_value = coefs[grade_interaction, "Pr(>|t|)"],
            significant = coefs[grade_interaction, "Pr(>|t|)"] < 0.05,
            stringsAsFactors = FALSE
          ))
        }
        # Check puberty interaction
        if (puberty_interaction %in% rownames(coefs)) {
          summary_df <- rbind(summary_df, data.frame(
            model_name = model_name,
            interaction_term = puberty_interaction,
            estimate = coefs[puberty_interaction, "Estimate"],
            p_value = coefs[puberty_interaction, "Pr(>|t|)"],
            significant = coefs[puberty_interaction, "Pr(>|t|)"] < 0.05,
            stringsAsFactors = FALSE
          ))
        }
      } else {
        coefs <- summary(model)$coefficients
        p_col <- ifelse("Pr(>|t|)" %in% colnames(coefs), "Pr(>|t|)", 4)
        
        # Check grade interaction
        if (grade_interaction %in% rownames(coefs)) {
          summary_df <- rbind(summary_df, data.frame(
            model_name = model_name,
            interaction_term = grade_interaction,
            estimate = coefs[grade_interaction, "Estimate"],
            p_value = coefs[grade_interaction, p_col],
            significant = coefs[grade_interaction, p_col] < 0.05,
            stringsAsFactors = FALSE
          ))
        }
        # Check puberty interaction
        if (puberty_interaction %in% rownames(coefs)) {
          summary_df <- rbind(summary_df, data.frame(
            model_name = model_name,
            interaction_term = puberty_interaction,
            estimate = coefs[puberty_interaction, "Estimate"],
            p_value = coefs[puberty_interaction, p_col],
            significant = coefs[puberty_interaction, p_col] < 0.05,
            stringsAsFactors = FALSE
          ))
        }
      }
    }
  }
  
  # Add extracted components for easier interpretation
  summary_df <- summary_df %>%
    mutate(
      metric = sapply(strsplit(model_name, "_"), function(x) x[1]),
      parameter = gsub(":grade1212th grade|:time_since_puberty", "", interaction_term),
      dev_factor = case_when(
        grepl(":grade", interaction_term) ~ "Grade",
        grepl(":time_since_puberty", interaction_term) ~ "Time Since Puberty",
        TRUE ~ "Unknown"
      )
    )
  
  return(summary_df)
}

# Call analyze function with required data
dev_interactions_rl <- analyze_developmental_interactions(rl_final_df, behav_final_df, 
                                                         performance_summary_rl, performance_summary_hybrid)
dev_interactions_hybrid <- analyze_developmental_interactions(hybrid_final_df, behav_final_df, 
                                                            performance_summary_rl, performance_summary_hybrid)

# Extract significant interactions
dev_interactions_summary_rl <- extract_developmental_interactions(dev_interactions_rl)
dev_interactions_summary_hybrid <- extract_developmental_interactions(dev_interactions_hybrid)

# Display significant interactions
cat("\n### Developmental Interactions in RL Parameter-Performance Relationships\n")
if (nrow(dev_interactions_summary_rl %>% filter(significant)) > 0) {
  kable(dev_interactions_summary_rl %>% filter(significant) %>% select(metric, parameter, dev_factor, estimate, p_value), 
        caption = "Significant Developmental Interactions - RL Parameters") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  cat("No significant developmental interactions found for RL parameters.\n")
}

cat("\n### Developmental Interactions in Hybrid Parameter-Performance Relationships\n")
if (nrow(dev_interactions_summary_hybrid %>% filter(significant)) > 0) {
  kable(dev_interactions_summary_hybrid %>% filter(significant) %>% select(metric, parameter, dev_factor, estimate, p_value), 
        caption = "Significant Developmental Interactions - Hybrid Parameters") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  cat("No significant developmental interactions found for hybrid parameters.\n")
}

# Visualize significant interactions
if (nrow(dev_interactions_summary_rl %>% filter(significant)) > 0) {
  ggplot(dev_interactions_summary_rl %>% filter(significant), 
         aes(x = parameter, y = estimate, fill = metric)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    facet_wrap(~dev_factor, scales = "free_x") +
    labs(title = "Developmental Differences in RL Parameter-Performance Relationships",
         x = "Parameter", 
         y = "Interaction Effect Size") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

if (nrow(dev_interactions_summary_hybrid %>% filter(significant)) > 0) {
  ggplot(dev_interactions_summary_hybrid %>% filter(significant), 
         aes(x = parameter, y = estimate, fill = metric)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    facet_wrap(~dev_factor, scales = "free_x") +
    labs(title = "Developmental Differences in Hybrid Parameter-Performance Relationships",
         x = "Parameter", 
         y = "Interaction Effect Size") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```


## Gender Differences in Parameter-Performance Relationship

```{r gender-parameter-performance}
# Function to analyze gender interactions in parameter-performance relationships
analyze_gender_interactions <- function(param_df, behav_df, performance_summary_rl, performance_summary_hybrid) {
  # Merge parameter and behavioral data
  combined_df <- param_df %>%
    inner_join(behav_df %>% select(sid, good_play_ratio, money, bad_pass_ratio, good_choice_ratio, bad_play_ratio), by = "sid")
  
  # Define key performance metrics (limiting to reduce complexity)
  performance_metrics <- c("good_play_ratio", "money", "bad_pass_ratio", "good_choice_ratio", "bad_play_ratio")
  
  # Use parameters that were significant in previous analysis
  significant_params_rl <- performance_summary_rl %>% 
    filter(significant) %>% 
    pull(parameter) %>% 
    unique()
  
  significant_params_hybrid <- performance_summary_hybrid %>% 
    filter(significant) %>% 
    pull(parameter) %>% 
    unique()
  
  # Use whichever parameters are significant and available
  available_params <- colnames(param_df)[colnames(param_df) %in% c(significant_params_rl, significant_params_hybrid)]
  
  results <- list()
  
  # For each performance metric and significant parameter, test for gender interactions
  for (metric in performance_metrics) {
    for (param in available_params) {
      # Gender interaction
      gender_formula <- paste(metric, "~", param, "*male + (1|schoolid)")
      gender_model <- try_fit_model(gender_formula, combined_df)
      
      # Store model
      results[[paste(metric, param, sep = "_")]] <- gender_model
    }
  }
  
  return(results)
}

# Function to extract significant gender interactions
extract_gender_interactions <- function(model_list) {
  summary_df <- data.frame(
    model_name = character(),
    interaction_term = character(),
    estimate = numeric(),
    p_value = numeric(),
    significant = logical(),
    stringsAsFactors = FALSE
  )
  
  for (model_name in names(model_list)) {
    model <- model_list[[model_name]]
    
    # Split model name to get components
    parts <- strsplit(model_name, "_")[[1]]
    metric <- parts[1]
    param <- parts[2]
    
    # Identify the interaction term to look for
    interaction_term <- paste0(param, ":male")
    
    if ("lmerModLmerTest" %in% class(model)) {
      coefs <- summary(model)$coefficients
      if (interaction_term %in% rownames(coefs)) {
        summary_df <- rbind(summary_df, data.frame(
          model_name = model_name,
          interaction_term = interaction_term,
          estimate = coefs[interaction_term, "Estimate"],
          p_value = coefs[interaction_term, "Pr(>|t|)"],
          significant = coefs[interaction_term, "Pr(>|t|)"] < 0.05,
          stringsAsFactors = FALSE
        ))
      }
    } else {
      coefs <- summary(model)$coefficients
      if (interaction_term %in% rownames(coefs)) {
        p_col <- ifelse("Pr(>|t|)" %in% colnames(coefs), "Pr(>|t|)", 4)
        
        summary_df <- rbind(summary_df, data.frame(
          model_name = model_name,
          interaction_term = interaction_term,
          estimate = coefs[interaction_term, "Estimate"],
          p_value = coefs[interaction_term, p_col],
          significant = coefs[interaction_term, p_col] < 0.05,
          stringsAsFactors = FALSE
        ))
      }
    }
  }
  
  # Add extracted components for easier interpretation
  summary_df <- summary_df %>%
    mutate(
      metric = sapply(strsplit(model_name, "_"), function(x) x[1]),
      parameter = gsub(":male", "", interaction_term)
    )
  
  return(summary_df)
}

# Call analyze function with required data
gender_interactions_rl <- analyze_gender_interactions(rl_final_df, behav_final_df,
                                                    performance_summary_rl, performance_summary_hybrid)
gender_interactions_hybrid <- analyze_gender_interactions(hybrid_final_df, behav_final_df,
                                                        performance_summary_rl, performance_summary_hybrid)

# Extract significant interactions
gender_interactions_summary_rl <- extract_gender_interactions(gender_interactions_rl)
gender_interactions_summary_hybrid <- extract_gender_interactions(gender_interactions_hybrid)

# Display significant interactions
cat("\n### Gender Interactions in RL Parameter-Performance Relationships\n")
if (nrow(gender_interactions_summary_rl %>% filter(significant)) > 0) {
  kable(gender_interactions_summary_rl %>% filter(significant) %>% select(metric, parameter, estimate, p_value), 
        caption = "Significant Gender Interactions - RL Parameters") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  cat("No significant gender interactions found for RL parameters.\n")
}

cat("\n### Gender Interactions in Hybrid Parameter-Performance Relationships\n")
if (nrow(gender_interactions_summary_hybrid %>% filter(significant)) > 0) {
  kable(gender_interactions_summary_hybrid %>% filter(significant) %>% select(metric, parameter, estimate, p_value), 
        caption = "Significant Gender Interactions - Hybrid Parameters") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  cat("No significant gender interactions found for hybrid parameters.\n")
}

# Visualize significant interactions
if (nrow(gender_interactions_summary_rl %>% filter(significant)) > 0) {
  ggplot(gender_interactions_summary_rl %>% filter(significant), 
         aes(x = parameter, y = estimate, fill = metric)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    labs(title = "Gender Differences in RL Parameter-Performance Relationships",
         x = "Parameter", 
         y = "Interaction Effect Size") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

if (nrow(gender_interactions_summary_hybrid %>% filter(significant)) > 0) {
  ggplot(gender_interactions_summary_hybrid %>% filter(significant), 
         aes(x = parameter, y = estimate, fill = metric)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    labs(title = "Gender Differences in Hybrid Parameter-Performance Relationships",
         x = "Parameter", 
         y = "Interaction Effect Size") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```

# Combined Model Analysis

## Identify Key Predictive Parameters

```{r key-parameters}
# Function to identify key predictive parameters for each risk outcome
identify_key_parameters <- function(outcome, df, model_name = NULL, param_list = NULL) {
  # Get appropriate parameters based on model type
  if (!is.null(param_list)) {
    # Use provided parameter list (for behavioral measures)
    all_params <- param_list
  } else if (!is.null(model_name)) {
    # Use model defaults (for RL and hybrid models)
    all_params <- colnames(df)[colnames(df) %in% model_defaults[[model_name]]$params]
  } else {
    # Fallback - use all numeric columns except certain ones
    numeric_cols <- sapply(df, is.numeric)
    exclude_cols <- c("sid", "grpid", "v_groupnumber", "male", "grade12", "time_since_puberty", 
                      risk_outcomes)
    numeric_cols[names(df) %in% exclude_cols] <- FALSE
    all_params <- names(df)[numeric_cols]
  }
  
  # Full model with parameters
  full_formula <- paste(outcome, "~", paste(all_params, collapse = " + "), 
                       "+ (1|schoolid)")
  full_model <- try_fit_model(full_formula, df)
  
  # Extract coefficients and p-values
  if ("lmerModLmerTest" %in% class(full_model)) {
    coefs <- summary(full_model)$coefficients
    p_col <- "Pr(>|t|)"
  } else {
    coefs <- summary(full_model)$coefficients
    p_col <- ifelse("Pr(>|t|)" %in% colnames(coefs), "Pr(>|t|)", 4)
  }
  
  param_rows <- match(all_params, rownames(coefs))
  param_rows <- param_rows[!is.na(param_rows)]
  
  # Identify significant parameters (p < 0.10)
  significant_params <- rownames(coefs)[param_rows[coefs[param_rows, p_col] < 0.10]]
  
  # Return results
  return(list(
    outcome = outcome,
    full_model = full_model,
    significant_params = significant_params,
    all_coefficients = coefs[param_rows, ]
  ))
}

# Define behavioral parameters
behav_params <- c("good_play_ratio", "money", "bad_play_ratio", "good_bad_ratio", "bad_pass_ratio", "good_choice_ratio")

# Identify key parameters for each risk outcome and model type
key_params_behav <- list()
key_params_rl <- list()
key_params_hybrid <- list()

for (outcome in risk_outcomes) {
  # Behavioral model
  key_params_behav[[outcome]] <- identify_key_parameters(outcome, behav_final_df, param_list = behav_params)
  
  # RL model
  key_params_rl[[outcome]] <- identify_key_parameters(outcome, rl_final_df, model_name = full_model_name)
  
  # Hybrid model
  key_params_hybrid[[outcome]] <- identify_key_parameters(outcome, hybrid_final_df, model_name = hybrid_full_model_name)
}

# Create summary of key parameters for each model type
create_key_params_summary <- function(key_params_results) {
  summary_df <- data.frame(
    outcome = character(),
    significant_parameters = character(),
    stringsAsFactors = FALSE
  )
  
  for (outcome in risk_outcomes) {
    summary_df <- rbind(summary_df, data.frame(
      outcome = outcome,
      significant_parameters = paste(key_params_results[[outcome]]$significant_params, collapse = ", "),
      stringsAsFactors = FALSE
    ))
  }
  
  return(summary_df)
}

key_params_summary_behav <- create_key_params_summary(key_params_behav)
key_params_summary_rl <- create_key_params_summary(key_params_rl)
key_params_summary_hybrid <- create_key_params_summary(key_params_hybrid)

# Display key parameters for each model type
cat("\n### Key Predictive Parameters - Behavioral Measures\n")
kable(key_params_summary_behav, caption = "Key Predictive Behavioral Measures by Risk Outcome") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

cat("\n### Key Predictive Parameters - RL Model\n")
kable(key_params_summary_rl, caption = "Key Predictive RL Parameters by Risk Outcome") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

cat("\n### Key Predictive Parameters - Hybrid Model\n")
kable(key_params_summary_hybrid, caption = "Key Predictive Hybrid Parameters by Risk Outcome") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

## Final Models with Gender and Developmental Factors

```{r final-models}
# Function to create focused model for each outcome
create_focused_model <- function(outcome, key_params, df, gender_interactions, model_type) {
  # Base formula with key parameters
  base_formula <- paste(outcome, "~", paste(key_params, collapse = " + "))
  
  # Add gender effects for parameters with significant gender interactions
  gender_params <- c()
  for (param in key_params) {
    # Filter the gender interactions based on model type and outcome
    relevant_interactions <- gender_interactions[
      gender_interactions$outcome == outcome & 
      gender_interactions$parameter == param,
    ]
    
    if(nrow(relevant_interactions) > 0) {
      gender_params <- c(gender_params, param)
    }
  }
  
  # Add gender interaction terms
  if(length(gender_params) > 0) {
    gender_formula <- paste(paste0(gender_params, "*male"), collapse = " + ")
    formula_str <- paste(base_formula, "+", gender_formula)
  } else {
    formula_str <- paste(base_formula, "+ male")
  }
  
  # Add developmental factors
  formula_str <- paste(formula_str, "+ grade12 + time_since_puberty")
  
  # Add random effects and controls
  formula_str <- paste(formula_str, "+ v_groupnumber + (1|schoolid)")
  
  # Fit model
  model <- try_fit_model(formula_str, df)
  
  return(list(
    outcome = outcome,
    model_type = model_type,
    formula = formula_str,
    model = model,
    summary = summary(model)
  ))
}

# Create focused models for each risk outcome and model type
focused_models_behav <- list()
focused_models_rl <- list()
focused_models_hybrid <- list()

for (outcome in risk_outcomes) {
  # Behavioral model
  behav_key_params <- key_params_behav[[outcome]]$significant_params
  if(length(behav_key_params) > 0) {
    focused_models_behav[[outcome]] <- create_focused_model(
      outcome, behav_key_params, behav_final_df, 
      significant_gender_interactions_behav, "Behavioral"
    )
  }
  
  # RL model
  rl_key_params <- key_params_rl[[outcome]]$significant_params
  if(length(rl_key_params) > 0) {
    focused_models_rl[[outcome]] <- create_focused_model(
      outcome, rl_key_params, rl_final_df, 
      significant_gender_interactions_rl, "RL"
    )
  }
  
  # Hybrid model
  hybrid_key_params <- key_params_hybrid[[outcome]]$significant_params
  if(length(hybrid_key_params) > 0) {
    focused_models_hybrid[[outcome]] <- create_focused_model(
      outcome, hybrid_key_params, hybrid_final_df, 
      significant_gender_interactions_hybrid, "Hybrid"
    )
  }
}

# Function to display model summaries by model type
display_model_summaries <- function(model_list, type_name) {
  cat(paste0("\n\n# Final Models - ", type_name, "\n"))
  
  if (length(model_list) == 0) {
    cat("No significant parameters found for any risk outcome.\n")
    return()
  }
  
  for (outcome in names(model_list)) {
    cat(paste0("\n## Final ", type_name, " Model for ", outcome, "\n"))
    cat("Formula:", model_list[[outcome]]$formula, "\n\n")
    print(model_list[[outcome]]$summary)
  }
}

# Display model summaries by model type
display_model_summaries(focused_models_behav, "Behavioral")
display_model_summaries(focused_models_rl, "RL")
display_model_summaries(focused_models_hybrid, "Hybrid")

# Function to extract significant predictors from models
extract_significant_predictors <- function(model_list) {
  result_df <- data.frame(
    outcome = character(),
    model_type = character(),
    parameter = character(),
    estimate = numeric(),
    std_error = numeric(),
    t_value = numeric(),
    p_value = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (outcome in names(model_list)) {
    model_info <- model_list[[outcome]]
    model <- model_info$model
    model_type <- model_info$model_type
    
    if ("lmerModLmerTest" %in% class(model)) {
      coefs <- summary(model)$coefficients
      p_col <- "Pr(>|t|)"
    } else {
      coefs <- summary(model)$coefficients
      p_col <- ifelse("Pr(>|t|)" %in% colnames(coefs), "Pr(>|t|)", 4)
    }
    
    # Get all rows except intercept
    pred_rows <- rownames(coefs)[-1]
    
    for (pred in pred_rows) {
      if (coefs[pred, p_col] < 0.05) {
        result_df <- rbind(result_df, data.frame(
          outcome = outcome,
          model_type = model_type,
          parameter = pred,
          estimate = coefs[pred, "Estimate"],
          std_error = coefs[pred, "Std. Error"],
          t_value = coefs[pred, "t value"],
          p_value = coefs[pred, p_col],
          stringsAsFactors = FALSE
        ))
      }
    }
  }
  
  return(result_df)
}

# Extract significant predictors for each model type
significant_predictors_behav <- extract_significant_predictors(focused_models_behav)
significant_predictors_rl <- extract_significant_predictors(focused_models_rl)
significant_predictors_hybrid <- extract_significant_predictors(focused_models_hybrid)

# Combine all significant predictors
all_significant_predictors <- rbind(
  significant_predictors_behav,
  significant_predictors_rl,
  significant_predictors_hybrid
)

# Function to display and visualize significant predictors
display_significant_predictors <- function(pred_df, title_suffix = "") {
  if (nrow(pred_df) > 0) {
    kable(pred_df, caption = paste0("Significant Predictors in Final Models", title_suffix)) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
    
    # Visualize significant predictors
    ggplot(pred_df, aes(x = parameter, y = estimate, fill = outcome)) +
      geom_bar(stat = "identity", position = position_dodge()) +
      geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error), 
                    position = position_dodge(width = 0.9), width = 0.25) +
      labs(title = paste0("Significant Predictors of Risk Behaviors", title_suffix),
           x = "Parameter", 
           y = "Effect Size") +
      facet_wrap(~model_type, scales = "free_x") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
  } else {
    cat(paste0("No significant predictors found in final models", title_suffix, ".\n"))
  }
}

# Display all significant predictors together
cat("\n### All Significant Predictors\n")
display_significant_predictors(all_significant_predictors)

# Display significant predictors by model type
cat("\n### Significant Predictors - Behavioral Models\n")
display_significant_predictors(significant_predictors_behav, " - Behavioral Models")

cat("\n### Significant Predictors - RL Models\n")
display_significant_predictors(significant_predictors_rl, " - RL Models")

cat("\n### Significant Predictors - Hybrid Models\n")
display_significant_predictors(significant_predictors_hybrid, " - Hybrid Models")
```



# Parameter Interpretation

Before discussing the implications, let's clarify the interpretation of the model parameters:

```{r parameter-definitions, echo=FALSE}
parameter_definitions <- data.frame(
  Parameter = c("boundary", "tau", "beta", "drift_con", "gain", "loss", "update", "decay"),
  Type = c("DDM", "DDM", "DDM", "DDM", "RL", "RL", "RL", "RL"),
  Definition = c(
    "Decision threshold - higher values indicate more cautious decision-making requiring more evidence",
    "Non-decision time - cognitive processing time unrelated to the decision process",
    "Response bias - tendency to favor one response option over another",
    "Drift rate consistancy - Influence of learning on drift rate",
    "Reward sensitivity",
    "Punishment sensitivity",
    "Value updating rate - how quickly expected values are updated based on new information",
    "Memory decay rate - how quickly prior information is forgotten"
  )
)

kable(parameter_definitions, caption = "Decision Model Parameter Definitions") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

# Hypothesis-Driven Model Comparison with AICc and FDR Correction
# -------------------------------------------------------------

suppressPackageStartupMessages({
  library(AICcmodavg)
  library(texreg)
  library(kableExtra)
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  library(stringr)
})

#' Visualize parameters for each supported model individually
#' 
#' @param results Results from analyze_hypothesis_outcome
#' @param outcome The risk outcome to visualize
#' @return List of ggplot objects
visualize_supported_models_individually <- function(results, outcome) {
  if (length(results$models) == 0 || nrow(results$supported_models) == 0) {
    return(NULL)
  }
  
  # Get supported models
  supported_model_names <- results$supported_models$Modnames
  
  # Create a list to store plots for each model
  model_plots <- list()
  
  # For each supported model, create a parameter plot
  for (model_name in supported_model_names) {
    # Extract model information
    model_row <- results$supported_models[results$supported_models$Modnames == model_name, ]
    hypothesis <- model_row$Hypothesis
    aicc_weight <- model_row$AICcWt
    
    # Extract parameters from this model
    param_data <- results$param_results[results$param_results$model_name == model_name, ]
    
    if (nrow(param_data) == 0) {
      next
    }
    
    # Create parameter groupings for visualization
    param_data$param_group <- sapply(param_data$parameter, function(param) {
      if (grepl("^gain|^loss", param)) return("Motivation")
      if (grepl("^update|^decay|^retend", param)) return("Learning")
      if (grepl("^boundary|^tau|^beta", param)) return("DDM/Decision")
      if (grepl("^drift_con$", param)) return("Evidence (Hybrid)")
      if (grepl("^con$", param)) return("Evidence (RL)")
      if (grepl("^good_|^bad_|^money", param)) return("Performance")
      if (grepl(":male$", param)) return("Gender Interaction")
      if (grepl("^male$", param)) return("Gender")
      if (grepl("^grade12|^time_since_puberty", param)) return("Developmental")
      return("Other")
    })
    
    # Create cleaner parameter labels
    param_data$param_label <- sapply(param_data$parameter, function(param) {
      # For interactions, format as "Parameter × Gender"
      if (grepl(":male$", param)) {
        base_param <- gsub(":male$", "", param)
        return(paste0(base_param, " × Gender"))
      }
      return(param)
    })
    
    # Order parameter groups
    group_order <- c("Performance", "Motivation", "Learning", "DDM/Decision", 
                     "Evidence (RL)", "Evidence (Hybrid)", "Gender Interaction", 
                     "Gender", "Developmental", "Other")
    param_data$param_group <- factor(param_data$param_group, levels = group_order)
    
    # Create visualization for this model
    p <- ggplot(param_data, 
                aes(x = param_label, y = estimate)) +
      geom_bar(stat = "identity", fill = "steelblue") +
      geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error), 
                    width = 0.25) +
      geom_text(aes(label = ifelse(significant, "*", ""), y = ifelse(estimate >= 0, 
                                                                     estimate + std_error, 
                                                                     estimate - std_error)), 
                vjust = ifelse(param_data$estimate >= 0, -0.5, 1.5)) +
      facet_wrap(~param_group, scales = "free_x") +
      labs(title = paste("Parameter Estimates -", outcome),
           subtitle = paste0(hypothesis, " Hypothesis (AICc weight = ", round(aicc_weight, 3), ")"),
           x = "Parameter", 
           y = "Standardized Estimate") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
    
    model_plots[[model_name]] <- p
  }
  
  return(model_plots)
}

#' Build hypothesis-driven models for each outcome and model type
#' 
#' @param outcome The risk outcome variable name
#' @param df The dataframe containing the data
#' @param model_type String identifying the model type ("behavioral", "rl", "hybrid")
#' @return List containing models and their formulas
build_hypothesis_models <- function(outcome, df, model_type) {
  # Initialize model list and formula tracking
  models <- list()
  model_formulas <- list()
  
  # Base formula components
  random_effects <- "(1|schoolid)"
  
  # 1. Behavioral Models
  if (model_type == "behavioral") {
    # Define hypotheses
    hypotheses <- list(
      individual_play = "good_play_ratio",
      individual_choice = "good_choice_ratio",
      money_only = "money",
      play_behavior = "good_play_ratio + bad_play_ratio",
      choice_performance = "good_choice_ratio + bad_play_ratio",
      full_performance = "good_choice_ratio + bad_play_ratio + money"
    )
  }
  
  # 2. RL Models
  else if (model_type == "rl") {
    # Check which parameters are available in the model
    available_params <- colnames(df)[colnames(df) %in% model_defaults[[full_model_name]]$params]
    
    # Check for update/decay parameters
    cognitive_params <- available_params[available_params %in% c("update", "decay", "retend")]
    cognitive_string <- paste(cognitive_params, collapse = " + ")
    
    # Define hypotheses
    hypotheses <- list(
      motivation = "gain + loss",
      cognitive = cognitive_string,
      motivation_cognitive = paste("gain + loss +", cognitive_string),
      full_rl = paste(available_params, collapse = " + ")
    )
  }
  
  # 3. Hybrid Models
  else if (model_type == "hybrid") {
    # Check which parameters are available in the model
    available_params <- colnames(df)[colnames(df) %in% model_defaults[[hybrid_full_model_name]]$params]
    
    # Identify parameter groups
    boundary_params <- available_params[grepl("^boundary", available_params)]
    boundary_string <- paste(boundary_params, collapse = " + ")
    
    ddm_params <- available_params[available_params %in% c("boundary", "tau", "beta", "boundary1", "tau1")]
    ddm_string <- paste(ddm_params, collapse = " + ")
    
    cognitive_params <- available_params[available_params %in% c("update", "decay", "retend")]
    cognitive_string <- paste(cognitive_params, collapse = " + ")
    
    # Define hypotheses
    hypotheses <- list(
      boundary_only = boundary_string,
      full_ddm = ddm_string,
      motivation = "gain + loss",
      cognitive = cognitive_string,
      ddm_motivation = paste(ddm_string, "+ gain + loss"),
      ddm_cognitive = paste(ddm_string, "+", cognitive_string),
      full_hybrid = paste(available_params, collapse = " + ")
    )
  }
  
  # Build models for each hypothesis
  for (hyp_name in names(hypotheses)) {
    param_string <- hypotheses[[hyp_name]]
    
    # Skip if parameter string is empty
    if (param_string == "") next
    
    # 1. Basic model (no controls)
    formula_str <- paste(outcome, "~", param_string, "+", random_effects)
    model_name <- paste(outcome, model_type, hyp_name, "basic", sep="_")
    models[[model_name]] <- try_fit_model(formula_str, df)
    model_formulas[[model_name]] <- formula_str
    
    # 2. With gender as control
    formula_str <- paste(outcome, "~", param_string, "+ male +", random_effects)
    model_name <- paste(outcome, model_type, hyp_name, "gender", sep="_")
    models[[model_name]] <- try_fit_model(formula_str, df)
    model_formulas[[model_name]] <- formula_str
    
    # 3. With gender interactions for motivation parameters (only for relevant hypotheses)
    if (grepl("gain|loss", param_string)) {
      # Create formula with gender interactions only for motivation parameters
      other_params <- gsub("gain \\+ loss", "", param_string)
      if (other_params != "") {
        formula_str <- paste(outcome, "~ (gain + loss) * male +", other_params, "+", random_effects)
      } else {
        formula_str <- paste(outcome, "~ (gain + loss) * male +", random_effects)
      }
      model_name <- paste(outcome, model_type, hyp_name, "gender_int", sep="_")
      models[[model_name]] <- try_fit_model(formula_str, df)
      model_formulas[[model_name]] <- formula_str
    }
    
    # 4. With developmental controls
    formula_str <- paste(outcome, "~", param_string, "+ grade12 + time_since_puberty +", random_effects)
    model_name <- paste(outcome, model_type, hyp_name, "dev", sep="_")
    models[[model_name]] <- try_fit_model(formula_str, df)
    model_formulas[[model_name]] <- formula_str
    
    # 5. Full controls (gender + developmental)
    formula_str <- paste(outcome, "~", param_string, "+ male + grade12 + time_since_puberty +", random_effects)
    model_name <- paste(outcome, model_type, hyp_name, "full", sep="_")
    models[[model_name]] <- try_fit_model(formula_str, df)
    model_formulas[[model_name]] <- formula_str
    
    # 6. Full controls with gender interaction for motivation
    if (grepl("gain|loss", param_string)) {
      # Create formula with gender interactions only for motivation parameters
      other_params <- gsub("gain \\+ loss", "", param_string)
      if (other_params != "") {
        formula_str <- paste(outcome, "~ (gain + loss) * male +", other_params, 
                             "+ grade12 + time_since_puberty +", random_effects)
      } else {
        formula_str <- paste(outcome, "~ (gain + loss) * male", 
                             "+ grade12 + time_since_puberty +", random_effects)
      }
      model_name <- paste(outcome, model_type, hyp_name, "full_gender_int", sep="_")
      models[[model_name]] <- try_fit_model(formula_str, df)
      model_formulas[[model_name]] <- formula_str
    }
  }
  
  # Return the list of models and their formulas
  return(list(models = models, formulas = model_formulas))
}

#' Compare models and extract parameter information with FDR correction
#' 
#' @param outcome The risk outcome variable name
#' @param df The dataframe containing the data
#' @param model_type String identifying the model type ("behavioral", "rl", "hybrid")
#' @return List containing model comparison and parameter results
analyze_hypothesis_outcome <- function(outcome, df, model_type) {
  # Build models
  model_results <- build_hypothesis_models(outcome, df, model_type)
  models <- model_results$models
  model_formulas <- model_results$formulas
  
  # Skip if no models were successfully built
  if (length(models) == 0) {
    return(list(
      outcome = outcome,
      model_type = model_type,
      models = list(),
      aicc_results = data.frame(),
      param_results = data.frame(),
      formulas = list(),
      supported_models = data.frame()
    ))
  }
  
  # Convert model names to vector for AICc comparison
  model_names <- names(models)
  
  # Compare models using AICc
  aictab_input <- models
  aicc_result <- aictab(cand.set = aictab_input, modnames = model_names)
  aicc_df <- as.data.frame(aicc_result)
  
  # Add model formulas to AICc table for reference
  aicc_df$Formula <- unlist(model_formulas[match(aicc_df$Modnames, model_names)])
  
  # Extract hypothesis names from model names
  aicc_df$Hypothesis <- sapply(aicc_df$Modnames, function(name) {
    parts <- strsplit(name, "_")[[1]]
    if (length(parts) >= 4) {
      return(parts[3])  # Extract hypothesis name from model name
    } else {
      return(NA)
    }
  })
  
  # Extract control type from model names
  aicc_df$Control <- sapply(aicc_df$Modnames, function(name) {
    parts <- strsplit(name, "_")[[1]]
    if (length(parts) >= 5) {
      return(parts[4])  # Extract control type from model name
    } else {
      return("basic")
    }
  })
  
  # Identify models with substantial support (AICc weight > 0.1)
  supported_models <- aicc_df[aicc_df$AICcWt > 0.1, ]
  
  # Calculate hypothesis weights (sum of AICc weights for each hypothesis)
  hypothesis_weights <- tapply(aicc_df$AICcWt, aicc_df$Hypothesis, sum)
  hypothesis_weights_df <- data.frame(
    Hypothesis = names(hypothesis_weights),
    TotalWeight = as.numeric(hypothesis_weights)
  )
  hypothesis_weights_df <- hypothesis_weights_df[order(hypothesis_weights_df$TotalWeight, decreasing = TRUE), ]
  
  # Extract parameter estimates and p-values for FDR correction
  # We'll organize by hypothesis to apply FDR within each hypothesis group
  param_results <- data.frame(
    outcome = character(),
    model_type = character(),
    model_name = character(),
    hypothesis = character(),
    parameter = character(),
    estimate = numeric(),
    std_error = numeric(),
    t_value = numeric(),
    p_value = numeric(),
    aicc_weight = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (i in seq_along(models)) {
    model_name <- model_names[i]
    model <- models[[i]]
    
    # Extract hypothesis name
    hypothesis <- NA
    parts <- strsplit(model_name, "_")[[1]]
    if (length(parts) >= 4) {
      hypothesis <- parts[3]
    }
    
    # Get AICc weight
    aicc_weight <- aicc_df$AICcWt[aicc_df$Modnames == model_name]
    
    if ("lmerModLmerTest" %in% class(model)) {
      coefs <- summary(model)$coefficients
      p_col <- "Pr(>|t|)"
    } else {
      coefs <- summary(model)$coefficients
      p_col <- ifelse("Pr(>|t|)" %in% colnames(coefs), "Pr(>|t|)", 4)
    }
    
    # Extract model parameters (excluding intercept and standard controls)
    param_rows <- rownames(coefs)
    param_rows <- param_rows[!grepl("^\\(Intercept\\)$|^schoolid", param_rows)]
    
    for (param in param_rows) {
      param_results <- rbind(param_results, data.frame(
        outcome = outcome,
        model_type = model_type,
        model_name = model_name,
        hypothesis = hypothesis,
        parameter = param,
        estimate = coefs[param, "Estimate"],
        std_error = coefs[param, "Std. Error"],
        t_value = coefs[param, "t value"],
        p_value = coefs[param, p_col],
        aicc_weight = aicc_weight,
        stringsAsFactors = FALSE
      ))
    }
  }
  
  # Apply FDR correction to p-values within each hypothesis
  if (nrow(param_results) > 0) {
    # Initialize p_adjusted column
    param_results$p_adjusted <- NA
    param_results$significant <- FALSE
    
    # Apply FDR correction within each hypothesis
    for (hyp in unique(param_results$hypothesis)) {
      if (is.na(hyp)) next
      
      hyp_rows <- which(param_results$hypothesis == hyp)
      param_results$p_adjusted[hyp_rows] <- p.adjust(param_results$p_value[hyp_rows], method = "fdr")
      param_results$significant[hyp_rows] <- param_results$p_adjusted[hyp_rows] < 0.05
    }
  }
  
  # Return results
  return(list(
    outcome = outcome,
    model_type = model_type,
    models = models,
    aicc_results = aicc_df,
    param_results = param_results,
    formulas = model_formulas,
    supported_models = supported_models,
    hypothesis_weights = hypothesis_weights_df
  ))
}

#' Visualize parameters from supported models (AICc weight > 0.1)
#' 
#' @param results Results from analyze_hypothesis_outcome
#' @param outcome The risk outcome to visualize
#' @return ggplot object
visualize_supported_models <- function(results, outcome) {
  if (length(results$models) == 0 || nrow(results$supported_models) == 0) {
    return(NULL)
  }
  
  # Get supported models
  supported_model_names <- results$supported_models$Modnames
  
  # Extract parameters from supported models
  param_data <- results$param_results[results$param_results$model_name %in% supported_model_names, ]
  
  if (nrow(param_data) == 0) {
    return(NULL)
  }
  
  # Create parameter groupings for visualization
  param_data$param_group <- sapply(param_data$parameter, function(param) {
    if (grepl("^gain|^loss", param)) return("Motivation")
    if (grepl("^update|^decay|^retend", param)) return("Learning")
    if (grepl("^boundary|^tau|^beta", param)) return("DDM/Decision")
    if (grepl("^drift_con$", param)) return("Evidence (Hybrid)")
    if (grepl("^con$", param)) return("Evidence (RL)")
    if (grepl("^good_|^bad_|^money", param)) return("Performance")
    if (grepl(":male$", param)) return("Gender Interaction")
    if (grepl("^male$", param)) return("Gender")
    if (grepl("^grade12|^time_since_puberty", param)) return("Developmental")
    return("Other")
  })
  
  # Create cleaner parameter labels
  param_data$param_label <- sapply(param_data$parameter, function(param) {
    # For interactions, format as "Parameter × Gender"
    if (grepl(":male$", param)) {
      base_param <- gsub(":male$", "", param)
      return(paste0(base_param, " × Gender"))
    }
    return(param)
  })
  
  # Add model label for visualization
  param_data$model_label <- sapply(param_data$model_name, function(name) {
    parts <- strsplit(name, "_")[[1]]
    if (length(parts) >= 5) {
      return(paste(parts[3], parts[4], sep="_"))  # Hypothesis + control type
    } else if (length(parts) >= 4) {
      return(paste(parts[3], "basic", sep="_"))
    } else {
      return(name)
    }
  })
  
  # Create visualization
  ggplot(param_data, 
         aes(x = param_label, y = estimate, fill = model_label)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error), 
                  position = position_dodge(width = 0.9), width = 0.25) +
    facet_wrap(~param_group, scales = "free_x") +
    geom_text(aes(label = ifelse(significant, "*", ""), y = ifelse(estimate >= 0, 
                                                                   estimate + std_error, 
                                                                   estimate - std_error)), 
              position = position_dodge(width = 0.9), vjust = ifelse(param_data$estimate >= 0, -0.5, 1.5)) +
    labs(title = paste("Parameter Estimates for", outcome, "- Supported Models (AICc weight > 0.1)"),
         subtitle = "* indicates significance after FDR correction",
         x = "Parameter", 
         y = "Standardized Estimate",
         fill = "Model") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom")
}

#' Create gender interaction plots for significant interactions
#' 
#' @param results Results from analyze_hypothesis_outcome
#' @param outcome The risk outcome to visualize
#' @return List of ggplot objects
create_interaction_plots <- function(results, outcome) {
  if (length(results$models) == 0 || nrow(results$supported_models) == 0) {
    return(NULL)
  }
  
  # Get supported models
  supported_model_names <- results$supported_models$Modnames
  
  # Find significant gender interactions in supported models
  interaction_data <- results$param_results[
    results$param_results$model_name %in% supported_model_names & 
      results$param_results$significant & 
      grepl(":male$", results$param_results$parameter), ]
  
  if (nrow(interaction_data) == 0) {
    return(NULL)
  }
  
  # Initialize list to store plots
  interaction_plots <- list()
  
  # For each significant interaction, create visualization
  for (i in 1:nrow(interaction_data)) {
    interaction <- interaction_data[i, ]
    model_name <- interaction$model_name
    parameter <- gsub(":male$", "", interaction$parameter)
    model <- results$models[[model_name]]
    
    # Extract hypothesis and control type for plot title
    parts <- strsplit(model_name, "_")[[1]]
    hypothesis <- parts[3]
    control_type <- ifelse(length(parts) >= 5, parts[4], "basic")
    
    # Create data for interaction plot
    if ("lmerModLmerTest" %in% class(model)) {
      fixed_effects <- fixef(model)
    } else {
      fixed_effects <- coef(model)
    }
    
    # Find main effect and interaction terms
    main_effect <- fixed_effects[parameter]
    interaction_effect <- fixed_effects[paste0(parameter, ":male")]
    intercept <- fixed_effects["(Intercept)"]
    male_effect <- ifelse("male" %in% names(fixed_effects), fixed_effects["male"], 0)
    
    # Create plotting data
    plot_data <- data.frame(
      param_value = c(-1, 0, 1), # Standardized parameter values
      female = intercept + main_effect * c(-1, 0, 1),
      male = intercept + male_effect + (main_effect + interaction_effect) * c(-1, 0, 1)
    )
    
    # Reshape for plotting
    plot_data_long <- tidyr::pivot_longer(plot_data, cols = c("female", "male"), 
                                          names_to = "gender", values_to = "outcome_value")
    
    # Create plot
    p <- ggplot(plot_data_long, aes(x = param_value, y = outcome_value, color = gender, group = gender)) +
      geom_line() +
      geom_point() +
      labs(title = paste("Gender Interaction for", parameter, "on", outcome),
           subtitle = paste("Hypothesis:", hypothesis, "| Control:", control_type,
                            "| AICc weight:", round(interaction$aicc_weight, 3)),
           x = parameter, 
           y = outcome,
           color = "Gender") +
      theme_minimal()
    
    interaction_plots[[paste(model_name, parameter, sep="_")]] <- p
  }
  
  return(interaction_plots)
}

# Run analysis for all outcomes and model types
# --------------------------------------------

# Define risk outcomes
risk_outcomes <- c("bsss_sd", "ysr_attentionproblems", "ysr_maggressive_t", "ysr_mconduct_t")

# Run analyses
cat("\n# Hypothesis-Driven Model Comparison Analysis\n")

behavioral_results <- list()
rl_results <- list()
hybrid_results <- list()

for (outcome in risk_outcomes) {
  cat(paste0("\nAnalyzing models for: ", outcome, "...\n"))
  behavioral_results[[outcome]] <- analyze_hypothesis_outcome(outcome, behav_final_df, "behavioral")
  rl_results[[outcome]] <- analyze_hypothesis_outcome(outcome, rl_final_df, "rl")
  hybrid_results[[outcome]] <- analyze_hypothesis_outcome(outcome, hybrid_final_df, "hybrid")
}

# Display results
cat("\n# Model Comparison Results\n")

for (outcome in risk_outcomes) {
  cat(paste0("\n## Models for ", outcome, "\n"))
  
  # Function to display model results with hypothesis weights
  display_model_results <- function(results, model_type) {
    cat(paste0("\n### ", model_type, " Models\n"))
    
    if (length(results$models) == 0 || nrow(results$aicc_results) == 0) {
      cat("No models were successfully built for this outcome and model type.\n")
      return()
    }
    
    # Display hypothesis weights
    cat("\n#### Hypothesis Evidence Weights\n")
    kable(results$hypothesis_weights, digits = 4, 
          caption = paste("Evidence Weights for Hypotheses -", model_type, "Models")) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
      print()
    
    # Display supported models (AICc weight > 0.1)
    cat("\n#### Supported Models (AICc weight > 0.1)\n")
    if (nrow(results$supported_models) > 0) {
      kable(results$supported_models[, c("Modnames", "Hypothesis", "Control", "K", "AICc", "Delta_AICc", "AICcWt")], 
            caption = paste("Supported", model_type, "Models for", outcome),
            digits = 4) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
        print()
      
      # Display formulas for supported models
      cat("\n**Model formulas:**\n\n")
      for (i in 1:nrow(results$supported_models)) {
        model_name <- results$supported_models$Modnames[i]
        formula <- results$supported_models$Formula[i]
        cat(paste0("- **", model_name, "**: ", formula, "\n"))
      }
    } else {
      cat("No models had substantial support (AICc weight > 0.1) for this outcome and model type.\n")
    }
  }
  
  # Display results for each model type
  display_model_results(behavioral_results[[outcome]], "Behavioral")
  display_model_results(rl_results[[outcome]], "RL")
  display_model_results(hybrid_results[[outcome]], "Hybrid")
}

# Parameter estimates for supported models
cat("\n# Parameter Estimates for Supported Models\n")

for (outcome in risk_outcomes) {
  cat(paste0("\n## Parameters for ", outcome, "\n"))
  
  # Function to display parameter estimates for supported models
  display_parameter_estimates <- function(results, model_type) {
    cat(paste0("\n### ", model_type, " Parameters\n"))
    
    if (length(results$models) == 0 || nrow(results$supported_models) == 0) {
      cat("No supported models for this outcome and model type.\n")
      return()
    }
    
    # Get supported models
    supported_model_names <- results$supported_models$Modnames
    
    # Extract significant parameters from supported models
    significant_params <- results$param_results[
      results$param_results$model_name %in% supported_model_names & 
        results$param_results$significant, ]
    
    if (nrow(significant_params) > 0) {
      # Add model information for display
      significant_params$hypothesis <- sapply(significant_params$model_name, function(name) {
        parts <- strsplit(name, "_")[[1]]
        if (length(parts) >= 4) {
          return(parts[3])
        } else {
          return(NA)
        }
      })
      
      significant_params$control <- sapply(significant_params$model_name, function(name) {
        parts <- strsplit(name, "_")[[1]]
        if (length(parts) >= 5) {
          return(parts[4])
        } else {
          return("basic")
        }
      })
      
      # Display table of significant parameters
      kable(significant_params[, c("parameter", "hypothesis", "control", "estimate", 
                                   "std_error", "p_value", "p_adjusted", "aicc_weight")], 
            caption = paste("Significant Parameters in Supported", model_type, "Models for", outcome),
            digits = 4) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
        print()
    } else {
      cat("No significant parameters after FDR correction in supported models.\n")
    }
    
    # Visualize parameters from supported models
    # Visualize parameters from supported models
    cat("\n#### Parameter Visualization\n")
    model_plots <- visualize_supported_models_individually(results, outcome)
    if (!is.null(model_plots) && length(model_plots) > 0) {
      for (model_name in names(model_plots)) {
        print(model_plots[[model_name]])
      }
    } else {
      cat("No parameter plots available for supported models.\n")
    }
    
    # Create gender interaction plots
    interaction_plots <- create_interaction_plots(results, outcome)
    if (!is.null(interaction_plots) && length(interaction_plots) > 0) {
      cat("\n#### Gender Interaction Plots\n")
      for (i in 1:length(interaction_plots)) {
        print(interaction_plots[[i]])
      }
    }
  }
  
  # Display parameter estimates for each model type
  display_parameter_estimates(behavioral_results[[outcome]], "Behavioral")
  display_parameter_estimates(rl_results[[outcome]], "RL")
  display_parameter_estimates(hybrid_results[[outcome]], "Hybrid")
}

# Theoretical Implications Section
cat("\n# Theoretical Implications\n")

# For each hypothesis, check evidence across outcomes
all_hypothesis_weights <- data.frame()

for (outcome in risk_outcomes) {
  # Behavioral
  if (length(behavioral_results[[outcome]]$models) > 0 && 
      nrow(behavioral_results[[outcome]]$hypothesis_weights) > 0) {
    hyp_weights <- behavioral_results[[outcome]]$hypothesis_weights
    hyp_weights$outcome <- outcome
    hyp_weights$model_type <- "Behavioral"
    all_hypothesis_weights <- rbind(all_hypothesis_weights, hyp_weights)
  }
  
  # RL
  if (length(rl_results[[outcome]]$models) > 0 && 
      nrow(rl_results[[outcome]]$hypothesis_weights) > 0) {
    hyp_weights <- rl_results[[outcome]]$hypothesis_weights
    hyp_weights$outcome <- outcome
    hyp_weights$model_type <- "RL"
    all_hypothesis_weights <- rbind(all_hypothesis_weights, hyp_weights)
  }
  
  # Hybrid
  if (length(hybrid_results[[outcome]]$models) > 0 && 
      nrow(hybrid_results[[outcome]]$hypothesis_weights) > 0) {
    hyp_weights <- hybrid_results[[outcome]]$hypothesis_weights
    hyp_weights$outcome <- outcome
    hyp_weights$model_type <- "Hybrid"
    all_hypothesis_weights <- rbind(all_hypothesis_weights, hyp_weights)
  }
}

if (nrow(all_hypothesis_weights) > 0) {
  # Create a hypothesis evidence heatmap across outcomes
  hypothesis_matrix <- reshape2::acast(all_hypothesis_weights, 
                                       Hypothesis ~ model_type + outcome, 
                                       value.var = "TotalWeight")
  
  # Replace NAs with zeros
  hypothesis_matrix[is.na(hypothesis_matrix)] <- 0
  
  # Display hypothesis evidence weights across outcomes
  cat("\n## Hypothesis Evidence Across Outcomes\n")
  
  # Convert matrix to data frame for kable
  hypothesis_df <- as.data.frame(hypothesis_matrix)
  hypothesis_df$Hypothesis <- rownames(hypothesis_matrix)
  hypothesis_df <- hypothesis_df[, c(ncol(hypothesis_df), 1:(ncol(hypothesis_df)-1))]
  
  kable(hypothesis_df, digits = 3,
        caption = "Evidence Weights for Each Hypothesis Across Outcomes") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = TRUE) %>%
    print()
  
  # Create a heatmap for hypothesis evidence
  hyp_heatmap_data <- reshape2::melt(hypothesis_matrix)
  names(hyp_heatmap_data) <- c("Hypothesis", "Model_Outcome", "Weight")
  
  # Split Model_Outcome into separate columns
  hyp_heatmap_data <- tidyr::separate(hyp_heatmap_data, Model_Outcome, 
                                      into = c("Model", "Outcome"), sep = "_")
  
  # Plot heatmap
  ggplot(hyp_heatmap_data, aes(x = Outcome, y = Hypothesis, fill = Weight)) +
    geom_tile(color = "white") +
    facet_wrap(~ Model, scales = "free_x") +
    scale_fill_gradient(low = "white", high = "steelblue") +
    labs(title = "Hypothesis Evidence Across Outcomes",
         x = "Risk Outcome", 
         y = "Hypothesis",
         fill = "Evidence Weight") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

# Collect significant parameters across outcomes
all_significant_params <- data.frame()

for (outcome in risk_outcomes) {
  # Only include parameters from supported models (AICc weight > 0.1)
  
  # Behavioral
  if (length(behavioral_results[[outcome]]$models) > 0 && 
      nrow(behavioral_results[[outcome]]$supported_models) > 0) {
    
    supported_models <- behavioral_results[[outcome]]$supported_models$Modnames
    significant_params <- behavioral_results[[outcome]]$param_results[
      behavioral_results[[outcome]]$param_results$model_name %in% supported_models &
        behavioral_results[[outcome]]$param_results$significant, ]
    
    if (nrow(significant_params) > 0) {
      significant_params$outcome <- outcome
      all_significant_params <- rbind(all_significant_params, significant_params)
    }
  }
  
  # RL
  if (length(rl_results[[outcome]]$models) > 0 && 
      nrow(rl_results[[outcome]]$supported_models) > 0) {
    
    supported_models <- rl_results[[outcome]]$supported_models$Modnames
    significant_params <- rl_results[[outcome]]$param_results[
      rl_results[[outcome]]$param_results$model_name %in% supported_models &
        rl_results[[outcome]]$param_results$significant, ]
    
    if (nrow(significant_params) > 0) {
      significant_params$outcome <- outcome
      all_significant_params <- rbind(all_significant_params, significant_params)
    }
  }
  
  # Hybrid
  if (length(hybrid_results[[outcome]]$models) > 0 && 
      nrow(hybrid_results[[outcome]]$supported_models) > 0) {
    
    supported_models <- hybrid_results[[outcome]]$supported_models$Modnames
    significant_params <- hybrid_results[[outcome]]$param_results[
      hybrid_results[[outcome]]$param_results$model_name %in% supported_models &
        hybrid_results[[outcome]]$param_results$significant, ]
    
    if (nrow(significant_params) > 0) {
      significant_params$outcome <- outcome
      all_significant_params <- rbind(all_significant_params, significant_params)
    }
  }
}

if (nrow(all_significant_params) > 0) {
  # Find parameters that are significant across multiple outcomes
  param_counts <- table(all_significant_params$parameter)
  multi_outcome_params <- names(param_counts[param_counts > 1])
  
  if (length(multi_outcome_params) > 0) {
    cat("\n## Parameters Significant Across Multiple Outcomes\n")
    
    for (param in multi_outcome_params) {
      param_data <- all_significant_params[all_significant_params$parameter == param, ]
      outcomes_affected <- unique(param_data$outcome)
      
      cat(paste0("- **", param, "** significantly predicts: ", 
                 paste(outcomes_affected, collapse = ", "), "\n"))
      
      for (outcome in outcomes_affected) {
        outcome_data <- param_data[param_data$outcome == outcome, ]
        for (i in 1:nrow(outcome_data)) {
          row <- outcome_data[i, ]
          effect_dir <- ifelse(row$estimate > 0, "positive", "negative")
          model_type <- row$model_type
          hyp_name <- row$hypothesis
          
          cat(paste0("  - ", outcome, " (", model_type, ", ", hyp_name, " hypothesis): ", 
                     effect_dir, " effect (β = ", round(row$estimate, 3), 
                     ", p-adjusted = ", round(row$p_adjusted, 3), 
                     ", AICc weight = ", round(row$aicc_weight, 3), ")\n"))
        }
      }
      cat("\n")
    }
  }
}

# Create a parameter significance heatmap
if (nrow(all_significant_params) > 0) {
  # Create parameter groups for better visualization
  all_significant_params$param_group <- sapply(all_significant_params$parameter, function(param) {
    if (grepl("^gain|^loss", param)) return("Motivation")
    if (grepl("^update|^decay|^retend", param)) return("Learning")
    if (grepl("^boundary|^tau|^beta", param)) return("DDM/Decision")
    if (grepl("^drift_con$", param)) return("Evidence (Hybrid)")
    if (grepl("^con$", param)) return("Evidence (RL)")
    if (grepl("^good_|^bad_|^money", param)) return("Performance")
    if (grepl(":male$", param)) {
      base_param <- gsub(":male$", "", param)
      if (grepl("^gain|^loss", base_param)) return("Motivation × Gender")
      if (grepl("^update|^decay|^retend", base_param)) return("Learning × Gender")
      if (grepl("^boundary|^tau|^beta", base_param)) return("DDM/Decision × Gender")
      return("Other × Gender")
    }
    if (grepl("^male$", param)) return("Gender")
    if (grepl("^grade12|^time_since_puberty", param)) return("Developmental")
    return("Other")
  })
  
  # Create cleaner parameter labels
  all_significant_params$clean_parameter <- sapply(all_significant_params$parameter, function(param) {
    if (grepl(":male$", param)) {
      base_param <- gsub(":male$", "", param)
      return(paste0(base_param, " × Gender"))
    }
    return(param)
  })
  
  # Create data for heatmap
  param_effect_data <- all_significant_params %>%
    dplyr::group_by(model_type, outcome, clean_parameter, param_group) %>%
    dplyr::summarize(
      avg_estimate = mean(estimate),
      max_aicc_weight = max(aicc_weight),
      .groups = 'drop'
    )
  
  # Set consistent parameter group order
  group_order <- c("Performance", "Motivation", "Learning", "DDM/Decision", 
                   "Evidence (RL)", "Evidence (Hybrid)", "Motivation × Gender", 
                   "Learning × Gender", "DDM/Decision × Gender", "Other × Gender",
                   "Gender", "Developmental", "Other")
  param_effect_data$param_group <- factor(param_effect_data$param_group, levels = group_order)
  
  # Plot heatmap
  cat("\n## Parameter Significance Patterns\n")
  
  # Create heatmap of effect sizes
  ggplot(param_effect_data, 
         aes(x = outcome, y = clean_parameter, fill = avg_estimate)) +
    geom_tile(color = "white", alpha = 0.8) +
    geom_text(aes(label = "*", 
                  color = ifelse(abs(avg_estimate) > 0.5, "white", "black")),
              size = 5) +
    scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
    scale_color_identity() +
    facet_grid(param_group ~ model_type, scales = "free_y", space = "free_y") +
    labs(title = "Parameter Effects Across Risk Outcomes",
         subtitle = "* indicates significance after FDR correction (AICc weight > 0.1)",
         x = "Risk Outcome", 
         y = "Parameter",
         fill = "Effect Size") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.text.y = element_text(size = 8),
          strip.text.y = element_text(angle = 0),
          panel.spacing = unit(0.5, "lines"))
}

# Theoretical discussion of findings
cat("\n## Key Theoretical Findings\n\n")

cat("Based on our hypothesis-driven analysis, we can draw several theoretical conclusions about the computational mechanisms underlying adolescent risk behaviors:\n\n")

# Check if motivation parameters are important across outcomes
if (nrow(all_significant_params) > 0) {
  motivation_params <- all_significant_params[grepl("^gain|^loss", all_significant_params$parameter), ]
  if (nrow(motivation_params) > 0) {
    motivation_outcomes <- unique(motivation_params$outcome)
    
    cat("### Motivation Parameters\n\n")
    cat(paste0("Reward sensitivity parameters (gain, loss) significantly predict ", 
               ifelse(length(motivation_outcomes) > 1, 
                      paste0("multiple risk behaviors: ", paste(motivation_outcomes, collapse = ", ")), 
                      paste0("risk behavior: ", motivation_outcomes)), 
               ".\n\n"))
    
    # Examine gain vs loss patterns
    gain_params <- motivation_params[grepl("^gain", motivation_params$parameter), ]
    loss_params <- motivation_params[grepl("^loss", motivation_params$parameter), ]
    
    if (nrow(gain_params) > 0) {
      gain_effect_dir <- ifelse(mean(gain_params$estimate) > 0, "positively", "negatively")
      cat(paste0("- **Reward sensitivity (gain)** ", gain_effect_dir, " predicts risk behaviors, suggesting that ",
                 ifelse(mean(gain_params$estimate) > 0, 
                        "adolescents who are more sensitive to rewards tend to engage in more risk behaviors.",
                        "adolescents who are less sensitive to rewards tend to engage in more risk behaviors."),
                 "\n\n"))
    }
    
    if (nrow(loss_params) > 0) {
      loss_effect_dir <- ifelse(mean(loss_params$estimate) > 0, "positively", "negatively")
      cat(paste0("- **Punishment sensitivity (loss)** ", loss_effect_dir, " predicts risk behaviors, suggesting that ",
                 ifelse(mean(loss_params$estimate) > 0, 
                        "adolescents who are more sensitive to punishments tend to engage in more risk behaviors.",
                        "adolescents who are less sensitive to punishments tend to engage in more risk behaviors."),
                 "\n\n"))
    }
  }
  
  # Check cognitive parameters
  cognitive_params <- all_significant_params[grepl("^update|^decay|^retend", all_significant_params$parameter), ]
  if (nrow(cognitive_params) > 0) {
    cognitive_outcomes <- unique(cognitive_params$outcome)
    
    cat("### Learning Parameters\n\n")
    cat(paste0("Learning parameters (update, decay) significantly predict ", 
               ifelse(length(cognitive_outcomes) > 1, 
                      paste0("multiple risk behaviors: ", paste(cognitive_outcomes, collapse = ", ")), 
                      paste0("risk behavior: ", cognitive_outcomes)), 
               ".\n\n"))
    
    # Examine specific learning parameter patterns
    update_params <- cognitive_params[grepl("^update", cognitive_params$parameter), ]
    decay_params <- cognitive_params[grepl("^decay", cognitive_params$parameter), ]
    
    if (nrow(update_params) > 0) {
      update_effect_dir <- ifelse(mean(update_params$estimate) > 0, "positively", "negatively")
      cat(paste0("- **Learning rate (update)** ", update_effect_dir, " predicts risk behaviors, suggesting that ",
                 ifelse(mean(update_params$estimate) > 0, 
                        "adolescents who update their value expectations more quickly tend to engage in more risk behaviors.",
                        "adolescents who update their value expectations more slowly tend to engage in more risk behaviors."),
                 "\n\n"))
    }
    
    if (nrow(decay_params) > 0) {
      decay_effect_dir <- ifelse(mean(decay_params$estimate) > 0, "positively", "negatively")
      cat(paste0("- **Memory decay** ", decay_effect_dir, " predicts risk behaviors, suggesting that ",
                 ifelse(mean(decay_params$estimate) > 0, 
                        "adolescents who forget previous experiences more quickly tend to engage in more risk behaviors.",
                        "adolescents who maintain memory of previous experiences longer tend to engage in more risk behaviors."),
                 "\n\n"))
    }
  }
  
  # Check DDM parameters
  ddm_params <- all_significant_params[grepl("^boundary|^tau|^beta", all_significant_params$parameter), ]
  if (nrow(ddm_params) > 0) {
    ddm_outcomes <- unique(ddm_params$outcome)
    
    cat("### Decision Process Parameters\n\n")
    cat(paste0("Decision process parameters (boundary, tau, beta) significantly predict ", 
               ifelse(length(ddm_outcomes) > 1, 
                      paste0("multiple risk behaviors: ", paste(ddm_outcomes, collapse = ", ")), 
                      paste0("risk behavior: ", ddm_outcomes)), 
               ".\n\n"))
    
    # Examine specific DDM parameter patterns
    boundary_params <- ddm_params[grepl("^boundary", ddm_params$parameter), ]
    tau_params <- ddm_params[grepl("^tau", ddm_params$parameter), ]
    beta_params <- ddm_params[grepl("^beta", ddm_params$parameter), ]
    
    if (nrow(boundary_params) > 0) {
      boundary_effect_dir <- ifelse(mean(boundary_params$estimate) > 0, "positively", "negatively")
      cat(paste0("- **Decision threshold (boundary)** ", boundary_effect_dir, " predicts risk behaviors, suggesting that ",
                 ifelse(mean(boundary_params$estimate) > 0, 
                        "adolescents who require more evidence before making decisions tend to engage in more risk behaviors.",
                        "adolescents who make decisions with less evidence tend to engage in more risk behaviors."),
                 "\n\n"))
    }
    
    if (nrow(tau_params) > 0) {
      tau_effect_dir <- ifelse(mean(tau_params$estimate) > 0, "positively", "negatively")
      cat(paste0("- **Non-decision time (tau)** ", tau_effect_dir, " predicts risk behaviors, suggesting that ",
                 ifelse(mean(tau_params$estimate) > 0, 
                        "adolescents with longer cognitive processing times tend to engage in more risk behaviors.",
                        "adolescents with shorter cognitive processing times tend to engage in more risk behaviors."),
                 "\n\n"))
    }
    
    if (nrow(beta_params) > 0) {
      beta_effect_dir <- ifelse(mean(beta_params$estimate) > 0, "positively", "negatively")
      cat(paste0("- **Response bias (beta)** ", beta_effect_dir, " predicts risk behaviors, suggesting that ",
                 ifelse(mean(beta_params$estimate) > 0, 
                        "adolescents with stronger response biases tend to engage in more risk behaviors.",
                        "adolescents with weaker response biases tend to engage in more risk behaviors."),
                 "\n\n"))
    }
  }
  
  # Check gender interactions
  gender_int_params <- all_significant_params[grepl(":male", all_significant_params$parameter), ]
  if (nrow(gender_int_params) > 0) {
    gender_int_outcomes <- unique(gender_int_params$outcome)
    
    cat("### Gender Differences\n\n")
    cat(paste0("Gender significantly moderates the relationship between computational parameters and ", 
               ifelse(length(gender_int_outcomes) > 1, 
                      paste0("multiple risk behaviors: ", paste(gender_int_outcomes, collapse = ", ")), 
                      paste0("risk behavior: ", gender_int_outcomes)), 
               ".\n\n"))
    
    # Examine specific gender interaction patterns
    for (param in unique(gsub(":male", "", gender_int_params$parameter))) {
      param_ints <- gender_int_params[grepl(paste0(param, ":male"), gender_int_params$parameter), ]
      if (nrow(param_ints) > 0) {
        param_effect_dir <- ifelse(mean(param_ints$estimate) > 0, "stronger", "weaker")
        cat(paste0("- The relationship between **", param, "** and risk behaviors is ", param_effect_dir, 
                   " for males compared to females.\n\n"))
      }
    }
  }
  
  # Check developmental parameters
  dev_params <- all_significant_params[grepl("^grade12|^time_since_puberty", all_significant_params$parameter), ]
  if (nrow(dev_params) > 0) {
    dev_outcomes <- unique(dev_params$outcome)
    
    cat("### Developmental Effects\n\n")
    cat(paste0("Developmental factors significantly predict ", 
               ifelse(length(dev_outcomes) > 1, 
                      paste0("multiple risk behaviors: ", paste(dev_outcomes, collapse = ", ")), 
                      paste0("risk behavior: ", dev_outcomes)), 
               ".\n\n"))
    
    # Examine specific developmental parameter patterns
    grade_params <- dev_params[grepl("^grade12", dev_params$parameter), ]
    puberty_params <- dev_params[grepl("^time_since_puberty", dev_params$parameter), ]
    
    if (nrow(grade_params) > 0) {
      grade_effect_dir <- ifelse(mean(grade_params$estimate) > 0, "higher", "lower")
      cat(paste0("- **Grade level** is associated with ", grade_effect_dir, " risk behaviors, suggesting developmental changes in risk-taking.\n\n"))
    }
    
    if (nrow(puberty_params) > 0) {
      puberty_effect_dir <- ifelse(mean(puberty_params$estimate) > 0, "higher", "lower")
      cat(paste0("- **Time since puberty** is associated with ", puberty_effect_dir, " risk behaviors, suggesting pubertal timing effects on risk-taking.\n\n"))
    }
  }
}
