---
title: "Model Recovery and PPC Analysis"
author: "Felix Pichardo"
date: "2025-03-13"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.show = 'all', fig.keep = 'all', dev = 'png', dpi = 300)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(viridis)
library(scales)
library(gridExtra)
library(ggrepel)
library(grid)
library(boot) # For bootstrap confidence intervals
```

# Setup and Configuration

```{r model-config}
# Enhanced Model Configuration
model_config <- list(
  # Define model families (the core algorithms)
  families = list(
    ev = list(
      display_name = "Expected Value",
      models = c("ev", "ev_ddm")
    ),
    pvl = list(
      display_name = "Prospect Valence Learning",
      # Group all PVL variants
      variants = list(
        delta = list(
          display_name = "PVLdelta",
          models = c("pvldelta", "pvldelta_ddm")
        ),
        decay = list(
          display_name = "PVLdecay",
          models = c("pvldecay", "pvldecay_ddm") 
        ),
        both = list(
          display_name = "PVLboth",
          models = c("pvlboth", "pvlboth_ddm")
        ),
        bothsd = list(
          display_name = "PVLbothsd",
          models = c("pvlbothsd", "pvlbothsd_ddm")
        ),
        puldelta = list(
          display_name = "PULdelta",
          models = c("puldelta", "puldelta_ddm")
        ),
        puldecay = list(
          display_name = "PULdecay",
          models = c("puldecay", "puldecay_ddm")
        ),
        pulboth = list(
          display_name = "PULboth",
          models = c("pulboth", "pulboth_ddm")
        ),
        pvsdelta = list(
          display_name = "PVSdelta",
          models = c("pvsdelta", "pvsdelta_ddm")
        ),
        pvsdecay = list(
          display_name = "PVSdecay",
          models = c("pvsdecay", "pvsdecay_ddm")
        ),
        pvsboth = list(
          display_name = "PVSboth",
          models = c("pvsboth", "pvsboth_ddm")
        )
      )
    ),
    vpp = list(
      display_name = "Value-Plus-Perseverance",
      # Group all VPP variants
      variants = list(
        delta = list(
          display_name = "VPPdeltag",
          models = c("vppdeltag", "vppdeltag_ddm")
        ),
        decay = list(
          display_name = "VPPdecayg",
          models = c("vppdecayg", "vppdecayg_ddm") 
        ),
        both = list(
          display_name = "VPPbothg",
          models = c("vppbothg", "vppbothg_ddm")
        ),
        delta = list(
          display_name = "VPPdeltagd",
          models = c("vppdeltagd", "vppdeltagd_ddm")
        ),
        decay = list(
          display_name = "VPPdecaygd",
          models = c("vppdecaygd", "vppdecaygd_ddm") 
        ),
        both = list(
          display_name = "VPPbothgd",
          models = c("vppbothgd", "vppbothgd_ddm")
        ),
        puldelta = list(
          display_name = "PULVPPdeltag",
          models = c("pulvppdeltag", "pulvppdeltag_ddm")
        ),
        puldecay = list(
          display_name = "PULVPPdecayg",
          models = c("pulvppdecayg", "pulvppdecayg_ddm")
        ),
        pulboth = list(
          display_name = "PULVPPbothg",
          models = c("pulvppbothg", "pulvppbothg_ddm")
        ),
        pvsdelta = list(
          display_name = "PVSVPPdeltag",
          models = c("pvsvppdeltag", "pvsvppdeltag_ddm")
        ),
        pvsdecay = list(
          display_name = "PVSVPPdecayg",
          models = c("pvsvppdecayg", "pvsvppdecayg_ddm")
        ),
        pvsboth = list(
          display_name = "PVSVPPbothg",
          models = c("pvsvppbothg", "pvsvppbothg_ddm")
        )
      )
    ),
    ddm = list(
      display_name = "DDM Only",
      models = c("ddm")
    )
  ),
  
  # Define model types (for categorization)
  types = list(
    rl_only = "Reinforcement Learning", 
    ddm_only = "Sequential Sampling",
    hybrid = "Hybrid (RL+DDM)"
  ),
  
  # Define parameter groups
  parameter_groups = list(
    "DDM Process" = c("boundary", "tau", "beta"),
    "Consistency/Drift" = c("drift", "drift_con", "con"),
    "Valuation" = c("wgt_pun", "wgt_rew", "gain", "loss", "gain_shape", "loss_shape"),
    "Learning Rate" = c("update", "retend", "decay"),
    "Perseveration" = c("k", "w", "ep"),
    "Other" = c("mag")
  ),
  
  # Define key statistics for PPC analysis
  key_statistics = list(
    deck_selection = c("good_deck_ratio", "new_good_deck_ratio", "new_bad_deck_ratio"),
    rl_performance = c("skip_ratio", "total_money", "avg_outcome"),
    play_rt = c("rt_play_mean", "rt_play_median", "rt_play_quantiles_10%", "rt_play_quantiles_30%", 
                "rt_play_quantiles_50%", "rt_play_quantiles_70%", "rt_play_quantiles_90%"),
    skip_rt = c("rt_skip_mean", "rt_skip_median", "rt_skip_quantiles_10%", "rt_skip_quantiles_30%", 
                "rt_skip_quantiles_50%", "rt_skip_quantiles_70%", "rt_skip_quantiles_90%"),
    choice = c("choice_prob")
  )
)

# Define consistent colors for model types
model_type_colors <- c(
  "RL Only" = "#1B9E77", 
  "DDM Only" = "#D95F02", 
  "Hybrid (RL+DDM)" = "#7570B3"
)

# Define a consistent color palette for models (10 distinct colors)
model_colors <- c(
  "PVLdelta Only" = "#4E79A7",
  "PVLdelta+DDM" = "#A0CBE8",
  "PVLdecay Only" = "#F28E2B",
  "PVLdecay+DDM" = "#FFBE7D",
  "PVLboth Only" = "#59A14F",
  "PVLboth+DDM" = "#8CD17D",
  "PVLbothsd Only" = "#B6992D",
  "PVLbothsd+DDM" = "#F1CE63",
  "Expected Value" = "#E15759",
  "Expected Value+DDM" = "#FF9D9A",
  "VPPdeltag Only" = "#79706E",
  "VPPdeltag+DDM" = "#BAB0AC",
  "VPPdecayg Only" = "#D37295",
  "VPPdecayg+DDM" = "#FABFD2",
  "VPPbothg Only" = "#B07AA1",
  "VPPbothg+DDM" = "#D4A6C8",
  "VPPdeltagd Only" = "#9D7660",
  "VPPdeltagd+DDM" = "#D7B5A6",
  "VPPdecaygd Only" = "#808080",
  "VPPdecaygd+DDM" = "#CCCCCC",
  "VPPbothgd Only" = "#1E466E",
  "VPPbothgd+DDM" = "#458CC7",
  "DDM" = "#000000"
)

# Build derived model lists automatically
build_model_lists <- function(config) {
  # Initialize lists
  all_models <- character()
  display_names <- list()
  rl_only_models <- character()
  ddm_only_models <- character()
  hybrid_models <- character()
  all_model_families <- list()
  
  # Process all model families
  for (family_name in names(config$families)) {
    family <- config$families[[family_name]]
    
    # Handle families with variants
    if ("variants" %in% names(family)) {
      for (variant_name in names(family$variants)) {
        variant <- family$variants[[variant_name]]
        
        # Process each model in the variant
        for (model in variant$models) {
          # Create display name
          display_name <- paste(variant$display_name, ifelse(grepl("_ddm$", model), "+DDM", "Only"))
          display_names[[model]] <- display_name
          
          # Determine model type and store in appropriate list
          if (grepl("_ddm$", model)) {
            hybrid_models <- c(hybrid_models, model)
          } else if (model == "ddm") {
            ddm_only_models <- c(ddm_only_models, model)
          } else {
            rl_only_models <- c(rl_only_models, model)
          }
          
          # Add to all models list
          all_models <- c(all_models, model)
          
          # Add to model families - group by base algorithm
          base_family <- ifelse(family_name == "ddm", "ddm", 
                                paste0(family_name, variant_name))
          
          if (is.null(all_model_families[[base_family]])) {
            all_model_families[[base_family]] <- character()
          }
          all_model_families[[base_family]] <- c(all_model_families[[base_family]], model)
        }
      }
    } else {
      # Simple family without variants (like EV or DDM)
      for (model in family$models) {
        # Create display name
        display_name <- paste(family$display_name, ifelse(grepl("_ddm$", model), "+DDM", ""))
        display_names[[model]] <- display_name
        
        # Determine model type and store in appropriate list
        if (grepl("_ddm$", model)) {
          hybrid_models <- c(hybrid_models, model)
        } else if (model == "ddm") {
          ddm_only_models <- c(ddm_only_models, model)
        } else {
          rl_only_models <- c(rl_only_models, model)
        }
        
        # Add to all models list
        all_models <- c(all_models, model)
        
        # Add to model families
        base_family <- ifelse(family_name == "ddm", "ddm", family_name)
        if (is.null(all_model_families[[base_family]])) {
          all_model_families[[base_family]] <- character()
        }
        all_model_families[[base_family]] <- c(all_model_families[[base_family]], model)
      }
    }
  }
  
  # Return all derived lists
  return(list(
    all_models = unique(all_models),
    rl_only_models = unique(rl_only_models),
    ddm_only_models = unique(ddm_only_models),
    hybrid_models = unique(hybrid_models),
    model_display_names = display_names,
    model_families = all_model_families
  ))
}

# Generate all the model lists from configuration
derived_lists <- build_model_lists(model_config)
all_models <- derived_lists$all_models
rl_only_models <- derived_lists$rl_only_models
ddm_only_models <- derived_lists$ddm_only_models
hybrid_models <- derived_lists$hybrid_models
model_display_names <- derived_lists$model_display_names
model_families <- derived_lists$model_families

# Function to calculate bootstrap confidence intervals
calc_boot_ci <- function(data, indices, fun) {
  return(fun(data[indices]))
}

# Helper function to add confidence intervals to data frames
add_ci <- function(df, value_col, group_cols = NULL, ci_level = 0.95) {
  # Ensure value_col is a string
  value_col <- enquo(value_col)
  
  # Group by variables if provided
  if (!is.null(group_cols)) {
    df <- df %>% group_by(across(all_of(group_cols)))
  }
  
  # Calculate mean and bootstrap CI
  result <- df %>%
    summarize(
      mean_val = mean(!!value_col, na.rm = TRUE),
      sd_val = sd(!!value_col, na.rm = TRUE),
      n = sum(!is.na(!!value_col)),
      .groups = "drop"
    ) %>%
    mutate(
      se = sd_val / sqrt(n),
      ci_lower = mean_val - qt(1 - (1 - ci_level) / 2, n - 1) * se,
      ci_upper = mean_val + qt(1 - (1 - ci_level) / 2, n - 1) * se
    )
  
  return(result)
}

# Print model lists for verification
cat("All models:", length(all_models), "\n")
cat("RL-only models:", length(rl_only_models), "\n")
cat("DDM-only models:", length(ddm_only_models), "\n")
cat("Hybrid models:", length(hybrid_models), "\n")
cat("Model families:", length(model_families), "\n")
```

```{r data-loading}
# Function to load recovery data with error handling
load_recovery_data <- function(model_name, base_dir = NULL) {
  if (is.null(base_dir)) {
    PROJ_DIR <- here::here()
    base_dir <- file.path(PROJ_DIR, "Data", "sim", "recovery")
  }
  
  file_path <- file.path(base_dir, paste0("recovery_igt_mod_batch_001_", model_name, "_desc-sim_params.rds"))
  
  if (file.exists(file_path)) {
    return(readRDS(file_path))
  } else {
    warning(paste("Recovery file not found for model:", model_name))
    return(NULL)
  }
}

# Function to load PPC result files flexibly
load_ppc_results <- function(model_name, base_dir = NULL) {
  if (is.null(base_dir)) {
    PROJ_DIR <- here::here()
    base_dir <- file.path(PROJ_DIR, "Data", "sim", "ppc")
  }
  
  file_path <- file.path(base_dir, paste0("ppc_results_igt_mod_", model_name, "_batch_001.rds"))
  
  if (file.exists(file_path)) {
    return(readRDS(file_path))
  } else {
    warning(paste("File not found for model:", model_name))
    return(NULL)
  }
}

# Paths to data files
PROJ_DIR <- here::here()
REC_SIM_DIR <- file.path(PROJ_DIR, "Data", "sim", "recovery")
PPC_DIR <- file.path(PROJ_DIR, "Data", "sim", "ppc")
PARAMS_DIR <- file.path(PROJ_DIR, "Data", "sim", "params")
TXT_SIM_DIR <- file.path(PROJ_DIR, "Data", "sim", "txt")
FIT_SIM_DIR <- file.path(PROJ_DIR, "Data", "sim", "fit")

# Automatically discover available recovery models
available_recovery_files <- list.files(REC_SIM_DIR, pattern = "recovery_igt_mod_batch_001_(.*)_desc-sim_params.rds", full.names = FALSE)
available_recovery_models <- available_recovery_files %>% 
  str_remove("recovery_igt_mod_batch_001_") %>%
  str_remove("_desc-sim_params.rds")

# Automatically discover available PPC models
available_ppc_files <- list.files(PPC_DIR, pattern = "ppc_results_igt_mod_.*_batch_001.rds", full.names = FALSE)
available_ppc_models <- available_ppc_files %>% 
  str_remove("ppc_results_igt_mod_") %>%
  str_remove("_batch_001.rds")

# Load data for all configured models that are available
recovery_data <- list()
for (model_name in all_models) {
  if (model_name %in% available_recovery_models) {
    recovery_data[[model_name]] <- load_recovery_data(model_name, REC_SIM_DIR)
  }
}

ppc_data <- list()
for (model_name in all_models) {
  if (model_name %in% available_ppc_models) {
    ppc_data[[model_name]] <- load_ppc_results(model_name, PPC_DIR)
  }
}

# Update model lists based on what's actually available
available_recovery_models <- names(recovery_data)
available_ppc_models <- names(ppc_data)

available_all_models <- union(available_recovery_models, available_ppc_models)
available_rl_models <- intersect(rl_only_models, available_all_models)
available_ddm_models <- intersect(ddm_only_models, available_all_models)
available_hybrid_models <- intersect(hybrid_models, available_all_models)

# Print availability stats
cat("Available Recovery models:", length(available_recovery_models), "out of", length(all_models), "\n")
cat("Available PPC models:", length(available_ppc_models), "out of", length(all_models), "\n")
```

# Parameter Recovery Analysis

## Overall Recovery Performance

```{r overall-recovery, fig.keep='all'}
# Create a function to extract overall metrics with error handling
extract_overall <- function(recovery_obj, model_name) {
  if (is.null(recovery_obj)) {
    return(NULL)
  }
  
  overall <- recovery_obj$overall
  overall$model <- model_name
  overall$model_display <- model_display_names[model_name]
  
  # Add model type classification
  overall$model_type <- case_when(
    model_name %in% rl_only_models ~ "RL Only",
    model_name %in% ddm_only_models ~ "DDM Only",
    model_name %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Unknown"
  )
  
  return(overall)
}

# Combine all overall metrics
overall_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_overall(recovery_data[[name]], name)
  })
)

# Create a wider format for easier comparison
overall_wide <- overall_df %>%
  pivot_wider(names_from = metric, values_from = value) %>%
  select(model, model_display, model_type, correlation, rmse, bias, relative_bias) %>%
  arrange(model_type, -correlation)

# Display nice table
kable(overall_wide, digits = 3, 
      col.names = c("Model", "Display Name", "Type", "Correlation", "RMSE", "Bias", "Relative Bias"),
      caption = "Overall Recovery Performance Metrics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Function to visualize overall performance
plot_overall_performance <- function(data, metric = "correlation") {
  # Define plot labels based on metric
  y_label <- case_when(
    metric == "correlation" ~ "Parameter Recovery Correlation (higher is better)",
    metric == "rmse" ~ "Parameter Recovery RMSE (lower is better)",
    metric == "relative_bias" ~ "Parameter Relative Bias (closer to 0 is better)",
    TRUE ~ metric
  )
  
  # Set up color direction based on metric (higher better for correlation, lower better for others)
  color_direction <- if(metric == "correlation") "high" else "low"
  midpoint <- if(metric == "correlation") 0.7 else 0.3
  limits <- if(metric == "correlation") c(0, 1) else NULL
  
  # Pre-sort the data by the metric value BEFORE creating the factor
  if (metric == "correlation") {
    sorted_data <- data %>% 
      group_by(model_type) %>%
      arrange(model_type, desc(!!sym(metric))) %>%
      ungroup() %>%
      # Create factor AFTER sorting
      mutate(model_display = factor(model_display, levels = model_display))
  } else {
    sorted_data <- data %>% 
      group_by(model_type) %>%
      arrange(model_type, !!sym(metric)) %>%
      ungroup() %>%
      # Create factor AFTER sorting
      mutate(model_display = factor(model_display, levels = model_display))
  }
  
  # Create plot without using reorder()
  p <- ggplot(sorted_data, aes(x = model_display, y = !!sym(metric), fill = !!sym(metric))) +
    geom_bar(stat = "identity") +
    scale_fill_gradient2(
      low = if(color_direction == "low") "green" else "red", 
      mid = "yellow", 
      high = if(color_direction == "low") "red" else "green",
      midpoint = midpoint,
      limits = limits
    ) +
    geom_text(aes(label = sprintf("%.2f", !!sym(metric))),
              position = position_stack(vjust = 0.5),
              color = "black") +
    coord_flip() +
    facet_wrap(~ model_type, scales = "free_y") +
    theme_minimal() +
    labs(
      title = paste("Model Recovery Performance -", toupper(metric)),
      subtitle = paste("Models ranked by", tolower(metric), "performance within each type"),
      x = "Model",
      y = y_label,
      fill = metric
    ) +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      strip.text = element_text(size = 12, face = "bold"),
      axis.title = element_text(size = 11),
      legend.title = element_text(size = 10)
    )
  
  return(p)
}

# Create overall performance visualizations
corr_plot <- plot_overall_performance(overall_wide, "correlation")
print(corr_plot)

rmse_plot <- plot_overall_performance(overall_wide, "rmse")
print(rmse_plot)

# Create a visualization that shows both correlation and RMSE for all models
tradeoff_plot <- ggplot(overall_wide, 
       aes(x = correlation, y = 1/rmse, 
           color = model_type, shape = model_type, 
           label = model_display)) +
  geom_point(size = 4, alpha = 0.7) +
  geom_text_repel(box.padding = 0.5, point.padding = 0.5, max.overlaps = 30, size = 3) +
  scale_color_manual(values = model_type_colors) +
  scale_shape_manual(values = c(16, 17, 15)) +
  theme_minimal() +
  labs(title = "Model Recovery Performance Tradeoff",
       subtitle = "Evaluating parameter recovery across all models",
       x = "Correlation (higher is better)",
       y = "1/RMSE (higher is better)",
       color = "Model Type",
       shape = "Model Type") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(tradeoff_plot)

# First, sort the data and create the factor levels properly
heatmap_data <- overall_wide %>%
  group_by(model_type) %>%
  arrange(model_type, desc(correlation)) %>%
  ungroup() %>%
  # Create factor with correct order
  mutate(model_display = factor(model_display, levels = unique(model_display)))

# Then create the plot without using reorder()
heatmap_plot <- ggplot(heatmap_data, 
      aes(y = model_display, 
          x = "Correlation", 
          fill = correlation)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f", correlation)), color = "black") +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.7, limits = c(0, 1)) +
  facet_wrap(~ model_type, scales = "free_y") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0),
        legend.position = "right") +
  labs(title = "Parameter Recovery Correlation by Model",
       subtitle = "Higher values (green) indicate better parameter recovery",
       x = "",
       y = "",
       fill = "Correlation")
print(heatmap_plot)
```

## Parameter Recovery Scatterplots

```{r parameter-recovery-scatterplots, fig.height=8, fig.width=12, fig.keep='all'}
# Function to extract parameter-specific data with error handling
extract_params <- function(recovery_obj, model_name) {
  if (is.null(recovery_obj) || !("by_parameter" %in% names(recovery_obj))) {
    return(NULL)
  }
  
  params <- recovery_obj$by_parameter
  params$model <- model_name
  params$model_display <- as.character(model_display_names[model_name])
  
  # Add model type classification
  params$model_type <- case_when(
    model_name %in% rl_only_models ~ "RL Only",
    model_name %in% ddm_only_models ~ "DDM Only",
    model_name %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Unknown"
  )
  
  # Add parameter type based on config
  params$param_type <- NA_character_
  for (type_name in names(model_config$parameter_groups)) {
    type_params <- model_config$parameter_groups[[type_name]]
    params$param_type[params$parameter %in% type_params] <- type_name
  }
  params$param_type[is.na(params$param_type)] <- "Other"
  
  return(params)
}

# Combine all parameter data
params_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_params(recovery_data[[name]], name)
  })
)

# Function to display parameter recovery scatter plots for multiple models
display_recovery_plots_grid <- function(param_name, model_list) {
  # Filter available models
  available_models <- intersect(model_list, names(recovery_data))
  
  # Initialize an empty list to store plots
  plots_list <- list()
  
  # Generate plots for each model
  for (model in available_models) {
    # Skip if plot data doesn't exist
    if (is.null(recovery_data[[model]]) || 
        is.null(recovery_data[[model]]$plots) || 
        is.null(recovery_data[[model]]$plots$individual) || 
        !param_name %in% names(recovery_data[[model]]$plots$individual)) {
      next
    }
    
    # Get the original plot
    orig_plot <- recovery_data[[model]]$plots$individual[[param_name]]
    
    # Check if it's a valid ggplot object
    if (!is.null(orig_plot) && inherits(orig_plot, "ggplot")) {
      # Add custom title and theme
      orig_plot <- orig_plot + 
        ggtitle(model_display_names[model]) +
        theme_minimal() +
        theme(plot.title = element_text(size = 10, face = "bold"))
      
      # Add to list
      plots_list[[model]] <- orig_plot
    }
  }
  
  # If we have plots, arrange them in a grid
  if (length(plots_list) > 0) {
    # Make sure we only have valid ggplot objects
    valid_plots <- Filter(function(p) inherits(p, "ggplot"), plots_list)
    
    if (length(valid_plots) > 0) {
      # Calculate grid dimensions
      n_plots <- length(valid_plots)
      n_cols <- min(4, n_plots)
      
      # Use try to catch any errors
      result <- try({
        grid_plot <- grid.arrange(
          grobs = valid_plots,
          top = textGrob(paste("Parameter Recovery for", param_name, "Across Models"),
                        gp = gpar(fontsize = 16, fontface = "bold")),
          ncol = n_cols
        )
        return(grid_plot)
      }, silent = TRUE)
      
      if (!inherits(result, "try-error")) {
        return(result)
      } else {
        cat("Error arranging plots:", param_name, "\n")
        return(NULL)
      }
    }
  }
  
  cat("No valid recovery plots available for parameter:", param_name, "\n")
  return(NULL)
}

# Get unique parameters from all models
all_parameters <- unique(params_df$parameter)

# Display recovery plots for key parameters across all available models
for (param in all_parameters) {
  cat(paste("\n## Parameter Recovery for", param, "\n"))
  plot <- display_recovery_plots_grid(param, available_all_models)
  if (!is.null(plot)) {
    print(plot)
  }
}
```

## Parameter Type Analysis

```{r parameter-type-analysis, fig.height=8, fig.width=12}
# Create a comparison of correlation by parameter type and model type
correlation_by_param_type <- params_df %>%
  group_by(model_type, param_type) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    mean_rmse = mean(rmse, na.rm = TRUE),
    parameter_count = n(),
    # Add 95% CI
    sd_correlation = sd(correlation, na.rm = TRUE),
    se_correlation = sd_correlation / sqrt(parameter_count),
    ci_lower = mean_correlation - qt(0.975, parameter_count - 1) * se_correlation,
    ci_upper = mean_correlation + qt(0.975, parameter_count - 1) * se_correlation,
    .groups = "drop"
  ) %>%
  arrange(param_type, desc(mean_correlation))

# Display the summary table
kable(correlation_by_param_type, digits = 3,
      col.names = c("Model Type", "Parameter Type", "Mean Correlation", "Mean RMSE", "# Parameters", 
                   "SD Correlation", "SE Correlation", "95% CI Lower", "95% CI Upper"),
      caption = "Parameter Recovery by Model Type and Parameter Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize the comparison with error bars
param_type_plot <- ggplot(correlation_by_param_type, 
       aes(x = param_type, y = mean_correlation, fill = model_type)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                position = position_dodge(width = 0.9),
                width = 0.25) +
  geom_text(aes(label = sprintf("%.2f", mean_correlation)),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3) +
  scale_y_continuous(limits = c(0, max(correlation_by_param_type$ci_upper) * 1.1)) +
  scale_fill_manual(values = model_type_colors) +
  coord_flip() +
  theme_minimal() +
  labs(title = "Parameter Recovery by Type",
       subtitle = "Average parameter recovery across different parameter categories",
       x = "Parameter Type",
       y = "Mean Correlation (with 95% CI)",
       fill = "Model Type") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )

print(param_type_plot)

# Plot correlation by parameter and model type
plot_parameter_recovery <- function(data, metric = "correlation", facet_var = "param_type") {
  # Define y-axis label based on metric
  y_label <- if(metric == "correlation") {
    "Correlation (higher is better)"
  } else {
    "RMSE (lower is better)"
  }
  
  # Set plot limits and direction based on metric
  y_limits <- if(metric == "correlation") {
    c(0, 1)
  } else {
    c(0, max(data[[metric]], na.rm = TRUE) * 1.1)
  }
  
  # Calculate summary data with 95% CI
  summary_data <- data %>%
    group_by(parameter, !!sym(facet_var), model_type) %>%
    summarize(
      mean_val = mean(!!sym(metric), na.rm = TRUE),
      count = n(),
      sd_val = sd(!!sym(metric), na.rm = TRUE),
      se_val = sd_val / sqrt(count),
      ci_lower = mean_val - qt(0.975, count - 1) * se_val,
      ci_upper = mean_val + qt(0.975, count - 1) * se_val,
      .groups = "drop"
    )
  
  # Create the plot with improved aesthetics and error bars
  p <- ggplot(summary_data, aes(x = parameter, y = mean_val, fill = model_type)) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                 position = position_dodge(width = 0.8),
                 width = 0.25) +
    facet_wrap(as.formula(paste("~", facet_var)), scales = "free_x", ncol = 2) +
    scale_fill_manual(values = model_type_colors) +
    scale_y_continuous(limits = y_limits) +
    labs(
      title = paste("Parameter Recovery (", toupper(metric), ") by Parameter Type"),
      subtitle = "Grouped by parameter type with 95% confidence intervals",
      y = y_label,
      x = "Parameter",
      fill = "Model Type"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      strip.text = element_text(size = 11, face = "bold"),
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12)
    )
  
  return(p)
}

# Plot correlation by parameter and model type
correlation_by_param <- plot_parameter_recovery(params_df, "correlation", "param_type")
print(correlation_by_param)

# Plot RMSE by parameter and model type
rmse_by_param <- plot_parameter_recovery(params_df, "rmse", "param_type")
print(rmse_by_param)

# Create a heatmap of parameter recovery by model and parameter
# Aggregate data for parameters across model families
param_recovery_heatmap <- params_df %>%
  group_by(param_type, parameter, model_type) %>%
  summarize(
    avg_correlation = mean(correlation, na.rm = TRUE),
    .groups = "drop"
  )

# Create a heatmap
param_heatmap <- ggplot(param_recovery_heatmap, 
       aes(x = parameter, y = model_type, fill = avg_correlation)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f", avg_correlation)), color = "black", size = 3) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.5, limits = c(0, 1)) +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.text = element_text(size = 11, face = "bold"),
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12)
  ) +
  labs(
    title = "Parameter Recovery Heatmap",
    subtitle = "Correlation values by parameter type, parameter, and model type",
    x = "Parameter",
    y = "Model Type",
    fill = "Average\nCorrelation"
  )
print(param_heatmap)
```

# Posterior Predictive Check (PPC) Analysis

## Extract PPC Data

```{r extract-ppc-data}
# Function to extract summary statistics with component detection
extract_summary_stats <- function(ppc_obj, model_name) {
  # Check if model exists
  if (is.null(ppc_obj)) {
    return(NULL)
  }
  
  # Determine model type
  model_type <- case_when(
    model_name %in% rl_only_models ~ "RL Only",
    model_name %in% ddm_only_models ~ "DDM Only",
    model_name %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Unknown"
  )
  
  # Check if the model has RL and SSM components or just one component
  if (is.list(ppc_obj$model$summary) && "rl" %in% names(ppc_obj$model$summary)) {
    # Hybrid model with both components
    rl_summary <- ppc_obj$model$summary$rl %>%
      mutate(component = "RL", model = model_name, model_type = model_type)
    
    ssm_summary <- ppc_obj$model$summary$ssm %>%
      mutate(component = "SSM", model = model_name, model_type = model_type)
    
    return(bind_rows(rl_summary, ssm_summary))
  } else {
    # Single component model
    summary_df <- ppc_obj$model$summary
    
    # For individual models, determine component type based on model name
    component_type <- case_when(
      model_name %in% rl_only_models ~ "RL",
      model_name %in% ddm_only_models ~ "SSM",
      TRUE ~ "Unknown"
    )
    
    # Clean up statistic names by removing misleading prefixes if present
    summary_df <- summary_df %>%
      mutate(statistic = str_remove(statistic, "^(rl_|ssm_)"))
    
    return(summary_df %>% mutate(component = component_type, model = model_name, model_type = model_type))
  }
}

# Combine all summary statistics
all_summaries <- bind_rows(
  lapply(names(ppc_data), function(name) {
    extract_summary_stats(ppc_data[[name]], name)
  })
)

# Replace model names with display names and add categorical factor for display order
all_summaries <- all_summaries %>%
  mutate(
    model_display = as.character(unlist(model_display_names[model])),
    model_display = factor(model_display)
  )

# Create separate datasets for RL and SSM components
rl_summaries <- all_summaries %>% filter(component == "RL")
ssm_summaries <- all_summaries %>% filter(component == "SSM")

# Confirm the correct assignment of components
component_check <- all_summaries %>%
  group_by(model, component) %>%
  summarise(statistics = paste(head(statistic, 3), collapse = ", "), .groups = "drop")

kable(component_check, 
      col.names = c("Model", "Component", "Example Statistics"),
      caption = "Component Assignment Check") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)
```

## Overall PPC Performance

```{r overall-ppc-performance, fig.height=10, fig.width=14}
# Calculate overall fit metrics for each model and component
overall_metrics <- all_summaries %>%
  group_by(model, model_display, component, model_type) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    median_ppp = median(mean_ppp, na.rm = TRUE),
    sd_ppp = sd(mean_ppp, na.rm = TRUE),
    n_stats = n(),
    se_ppp = sd_ppp / sqrt(n_stats),
    ci_lower_ppp = mean_ppp - qt(0.975, n_stats - 1) * se_ppp,
    ci_upper_ppp = mean_ppp + qt(0.975, n_stats - 1) * se_ppp,
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    sd_extreme_ratio = sd(extreme_ratio, na.rm = TRUE),
    se_extreme_ratio = sd_extreme_ratio / sqrt(n_stats),
    ci_lower_er = mean_extreme_ratio - qt(0.975, n_stats - 1) * se_extreme_ratio,
    ci_upper_er = mean_extreme_ratio + qt(0.975, n_stats - 1) * se_extreme_ratio,
    extreme_stats_count = sum(extreme_ratio > 0.3, na.rm = TRUE),
    total_stats = n(),
    pct_problematic = extreme_stats_count / total_stats * 100,
    .groups = "drop"
  ) %>%
  arrange(component, pct_problematic)

# Display the overall metrics table
kable(overall_metrics, digits = 3,
      col.names = c("Model", "Display Name", "Component", "Model Type", 
                    "Mean PPP", "Median PPP", "SD PPP", "N Stats", "SE PPP", 
                    "CI Lower PPP", "CI Upper PPP", 
                    "Mean Extreme Ratio", "SD Extreme Ratio", "SE Extreme Ratio",
                    "CI Lower ER", "CI Upper ER",
                    "# Problematic Stats", "Total Stats", "% Problematic"),
      caption = "Overall PPC Performance by Model and Component") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize overall model performance by component with error bars
component_perf_plot <- overall_metrics %>%
  mutate(label_text = sprintf("%.1f%%", pct_problematic)) %>%
  ggplot(aes(x = reorder(model_display, mean_extreme_ratio), 
             y = mean_extreme_ratio, 
             fill = mean_ppp)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = ci_lower_er, ymax = ci_upper_er), width = 0.2) +
  geom_text(aes(label = label_text), 
            position = position_stack(vjust = 0.5), 
            color = "white", fontface = "bold") +
  facet_wrap(~ component, scales = "free_y") +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.4, limits = c(0, 0.5),
                     name = "Mean PPP\n(closer to 0.5 is better)") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Model Performance by Component",
       subtitle = "Percentage of problematic statistics shown in bars with 95% confidence intervals",
       x = "Model", 
       y = "Mean Proportion of Extreme PPP Values",
       fill = "Mean PPP") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(component_perf_plot)

# Create a more detailed model comparison by component with error bars
model_comp_plot <- overall_metrics %>%
  ggplot(aes(x = reorder(model_display, -mean_ppp), 
             y = mean_ppp, 
             fill = component)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = ci_lower_ppp, ymax = ci_upper_ppp),
                position = position_dodge(width = 0.9),
                width = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, 
            size = 3) +
  scale_y_continuous(limits = c(0, 0.7)) +
  scale_fill_brewer(palette = "Set1") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Mean PPP by Model and Component",
       subtitle = "Values closer to 0.5 indicate better fit (with 95% confidence intervals)",
       x = "Model", 
       y = "Mean PPP",
       fill = "Component") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(model_comp_plot)

# Create a scatter plot of mean PPP vs. extreme ratio
ppp_scatter <- ggplot(overall_metrics, 
       aes(x = abs(mean_ppp - 0.5), y = mean_extreme_ratio, 
           color = component, shape = model_type, label = model_display)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_errorbar(aes(ymin = ci_lower_er, ymax = ci_upper_er), width = 0.01, alpha = 0.5) +
  geom_errorbarh(aes(xmin = abs(ci_lower_ppp - 0.5), xmax = abs(ci_upper_ppp - 0.5)), height = 0.01, alpha = 0.5) +
  geom_text_repel(size = 3, nudge_x = 0.02, nudge_y = 0.02, max.overlaps = 30) +
  scale_x_continuous(limits = c(0, 0.3), 
                    labels = scales::percent) +
  scale_y_continuous(limits = c(0, 0.7), 
                    labels = scales::percent) +
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(16, 17, 15)) +
  theme_minimal() +
  labs(title = "Model Performance: Mean PPP Deviation vs. Extreme Ratio",
       subtitle = "Better models appear in the bottom-left corner (with 95% confidence intervals)",
       x = "Mean PPP Deviation from 0.5", 
       y = "Mean Proportion of Extreme PPP Values",
       color = "Component",
       shape = "Model Type") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(ppp_scatter)

# Create a faceted version to better separate model types
faceted_ppp_scatter <- ggplot(overall_metrics, 
       aes(x = abs(mean_ppp - 0.5), y = mean_extreme_ratio, 
           color = component, label = model_display)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_errorbar(aes(ymin = ci_lower_er, ymax = ci_upper_er), width = 0.01, alpha = 0.5) +
  geom_errorbarh(aes(xmin = abs(ci_lower_ppp - 0.5), xmax = abs(ci_upper_ppp - 0.5)), height = 0.01, alpha = 0.5) +
  geom_text_repel(size = 3, nudge_x = 0.02, nudge_y = 0.02, max.overlaps = 15) +
  facet_wrap(~ model_type) +
  scale_x_continuous(limits = c(0, 0.3), 
                    labels = scales::percent) +
  scale_y_continuous(limits = c(0, 0.7), 
                    labels = scales::percent) +
  scale_color_brewer(palette = "Set1") +
  theme_minimal() +
  labs(title = "Model Performance by Type: Mean PPP Deviation vs. Extreme Ratio",
       subtitle = "Better models appear in the bottom-left corner (with 95% confidence intervals)",
       x = "Mean PPP Deviation from 0.5", 
       y = "Mean Proportion of Extreme PPP Values",
       color = "Component") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(faceted_ppp_scatter)
```

## RT Analysis 

```{r rt-analysis, fig.height=10, fig.width=14, fig.keep='all'}
# Get RT statistics from the configuration
play_rt_stats <- model_config$key_statistics$play_rt
skip_rt_stats <- model_config$key_statistics$skip_rt
rt_all_stats <- c(play_rt_stats, skip_rt_stats)

# Create human-readable labels for RT metrics
rt_metric_labels <- c(
  "rt_play_mean" = "Play RT - Mean",
  "rt_play_median" = "Play RT - Median",
  "rt_play_quantiles_10%" = "Play RT - 10th Percentile",
  "rt_play_quantiles_30%" = "Play RT - 30th Percentile",
  "rt_play_quantiles_50%" = "Play RT - 50th Percentile",
  "rt_play_quantiles_70%" = "Play RT - 70th Percentile",
  "rt_play_quantiles_90%" = "Play RT - 90th Percentile",
  "rt_skip_mean" = "Skip RT - Mean",
  "rt_skip_median" = "Skip RT - Median",
  "rt_skip_quantiles_10%" = "Skip RT - 10th Percentile",
  "rt_skip_quantiles_30%" = "Skip RT - 30th Percentile",
  "rt_skip_quantiles_50%" = "Skip RT - 50th Percentile",
  "rt_skip_quantiles_70%" = "Skip RT - 70th Percentile",
  "rt_skip_quantiles_90%" = "Skip RT - 90th Percentile"
)

# Filter for RT statistics across models with DDM components
rt_metrics <- ssm_summaries %>%
  filter(statistic %in% rt_all_stats) %>%
  mutate(
    metric_label = rt_metric_labels[statistic],
    rt_type = ifelse(grepl("^rt_play", statistic), "Play RT", "Skip RT"),
    statistic_type = case_when(
      grepl("mean$", statistic) ~ "Mean",
      grepl("median$", statistic) ~ "Median",
      grepl("quantiles", statistic) ~ str_extract(statistic, "[0-9]+%"),
      TRUE ~ "Other"
    )
  )

# Create a comparison table
rt_comparison <- rt_metrics %>%
  select(model_display, statistic, mean_ppp, extreme_ratio) %>%
  pivot_wider(names_from = statistic, 
              values_from = c(mean_ppp, extreme_ratio)) %>%
  arrange(model_display)

# Function to create a properly formatted table with headers
create_metrics_table <- function(data, stat_groups, title) {
  # Calculate the number of statistics in each group for header spans
  group_counts <- sapply(stat_groups, length)
  
  # Create header row labels
  header_labels <- c(" " = 1)
  for (group_name in names(stat_groups)) {
    header_labels <- c(header_labels, "Mean PPP Values" = group_counts[group_name])
  }
  for (group_name in names(stat_groups)) {
    header_labels <- c(header_labels, "Extreme Ratios" = group_counts[group_name])
  }
  
  # Display the table with better formatting
  kable(data, digits = 3, caption = title) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    add_header_above(header_labels)
}

# Display the RT metrics table
create_metrics_table(
  rt_comparison, 
  list(
    play_rt = play_rt_stats,
    skip_rt = skip_rt_stats
  ),
  "RT Metrics: Mean PPP Values and Extreme Ratios by Model"
)

# Calculate summary statistics for RT metrics by model
rt_summary_by_model <- rt_metrics %>%
  group_by(model_display, rt_type) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    sd_ppp = sd(mean_ppp, na.rm = TRUE),
    n_stats = n(),
    se_ppp = sd_ppp / sqrt(n_stats),
    ci_lower = mean_ppp - qt(0.975, n_stats - 1) * se_ppp,
    ci_upper = mean_ppp + qt(0.975, n_stats - 1) * se_ppp,
    mean_extreme = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

# Create comparison plot for Play vs Skip RT by model
rt_comparison_plot <- ggplot(rt_summary_by_model, 
       aes(x = reorder(model_display, mean_ppp), y = mean_ppp, fill = rt_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(width = 0.9),
                width = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_brewer(palette = "Set1") +
  coord_flip() +
  theme_minimal() +
  labs(title = "RT Fit by Model: Play vs. Skip Reaction Times",
       subtitle = "Mean PPP values with 95% confidence intervals (values closer to 0.5 indicate better fit)",
       x = "Model", 
       y = "Mean PPP Value",
       fill = "RT Type") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(rt_comparison_plot)

# Visualize RT metrics distribution for Play RTs
play_rt_plot <- rt_metrics %>%
  filter(rt_type == "Play RT") %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d(name = "Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "right") +
  labs(title = "Mean PPP Values for PLAY Reaction Time Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(play_rt_plot)

# Visualize RT metrics distribution for Skip RTs
skip_rt_plot <- rt_metrics %>%
  filter(rt_type == "Skip RT") %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d(name = "Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "right") +
  labs(title = "Mean PPP Values for SKIP/PASS Reaction Time Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(skip_rt_plot)

# Create a heatmap for RT metrics across all models
rt_metrics_heatmap <- rt_metrics %>%
  ggplot(aes(x = statistic, y = model_display, fill = mean_ppp)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), color = "black", size = 3) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                      midpoint = 0.5, limits = c(0, 1)) +
  facet_grid(. ~ rt_type, scales = "free_x", space = "free") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "RT Metrics Heatmap: Mean PPP Values",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Model",
       fill = "Mean PPP") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(rt_metrics_heatmap)

# Create a similar heatmap for extreme ratios
extreme_ratio_heatmap <- rt_metrics %>%
  ggplot(aes(x = statistic, y = model_display, fill = extreme_ratio)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", extreme_ratio)), color = "black", size = 3) +
  scale_fill_gradient2(low = "green", mid = "yellow", high = "red", 
                      midpoint = 0.5, limits = c(0, 1)) +
  facet_grid(. ~ rt_type, scales = "free_x", space = "free") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "RT Metrics Heatmap: Extreme Ratio Values",
       subtitle = "Lower values indicate better fit (fewer subjects with extreme PPP values)",
       x = "Statistic", y = "Model",
       fill = "Extreme\nRatio") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(extreme_ratio_heatmap)

# Analyze RT misfit magnitudes
# Function to calculate RT misfit in ms
calculate_rt_misfit <- function(model_name) {
  if (!model_name %in% names(ppc_data) || 
      is.null(ppc_data[[model_name]]$subjects)) {
    return(NULL)
  }
  
  # Get all subjects
  subject_ids <- names(ppc_data[[model_name]]$subjects)
  
  # Initialize empty dataframe for misfits
  rt_misfits <- data.frame()
  
  # Iterate through subjects and extract RT statistics
  for (subject_id in subject_ids) {
    subject_data <- ppc_data[[model_name]]$subjects[[subject_id]]
    
    # Remove the specific row if it exists to avoid errors
    if (!is.null(subject_data$summary$ssm) && "has_rt_data" %in% rownames(subject_data$summary$ssm)) {
      subject_data$summary$ssm <- subject_data$summary$ssm[-which(rownames(subject_data$summary$ssm) == "has_rt_data"), ]
    }
    
    # Check if subject has SSM summary
    if (!is.list(subject_data$summary) || 
        !("ssm" %in% names(subject_data$summary))) {
      next
    }
    
    # Extract RT metrics
    subject_rt <- subject_data$summary$ssm
    
    # Filter for RT metrics
    rt_rows <- subject_rt %>%
      filter(grepl("rt_", statistic))
    
    # Calculate absolute difference in ms (convert to ms by multiplying by 1000)
    rt_rows <- rt_rows %>%
      mutate(
        misfit_ms = abs(observed - predicted_mean) * 1000,
        relative_misfit = abs(observed - predicted_mean) / observed,
        subject_id = subject_id,
        model = model_name
      )
    
    # Combine with the main dataframe
    rt_misfits <- bind_rows(rt_misfits, rt_rows)
  }
  
  return(rt_misfits)
}

# Calculate RT misfits for all hybrid models
rt_misfit_models <- available_hybrid_models
all_rt_misfits <- bind_rows(
  lapply(rt_misfit_models, calculate_rt_misfit)
)
```

```{r rt-analysis2, fig.height=10, fig.width=14, fig.keep='all'}

# Process RT misfit data if we have it
if (nrow(all_rt_misfits) > 0) {
  # Add model display names and RT type
  all_rt_misfits <- all_rt_misfits %>%
    mutate(
      model_display = model_display_names[model],
      rt_type = case_when(
        grepl("^rt_play", statistic) ~ "Play RT",
        grepl("^rt_skip", statistic) ~ "Skip RT",
        TRUE ~ "Other RT"
      ),
      metric_label = rt_metric_labels[statistic],
      statistic_clean = case_when(
        grepl("mean$", statistic) ~ "Mean",
        grepl("median$", statistic) ~ "Median",
        grepl("quantiles", statistic) ~ str_extract(statistic, "[0-9]+%"),
        TRUE ~ statistic
      )
    )
  
  # Summarize by model, statistic, and RT type
  rt_misfit_summary <- all_rt_misfits %>%
    group_by(model_display, statistic, rt_type, metric_label) %>%
    summarize(
      mean_misfit_ms = mean(misfit_ms, na.rm = TRUE),
      median_misfit_ms = median(misfit_ms, na.rm = TRUE),
      sd_misfit_ms = sd(misfit_ms, na.rm = TRUE),
      n_subjects = n(),
      se_misfit_ms = sd_misfit_ms / sqrt(n_subjects),
      ci_lower = mean_misfit_ms - qt(0.975, n_subjects - 1) * se_misfit_ms,
      ci_upper = mean_misfit_ms + qt(0.975, n_subjects - 1) * se_misfit_ms,
      max_misfit_ms = max(misfit_ms, na.rm = TRUE),
      mean_relative_misfit = mean(relative_misfit, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    arrange(rt_type, statistic, mean_misfit_ms)
  
  # Display summary table
  kable(rt_misfit_summary %>% 
          select(model_display, rt_type, statistic, mean_misfit_ms, median_misfit_ms, 
                ci_lower, ci_upper, max_misfit_ms, mean_relative_misfit, n_subjects), 
        digits = 1,
        col.names = c("Model", "RT Type", "Statistic", "Mean Misfit (ms)", 
                     "Median Misfit (ms)", "95% CI Lower", "95% CI Upper", 
                     "Max Misfit (ms)", "Mean Relative Misfit", "# Subjects"),
        caption = "RT Misfit Magnitudes in Milliseconds") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                  full_width = FALSE)
  
  # Create visualization of mean RT misfits by model and statistic
  # First, ensure each statistic appears only in its relevant RT type facet
  rt_misfit_plot_data <- rt_misfit_summary %>%
    # Keep only the relevant statistics for each RT type
    filter(
      (rt_type == "Play RT" & grepl("^rt_play", statistic)) |
      (rt_type == "Skip RT" & grepl("^rt_skip", statistic))
    ) %>%
    # Create cleaner labels without the rt_play/rt_skip prefix
    mutate(
      stat_label = gsub("^rt_(play|skip)_", "", statistic)
    )
  
  # Then create the plot with the filtered data
  rt_misfit_plot <- ggplot(rt_misfit_plot_data, 
         aes(x = stat_label, y = mean_misfit_ms, fill = unname(unlist(model_display)))) +
    geom_bar(stat = "identity", position = "dodge") +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                 position = position_dodge(width = 0.9),
                 width = 0.25) +
    facet_wrap(~ rt_type, scales = "free_y") +
    scale_fill_viridis_d(name = "Model") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "right") +
    labs(title = "Mean RT Misfit Magnitude by Model and Statistic",
         subtitle = "With 95% confidence intervals",
         x = "RT Statistic",
         y = "Mean Misfit (ms)",
         fill = "Model") +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      strip.text = element_text(size = 12, face = "bold"),
      axis.title = element_text(size = 11),
      legend.title = element_text(size = 10)
    )
  print(rt_misfit_plot)
  
  # Create a boxplot of RT misfit distributions by model
  rt_boxplot <- ggplot(all_rt_misfits, 
         aes(x = as.character(unlist(all_rt_misfits$model_display)), y = misfit_ms, fill = as.character(unlist(model_display)))) +
    geom_boxplot(outlier.shape = 1, outlier.size = 1) +
    facet_wrap(~ rt_type, scales = "free_y") +
    scale_fill_viridis_d(name = "Model") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    labs(title = "Distribution of RT Misfits by Model",
         subtitle = "Boxplots show median, IQR, and range (excluding outliers)",
         x = "Model",
         y = "Misfit Magnitude (ms)") +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      strip.text = element_text(size = 12, face = "bold"),
      axis.title = element_text(size = 11)
    )
  print(rt_boxplot)
  
  # Create a violin plot for RT misfit distributions
  rt_violin <- ggplot(all_rt_misfits, 
         aes(x = as.character(unlist(all_rt_misfits$model_display)), y = misfit_ms, fill = as.character(unlist(model_display)))) +
    geom_violin(trim = TRUE, scale = "width") +
    geom_boxplot(width = 0.2, outlier.shape = NA, alpha = 0.5) +
    facet_wrap(~ rt_type, scales = "free_y") +
    scale_fill_viridis_d(name = "Model") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    coord_cartesian(ylim = c(0, 500)) +  # Limit y-axis to focus on majority of data
    labs(title = "Distribution of RT Misfits by Model",
         subtitle = "Violin plots show distribution shape with embedded boxplots",
         x = "Model",
         y = "Misfit Magnitude (ms)") +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      strip.text = element_text(size = 12, face = "bold"),
      axis.title = element_text(size = 11)
    )
  print(rt_violin)
  
  # Calculate mean RT misfits by quantile to examine patterns
  quantile_misfits <- all_rt_misfits %>%
    filter(grepl("quantiles", statistic)) %>%
    mutate(
      quantile = as.numeric(gsub("[^0-9]", "", statistic_clean)) / 100
    ) %>%
    group_by(model_display, rt_type, quantile) %>%
    summarize(
      mean_misfit_ms = mean(misfit_ms, na.rm = TRUE),
      sd_misfit_ms = sd(misfit_ms, na.rm = TRUE),
      n = n(),
      se_misfit_ms = sd_misfit_ms / sqrt(n),
      ci_lower = mean_misfit_ms - qt(0.975, n - 1) * se_misfit_ms,
      ci_upper = mean_misfit_ms + qt(0.975, n - 1) * se_misfit_ms,
      .groups = "drop"
    )
  
  # Create a line plot of RT misfits by quantile
  quantile_rt_plot <- ggplot(quantile_misfits, 
         aes(x = quantile, y = mean_misfit_ms, color = as.character(unlist(model_display)), group = as.character(unlist(model_display)))) +
    geom_line(size = 1) +
    geom_point(size = 3) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper, fill = as.character(unlist(model_display))), 
                alpha = 0.2, color = NA) +
    facet_wrap(~ rt_type, scales = "free_y") +
    scale_color_viridis_d(name = "Model") +
    scale_fill_viridis_d(name = "Model") +
    theme_minimal() +
    labs(title = "RT Misfit Patterns Across RT Quantiles",
         subtitle = "With 95% confidence intervals",
         x = "RT Quantile",
         y = "Mean Misfit (ms)",
         color = "Model",
         fill = "Model") +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      strip.text = element_text(size = 12, face = "bold"),
      axis.title = element_text(size = 11),
      legend.title = element_text(size = 10)
    )
  print(quantile_rt_plot)
}
```


```{r rt-misfit-heatmap, fig.keep='all'}
# Create a heatmap of misfit patterns across all RT metrics and models
if (exists("rt_misfit_summary") && nrow(rt_misfit_summary) > 0) {
  # First ensure we have labels for all statistics
  all_stats <- unique(rt_misfit_summary$statistic)
  missing_labels <- setdiff(all_stats, names(rt_metric_labels))
  
  # Create temporary labels for any missing ones
  temp_labels <- setNames(missing_labels, missing_labels)
  all_labels <- c(rt_metric_labels, temp_labels)
  
  # Now create the heatmap data
  rt_misfit_heatmap <- rt_misfit_summary %>%
    mutate(
      # Just use the labels directly without trying to factor with levels
      statistic_label = all_labels[statistic]
    )
  
  # Check data is valid before plotting
  if (is.numeric(rt_misfit_heatmap$mean_misfit_ms) && 
      !any(is.na(rt_misfit_heatmap$statistic_label)) &&
      nrow(rt_misfit_heatmap) > 0) {
    
    # Create the heatmap - now with proper data checks
    rt_misfit_heatmap_plot <- ggplot(rt_misfit_heatmap, 
           aes(x = as.character(unlist(statistic_label)), y = as.character(unlist(model_display)), fill = mean_misfit_ms)) +
      geom_tile(color = "white") +
      geom_text(aes(label = sprintf("%.1f", mean_misfit_ms)), color = "black", size = 3) +
      scale_fill_gradient(low = "green", high = "red", name = "Mean Misfit (ms)") +
      facet_grid(. ~ rt_type, scales = "free_x", space = "free") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      labs(title = "RT Misfit Magnitude Heatmap",
           subtitle = "Lower values (green) indicate better RT prediction accuracy",
           x = "RT Metric",
           y = "Model") +
      theme(
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        strip.text = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 11),
        legend.title = element_text(size = 10)
      )
    print(rt_misfit_heatmap_plot)
  } else {
    cat("Cannot create RT misfit heatmap - invalid data\n")
  }
} else {
  cat("No RT misfit summary data available for heatmap\n")
}
```

## Choice vs. RT+Choice Models

```{r choice-vs-rt-models, fig.height=10, fig.width=14}
# Compare choice metrics across models
choice_stats <- model_config$key_statistics$choice
deck_selection_stats <- model_config$key_statistics$deck_selection
rl_performance_stats <- model_config$key_statistics$rl_performance
choice_all_stats <- c(choice_stats, deck_selection_stats, rl_performance_stats)

# Human-readable labels for choice metrics
choice_metric_labels <- c(
  "choice_prob" = "Choice Probability",
  "good_deck_ratio" = "Good Deck Ratio",
  "new_good_deck_ratio" = "New Good Deck Ratio",
  "new_bad_deck_ratio" = "New Bad Deck Ratio",
  "skip_ratio" = "Skip Ratio",
  "total_money" = "Total Money",
  "avg_outcome" = "Average Outcome"
)

# Get choice metrics for all models
choice_metrics <- all_summaries %>%
  filter(statistic %in% choice_all_stats) %>%
  mutate(metric_label = choice_metric_labels[statistic])

# Summarize choice metrics by model
choice_summary <- choice_metrics %>%
  group_by(model, model_display, model_type) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    sd_ppp = sd(mean_ppp, na.rm = TRUE),
    n_stats = n(),
    se_ppp = sd_ppp / sqrt(n_stats),
    ci_lower_ppp = mean_ppp - qt(0.975, n_stats - 1) * se_ppp,
    ci_upper_ppp = mean_ppp + qt(0.975, n_stats - 1) * se_ppp,
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    sd_extreme_ratio = sd(extreme_ratio, na.rm = TRUE),
    se_extreme_ratio = sd_extreme_ratio / sqrt(n_stats),
    ci_lower_er = mean_extreme_ratio - qt(0.975, n_stats - 1) * se_extreme_ratio,
    ci_upper_er = mean_extreme_ratio + qt(0.975, n_stats - 1) * se_extreme_ratio,
    .groups = "drop"
  )

# Summarize RT metrics by model (hybrid models only)
rt_summary <- rt_metrics %>%
  group_by(model, model_display) %>%
  summarize(
    rt_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    rt_sd_ppp = sd(mean_ppp, na.rm = TRUE),
    rt_n_stats = n(),
    rt_se_ppp = rt_sd_ppp / sqrt(rt_n_stats),
    rt_ci_lower_ppp = rt_mean_ppp - qt(0.975, rt_n_stats - 1) * rt_se_ppp,
    rt_ci_upper_ppp = rt_mean_ppp + qt(0.975, rt_n_stats - 1) * rt_se_ppp,
    rt_mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    rt_sd_extreme_ratio = sd(extreme_ratio, na.rm = TRUE),
    rt_se_extreme_ratio = rt_sd_extreme_ratio / sqrt(rt_n_stats),
    rt_ci_lower_er = rt_mean_extreme_ratio - qt(0.975, rt_n_stats - 1) * rt_se_extreme_ratio,
    rt_ci_upper_er = rt_mean_extreme_ratio + qt(0.975, rt_n_stats - 1) * rt_se_extreme_ratio,
    .groups = "drop"
  )

# Combine for hybrid models
choice_rt_comparison <- choice_summary %>%
  filter(model_type == "Hybrid (RL+DDM)") %>%
  left_join(rt_summary, by = c("model", "model_display")) %>%
  mutate(
    choice_fit = abs(mean_ppp - 0.5),  # Closer to 0 is better
    rt_fit = abs(rt_mean_ppp - 0.5),    # Closer to 0 is better
    overall_fit = (choice_fit + rt_fit) / 2  # Average misfit
  ) %>%
  arrange(overall_fit)

# Display comparison table
kable(choice_rt_comparison %>% 
        select(model_display, mean_ppp, mean_extreme_ratio, 
              rt_mean_ppp, rt_mean_extreme_ratio, 
              choice_fit, rt_fit, overall_fit), 
      digits = 3,
      col.names = c("Model", "Choice Mean PPP", "Choice Extreme Ratio",
                   "RT Mean PPP", "RT Extreme Ratio", 
                   "Choice Fit", "RT Fit", "Overall Fit"),
      caption = "Choice vs. RT Fit for Hybrid Models") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Create a comprehensive comparison of all models
all_model_comparison <- choice_summary %>%
  full_join(rt_summary, by = c("model", "model_display"), suffix = c("_choice", "_rt")) %>%
  mutate(
    model_type = case_when(
      model %in% rl_only_models ~ "RL Only",
      model %in% ddm_only_models ~ "DDM Only",
      model %in% hybrid_models ~ "Hybrid (RL+DDM)",
      TRUE ~ "Unknown"
    ),
    choice_fit = abs(mean_ppp - 0.5),
    rt_fit = if_else(is.na(rt_mean_ppp), NA_real_, abs(rt_mean_ppp - 0.5)),
    overall_fit = case_when(
      model_type == "RL Only" ~ choice_fit,
      model_type == "DDM Only" ~ rt_fit,
      model_type == "Hybrid (RL+DDM)" ~ (choice_fit + rt_fit) / 2,
      TRUE ~ NA_real_
    )
  ) %>%
  arrange(model_type, overall_fit)

# Display the comprehensive comparison
kable(all_model_comparison %>% 
        select(model_display, model_type, 
               mean_ppp, mean_extreme_ratio, 
               rt_mean_ppp, rt_mean_extreme_ratio, 
               choice_fit, rt_fit, overall_fit), 
      digits = 3,
      col.names = c("Model", "Type", 
                   "Choice Mean PPP", "Choice Extreme Ratio",
                   "RT Mean PPP", "RT Extreme Ratio", 
                   "Choice Fit", "RT Fit", "Overall Fit"),
      caption = "Comprehensive Comparison of All Models") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Create visualization of choice fit vs. RT fit with confidence intervals
choice_rt_scatter <- ggplot(choice_rt_comparison, 
       aes(x = choice_fit, y = rt_fit, color = model_display)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = abs(rt_ci_lower_ppp - 0.5), ymax = abs(rt_ci_upper_ppp - 0.5)), 
                width = 0.01, alpha = 0.5) +
  geom_errorbarh(aes(xmin = abs(ci_lower_ppp - 0.5), xmax = abs(ci_upper_ppp - 0.5)), 
                height = 0.01, alpha = 0.5) +
  geom_text_repel(aes(label = model_display), box.padding = 0.5, max.overlaps = 30) +
  scale_x_continuous(limits = c(0, 0.5)) +
  scale_y_continuous(limits = c(0, 0.5)) +
  scale_color_viridis_d() +
  theme_minimal() +
  labs(title = "Choice Fit vs. RT Fit Tradeoff in Hybrid Models",
       subtitle = "Lower values indicate better fit (less deviation from PPP = 0.5)",
       x = "Choice Fit Deviation",
       y = "RT Fit Deviation",
       color = "Model") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.position = "none"
  )
print(choice_rt_scatter)

# Create a comparison scatter plot of choice vs. RT extreme ratios
extreme_ratio_scatter <- ggplot(choice_rt_comparison, 
       aes(x = mean_extreme_ratio, y = rt_mean_extreme_ratio, color = model_display)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = rt_ci_lower_er, ymax = rt_ci_upper_er), 
                width = 0.01, alpha = 0.5) +
  geom_errorbarh(aes(xmin = ci_lower_er, xmax = ci_upper_er), 
                height = 0.01, alpha = 0.5) +
  geom_text_repel(aes(label = model_display), box.padding = 0.5, max.overlaps = 30) +
  scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_color_viridis_d() +
  theme_minimal() +
  labs(title = "Choice vs. RT Extreme Ratio Tradeoff",
       subtitle = "Lower values indicate better fit (fewer extreme PPP values)",
       x = "Choice Extreme Ratio",
       y = "RT Extreme Ratio",
       color = "Model") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.position = "none"
  )
print(extreme_ratio_scatter)

# Compare RL vs. Hybrid models - Performance on choice metrics
rl_hybrid_choice_comparison <- choice_summary %>%
  filter(model_type %in% c("RL Only", "Hybrid (RL+DDM)")) %>%
  mutate(
    base_model = str_remove(model, "_ddm$"),
    has_matching_pair = base_model %in% str_remove(model[model_type == "Hybrid (RL+DDM)"], "_ddm$")
  )

# Focus on models that have both RL-only and hybrid versions
matched_models <- rl_hybrid_choice_comparison %>%
  filter(model_type == "RL Only", has_matching_pair) %>%
  pull(base_model)

matched_comparison <- rl_hybrid_choice_comparison %>%
  filter(base_model %in% matched_models) %>%
  select(model, model_display, model_type, base_model, mean_ppp, mean_extreme_ratio) %>%
  arrange(base_model, model_type)

# Visualize the matched comparison
matched_comparison_plot <- ggplot(matched_comparison, 
       aes(x = reorder(base_model, mean_ppp), y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3) +
  scale_fill_manual(values = model_type_colors) +
  theme_minimal() +
  labs(title = "Impact of Adding RT Component on Choice Performance",
       subtitle = "Comparing RL-only vs Hybrid versions of the same base models",
       x = "Base Model",
       y = "Mean PPP (Choice Metrics)",
       fill = "Model Type") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.title = element_text(size = 10)
  )
print(matched_comparison_plot)

# Detail model comparison: PPP for choice metrics vs. RT metrics
hybrid_metric_comparison <- bind_rows(
  choice_metrics %>% 
    filter(model %in% hybrid_models) %>%
    mutate(metric_type = "Choice"),
  rt_metrics %>% 
    filter(model %in% hybrid_models) %>%
    mutate(metric_type = "RT")
)

# Visualize the comparison
hybrid_metrics_plot <- ggplot(hybrid_metric_comparison, 
       aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  facet_wrap(~ metric_type, scales = "free_x") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d(name = "Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "right") +
  labs(title = "PPP Values for Choice vs. RT Metrics in Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", 
       y = "Mean PPP Value") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(hybrid_metrics_plot)
```

# Individual Differences Analysis

## Subject-Level Prediction Scatter Plots

```{r subject-level-plots, fig.height=10, fig.width=12, fig.keep='all'}
# Function to create subject-level prediction scatter plot
create_subject_scatter <- function(model_name, metric_name, component = "rl") {
  if (!model_name %in% names(ppc_data)) {
    return(NULL)
  }
  
  # Get all subjects
  subject_ids <- names(ppc_data[[model_name]]$subjects)
  
  # Initialize empty dataframe for observed and predicted values
  scatter_data <- data.frame()
  
  # Iterate through subjects
  for (subject_id in subject_ids) {
    subject_data <- ppc_data[[model_name]]$subjects[[subject_id]]
    
    # Check access path based on component
    if (component == "rl") {
      # For RL-only models or RL component of hybrid models
      if ("summary" %in% names(subject_data) && 
          (is.data.frame(subject_data$summary) || 
           (is.list(subject_data$summary) && "rl" %in% names(subject_data$summary)))) {
        
        # Get the summary data
        if (is.data.frame(subject_data$summary)) {
          summary_df <- subject_data$summary
        } else {
          summary_df <- subject_data$summary$rl
        }
        
        # Find the row for this metric
        metric_row <- summary_df[summary_df$statistic == metric_name, ]
        
        if (nrow(metric_row) > 0) {
          # Extract observed and predicted values
          observed <- metric_row$observed
          predicted <- metric_row$predicted_mean
          
          # Add to dataframe
          scatter_data <- bind_rows(scatter_data, 
                                   data.frame(
                                     subject_id = subject_id,
                                     observed = observed,
                                     predicted = predicted
                                   ))
        }
      }
    } else if (component == "ssm") {
      # For DDM-only models or SSM component of hybrid models
      if ("summary" %in% names(subject_data) && 
          (is.data.frame(subject_data$summary) || 
           (is.list(subject_data$summary) && "ssm" %in% names(subject_data$summary)))) {
        
        # Get the summary data
        if (is.data.frame(subject_data$summary)) {
          summary_df <- subject_data$summary
        } else {
          summary_df <- subject_data$summary$ssm
        }
        
        # Find the row for this metric
        metric_row <- summary_df[summary_df$statistic == metric_name, ]
        
        if (nrow(metric_row) > 0) {
          # Extract observed and predicted values
          observed <- metric_row$observed
          predicted <- metric_row$predicted_mean
          
          # Add to dataframe
          scatter_data <- bind_rows(scatter_data, 
                                   data.frame(
                                     subject_id = subject_id,
                                     observed = observed,
                                     predicted = predicted
                                   ))
        }
      }
    }
  }
  
  # If we have data, create the scatter plot
  if (nrow(scatter_data) > 0) {
    # Calculate correlation
    correlation <- round(cor(scatter_data$observed, scatter_data$predicted, use = "pairwise.complete.obs"), 3)
    
    # Calculate RMSE
    rmse <- round(sqrt(mean((scatter_data$observed - scatter_data$predicted)^2, na.rm = TRUE)), 3)
    
    # Calculate bootstrap CI for correlation
    boot_correlation <- function(data, indices) {
      cor(data$observed[indices], data$predicted[indices], use = "pairwise.complete.obs")
    }
    
    # Run bootstrap if we have enough data points
    if (nrow(scatter_data) >= 10) {
      boot_result <- boot(scatter_data, boot_correlation, R = 1000)
      ci <- boot.ci(boot_result, type = "perc")
      ci_text <- sprintf("\n95%% CI: [%.3f, %.3f]", ci$percent[4], ci$percent[5])
    } else {
      ci_text <- ""
    }
    
    # Create the scatter plot with 95% prediction bands
    result_plot <- ggplot(scatter_data, aes(x = observed, y = predicted)) +
      geom_point(alpha = 0.7) +
      geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red") +
      geom_smooth(method = "lm", formula = y ~ x, color = "blue", level = 0.95) +
      annotate("text", x = min(scatter_data$observed, na.rm = TRUE), 
               y = max(scatter_data$predicted, na.rm = TRUE),
               label = paste("r =", correlation, ci_text, "\nRMSE =", rmse),
               hjust = 0, vjust = 1) +
      labs(
        title = paste("Subject-Level Predictions for", metric_name),
        subtitle = paste("Model:", model_display_names[model_name]),
        x = "Observed Value",
        y = "Predicted Value"
      ) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 11)
      )
    
    return(result_plot)
  } else {
    return(NULL)
  }
}

# Function to create multi-model comparison for a specific metric
create_metric_comparison <- function(metric_name, model_list, component = "rl") {
  # Filter available models
  available_models <- intersect(model_list, names(ppc_data))
  
  # Initialize a list to store results for each model
  results_list <- list()
  
  # Generate results for each model
  for (model in available_models) {
    # Get subject-level data
    scatter_data <- data.frame()
    
    # Get all subjects
    subject_ids <- names(ppc_data[[model]]$subjects)
    
    # Get model display name safely
    model_display_name <- ifelse(model %in% names(model_display_names), 
                                as.character(model_display_names[[model]]), 
                                model)
    
    # Iterate through subjects
    for (subject_id in subject_ids) {
      subject_data <- ppc_data[[model]]$subjects[[subject_id]]
      
      # Check access path based on component
      if (component == "rl") {
        # For RL-only models or RL component of hybrid models
        if ("summary" %in% names(subject_data) && 
            (is.data.frame(subject_data$summary) || 
             (is.list(subject_data$summary) && "rl" %in% names(subject_data$summary)))) {
          
          # Get the summary data
          if (is.data.frame(subject_data$summary)) {
            summary_df <- subject_data$summary
          } else {
            summary_df <- subject_data$summary$rl
          }
          
          # Find the row for this metric
          metric_row <- summary_df[summary_df$statistic == metric_name, ]
          
          if (nrow(metric_row) > 0) {
            # Extract observed and predicted values
            observed <- metric_row$observed
            predicted <- metric_row$predicted_mean
            
            # Add to dataframe
            scatter_data <- bind_rows(scatter_data, 
                                     data.frame(
                                       subject_id = subject_id,
                                       observed = observed,
                                       predicted = predicted,
                                       model = model,
                                       model_display = model_display_name
                                     ))
          }
        }
      } else if (component == "ssm") {
        # For DDM-only models or SSM component of hybrid models
        if ("summary" %in% names(subject_data) && 
            (is.data.frame(subject_data$summary) || 
             (is.list(subject_data$summary) && "ssm" %in% names(subject_data$summary)))) {
          
          # Get the summary data
          if (is.data.frame(subject_data$summary)) {
            summary_df <- subject_data$summary
          } else {
            summary_df <- subject_data$summary$ssm
          }
          
          # Find the row for this metric
          metric_row <- summary_df[summary_df$statistic == metric_name, ]
          
          if (nrow(metric_row) > 0) {
            # Extract observed and predicted values
            observed <- metric_row$observed
            predicted <- metric_row$predicted_mean
            
            # Add to dataframe
            scatter_data <- bind_rows(scatter_data, 
                                     data.frame(
                                       subject_id = subject_id,
                                       observed = observed,
                                       predicted = predicted,
                                       model = model,
                                       model_display = model_display_name
                                     ))
          }
        }
      }
    }
    
    # Add to results list if we have data
    if (nrow(scatter_data) > 0) {
      results_list[[model]] <- scatter_data
    }
  }
  
  # Combine all results
  all_results <- bind_rows(results_list)
  
  # If we have data, create comparison plot
  if (nrow(all_results) > 0 && ncol(all_results) >= 5) { # Ensure we have all needed columns
    # Ensure model_display is a character vector
    all_results$model_display <- as.character(all_results$model_display)
    
    # Calculate stats for each model
    model_stats <- all_results %>%
      group_by(model, model_display) %>%
      summarize(
        correlation = cor(observed, predicted, use = "pairwise.complete.obs"),
        rmse = sqrt(mean((observed - predicted)^2, na.rm = TRUE)),
        n = n(),
        .groups = "drop"
      ) %>%
      arrange(desc(correlation))
    
    # Create factor levels for ordered display
    model_display_order <- model_stats$model_display[order(-model_stats$correlation)]
    
    # Create faceted plot comparing models
    result_plot <- all_results %>%
      # Join with stats to get ordered facets
      left_join(model_stats, by = c("model", "model_display"), suffix = c("", ".stat")) %>%
      # Order factor levels by correlation
      mutate(
        model_display = factor(
          model_display,
          levels = model_display_order
        )
      ) %>%
      ggplot(aes(x = observed, y = predicted)) +
      geom_point(alpha = 0.5) +
      geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red") +
      geom_smooth(method = "lm", formula = y ~ x, color = "blue") +
      geom_text(
        data = model_stats %>% 
              mutate(model_display = factor(model_display, levels = model_display_order)),
        aes(
          # Position at top-left of each panel
          x = min(all_results$observed, na.rm = TRUE) + 0.05,
          y = max(all_results$predicted, na.rm = TRUE) - 0.05,
          label = sprintf("r = %.3f\nRMSE = %.3f", correlation, rmse)
        ),
        hjust = 0, vjust = 1, size = 3
      ) +
      facet_wrap(~ model_display) +
      labs(
        title = paste("Subject-Level Predictions for", metric_name, "Across Models"),
        subtitle = "Models ordered by correlation (higher is better)",
        x = "Observed Value",
        y = "Predicted Value"
      ) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        strip.text = element_text(size = 10, face = "bold"),
        axis.title = element_text(size = 11)
      )
    
    return(result_plot)
  } else {
    return(NULL)
  }
}

# Create comparisons for key metrics across models
# RL Metrics
rl_metrics_to_plot <- c("good_deck_ratio", "new_good_deck_ratio", "total_money")

# Select a subset of models for better readability
selected_models <- c(
  # Include a mix of RL model types
  "pvldelta", "pvldelta_ddm", 
  "pvldecay", "pvldecay_ddm",
  "ev", "ev_ddm",
  "vppdeltag", "vppdeltag_ddm"
)

# Create comparison plots for RL metrics
for (metric in rl_metrics_to_plot) {
  cat(paste("\n### Cross-Model Comparison for", metric, "\n"))
  comparison_plot <- create_metric_comparison(metric, selected_models, "rl")
  if (!is.null(comparison_plot)) {
    print(comparison_plot)
    # Clean up
    rm(comparison_plot)
    gc()
  } else {
    cat("No data available for multi-model comparison\n")
  }
}

# RT Metrics
rt_metrics_to_plot <- c("rt_play_mean", "rt_skip_mean", "choice_prob")
rt_models_to_compare <- intersect(available_hybrid_models, selected_models)

# Create comparison plots for RT metrics
for (metric in rt_metrics_to_plot) {
  cat(paste("\n### Cross-Model Comparison for", metric, "\n"))
  comparison_plot <- create_metric_comparison(metric, rt_models_to_compare, "ssm")
  if (!is.null(comparison_plot)) {
    print(comparison_plot)
    # Clean up
    rm(comparison_plot)
    gc()
  } else {
    cat("No data available for multi-model comparison\n")
  }
}
```

## Individual Differences Capture

```{r individual-diff-capture, fig.height=10, fig.width=14, fig.keep='all'}
# Function to calculate individual difference correlations
calculate_individual_correlations <- function(model_name, metrics, component = "rl") {
  if (!model_name %in% names(ppc_data)) {
    return(NULL)
  }
  
  # Initialize results dataframe
  results <- data.frame()
  
  # Process each metric
  for (metric_name in metrics) {
    # Get subject-level data
    scatter_data <- data.frame()
    
    # Get all subjects
    subject_ids <- names(ppc_data[[model_name]]$subjects)
    
    # Iterate through subjects
    for (subject_id in subject_ids) {
      subject_data <- ppc_data[[model_name]]$subjects[[subject_id]]
      
      # Check access path based on component
      if (component == "rl") {
        # For RL-only models or RL component of hybrid models
        if ("summary" %in% names(subject_data) && 
            (is.data.frame(subject_data$summary) || 
             (is.list(subject_data$summary) && "rl" %in% names(subject_data$summary)))) {
          
          # Get the summary data
          if (is.data.frame(subject_data$summary)) {
            summary_df <- subject_data$summary
          } else {
            summary_df <- subject_data$summary$rl
          }
          
          # Find the row for this metric
          metric_row <- summary_df[summary_df$statistic == metric_name, ]
          
          if (nrow(metric_row) > 0) {
            # Extract observed and predicted values
            observed <- metric_row$observed
            predicted <- metric_row$predicted_mean
            
            # Add to dataframe
            scatter_data <- bind_rows(scatter_data, 
                                     data.frame(
                                       subject_id = subject_id,
                                       observed = observed,
                                       predicted = predicted
                                     ))
          }
        }
      } else if (component == "ssm") {
        # For DDM-only models or SSM component of hybrid models
        if ("summary" %in% names(subject_data) && 
            (is.data.frame(subject_data$summary) || 
             (is.list(subject_data$summary) && "ssm" %in% names(subject_data$summary)))) {
          
          # Get the summary data
          if (is.data.frame(subject_data$summary)) {
            summary_df <- subject_data$summary
          } else {
            summary_df <- subject_data$summary$ssm
          }
          
          # Find the row for this metric
          metric_row <- summary_df[summary_df$statistic == metric_name, ]
          
          if (nrow(metric_row) > 0) {
            # Extract observed and predicted values
            observed <- metric_row$observed
            predicted <- metric_row$predicted_mean
            
            # Add to dataframe
            scatter_data <- bind_rows(scatter_data, 
                                     data.frame(
                                       subject_id = subject_id,
                                       observed = observed,
                                       predicted = predicted
                                     ))
          }
        }
      }
    }
    
    # Calculate correlation and RMSE if we have data
    if (nrow(scatter_data) > 0) {
      correlation <- cor(scatter_data$observed, scatter_data$predicted, 
                        use = "pairwise.complete.obs")
      rmse <- sqrt(mean((scatter_data$observed - scatter_data$predicted)^2, na.rm = TRUE))
      
      # Calculate bootstrap CI for correlation if sufficient data
      if (nrow(scatter_data) >= 10) {
        boot_correlation <- function(data, indices) {
          cor(data$observed[indices], data$predicted[indices], use = "pairwise.complete.obs")
        }
        
        boot_result <- boot(scatter_data, boot_correlation, R = 1000)
        ci <- boot.ci(boot_result, type = "perc")
        ci_lower <- ci$percent[4]
        ci_upper <- ci$percent[5]
      } else {
        ci_lower <- NA
        ci_upper <- NA
      }
      
      # Add to results
      results <- bind_rows(results, 
                          data.frame(
                            model = model_name,
                            metric = metric_name,
                            correlation = correlation,
                            ci_lower = ci_lower,
                            ci_upper = ci_upper,
                            rmse = rmse,
                            n_subjects = nrow(scatter_data)
                          ))
    }
  }
  
  # Add model display name
  if (nrow(results) > 0) {
    results$model_display <- as.character(unlist(model_display_names[model_name]))
    results$component <- component
  }
  
  return(results)
}

# Calculate individual difference correlations for RL metrics
rl_metrics <- c("good_deck_ratio", "new_good_deck_ratio", "total_money", "avg_outcome", "skip_ratio")
rl_models <- available_all_models  # Use all available models

rl_indiv_correlations <- bind_rows(
  lapply(rl_models, function(model) {
    calculate_individual_correlations(model, rl_metrics, "rl")
  })
)

# Calculate individual difference correlations for RT metrics
rt_metrics <- c("rt_play_mean", "rt_skip_mean", "choice_prob")
rt_models <- c(available_hybrid_models, available_ddm_models)  # Use all hybrid and DDM models

rt_indiv_correlations <- bind_rows(
  lapply(rt_models, function(model) {
    calculate_individual_correlations(model, rt_metrics, "ssm")
  })
)

# Combine all individual difference correlations
all_indiv_correlations <- bind_rows(rl_indiv_correlations, rt_indiv_correlations)

# Create a nicely formatted metrics column
all_indiv_correlations <- all_indiv_correlations %>%
  mutate(
    metric_display = case_when(
      metric == "good_deck_ratio" ~ "Good Deck Ratio",
      metric == "new_good_deck_ratio" ~ "New Good Deck Ratio",
      metric == "new_bad_deck_ratio" ~ "New Bad Deck Ratio",
      metric == "total_money" ~ "Total Money",
      metric == "avg_outcome" ~ "Average Outcome",
      metric == "skip_ratio" ~ "Skip Ratio",
      metric == "rt_play_mean" ~ "Play RT (Mean)",
      metric == "rt_skip_mean" ~ "Skip RT (Mean)",
      metric == "choice_prob" ~ "Choice Probability",
      TRUE ~ metric
    )
  )

# Display summary table
if (nrow(all_indiv_correlations) > 0) {
  kable(all_indiv_correlations %>% 
          select(model_display, component, metric_display, correlation, ci_lower, ci_upper, rmse, n_subjects), 
        digits = 3,
        col.names = c("Model", "Component", "Metric", "Correlation", "95% CI Lower", "95% CI Upper", "RMSE", "# Subjects"),
        caption = "Individual Difference Correlations") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                  full_width = FALSE)
  
  # Create visualization for RL metrics
  rl_indiv_plot <- ggplot(all_indiv_correlations %>% filter(component == "RL"), 
       aes(x = metric_display, y = correlation, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                position = position_dodge(width = 0.9),
                width = 0.25) +
  scale_fill_viridis_d(name = "Model") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Individual Difference Prediction: RL Metrics",
       subtitle = "Correlation between observed and predicted values (with 95% confidence intervals)",
       x = "Metric",
       y = "Correlation") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
  print(rl_indiv_plot)
  
  # Create visualization for RT metrics
  ssm_indiv_plot <- ggplot(all_indiv_correlations %>% filter(component == "SSM"), 
       aes(x = metric_display, y = correlation, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                position = position_dodge(width = 0.9),
                width = 0.25) +
  scale_fill_viridis_d(name = "Model") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Individual Difference Prediction: RT Metrics",
       subtitle = "Correlation between observed and predicted values (with 95% confidence intervals)",
       x = "Metric",
       y = "Correlation") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
  print(ssm_indiv_plot)
  
  # Find top-performing models for each metric
  top_models <- all_indiv_correlations %>%
    group_by(metric, metric_display, component) %>%
    slice_max(order_by = correlation, n = 1) %>%
    ungroup() %>%
    select(metric, metric_display, component, model_display, correlation, rmse)
  
  # Display top models by metric
  kable(top_models, digits = 3,
        col.names = c("Metric ID", "Metric", "Component", "Best Model", "Correlation", "RMSE"),
        caption = "Top-Performing Models by Metric for Individual Difference Prediction") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                  full_width = FALSE)
  
  # Create a heatmap of individual difference correlations
  indiv_corr_heatmap <- all_indiv_correlations %>%
    ggplot(aes(x = metric_display, y = model_display, fill = correlation)) +
    geom_tile(color = "white") +
    geom_text(aes(label = sprintf("%.2f", correlation)), color = "black", size = 2.5) +
    scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                       midpoint = 0.5, limits = c(0, 1)) +
    facet_wrap(~ component, scales = "free", ncol = 1) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Individual Difference Correlations Heatmap",
         subtitle = "By model and metric (higher values indicate better prediction of individual differences)",
         x = "Metric",
         y = "Model",
         fill = "Correlation") +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      strip.text = element_text(size = 12, face = "bold"),
      axis.title = element_text(size = 11),
      legend.title = element_text(size = 10)
    )
  print(indiv_corr_heatmap)
}
```

# Integrated Model Assessment

## Combined Recovery and PPC Performance

```{r combined-assessment, fig.height=12, fig.width=14, fig.keep='all'}
# Create dataframes for component-specific model performance
create_component_performance <- function(data, component_type) {
  data %>%
    filter(component == component_type) %>%
    group_by(model, model_display) %>%
    summarize(
      mean_ppp = mean(mean_ppp, na.rm = TRUE),
      extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
      problematic_stats = sum(extreme_ratio > 0.3, na.rm = TRUE),
      total_stats = n(),
      pct_problematic = problematic_stats / total_stats * 100,
      .groups = "drop"
    ) %>%
    rename_with(~ paste0(component_type, "_", .), .cols = c(mean_ppp, extreme_ratio, problematic_stats, total_stats, pct_problematic))
}

# Create data frames for component-specific model performance
rl_component_performance <- create_component_performance(all_summaries, "RL")
ssm_component_performance <- create_component_performance(all_summaries, "SSM")

# Create a base dataframe with all model information
all_models_df <- tibble(
  model = available_all_models,
  model_display = unlist(model_display_names[available_all_models])
)

# Ensure consistent data types for joining
rl_component_performance <- rl_component_performance %>%
  mutate(model_display = as.character(model_display))

ssm_component_performance <- ssm_component_performance %>%
  mutate(model_display = as.character(model_display))

# Join the component performances
model_performance <- all_models_df %>%
  left_join(rl_component_performance, by = c("model", "model_display")) %>%
  left_join(ssm_component_performance, by = c("model", "model_display")) %>%
  mutate(
    # Add model type
    model_type = case_when(
      model %in% rl_only_models ~ "RL Only",
      model %in% ddm_only_models ~ "DDM Only",
      model %in% hybrid_models ~ "Hybrid (RL+DDM)",
      TRUE ~ "Unknown"
    ),
    
    # Calculate overall metrics for all models
    overall_mean_ppp = case_when(
      model %in% rl_only_models ~ RL_mean_ppp,
      model %in% ddm_only_models ~ SSM_mean_ppp,
      model %in% hybrid_models ~ (RL_mean_ppp + SSM_mean_ppp) / 2,
      TRUE ~ NA_real_
    ),
    overall_extreme_ratio = case_when(
      model %in% rl_only_models ~ RL_extreme_ratio,
      model %in% ddm_only_models ~ SSM_extreme_ratio,
      model %in% hybrid_models ~ (RL_extreme_ratio + SSM_extreme_ratio) / 2,
      TRUE ~ NA_real_
    )
  ) %>%
  arrange(model_type, overall_extreme_ratio)

# Get parameter recovery performance
param_recovery <- overall_wide %>%
  select(model, correlation, rmse, bias, relative_bias)

# Combine with PPC performance
combined_performance <- model_performance %>%
  left_join(param_recovery, by = "model") %>%
  select(model, model_display, model_type, 
         correlation, rmse, 
         overall_mean_ppp, overall_extreme_ratio,
         RL_mean_ppp, RL_extreme_ratio,
         SSM_mean_ppp, SSM_extreme_ratio)

# Display the combined table
kable(combined_performance, digits = 3,
      col.names = c("Model", "Display Name", "Type", 
                    "Param Correlation", "Param RMSE", 
                    "Overall PPP", "Overall Extreme Ratio",
                    "RL Mean PPP", "RL Extreme Ratio",
                    "SSM Mean PPP", "SSM Extreme Ratio"),
      caption = "Combined Parameter Recovery and PPC Performance") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Create scatter plot of parameter recovery vs. PPC performance
recovery_ppc_scatter <- combined_performance %>%
  mutate(
    ppp_quality = abs(overall_mean_ppp - 0.5),  # Lower is better
    ppp_score = 1 - ppp_quality * 2  # Scale to [0,1], higher is better
  ) %>%
  ggplot(aes(x = correlation, y = ppp_score, 
             color = model_type, shape = model_type, 
             label = model_display)) +
  geom_point(size = 4, alpha = 0.7) +
  geom_text_repel(size = 3, box.padding = 0.5, max.overlaps = 30) +
  scale_color_manual(values = model_type_colors) +
  scale_shape_manual(values = c(16, 17, 15)) +
  theme_minimal() +
  labs(title = "Model Performance: Parameter Recovery vs. PPC",
       subtitle = "Better models appear in the upper-right corner",
       x = "Parameter Recovery Correlation (higher is better)", 
       y = "PPC Score (higher is better)",
       color = "Model Type",
       shape = "Model Type") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(recovery_ppc_scatter)

# Create a similar plot using extreme ratio
extreme_ratio_scatter <- combined_performance %>%
  ggplot(aes(x = correlation, y = 1 - overall_extreme_ratio, 
             color = model_type, shape = model_type, 
             label = model_display)) +
  geom_point(size = 4, alpha = 0.7) +
  geom_text_repel(size = 3, box.padding = 0.5, max.overlaps = 30) +
  scale_color_manual(values = model_type_colors) +
  scale_shape_manual(values = c(16, 17, 15)) +
  theme_minimal() +
  labs(title = "Model Performance: Parameter Recovery vs. PPC",
       subtitle = "Better models appear in the upper-right corner",
       x = "Parameter Recovery Correlation (higher is better)", 
       y = "1 - Extreme Ratio (higher is better)",
       color = "Model Type",
       shape = "Model Type") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(extreme_ratio_scatter)

# Create a faceted version by model type
faceted_model_scatter <- combined_performance %>%
  ggplot(aes(x = correlation, y = 1 - overall_extreme_ratio, 
             color = model_display, 
             label = model_display)) +
  geom_point(size = 3, alpha = 0.7) +
  geom_text_repel(size = 3, box.padding = 0.5, max.overlaps = 10) +
  facet_wrap(~ model_type) +
  scale_color_viridis_d() +
  theme_minimal() +
  labs(title = "Model Performance by Type: Parameter Recovery vs. PPC",
       subtitle = "Better models appear in the upper-right corner",
       x = "Parameter Recovery Correlation (higher is better)", 
       y = "1 - Extreme Ratio (higher is better)",
       color = "Model") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.position = "none"
  )
print(faceted_model_scatter)

# Create a comprehensive ranking of models
model_ranking <- combined_performance %>%
  # Create standardized scores (z-scores)
  mutate(
    # For parameter recovery, higher correlation is better, lower RMSE is better
    z_param_corr = scale(correlation)[,1],
    z_param_rmse = -scale(rmse)[,1],  # Negative so higher is better
    
    # For PPC, closer to 0.5 is better, so use negative absolute deviation
    z_ppp_quality = -scale(abs(overall_mean_ppp - 0.5))[,1],
    z_extreme_ratio = -scale(overall_extreme_ratio)[,1],  # Lower extreme ratio is better
    
    # Overall parameter recovery score
    param_recovery_score = (z_param_corr + z_param_rmse) / 2,
    
    # Overall PPC score
    ppc_score = (z_ppp_quality + z_extreme_ratio) / 2,
    
    # Total score
    total_score = (param_recovery_score + ppc_score) / 2
  ) %>%
  # Add rank variables
  arrange(desc(total_score)) %>%
  mutate(
    overall_rank = row_number(),
    param_rank = rank(-param_recovery_score),
    ppc_rank = rank(-ppc_score)
  ) %>%
  # Sort by overall rank
  arrange(overall_rank)

# Display the rankings
kable(model_ranking %>% 
        select(model_display, model_type, overall_rank, param_rank, ppc_rank, 
               total_score, param_recovery_score, ppc_score), 
      digits = 2,
      col.names = c("Model", "Type", "Overall Rank", "Param Rank", "PPC Rank", 
                   "Total Score", "Param Score", "PPC Score"),
      caption = "Model Ranking Based on Standardized Performance Scores") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Visualize the rankings
model_ranking_plot <- ggplot(model_ranking, 
       aes(x = param_recovery_score, y = ppc_score, 
           color = model_type, shape = model_type, 
           label = model_display)) +
  geom_point(size = 4, alpha = 0.7) +
  geom_text_repel(size = 3, box.padding = 0.5, max.overlaps = 30) +
  # Add diagonal line for balanced models
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray") +
  scale_color_manual(values = model_type_colors) +
  scale_shape_manual(values = c(16, 17, 15)) +
  theme_minimal() +
  labs(title = "Model Performance: Parameter Recovery vs. PPC Scores",
       subtitle = "Better models appear in the upper-right corner",
       x = "Parameter Recovery Score (standardized)", 
       y = "PPC Score (standardized)",
       color = "Model Type",
       shape = "Model Type") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(model_ranking_plot)

# Create a comprehensive heatmap of all performance metrics
performance_heatmap_data <- combined_performance %>%
  select(model_display, model_type, correlation, rmse, 
         RL_mean_ppp, RL_extreme_ratio,
         SSM_mean_ppp, SSM_extreme_ratio) %>%
  mutate(
    # Transform metrics so higher is always better
    correlation = correlation,  # already higher is better
    rmse_inv = 1 / rmse,  # invert RMSE so higher is better
    RL_ppp_quality = 1 - 2 * abs(RL_mean_ppp - 0.5),  # transform to 0-1, higher is better
    RL_fit_quality = 1 - RL_extreme_ratio,  # invert extreme ratio
    SSM_ppp_quality = if_else(is.na(SSM_mean_ppp), NA_real_, 1 - 2 * abs(SSM_mean_ppp - 0.5)),
    SSM_fit_quality = if_else(is.na(SSM_extreme_ratio), NA_real_, 1 - SSM_extreme_ratio)
  ) %>%
  # Gather to long format for heatmap
  pivot_longer(
    cols = c(correlation, rmse_inv, 
             RL_ppp_quality, RL_fit_quality,
             SSM_ppp_quality, SSM_fit_quality),
    names_to = "metric",
    values_to = "score"
  ) %>%
  mutate(
    # Create readable metric labels
    metric_label = case_when(
      metric == "correlation" ~ "Parameter Recovery\nCorrelation",
      metric == "rmse_inv" ~ "Parameter Recovery\n1/RMSE",
      metric == "RL_ppp_quality" ~ "RL PPP Quality",
      metric == "RL_fit_quality" ~ "RL % Good Fit",
      metric == "SSM_ppp_quality" ~ "RT PPP Quality",
      metric == "SSM_fit_quality" ~ "RT % Good Fit",
      TRUE ~ metric
    ),
    # Order factors
    metric_label = factor(metric_label, levels = c(
      "Parameter Recovery\nCorrelation", "Parameter Recovery\n1/RMSE",
      "RL PPP Quality", "RL % Good Fit",
      "RT PPP Quality", "RT % Good Fit"
    ))
  )

# Create heatmap of all performance metrics
performance_heatmap <- ggplot(performance_heatmap_data, 
       aes(x = metric_label, y = model_display, fill = score)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", score)), 
            color = "black", size = 2.5) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.5, na.value = "gray90") +
  facet_wrap(~ model_type, scales = "free_y", ncol = 1) +
  theme_minimal() +
  labs(title = "Comprehensive Model Performance Heatmap",
       subtitle = "All metrics transformed so higher values (green) are better",
       x = "Performance Metric",
       y = "Model",
       fill = "Score\n(higher is better)") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10),
    axis.text.x = element_text(angle = 0)
  )
print(performance_heatmap)
```

## Model-Specific Analysis

```{r model-specific, fig.height=10, fig.width=14, fig.keep='all'}
# Get the top-performing models from each category
top_models <- model_ranking %>%
  group_by(model_type) %>%
  slice_min(order_by = overall_rank, n = 2) %>%
  ungroup() %>%
  pull(model)

# Get parameter recovery details for top models
top_model_params <- params_df %>%
  filter(model %in% top_models) %>%
  select(model, model_display, parameter, param_type, correlation, rmse) %>%
  arrange(model, param_type, parameter)

# Display parameter recovery for top models
kable(top_model_params, digits = 3,
      caption = "Parameter Recovery for Top-Performing Models") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Create a visualization of parameter recovery for top models
top_model_param_plot <- ggplot(top_model_params, 
       aes(x = parameter, y = correlation, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ param_type, scales = "free_x") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Parameter Recovery for Top-Performing Models",
       subtitle = "Grouped by parameter type",
       x = "Parameter",
       y = "Correlation",
       fill = "Model") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(top_model_param_plot)

# Get PPC performance for top models
top_model_ppc <- all_summaries %>%
  filter(model %in% top_models) %>%
  group_by(model, model_display, component) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    abs_dev = mean(abs(mean_ppp - 0.5), na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

# Display PPC performance for top models
kable(top_model_ppc, digits = 3,
      caption = "PPC Performance for Top-Performing Models") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Create a visualization of PPC performance for top models
top_model_ppc_plot <- ggplot(top_model_ppc, 
       aes(x = abs_dev, y = 1 - mean_extreme_ratio, color = model_display)) +
  geom_point(size = 4) +
  geom_text_repel(aes(label = model_display), box.padding = 0.5) +
  facet_wrap(~ component, scales = "free") +
  scale_x_continuous(limits = c(0, 0.5)) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  theme_minimal() +
  labs(title = "PPC Performance for Top-Performing Models",
       subtitle = "Better models appear in the upper-left corner",
       x = "Mean PPP Deviation from 0.5", 
       y = "Proportion of Good Fits (1 - Extreme Ratio)",
       color = "Model") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(top_model_ppc_plot)

# Create a detailed analysis of parameter trade-offs
# Identify common parameters across models for comparison
common_params <- params_df %>%
  count(parameter) %>%
  filter(n >= length(available_all_models) / 2) %>%  # Parameter exists in at least half the models
  pull(parameter)

# Get parameter correlations for common parameters
param_comparison <- params_df %>%
  filter(parameter %in% common_params) %>%
  select(model, model_display, model_type, parameter, correlation) %>%
  spread(parameter, correlation)

# Display parameter trade-off table
kable(param_comparison, digits = 3,
      caption = "Parameter Recovery Trade-offs Across Models") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Create a radar chart of parameter recovery for selected models
# Prep data for radar chart
radar_data <- params_df %>%
  filter(model %in% top_models, parameter %in% common_params) %>%
  select(model, model_display, parameter, correlation) %>%
  spread(parameter, correlation)

# Function to create a basic radar chart
create_radar_chart <- function(data, id_column, value_columns) {
  # Convert to long format
  long_data <- data %>%
    gather(key = "parameter", value = "correlation", all_of(value_columns))
  
  # Calculate angle for each parameter
  n_params <- length(value_columns)
  angles <- seq(0, 2 * pi, length.out = n_params + 1)
  
  # Add row for plot closure
  plot_data <- long_data %>%
    group_by(!!sym(id_column)) %>%
    mutate(
      angle = angles[match(parameter, value_columns)],
      hjust = ifelse(angle < pi, 0, 1),
      vjust = ifelse(angle < pi/2 | angle > 3*pi/2, 0, 1)
    ) %>%
    ungroup()
  
  # Create the radar chart
  ggplot(plot_data, aes(x = angle, y = correlation, 
                         color = !!sym(id_column), 
                         group = !!sym(id_column))) +
    geom_line() +
    geom_point() +
    coord_polar() +
    scale_y_continuous(limits = c(0, 1)) +
    scale_x_continuous(
      breaks = angles,
      labels = c(value_columns, ""),
      limits = c(0, 2*pi)
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 10),
      panel.grid.major.x = element_line(color = "gray", size = 0.3),
      panel.grid.major.y = element_line(color = "gray", size = 0.3, linetype = "dashed")
    )
}

# Create radar chart if we have enough data
if (nrow(radar_data) > 0 && length(common_params) >= 3) {
  radar_chart <- create_radar_chart(radar_data, "model_display", common_params)
  radar_plot <- radar_chart + 
    labs(title = "Parameter Recovery Comparison for Top Models",
         subtitle = "Radar chart showing correlation values for common parameters",
         color = "Model") +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      legend.title = element_text(size = 10)
    )
  print(radar_plot)
}
```

```{r}

```

