---
title: "Parameter Recovery Plots"
author: "Felix Pichardo"
date: "2025-03-21"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.show = 'all', fig.keep = 'all', dev = 'png', dpi = 300)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(viridis)
library(scales)
library(gridExtra)
library(ggrepel)
library(grid)
```

# Setup and Configuration

```{r model-config}
# Simplified Model Configuration
model_config <- list(
  # Define model families (the core algorithms)
  families = list(
    ev = list(
      display_name = "Expected Value",
      models = c("ev", "ev_ddm")
    ),
    pvl = list(
      display_name = "Prospect Valence Learning",
      # Group all PVL variants
      variants = list(
        delta = list(
          display_name = "PVLdelta",
          models = c("pvldelta", "pvldelta_ddm")
        ),
        decay = list(
          display_name = "PVLdecay",
          models = c("pvldecay", "pvldecay_ddm") 
        ),
        both = list(
          display_name = "PVLboth",
          models = c("pvlboth", "pvlboth_ddm")
        ),
        bothsd = list(
          display_name = "PVLbothsd",
          models = c("pvlbothsd", "pvlbothsd_ddm")
        ),
        puldelta = list(
          display_name = "PULdelta",
          models = c("puldelta", "puldelta_ddm")
        ),
        puldecay = list(
          display_name = "PULdecay",
          models = c("puldecay", "puldecay_ddm")
        ),
        pulboth = list(
          display_name = "PULboth",
          models = c("pulboth", "pulboth_ddm")
        ),
        pvsdelta = list(
          display_name = "PVSdelta",
          models = c("pvsdelta", "pvsdelta_ddm")
        ),
        pvsdecay = list(
          display_name = "PVSdecay",
          models = c("pvsdecay", "pvsdecay_ddm")
        ),
        pvsboth = list(
          display_name = "PVSboth",
          models = c("pvsboth", "pvsboth_ddm")
        )
      )
    ),
    vpp = list(
      display_name = "Value-Plus-Perseverance",
      # Group all VPP variants
      variants = list(
        delta = list(
          display_name = "VPPdeltag",
          models = c("vppdeltag", "vppdeltag_ddm")
        ),
        decay = list(
          display_name = "VPPdecayg",
          models = c("vppdecayg", "vppdecayg_ddm") 
        ),
        both = list(
          display_name = "VPPbothg",
          models = c("vppbothg", "vppbothg_ddm")
        ),
        delta = list(
          display_name = "VPPdeltagd",
          models = c("vppdeltagd", "vppdeltagd_ddm")
        ),
        decay = list(
          display_name = "VPPdecaygd",
          models = c("vppdecaygd", "vppdecaygd_ddm") 
        ),
        both = list(
          display_name = "VPPbothgd",
          models = c("vppbothgd", "vppbothgd_ddm")
        ),
        puldelta = list(
          display_name = "PULVPPdeltag",
          models = c("pulvppdeltag", "pulvppdeltag_ddm")
        ),
        puldecay = list(
          display_name = "PULVPPdecayg",
          models = c("pulvppdecayg", "pulvppdecayg_ddm")
        ),
        pulboth = list(
          display_name = "PULVPPbothg",
          models = c("pulvppbothg", "pulvppbothg_ddm")
        ),
        pvsdelta = list(
          display_name = "PVSVPPdeltag",
          models = c("pvsvppdeltag", "pvsvppdeltag_ddm")
        ),
        pvsdecay = list(
          display_name = "PVSVPPdecayg",
          models = c("pvsvppdecayg", "pvsvppdecayg_ddm")
        ),
        pvsboth = list(
          display_name = "PVSVPPbothg",
          models = c("pvsvppbothg", "pvsvppbothg_ddm")
        )
      )
    ),
    ddm = list(
      display_name = "DDM Only",
      models = c("ddm")
    )
  ),
  
  # Define model types (for categorization)
  types = list(
    rl_only = "Reinforcement Learning", 
    ddm_only = "Sequential Sampling",
    hybrid = "Hybrid (RL+DDM)"
  ),
  
  # Define parameter groups
  parameter_groups = list(
    "DDM Process" = c("boundary", "tau", "beta"),
    "Consistency/Drift" = c("drift", "drift_con", "con"),
    "Valuation" = c("wgt_pun", "wgt_rew", "gain", "loss", "gain_shape", "loss_shape"),
    "Learning Rate" = c("update", "retend", "decay"),
    "Perseveration" = c("k", "w", "ep"),
    "Other" = c("mag")
  )
)

# Build derived model lists
build_model_lists <- function(config) {
  # Initialize lists
  all_models <- character()
  display_names <- list()
  rl_only_models <- character()
  ddm_only_models <- character()
  hybrid_models <- character()
  all_model_families <- list()
  
  # Process all model families
  for (family_name in names(config$families)) {
    family <- config$families[[family_name]]
    
    # Handle families with variants
    if ("variants" %in% names(family)) {
      for (variant_name in names(family$variants)) {
        variant <- family$variants[[variant_name]]
        
        # Process each model in the variant
        for (model in variant$models) {
          # Create display name
          display_name <- paste(variant$display_name, ifelse(grepl("_ddm$", model), "+DDM", "Only"))
          display_names[[model]] <- display_name
          
          # Determine model type and store in appropriate list
          if (grepl("_ddm$", model)) {
            hybrid_models <- c(hybrid_models, model)
          } else if (model == "ddm") {
            ddm_only_models <- c(ddm_only_models, model)
          } else {
            rl_only_models <- c(rl_only_models, model)
          }
          
          # Add to all models list
          all_models <- c(all_models, model)
          
          # Add to model families
          base_family <- ifelse(family_name == "ddm", "ddm", 
                                paste0(family_name, variant_name))
          
          if (is.null(all_model_families[[base_family]])) {
            all_model_families[[base_family]] <- character()
          }
          all_model_families[[base_family]] <- c(all_model_families[[base_family]], model)
        }
      }
    } else {
      # Simple family without variants (like EV or DDM)
      for (model in family$models) {
        # Create display name
        display_name <- paste(family$display_name, ifelse(grepl("_ddm$", model), "+DDM", ""))
        display_names[[model]] <- display_name
        
        # Determine model type and store in appropriate list
        if (grepl("_ddm$", model)) {
          hybrid_models <- c(hybrid_models, model)
        } else if (model == "ddm") {
          ddm_only_models <- c(ddm_only_models, model)
        } else {
          rl_only_models <- c(rl_only_models, model)
        }
        
        # Add to all models list
        all_models <- c(all_models, model)
        
        # Add to model families
        base_family <- ifelse(family_name == "ddm", "ddm", family_name)
        if (is.null(all_model_families[[base_family]])) {
          all_model_families[[base_family]] <- character()
        }
        all_model_families[[base_family]] <- c(all_model_families[[base_family]], model)
      }
    }
  }
  
  # Return all derived lists
  return(list(
    all_models = unique(all_models),
    rl_only_models = unique(rl_only_models),
    ddm_only_models = unique(ddm_only_models),
    hybrid_models = unique(hybrid_models),
    model_display_names = display_names,
    model_families = all_model_families
  ))
}

# Generate all the model lists from configuration
derived_lists <- build_model_lists(model_config)
all_models <- derived_lists$all_models
rl_only_models <- derived_lists$rl_only_models
ddm_only_models <- derived_lists$ddm_only_models
hybrid_models <- derived_lists$hybrid_models
model_display_names <- derived_lists$model_display_names
model_families <- derived_lists$model_families

# Define model type colors
model_type_colors <- c(
  "RL Only" = "#1B9E77", 
  "DDM Only" = "#D95F02", 
  "Hybrid (RL+DDM)" = "#7570B3"
)

# Print model lists for verification
cat("All models:", length(all_models), "\n")
cat("RL-only models:", length(rl_only_models), "\n")
cat("DDM-only models:", length(ddm_only_models), "\n")
cat("Hybrid models:", length(hybrid_models), "\n")
cat("Model families:", length(model_families), "\n")
```

```{r data-loading}
# Function to load recovery data with error handling
load_recovery_data <- function(model_name, base_dir = NULL) {
  if (is.null(base_dir)) {
    PROJ_DIR <- here::here()
    base_dir <- file.path(PROJ_DIR, "Data", "sim", "recovery")
  }
  
  file_path <- file.path(base_dir, paste0("recovery_igt_mod_batch_001_", model_name, "_desc-sim_params.rds"))
  
  if (file.exists(file_path)) {
    return(readRDS(file_path))
  } else {
    warning(paste("Recovery file not found for model:", model_name))
    return(NULL)
  }
}

# Paths to data files
PROJ_DIR <- here::here()
REC_SIM_DIR <- file.path(PROJ_DIR, "Data", "sim", "recovery")

# Automatically discover available recovery models
available_recovery_files <- list.files(REC_SIM_DIR, pattern = "recovery_igt_mod_batch_001_(.*)_desc-sim_params.rds", full.names = FALSE)
available_recovery_models <- available_recovery_files %>% 
  str_remove("recovery_igt_mod_batch_001_") %>%
  str_remove("_desc-sim_params.rds")

# Display discovered models
cat("Discovered recovery models:", length(available_recovery_models), "\n")
print(available_recovery_models)

# Load recovery data for all available models
recovery_data <- list()
for (model_name in available_recovery_models) {
  recovery_data[[model_name]] <- load_recovery_data(model_name, REC_SIM_DIR)
}
```

# Overall Parameter Recovery Plots

These plots show the overall performance of each model in recovering parameter values. The plots include correlation, RMSE, and bias metrics for all parameters.

```{r overall-recovery-plots, fig.height=10, fig.width=12}
# Function to display and annotate overall recovery plot for a model
display_overall_plot <- function(model_name) {
  # Check if model exists and has plot
  if (!model_name %in% names(recovery_data) || 
      is.null(recovery_data[[model_name]]) || 
      is.null(recovery_data[[model_name]]$plots) || 
      is.null(recovery_data[[model_name]]$plots$overall)) {
    cat("No overall plot available for model:", model_name, "\n")
    return(NULL)
  }
  
  # Get the plot
  plot <- recovery_data[[model_name]]$plots$overall
  
  # Add model name to the title
  model_display_name <- model_display_names[[model_name]]
  
  # Check if it's a ggplot object
  if (inherits(plot, "ggplot")) {
    # Update the plot with model information
    plot <- plot + 
      ggtitle(paste("Overall Parameter Recovery for", model_display_name)) +
      theme(plot.title = element_text(size = 14, face = "bold"))
  } else {
    cat("Plot for model", model_name, "is not a ggplot object\n")
    return(NULL)
  }
  
  return(plot)
}

# Display overall plots for all models
for (model_name in names(recovery_data)) {
  cat("\n## Overall Recovery Plot for", model_display_names[[model_name]], "\n")
  plot <- display_overall_plot(model_name)
  if (!is.null(plot)) {
    print(plot)
  }
}
```

# Parameter-Specific Recovery Plots

These plots show the relationship between true and recovered parameter values for each parameter and model. Each plot includes the correlation and RMSE metrics to quantify recovery performance.

```{r parameter-plots, fig.height=10, fig.width=14}
# Function to display individual parameter recovery plots by parameter
display_parameter_plots <- function(param_name) {
  # Initialize list to store plots
  plots_list <- list()
  
  # For each model
  for (model_name in names(recovery_data)) {
    # Check if model has individual plots and this parameter
    if (!is.null(recovery_data[[model_name]]) && 
        !is.null(recovery_data[[model_name]]$plots) && 
        !is.null(recovery_data[[model_name]]$plots$individual) && 
        param_name %in% names(recovery_data[[model_name]]$plots$individual)) {
      
      # Get the plot
      plot <- recovery_data[[model_name]]$plots$individual[[param_name]]
      
      # Check if it's a valid ggplot object
      if (!is.null(plot) && inherits(plot, "ggplot")) {
        # Add model name to the title
        model_display_name <- model_display_names[[model_name]]
        
        # Update plot title
        plot <- plot + 
          ggtitle(model_display_name) +
          theme(plot.title = element_text(size = 12, face = "bold"))
        
        # Add to list
        plots_list[[model_name]] <- plot
      }
    }
  }
  
  # Display plots if we have any
  if (length(plots_list) > 0) {
    # Print each plot individually instead of using grid.arrange
    cat("Found", length(plots_list), "plots for parameter:", param_name, "\n")
    
    # Print each plot with a caption
    for (model_name in names(plots_list)) {
      cat("\n### Model:", model_display_names[[model_name]], "\n")
      print(plots_list[[model_name]])
    }
    
    return(TRUE)
  } else {
    cat("No plots available for parameter:", param_name, "\n")
    return(FALSE)
  }
}

# Get list of all parameters from all models
all_parameters <- unique(
  unlist(
    lapply(recovery_data, function(x) {
      if (!is.null(x) && !is.null(x$plots) && !is.null(x$plots$individual)) {
        return(names(x$plots$individual))
      } else {
        return(NULL)
      }
    })
  )
)

# Display plots for each parameter
cat("Found", length(all_parameters), "unique parameters across all models\n")
for (param in all_parameters) {
  cat("\n## Recovery Plots for Parameter:", param, "\n")
  success <- display_parameter_plots(param)
}
```

# Parameter Recovery by Model Type

Compare parameter recovery performance across different model types.

```{r recovery-by-model-type, fig.height=8, fig.width=12}
# Extract recovery metrics from all models
extract_recovery_metrics <- function() {
  # Initialize dataframe
  metrics_df <- data.frame()
  
  # Process each model
  for (model_name in names(recovery_data)) {
    model_data <- recovery_data[[model_name]]
    
    # Skip if model data is missing or doesn't have by_parameter
    if (is.null(model_data) || is.null(model_data$by_parameter)) {
      next
    }
    
    # Extract metrics
    model_metrics <- model_data$by_parameter
    
    # Add model information
    model_metrics$model <- model_name
    model_metrics$model_display <- as.character(model_display_names[[model_name]])
    model_metrics$model_type <- case_when(
      model_name %in% rl_only_models ~ "RL Only",
      model_name %in% ddm_only_models ~ "DDM Only",
      model_name %in% hybrid_models ~ "Hybrid (RL+DDM)",
      TRUE ~ "Unknown"
    )
    
    # Add parameter type
    model_metrics$param_type <- NA_character_
    for (type_name in names(model_config$parameter_groups)) {
      type_params <- model_config$parameter_groups[[type_name]]
      model_metrics$param_type[model_metrics$parameter %in% type_params] <- type_name
    }
    model_metrics$param_type[is.na(model_metrics$param_type)] <- "Other"
    
    # Combine with main dataframe
    metrics_df <- bind_rows(metrics_df, model_metrics)
  }
  
  return(metrics_df)
}

# Get all recovery metrics
all_metrics <- extract_recovery_metrics()

# Create summary by model type and parameter type
recovery_summary <- all_metrics %>%
  group_by(model_type, param_type) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    sd_correlation = sd(correlation, na.rm = TRUE),
    n_parameters = n(),
    se_correlation = sd_correlation / sqrt(n_parameters),
    ci_lower = mean_correlation - qt(0.975, n_parameters - 1) * se_correlation,
    ci_upper = mean_correlation + qt(0.975, n_parameters - 1) * se_correlation,
    mean_rmse = mean(rmse, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(param_type, desc(mean_correlation))

# Display summary table
kable(recovery_summary, digits = 3,
      col.names = c("Model Type", "Parameter Type", "Mean Correlation", 
                   "SD Correlation", "N Parameters", "SE Correlation", 
                   "95% CI Lower", "95% CI Upper", "Mean RMSE"),
      caption = "Parameter Recovery by Model Type and Parameter Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
               full_width = FALSE)

# Create visualization
type_comparison_plot <- ggplot(recovery_summary, 
       aes(x = param_type, y = mean_correlation, fill = model_type)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
               position = position_dodge(width = 0.9),
               width = 0.25) +
  scale_fill_manual(values = model_type_colors) +
  coord_flip() +
  labs(title = "Parameter Recovery by Type",
       subtitle = "Mean correlation with 95% confidence intervals",
       x = "Parameter Type",
       y = "Mean Correlation",
       fill = "Model Type") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(type_comparison_plot)

# Create a model ranking by mean correlation
model_ranking <- all_metrics %>%
  group_by(model, model_display, model_type) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    sd_correlation = sd(correlation, na.rm = TRUE),
    n_parameters = n(),
    se_correlation = sd_correlation / sqrt(n_parameters),
    ci_lower = mean_correlation - qt(0.975, n_parameters - 1) * se_correlation,
    ci_upper = mean_correlation + qt(0.975, n_parameters - 1) * se_correlation,
    mean_rmse = mean(rmse, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(model_type, desc(mean_correlation))

# Display model ranking
kable(model_ranking, digits = 3,
      col.names = c("Model", "Display Name", "Model Type", "Mean Correlation", 
                   "SD Correlation", "N Parameters", "SE Correlation", 
                   "95% CI Lower", "95% CI Upper", "Mean RMSE"),
      caption = "Model Ranking by Parameter Recovery Performance") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
               full_width = FALSE)

# Create a visualization of model rankings
ranking_plot <- ggplot(model_ranking, 
       aes(x = reorder(model_display, mean_correlation), y = mean_correlation, fill = model_type)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.25) +
  geom_text(aes(label = sprintf("%.3f", mean_correlation)),
            position = position_stack(vjust = 0.5),
            color = "white", fontface = "bold") +
  scale_fill_manual(values = model_type_colors) +
  facet_wrap(~ model_type, scales = "free_y") +
  coord_flip() +
  labs(title = "Model Ranking by Parameter Recovery",
       subtitle = "Mean correlation across parameters with 95% confidence intervals",
       x = "Model",
       y = "Mean Correlation",
       fill = "Model Type") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(ranking_plot)
```

# Parameter-Specific Comparison Across Models

These visualizations compare how well each model recovers specific parameters. This helps identify which models are most reliable for estimating particular cognitive parameters.

```{r parameter-comparison, fig.height=8, fig.width=12}
# Create a comparison of correlation by parameter across models
parameter_comparison <- all_metrics %>%
  group_by(parameter, model_type) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    sd_correlation = sd(correlation, na.rm = TRUE),
    n_models = n(),
    se_correlation = sd_correlation / sqrt(n_models),
    ci_lower = mean_correlation - qt(0.975, max(n_models - 1, 1)) * se_correlation,
    ci_upper = mean_correlation + qt(0.975, max(n_models - 1, 1)) * se_correlation,
    .groups = "drop"
  ) %>%
  arrange(parameter, desc(mean_correlation))

# Display the parameter comparison table
kable(parameter_comparison, digits = 3,
      col.names = c("Parameter", "Model Type", "Mean Correlation", 
                   "SD Correlation", "N Models", "SE Correlation", 
                   "95% CI Lower", "95% CI Upper"),
      caption = "Parameter Recoverability by Model Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
               full_width = FALSE)

# Create a visualization of parameter recoverability
param_plot <- ggplot(parameter_comparison, 
       aes(x = reorder(parameter, mean_correlation), y = mean_correlation, fill = model_type)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
               position = position_dodge(width = 0.9),
               width = 0.25) +
  scale_fill_manual(values = model_type_colors) +
  coord_flip() +
  labs(title = "Parameter Recoverability by Model Type",
       subtitle = "Mean correlation with 95% confidence intervals",
       x = "Parameter",
       y = "Mean Correlation",
       fill = "Model Type") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(param_plot)

# Create a heatmap of parameter recovery by model
# Get top models for visualization
top_models <- model_ranking %>%
  group_by(model_type) %>%
  slice_max(order_by = mean_correlation, n = 5) %>%
  pull(model)

# Filter metrics to top models
top_model_metrics <- all_metrics %>%
  filter(model %in% top_models)

# Create the heatmap
heatmap_plot <- ggplot(top_model_metrics, 
       aes(x = parameter, y = model_display, fill = correlation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", correlation)), color = "black", size = 3) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.5, limits = c(0, 1)) +
  facet_wrap(~ model_type, scales = "free_y") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  ) +
  labs(title = "Parameter Recovery Heatmap for Top Models",
       subtitle = "Correlation by model and parameter",
       x = "Parameter",
       y = "Model",
       fill = "Correlation")
print(heatmap_plot)
```
