---
title: "Posterior Predictive Check Analysis"
author: "Felix Pichardo"
date: "2025-03-07"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(viridis)
library(scales)
library(gridExtra)
```

# Introduction

This document analyzes the posterior predictive checks (PPCs) performed on several computational models of decision-making in the modified Iowa Gambling Task (mIGT). PPCs evaluate a model's ability to reproduce patterns observed in the empirical data by comparing statistics derived from observed data to statistics calculated from simulated data generated using posterior parameter estimates.

## Models Evaluated

We evaluate several types of models:

1. **Reinforcement Learning (RL) Models**
   - Expected Value (EV)
   - Prospect Valence Learning with Delta rule (PVLdelta)
   - Prospect Valence Learning with Decay rule (PVLdecay)

2. **Sequential Sampling Model (SSM)**
   - Drift Diffusion Model (DDM)

3. **Hybrid Models (RL+SSM)**
   - EV+DDM
   - PVLdelta+DDM
   - PVLdecay+DDM

## Posterior Predictive Checks (PPC)

For each model, we assess how well it captures key behavioral patterns by calculating posterior predictive p-values (PPP values). These values represent the probability that the simulated data are more extreme than the observed data. Values close to 0.5 indicate good fit, while values close to 0 or 1 indicate poor fit. We consider PPP values below 0.05 or above 0.95 as "extreme" and potentially problematic.

```{r load-data}
# Function to load PPC result files
load_ppc_results <- function(file_path) {
  readRDS(file_path)
}

# Paths to data files
PROJ_DIR <- here::here()
PPC_DIR <- file.path(PROJ_DIR, "Data", "sim", "ppc")

# List of files to process - all models
ppc_files <- list.files(PPC_DIR, pattern = "ppc_results_igt_mod_.*_batch_001.rds", full.names = TRUE)

# Load all PPC objects
ppc_data <- list()
for (file in ppc_files) {
  model_name <- basename(file) %>% 
    str_remove("ppc_results_igt_mod_") %>%
    str_remove("_batch_001.rds")
  
  ppc_data[[model_name]] <- load_ppc_results(file)
}

# Create a list of model names with proper formatting for display
model_display_names <- c(
  "ddm" = "DDM Only",
  "ev" = "EV Only",
  "pvldecay" = "PVLdecay Only",
  "pvldelta" = "PVLdelta Only",
  "ev_ddm" = "EV+DDM",
  "pvldecay_ddm" = "PVLdecay+DDM",
  "pvldelta_ddm" = "PVLdelta+DDM"
)

# Group models by type
rl_only_models <- c("ev", "pvldecay", "pvldelta")
ddm_only_models <- c("ddm") 
hybrid_models <- c("ev_ddm", "pvldecay_ddm", "pvldelta_ddm")
```

# Data Extraction and Processing

```{r extract-summary-stats}
# Function to extract summary statistics
extract_summary_stats <- function(ppc_obj, model_name) {
  # Check if the model has RL and SSM components or just one component
  if (is.list(ppc_obj$model$summary) && "rl" %in% names(ppc_obj$model$summary)) {
    # Hybrid model with both components
    rl_summary <- ppc_obj$model$summary$rl %>%
      mutate(component = "RL", model = model_name)
    
    ssm_summary <- ppc_obj$model$summary$ssm %>%
      mutate(component = "SSM", model = model_name)
    
    return(bind_rows(rl_summary, ssm_summary))
  } else {
    # Single component model
    summary_df <- ppc_obj$model$summary
    
    # For individual models, determine component type based on model name
    # rather than using statistics which have misleading prefixes
    component_type <- case_when(
      model_name %in% c("ev", "pvldecay", "pvldelta") ~ "RL",
      model_name == "ddm" ~ "SSM",
      TRUE ~ "Unknown"
    )
    
    # Clean up statistic names by removing misleading prefixes if present
    summary_df <- summary_df %>%
      mutate(statistic = str_remove(statistic, "^(rl_|ssm_)"))
    
    return(summary_df %>% mutate(component = component_type, model = model_name))
  }
}

# Combine all summary statistics
all_summaries <- bind_rows(
  lapply(names(ppc_data), function(name) {
    extract_summary_stats(ppc_data[[name]], name)
  })
)

# Replace model names with display names
all_summaries <- all_summaries %>%
  mutate(model_display = model_display_names[model])

# Reorder factor levels for consistent ordering in plots
all_summaries$model_display <- factor(all_summaries$model_display,
                                      levels = c("DDM Only", "EV Only", "PVLdecay Only", "PVLdelta Only",
                                                "EV+DDM", "PVLdecay+DDM", "PVLdelta+DDM"))

# Create separate datasets for RL and SSM components
rl_summaries <- all_summaries %>% filter(component == "RL")
ssm_summaries <- all_summaries %>% filter(component == "SSM")

# Confirm the correct assignment of components
component_check <- all_summaries %>%
  group_by(model, component) %>%
  summarise(statistics = paste(head(statistic, 3), collapse = ", "), .groups = "drop")

print(component_check)
```

# Overall PPC Performance

First, let's examine the overall PPC performance across all models to get a high-level view of model fit.

```{r overall-performance}
# Calculate overall fit metrics for each model and component
overall_metrics <- all_summaries %>%
  group_by(model, model_display, component) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    median_ppp = median(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    extreme_stats_count = sum(extreme_ratio > 0.3, na.rm = TRUE),
    total_stats = n(),
    pct_problematic = extreme_stats_count / total_stats * 100,
    .groups = "drop"
  ) %>%
  arrange(component, mean_extreme_ratio)

# Display the overall metrics table
kable(overall_metrics, digits = 3,
      col.names = c("Model", "Display Name", "Component", "Mean PPP", "Median PPP", 
                    "Mean Extreme Ratio", "# Problematic Stats", "Total Stats", "% Problematic"),
      caption = "Overall PPC Performance by Model and Component") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  pack_rows("Reinforcement Learning (RL) Component", 
            sum(overall_metrics$component == "RL" & overall_metrics$model %in% rl_only_models), 
            sum(overall_metrics$component == "RL")) %>%
  pack_rows("Sequential Sampling (SSM) Component", 
            sum(overall_metrics$component == "RL") + 1, 
            nrow(overall_metrics))

# Visualize overall model performance by component
ggplot(overall_metrics, 
       aes(x = reorder(model_display, mean_extreme_ratio), 
           y = mean_extreme_ratio, 
           fill = mean_ppp)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", pct_problematic)), 
            position = position_stack(vjust = 0.5), 
            color = "white", fontface = "bold") +
  facet_wrap(~ component, scales = "free_y") +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.4, limits = c(0, 0.5),
                     name = "Mean PPP\n(closer to 0.5 is better)") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Model Performance by Component",
       subtitle = "Percentage of problematic statistics shown in bars (lower is better)",
       x = NULL, 
       y = "Mean Proportion of Extreme PPP Values")
```

# Reinforcement Learning (RL) Component Analysis

## RL Metrics Across All Models with RL Components

Let's analyze how well each model with an RL component captures key reinforcement learning statistics.

```{r rl-metrics}
# Define key RL statistics to focus on
rl_key_stats <- c("good_deck_ratio", "new_good_deck_ratio", "new_bad_deck_ratio", 
                 "skip_ratio", "total_money", "avg_outcome")

# Filter for key RL statistics across all models with RL components
rl_metrics <- rl_summaries %>%
  filter(statistic %in% rl_key_stats)

# Create a comparison table
rl_comparison <- rl_metrics %>%
  select(model_display, statistic, mean_ppp, extreme_ratio) %>%
  pivot_wider(names_from = statistic, 
              values_from = c(mean_ppp, extreme_ratio)) %>%
  arrange(model_display)

# Display the table with better formatting
kable(rl_comparison, digits = 3,
      caption = "RL Metrics: Mean PPP Values and Extreme Ratios by Model") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  add_header_above(c(" " = 1, 
                   "Mean PPP Values" = length(rl_key_stats), 
                   "Extreme Ratios" = length(rl_key_stats)))

# Create a visualization of RL metrics
ggplot(rl_metrics, aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for RL Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Visualize extreme ratios for RL statistics
ggplot(rl_metrics, aes(x = statistic, y = extreme_ratio, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Proportion of Subjects with Extreme PPP Values for RL Statistics",
       subtitle = "Lower values indicate better fit (fewer extreme PPP values)",
       x = "Statistic", y = "Proportion of Subjects")
```

## Deck Selection Metrics Analysis

Now let's analyze the different deck selection metrics, comparing the original good deck ratio with the new metrics focusing on specific decks.

```{r deck-selection-metrics}
# Define deck selection statistics
deck_selection_stats <- c("good_deck_ratio", "new_good_deck_ratio", "new_bad_deck_ratio")

# Filter for deck selection statistics across all models with RL components
deck_selection_metrics <- rl_summaries %>%
  filter(statistic %in% deck_selection_stats)

# Create a comparison table
deck_metrics_comparison <- deck_selection_metrics %>%
  select(model_display, statistic, mean_ppp, extreme_ratio) %>%
  pivot_wider(names_from = statistic, 
              values_from = c(mean_ppp, extreme_ratio)) %>%
  arrange(model_display)

# Display the table with better formatting
kable(deck_metrics_comparison, digits = 3,
      caption = "Deck Selection Metrics: Mean PPP Values and Extreme Ratios by Model") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  add_header_above(c(" " = 1, 
                   "Mean PPP Values" = length(deck_selection_stats), 
                   "Extreme Ratios" = length(deck_selection_stats)))

# Create labels for metrics in the visualization
deck_metric_labels <- c(
  "good_deck_ratio" = "Original Good Decks (3+4) / All Selections",
  "new_good_deck_ratio" = "New Good Decks (3+4) / Decks 1,3,4",
  "new_bad_deck_ratio" = "Bad Deck (1) / Decks 1,3,4"
)

# Visualize deck selection metrics
deck_metrics_plot <- deck_selection_metrics %>%
  mutate(metric_label = deck_metric_labels[statistic]) %>%
  ggplot(aes(x = metric_label, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for Deck Selection Metrics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Metric", y = "Mean PPP Value")

deck_metrics_plot

# Visualize extreme ratios for deck selection metrics
deck_extreme_plot <- deck_selection_metrics %>%
  mutate(metric_label = deck_metric_labels[statistic]) %>%
  ggplot(aes(x = metric_label, y = extreme_ratio, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Proportion of Subjects with Extreme PPP Values for Deck Selection Metrics",
       subtitle = "Lower values indicate better fit (fewer extreme PPP values)",
       x = "Metric", y = "Proportion of Subjects")

deck_extreme_plot

# Compare deck selection metrics within each model
deck_within_model <- deck_selection_metrics %>%
  mutate(metric_label = deck_metric_labels[statistic]) %>%
  ggplot(aes(x = model_display, y = mean_ppp, fill = metric_label)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Deck Selection Metrics Within Each Model",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Model", y = "Mean PPP Value")

deck_within_model
```

## Comparison: RL-Only vs. Hybrid Models (RL Component)

Let's directly compare how the RL components perform in RL-only models versus their hybrid counterparts.

```{r rl-hybrid-comparison}
# Create a dataset for RL model comparison (RL-only vs. hybrid)
rl_model_comparison <- rl_metrics %>%
  mutate(model_type = case_when(
    model %in% rl_only_models ~ "RL-Only",
    model %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Other"
  )) %>%
  # Extract base model name for pairing
  mutate(base_model = case_when(
    model == "ev" | model == "ev_ddm" ~ "EV",
    model == "pvldecay" | model == "pvldecay_ddm" ~ "PVLdecay",
    model == "pvldelta" | model == "pvldelta_ddm" ~ "PVLdelta",
    TRUE ~ "Other"
  ))

# Calculate average metrics by base model and model type
rl_comparison_summary <- rl_model_comparison %>%
  group_by(base_model, model_type) %>%
  summarize(
    mean_ppp_overall = mean(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(base_model, model_type)

# Display the comparison table
kable(rl_comparison_summary, digits = 3,
      col.names = c("Base Model", "Model Type", "Mean PPP", "Mean Extreme Ratio"),
      caption = "RL Component: RL-Only vs. Hybrid Models") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize the comparison for each RL statistic
rl_stat_comparison <- rl_model_comparison %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  facet_wrap(~ base_model, ncol = 3) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("RL-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "RL Component Performance: RL-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

rl_stat_comparison

# Visualize the comparison specifically for deck selection metrics
deck_selection_comparison <- rl_model_comparison %>%
  filter(statistic %in% deck_selection_stats) %>%
  mutate(metric_label = deck_metric_labels[statistic]) %>%
  ggplot(aes(x = metric_label, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  facet_wrap(~ base_model, ncol = 3) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("RL-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Deck Selection Metrics: RL-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Metric", y = "Mean PPP Value")

deck_selection_comparison
```

# Sequential Sampling Model (SSM) Component Analysis

## SSM Metrics Across All Models with DDM Components

Now let's analyze how well each model with a DDM component captures key sequential sampling statistics, including both play and pass reaction times.

```{r ssm-metrics}
# Define key SSM statistics to focus on, ensuring both play and pass metrics are included
ssm_key_stats <- c(
  # Choice probabilities
  "choice_prob", 
  # Play reaction times
  "rt_play_mean", "rt_play_median", 
  "rt_play_quantiles_10%", "rt_play_quantiles_90%",
  # Skip/Pass reaction times
  "rt_skip_mean", "rt_skip_median", 
  "rt_skip_quantiles_10%", "rt_skip_quantiles_90%"
)

# Filter for key SSM statistics across all models with DDM components
ssm_metrics <- ssm_summaries %>%
  filter(statistic %in% ssm_key_stats)

# Create a comparison table
ssm_comparison <- ssm_metrics %>%
  select(model_display, statistic, mean_ppp, extreme_ratio) %>%
  pivot_wider(names_from = statistic, 
              values_from = c(mean_ppp, extreme_ratio)) %>%
  arrange(model_display)

# Display the table with better formatting
kable(ssm_comparison, digits = 3,
      caption = "SSM Metrics: Mean PPP Values and Extreme Ratios by Model") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  add_header_above(c(" " = 1, 
                   "Mean PPP Values" = length(ssm_key_stats), 
                   "Extreme Ratios" = length(ssm_key_stats)))

# Group reaction time metrics for clearer visualization
play_rt_stats <- c("rt_play_mean", "rt_play_median", "rt_play_quantiles_10%", "rt_play_quantiles_90%")
skip_rt_stats <- c("rt_skip_mean", "rt_skip_median", "rt_skip_quantiles_10%", "rt_skip_quantiles_90%")

# Visualize Play RT metrics
play_rt_plot <- ssm_metrics %>%
  filter(statistic %in% play_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for PLAY Reaction Time Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Visualize Skip/Pass RT metrics
skip_rt_plot <- ssm_metrics %>%
  filter(statistic %in% skip_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for SKIP/PASS Reaction Time Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Display the plots
play_rt_plot
skip_rt_plot

# Visualize Choice Probability metrics
choice_prob_plot <- ssm_metrics %>%
  filter(statistic == "choice_prob") %>%
  ggplot(aes(x = model_display, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Mean PPP Values for Choice Probability",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Model", y = "Mean PPP Value")

choice_prob_plot
```

## Comparison: DDM-Only vs. Hybrid Models (SSM Component)

Let's directly compare how the SSM components perform in the DDM-only model versus the hybrid models.

```{r ddm-hybrid-comparison}
# Create a dataset for SSM model comparison (DDM-only vs. hybrid)
ssm_model_comparison <- ssm_metrics %>%
  mutate(model_type = case_when(
    model %in% ddm_only_models ~ "DDM-Only",
    model %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Other"
  ))

# Calculate average metrics by model type and statistic
ssm_stat_summary <- ssm_model_comparison %>%
  group_by(model_type, statistic) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

# Create separate summaries for different RT types
play_rt_summary <- ssm_stat_summary %>%
  filter(statistic %in% play_rt_stats) %>%
  group_by(model_type) %>%
  summarize(
    play_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    play_mean_extreme = mean(mean_extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

skip_rt_summary <- ssm_stat_summary %>%
  filter(statistic %in% skip_rt_stats) %>%
  group_by(model_type) %>%
  summarize(
    skip_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    skip_mean_extreme = mean(mean_extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

# Combine the summaries
rt_type_summary <- full_join(play_rt_summary, skip_rt_summary, by = "model_type")

# Display the summary table
kable(rt_type_summary, digits = 3,
      col.names = c("Model Type", "Play Mean PPP", "Play Mean Extreme Ratio", 
                    "Skip Mean PPP", "Skip Mean Extreme Ratio"),
      caption = "SSM Component: Play vs. Skip RT Performance") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize the comparison for play RTs
play_rt_comparison <- ssm_model_comparison %>%
  filter(statistic %in% play_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("DDM-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "PLAY RT Performance: DDM-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Visualize the comparison for skip RTs
skip_rt_comparison <- ssm_model_comparison %>%
  filter(statistic %in% skip_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("DDM-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "SKIP RT Performance: DDM-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Display the plots
play_rt_comparison
skip_rt_comparison

# Detailed hybrid model comparison for SSM
hybrid_ssm_comparison <- ssm_metrics %>%
  filter(model %in% hybrid_models) %>%
  mutate(model_short = case_when(
    model == "ev_ddm" ~ "EV+DDM",
    model == "pvldecay_ddm" ~ "PVLdecay+DDM",
    model == "pvldelta_ddm" ~ "PVLdelta+DDM",
    TRUE ~ model
  )) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_short)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  facet_wrap(~ factor(grepl("play", statistic), labels = c("Skip/Pass RT", "Play RT")), scales = "free_x") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "SSM Component Performance Across Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

hybrid_ssm_comparison
```

# Cross-Model Comparison

Let's examine key metrics across all models to identify the strengths and weaknesses of each approach.

```{r cross-model-comparison}
# Create data frames for component-specific model performance
rl_component_performance <- all_summaries %>%
  filter(component == "RL") %>%
  group_by(model, model_display) %>%
  summarize(
    rl_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    rl_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    rl_problematic_stats = sum(extreme_ratio > 0.3, na.rm = TRUE),
    rl_total_stats = n(),
    rl_pct_problematic = rl_problematic_stats / rl_total_stats * 100,
    .groups = "drop"
  )

ssm_component_performance <- all_summaries %>%
  filter(component == "SSM") %>%
  group_by(model, model_display) %>%
  summarize(
    ssm_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    ssm_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    ssm_problematic_stats = sum(extreme_ratio > 0.3, na.rm = TRUE),
    ssm_total_stats = n(),
    ssm_pct_problematic = ssm_problematic_stats / ssm_total_stats * 100,
    .groups = "drop"
  )

# Combine all models and fill in missing values appropriately
all_models <- tibble(
  model = c(rl_only_models, ddm_only_models, hybrid_models),
  model_display = model_display_names[c(rl_only_models, ddm_only_models, hybrid_models)]
)

model_performance <- all_models %>%
  left_join(rl_component_performance, by = c("model", "model_display")) %>%
  left_join(ssm_component_performance, by = c("model", "model_display")) %>%
  mutate(
    # Fill in missing values with NA for models without certain components
    rl_mean_ppp = ifelse(model %in% rl_only_models | model %in% hybrid_models, rl_mean_ppp, NA),
    rl_extreme_ratio = ifelse(model %in% rl_only_models | model %in% hybrid_models, rl_extreme_ratio, NA),
    ssm_mean_ppp = ifelse(model %in% ddm_only_models | model %in% hybrid_models, ssm_mean_ppp, NA),
    ssm_extreme_ratio = ifelse(model %in% ddm_only_models | model %in% hybrid_models, ssm_extreme_ratio, NA),
    
    # Calculate overall metrics for hybrid models
    overall_mean_ppp = case_when(
      model %in% rl_only_models ~ rl_mean_ppp,
      model %in% ddm_only_models ~ ssm_mean_ppp,
      model %in% hybrid_models ~ (rl_mean_ppp + ssm_mean_ppp) / 2,
      TRUE ~ NA_real_
    ),
    overall_extreme_ratio = case_when(
      model %in% rl_only_models ~ rl_extreme_ratio,
      model %in% ddm_only_models ~ ssm_extreme_ratio,
      model %in% hybrid_models ~ (rl_extreme_ratio + ssm_extreme_ratio) / 2,
      TRUE ~ NA_real_
    )
  ) %>%
  arrange(desc(overall_mean_ppp))

# Display the combined performance table
kable(model_performance %>% 
        select(model_display, rl_mean_ppp, rl_extreme_ratio, 
               ssm_mean_ppp, ssm_extreme_ratio, 
               overall_mean_ppp, overall_extreme_ratio),
      digits = 3,
      col.names = c("Model", "RL Mean PPP", "RL Extreme Ratio", 
                   "SSM Mean PPP", "SSM Extreme Ratio", 
                   "Overall Mean PPP", "Overall Extreme Ratio"),
      caption = "Component-Specific and Overall Model Performance") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create a visualization of model performance by component
component_performance_plot <- all_summaries %>%
  group_by(model_display, component) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = model_display, y = mean_extreme_ratio, fill = component)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5,
            size = 3) +
  scale_y_continuous(limits = c(0, max(overall_metrics$mean_extreme_ratio) * 1.2),
                    labels = scales::percent) +
  scale_fill_manual(values = c("RL" = "#1B9E77", "SSM" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Model Performance by Component",
       subtitle = "Lower extreme ratio values indicate better fit; PPP values shown above bars",
       x = "Model", y = "Mean Proportion of Extreme PPP Values",
       fill = "Component")

component_performance_plot

# Create a heatmap for key statistics across all models
# Select key statistics for the heatmap
key_rl_stats <- c("good_deck_ratio", "new_good_deck_ratio", "new_bad_deck_ratio", "skip_ratio", "avg_outcome", "total_money")
key_play_stats <- c("rt_play_mean", "rt_play_median")
key_skip_stats <- c("rt_skip_mean", "rt_skip_median")
key_choice_stats <- c("choice_prob")

# Gather all key stats
key_stats_all <- c(key_rl_stats, key_play_stats, key_skip_stats, key_choice_stats)

# Filter for key statistics
key_stats_data <- all_summaries %>%
  filter(statistic %in% key_stats_all) %>%
  mutate(metric_group = case_when(
    statistic %in% c("good_deck_ratio", "new_good_deck_ratio", "new_bad_deck_ratio") ~ "Deck Selection",
    statistic %in% c("skip_ratio", "avg_outcome", "total_money") ~ "Other RL Metrics",
    statistic %in% key_play_stats ~ "Play RT",
    statistic %in% key_skip_stats ~ "Skip RT",
    statistic %in% key_choice_stats ~ "Choice",
    TRUE ~ "Other"
  ))

# Create heatmap for PPP values
key_stats_heatmap <- key_stats_data %>%
  ggplot(aes(x = statistic, y = model_display, fill = mean_ppp)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), color = "black", size = 3) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.5, limits = c(0, 1)) +
  facet_grid(. ~ metric_group, scales = "free", space = "free_x") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "PPP Values for Key Statistics Across All Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Model",
       fill = "Mean PPP Value")

key_stats_heatmap

# Create heatmap for extreme ratios
extreme_ratio_heatmap <- key_stats_data %>%
  ggplot(aes(x = statistic, y = model_display, fill = extreme_ratio)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.0f%%", extreme_ratio*100)), color = "black", size = 3) +
  scale_fill_gradient(low = "green", high = "red", limits = c(0, 1)) +
  facet_grid(. ~ metric_group, scales = "free", space = "free_x") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Proportion of Subjects with Extreme PPP Values",
       subtitle = "Lower values indicate better fit",
       x = "Statistic", y = "Model",
       fill = "Extreme Ratio")

extreme_ratio_heatmap
```

# Integration with Parameter Recovery Results

Let's analyze the relationship between parameter recovery and PPC performance:

```{r param-recovery-integration}
# Extract overall metrics from the recovery RMD file
# Create a function to extract overall metrics
extract_overall <- function(recovery_obj, model_name) {
  overall <- recovery_obj$overall
  overall$model <- model_name
  return(overall)
}

# Paths to recovery data files
REC_SIM_DIR <- file.path(PROJ_DIR, "Data", "sim", "recovery")

# List of files to process
recovery_files = list.files(REC_SIM_DIR, 
                            pattern = "recovery_igt_mod_batch_001_.*_desc-sim_params.rds", 
                            full.names = TRUE)

# Load all recovery objects
recovery_data <- list()
for (file in recovery_files) {
  model_name <- basename(file) %>% 
    str_remove("recovery_igt_mod_batch_001_") %>%
    str_remove("_desc-sim_params.rds")
  
  recovery_data[[model_name]] <- readRDS(file)
}

# Combine all overall metrics
overall_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_overall(recovery_data[[name]], name)
  })
)

# Create recovery performance data frame
recovery_performance <- overall_df %>%
  pivot_wider(names_from = metric, values_from = value) %>%
  select(model, correlation, rmse, bias, relative_bias)

# Combine with PPC performance
combined_performance <- recovery_performance %>%
  left_join(model_performance, by = "model") %>%
  select(model_display, correlation, rmse, relative_bias, 
         rl_mean_ppp, rl_extreme_ratio, 
         ssm_mean_ppp, ssm_extreme_ratio,
         overall_mean_ppp, overall_extreme_ratio)

# Create a formatted table
kable(combined_performance, digits = 3,
      col.names = c("Model", "Param Correlation", "Param RMSE", "Param Rel Bias", 
                   "RL Mean PPP", "RL Extreme Ratio", 
                   "SSM Mean PPP", "SSM Extreme Ratio",
                   "Overall Mean PPP", "Overall Extreme Ratio"),
      caption = "Combined Parameter Recovery and PPC Performance") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create a scatter plot of parameter recovery vs PPC performance
scatter_plot <- combined_performance %>%
  ggplot(aes(x = correlation, y = 1 - overall_extreme_ratio, 
             color = model_display, size = 1/rmse)) +
  geom_point(alpha = 0.8) +
  geom_text(aes(label = model_display), hjust = -0.2, vjust = 0, size = 3) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_size_continuous(name = "Inverse RMSE\n(Larger is better)") +
  theme_minimal() +
  labs(title = "Parameter Recovery vs PPC Performance",
       subtitle = "Better models appear in the upper-right (high recovery correlation, low extreme PPP ratios)",
       x = "Parameter Recovery Correlation", 
       y = "PPC Goodness (1 - Mean Extreme Ratio)",
       color = "Model")

scatter_plot

# Create component-specific scatter plots
rl_scatter <- combined_performance %>%
  filter(!is.na(rl_extreme_ratio)) %>%
  ggplot(aes(x = correlation, y = 1 - rl_extreme_ratio, 
             color = model_display, size = 1/rmse)) +
  geom_point(alpha = 0.8) +
  geom_text(aes(label = model_display), hjust = -0.2, vjust = 0, size = 3) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_size_continuous(name = "Inverse RMSE\n(Larger is better)") +
  theme_minimal() +
  labs(title = "Parameter Recovery vs RL Component PPC Performance",
       subtitle = "Better models appear in the upper-right",
       x = "Parameter Recovery Correlation", 
       y = "RL Component PPC Goodness (1 - Extreme Ratio)",
       color = "Model")

ssm_scatter <- combined_performance %>%
  filter(!is.na(ssm_extreme_ratio)) %>%
  ggplot(aes(x = correlation, y = 1 - ssm_extreme_ratio, 
             color = model_display, size = 1/rmse)) +
  geom_point(alpha = 0.8) +
  geom_text(aes(label = model_display), hjust = -0.2, vjust = 0, size = 3) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_size_continuous(name = "Inverse RMSE\n(Larger is better)") +
  theme_minimal() +
  labs(title = "Parameter Recovery vs SSM Component PPC Performance",
       subtitle = "Better models appear in the upper-right",
       x = "Parameter Recovery Correlation", 
       y = "SSM Component PPC Goodness (1 - Extreme Ratio)",
       color = "Model")

# Display component-specific plots
rl_scatter
ssm_scatter
```

# Additional Analysis of New Deck Selection Metrics

Let's dig deeper into the new deck selection metrics to see how models differ in their ability to capture deck selection patterns focusing on specific decks.

```{r new-deck-analysis}
# Extract block-level statistics for different deck selection metrics
# Get block-level data from plots

# Filter for models that have block-level statistics
# First check if block-level plots exist in the PPC objects
models_with_blocks <- names(ppc_data)[sapply(ppc_data, function(x) {
  "plots" %in% names(x) && "learning_curve" %in% names(x$plots)
})]

# Initialize container for block data
block_data_all <- data.frame()

# Extract block-level data for different deck selection metrics
for (model_name in models_with_blocks) {
  # Check if these new metrics exist
  if (any(grepl("new_good_learning_curve|new_bad_learning_curve", names(ppc_data[[model_name]]$plots)))) {
    # Extract original good deck data
    orig_data <- ggplot_build(ppc_data[[model_name]]$plots$learning_curve)$data[[2]]
    orig_data$metric <- "original_good_ratio"
    orig_data$model <- model_name
    
    # Extract new good deck data
    new_good_data <- ggplot_build(ppc_data[[model_name]]$plots$new_good_learning_curve)$data[[2]]
    new_good_data$metric <- "new_good_ratio"
    new_good_data$model <- model_name
    
    # Extract new bad deck data
    new_bad_data <- ggplot_build(ppc_data[[model_name]]$plots$new_bad_learning_curve)$data[[2]]
    new_bad_data$metric <- "new_bad_ratio"
    new_bad_data$model <- model_name
    
    # Combine data
    model_block_data <- bind_rows(orig_data, new_good_data, new_bad_data)
    block_data_all <- bind_rows(block_data_all, model_block_data)
  }
}

# If we successfully extracted block data, create plots
if (nrow(block_data_all) > 0) {
  # Clean up the dataset
  block_data_clean <- block_data_all %>%
    rename(block = x, value = y) %>%
    mutate(model_display = model_display_names[model]) %>%
    mutate(metric_label = case_when(
      metric == "original_good_ratio" ~ "Original Good Decks (3+4) / All Selections",
      metric == "new_good_ratio" ~ "New Good Decks (3+4) / Decks 1,3,4",
      metric == "new_bad_ratio" ~ "Bad Deck (1) / Decks 1,3,4",
      TRUE ~ metric
    ))
  
  # Create learning curve visualization for different metrics
  learning_curve_comparison <- block_data_clean %>%
    ggplot(aes(x = block, y = value, color = metric_label)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    facet_wrap(~ model_display, scales = "free_y") +
    scale_color_viridis_d() +
    theme_minimal() +
    labs(title = "Learning Curves for Different Deck Selection Metrics",
         subtitle = "Observed data across blocks",
         x = "Block", y = "Proportion",
         color = "Metric")
  
  learning_curve_comparison
  
  # Create a comparison of each metric across models
  metric_across_models <- block_data_clean %>%
    ggplot(aes(x = block, y = value, color = model_display)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    facet_wrap(~ metric_label, scales = "free_y") +
    scale_color_viridis_d() +
    theme_minimal() +
    labs(title = "Deck Selection Metrics Across Models",
         subtitle = "Observed data across blocks",
         x = "Block", y = "Proportion",
         color = "Model")
  
  metric_across_models
}
```

```{r}

```

