---
title: "Posterior Predictive Check Analysis"
author: "Felix Pichardo"
date: "2025-03-07"
output: 
  word_document:
    toc: true
    toc_depth: 3
    fig_width: 8
    fig_height: 6
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, dpi = 300)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(viridis)
library(scales)
library(gridExtra)
library(ggrepel) # For label repulsion in plots

# Helper function for Word-compatible tables - with col.names support
make_word_table <- function(df, caption_text, digits = 3, col.names = NULL) {
  if (is.null(col.names)) {
    return(kable(df, caption = caption_text, digits = digits))
  } else {
    return(kable(df, caption = caption_text, digits = digits, col.names = col.names))
  }
}
```

# Introduction

This document analyzes the posterior predictive checks (PPCs) performed on several computational models of decision-making in the modified Iowa Gambling Task (mIGT). PPCs evaluate a model's ability to reproduce patterns observed in the empirical data by comparing statistics derived from observed data to statistics calculated from simulated data generated using posterior parameter estimates.

## Models Evaluated

We evaluate several types of models:

1. **Reinforcement Learning (RL) Models**
   - Expected Value (EV)
   - Prospect Valence Learning (PVL) variants
      - With Delta rule (PVLdelta)
      - With Decay rule (PVLdecay)
      - With Both rules (PVLboth)
      - With Both rules and Selective Decay (PVLbothsd)
   - Value-Plus-Perseverance (VPP) variants (with a general [g] only and general+deck [gd] specific perseveration)
      - With Delta rule (VPPdelta)
      - With Decay rule (VPPdecay)
      - With Both rules (VPPboth)

2. **Sequential Sampling Model (SSM)**
   - Drift Diffusion Model (DDM)

3. **Hybrid Models (RL+SSM)**
   - RL models combined with DDM

## Posterior Predictive Checks (PPC)

For each model, we assess how well it captures key behavioral patterns by calculating posterior predictive p-values (PPP values). These values represent the probability that the simulated data are more extreme than the observed data. Values close to 0.5 indicate good fit, while values close to 0 or 1 indicate poor fit. We consider PPP values below 0.05 or above 0.95 as "extreme" and potentially problematic.

```{r model-config}
# Enhanced Model Configuration
model_config <- list(
  # Define model families (the core algorithms)
  families = list(
    ev = list(
      display_name = "Expected Value",
      models = c("ev", "ev_ddm")
    ),
    pvl = list(
      display_name = "Prospect Valence Learning",
      # Group all PVL variants
      variants = list(
        delta = list(
          display_name = "PVLdelta",
          models = c("pvldelta", "pvldelta_ddm")
        ),
        decay = list(
          display_name = "PVLdecay",
          models = c("pvldecay", "pvldecay_ddm") 
        ),
        both = list(
          display_name = "PVLboth",
          models = c("pvlboth", "pvlboth_ddm")
        ),
        bothsd = list(
          display_name = "PVLbothsd",
          models = c("pvlbothsd", "pvlbothsd_ddm")
        )
      )
    ),
    vpp = list(
      display_name = "Value-Plus-Perseverance",
      # Group all VPP variants
      variants = list(
        delta = list(
          display_name = "VPPdeltag",
          models = c("vppdeltag", "vppdeltag_ddm")
        ),
        decay = list(
          display_name = "VPPdecayg",
          models = c("vppdecayg", "vppdecayg_ddm") 
        ),
        both = list(
          display_name = "VPPbothg",
          models = c("vppbothg", "vppbothg_ddm")
        ),
        delta = list(
          display_name = "VPPdeltagd",
          models = c("vppdeltagd", "vppdeltagd_ddm")
        ),
        decay = list(
          display_name = "VPPdecaygd",
          models = c("vppdecaygd", "vppdecaygd_ddm") 
        ),
        both = list(
          display_name = "VPPbothgd",
          models = c("vppbothgd", "vppbothgd_ddm")
        )
      )
    ),
    ddm = list(
      display_name = "DDM Only",
      models = c("ddm")
    )
  ),
  
  # Define model types (for categorization)
  types = list(
    rl_only = "Reinforcement Learning", 
    ddm_only = "Sequential Sampling",
    hybrid = "Hybrid (RL+DDM)"
  ),
  
  # Define parameter groups
  parameter_groups = list(
    "DDM Process" = c("boundary", "tau", "beta"),
    "Consistency/Drift" = c("drift", "drift_con", "con"),
    "Valuation" = c("wgt_pun", "wgt_rew", "gain", "loss"),
    "Learning Rate" = c("update", "retend", "decay"),
    "Perseveration" = c("k", "w", "ep")
  ),
  
  # Define key statistics for PPC analysis
  key_statistics = list(
    deck_selection = c("good_deck_ratio", "new_good_deck_ratio", "new_bad_deck_ratio"),
    rl_performance = c("skip_ratio", "total_money", "avg_outcome"),
    play_rt = c("rt_play_mean", "rt_play_median", "rt_play_quantiles_10%", "rt_play_quantiles_90%"),
    skip_rt = c("rt_skip_mean", "rt_skip_median", "rt_skip_quantiles_10%", "rt_skip_quantiles_90%"),
    choice = c("choice_prob")
  )
)

# Build derived model lists automatically
build_model_lists <- function(config) {
  # Initialize lists
  all_models <- character()
  display_names <- list()
  rl_only_models <- character()
  ddm_only_models <- character()
  hybrid_models <- character()
  all_model_families <- list()
  
  # Process all model families
  for (family_name in names(config$families)) {
    family <- config$families[[family_name]]
    
    # Handle families with variants
    if ("variants" %in% names(family)) {
      for (variant_name in names(family$variants)) {
        variant <- family$variants[[variant_name]]
        
        # Process each model in the variant
        for (model in variant$models) {
          # Create display name
          display_name <- paste(variant$display_name, ifelse(grepl("_ddm$", model), "+DDM", "Only"))
          display_names[[model]] <- display_name
          
          # Determine model type and store in appropriate list
          if (grepl("_ddm$", model)) {
            hybrid_models <- c(hybrid_models, model)
          } else if (model == "ddm") {
            ddm_only_models <- c(ddm_only_models, model)
          } else {
            rl_only_models <- c(rl_only_models, model)
          }
          
          # Add to all models list
          all_models <- c(all_models, model)
          
          # Add to model families - group by base algorithm
          base_family <- ifelse(family_name == "ddm", "ddm", 
                                paste0(family_name, variant_name))
          
          if (is.null(all_model_families[[base_family]])) {
            all_model_families[[base_family]] <- character()
          }
          all_model_families[[base_family]] <- c(all_model_families[[base_family]], model)
        }
      }
    } else {
      # Simple family without variants (like EV or DDM)
      for (model in family$models) {
        # Create display name
        display_name <- paste(family$display_name, ifelse(grepl("_ddm$", model), "+DDM", ""))
        display_names[[model]] <- display_name
        
        # Determine model type and store in appropriate list
        if (grepl("_ddm$", model)) {
          hybrid_models <- c(hybrid_models, model)
        } else if (model == "ddm") {
          ddm_only_models <- c(ddm_only_models, model)
        } else {
          rl_only_models <- c(rl_only_models, model)
        }
        
        # Add to all models list
        all_models <- c(all_models, model)
        
        # Add to model families
        base_family <- ifelse(family_name == "ddm", "ddm", family_name)
        if (is.null(all_model_families[[base_family]])) {
          all_model_families[[base_family]] <- character()
        }
        all_model_families[[base_family]] <- c(all_model_families[[base_family]], model)
      }
    }
  }
  
  # Return all derived lists
  return(list(
    all_models = unique(all_models),
    rl_only_models = unique(rl_only_models),
    ddm_only_models = unique(ddm_only_models),
    hybrid_models = unique(hybrid_models),
    model_display_names = display_names,
    model_families = all_model_families
  ))
}

# Generate all the model lists from configuration
derived_lists <- build_model_lists(model_config)
all_models <- derived_lists$all_models
rl_only_models <- derived_lists$rl_only_models
ddm_only_models <- derived_lists$ddm_only_models
hybrid_models <- derived_lists$hybrid_models
model_display_names <- derived_lists$model_display_names
model_families <- derived_lists$model_families

# Print model lists for verification
cat("All models:", length(all_models), "\n")
cat("RL-only models:", length(rl_only_models), "\n")
cat("DDM-only models:", length(ddm_only_models), "\n")
cat("Hybrid models:", length(hybrid_models), "\n")
cat("Model families:", length(model_families), "\n")
```

```{r load-data}
# Function to load PPC result files flexibly
load_ppc_results <- function(model_name, base_dir = NULL) {
  if (is.null(base_dir)) {
    PROJ_DIR <- here::here()
    base_dir <- file.path(PROJ_DIR, "Data", "sim", "ppc")
  }
  
  file_path <- file.path(base_dir, paste0("ppc_results_igt_mod_", model_name, "_batch_001.rds"))
  
  if (file.exists(file_path)) {
    return(readRDS(file_path))
  } else {
    warning(paste("File not found for model:", model_name))
    return(NULL)
  }
}

# Paths to data files
PROJ_DIR <- here::here()
PPC_DIR <- file.path(PROJ_DIR, "Data", "sim", "ppc")

# Automatically discover available models in the directory
available_files <- list.files(PPC_DIR, pattern = "ppc_results_igt_mod_.*_batch_001.rds", full.names = FALSE)
available_models <- available_files %>% 
  str_remove("ppc_results_igt_mod_") %>%
  str_remove("_batch_001.rds")

# Load data for all configured models that are available
ppc_data <- list()
for (model_name in all_models) {
  if (model_name %in% available_models) {
    ppc_data[[model_name]] <- load_ppc_results(model_name, PPC_DIR)
  }
}

# Update model lists based on what's actually available
available_all_models <- names(ppc_data)
available_rl_models <- intersect(rl_only_models, available_all_models)
available_ddm_models <- intersect(ddm_only_models, available_all_models)
available_hybrid_models <- intersect(hybrid_models, available_all_models)

# Print availability stats
cat("Available models:", length(available_all_models), "out of", length(all_models), "\n")
```

# Data Extraction and Processing

```{r extract-summary-stats}
# Function to extract summary statistics with component detection
extract_summary_stats <- function(ppc_obj, model_name) {
  # Check if model exists
  if (is.null(ppc_obj)) {
    return(NULL)
  }
  
  # Determine model type
  model_type <- case_when(
    model_name %in% rl_only_models ~ "RL Only",
    model_name %in% ddm_only_models ~ "DDM Only",
    model_name %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Unknown"
  )
  
  # Check if the model has RL and SSM components or just one component
  if (is.list(ppc_obj$model$summary) && "rl" %in% names(ppc_obj$model$summary)) {
    # Hybrid model with both components
    rl_summary <- ppc_obj$model$summary$rl %>%
      mutate(component = "RL", model = model_name, model_type = model_type)
    
    ssm_summary <- ppc_obj$model$summary$ssm %>%
      mutate(component = "SSM", model = model_name, model_type = model_type)
    
    return(bind_rows(rl_summary, ssm_summary))
  } else {
    # Single component model
    summary_df <- ppc_obj$model$summary
    
    # For individual models, determine component type based on model name
    component_type <- case_when(
      model_name %in% rl_only_models ~ "RL",
      model_name %in% ddm_only_models ~ "SSM",
      TRUE ~ "Unknown"
    )
    
    # Clean up statistic names by removing misleading prefixes if present
    summary_df <- summary_df %>%
      mutate(statistic = str_remove(statistic, "^(rl_|ssm_)"))
    
    return(summary_df %>% mutate(component = component_type, model = model_name, model_type = model_type))
  }
}

# Combine all summary statistics
all_summaries <- bind_rows(
  lapply(names(ppc_data), function(name) {
    extract_summary_stats(ppc_data[[name]], name)
  })
)

# Replace model names with display names and add categorical factor for display order
all_summaries <- all_summaries %>%
  mutate(
    model_display = model_display_names[model],
    model_display = factor(model_display, levels = model_display_names[all_models])
  )

# Create separate datasets for RL and SSM components
rl_summaries <- all_summaries %>% filter(component == "RL")
ssm_summaries <- all_summaries %>% filter(component == "SSM")

# Confirm the correct assignment of components
component_check <- all_summaries %>%
  group_by(model, component) %>%
  summarise(statistics = paste(head(statistic, 3), collapse = ", "), .groups = "drop")

make_word_table(component_check, 
      caption_text = "Component Assignment Check",
      col.names = c("Model", "Component", "Example Statistics"))
```

# Overall PPC Performance

First, let's examine the overall PPC performance across all models to get a high-level view of model fit.

```{r overall-performance, fig.height=8, fig.width=10}
# Calculate overall fit metrics for each model and component
overall_metrics <- all_summaries %>%
  group_by(model, model_display, component, model_type) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    median_ppp = median(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    extreme_stats_count = sum(extreme_ratio > 0.3, na.rm = TRUE),
    total_stats = n(),
    pct_problematic = extreme_stats_count / total_stats * 100,
    .groups = "drop"
  ) %>%
  arrange(component, mean_extreme_ratio)

# Display the overall metrics table
make_word_table(overall_metrics, digits = 3,
      caption_text = "Overall PPC Performance by Model and Component",
      col.names = c("Model", "Display Name", "Component", "Model Type", "Mean PPP", "Median PPP", 
                    "Mean Extreme Ratio", "# Problematic Stats", "Total Stats", "% Problematic"))

# Visualize overall model performance by component
ggplot(overall_metrics, 
       aes(x = reorder(model_display, mean_extreme_ratio), 
           y = mean_extreme_ratio, 
           fill = mean_ppp)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", pct_problematic)), 
            position = position_stack(vjust = 0.5), 
            color = "white", fontface = "bold") +
  facet_wrap(~ component, scales = "free_y") +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.4, limits = c(0, 0.5),
                     name = "Mean PPP\n(closer to 0.5 is better)") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Model Performance by Component",
       subtitle = "Percentage of problematic statistics shown in bars (lower is better)",
       x = NULL, 
       y = "Mean Proportion of Extreme PPP Values")

# Create a more detailed model comparison by component
ggplot(overall_metrics, 
       aes(x = reorder(model_display, -mean_ppp), 
           y = mean_ppp, 
           fill = component)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, 
            size = 3) +
  scale_y_continuous(limits = c(0, 0.7)) +
  scale_fill_brewer(palette = "Set1") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Mean PPP by Model and Component",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Model", 
       y = "Mean PPP",
       fill = "Component")

# Create a scatter plot of mean PPP vs. extreme ratio
ggplot(overall_metrics, 
       aes(x = abs(mean_ppp - 0.5), y = mean_extreme_ratio, 
           color = component, shape = model_type, label = model_display)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_text_repel(size = 3, nudge_x = 0.02, nudge_y = 0.02) +
  scale_x_continuous(limits = c(0, 0.3), 
                    labels = scales::percent) +
  scale_y_continuous(limits = c(0, 0.7), 
                    labels = scales::percent) +
  scale_color_brewer(palette = "Set1") +
  theme_minimal() +
  labs(title = "Model Performance: Mean PPP Deviation vs. Extreme Ratio",
       subtitle = "Better models appear in the bottom-left corner",
       x = "Mean PPP Deviation from 0.5", 
       y = "Mean Proportion of Extreme PPP Values",
       color = "Component",
       shape = "Model Type")
```

# Reinforcement Learning (RL) Component Analysis

## RL Metrics Across All Models with RL Components

Let's analyze how well each model with an RL component captures key reinforcement learning statistics.

```{r rl-metrics, fig.height=8, fig.width=10}
# Get key RL statistics based on the configuration
rl_key_stats <- unlist(model_config$key_statistics[c("deck_selection", "rl_performance")])

# Filter for key RL statistics across all models with RL components
rl_metrics <- rl_summaries %>%
  filter(statistic %in% rl_key_stats)

# Create a comparison table with dynamic columns
rl_comparison <- rl_metrics %>%
  select(model_display, statistic, mean_ppp, extreme_ratio) %>%
  pivot_wider(names_from = statistic, 
              values_from = c(mean_ppp, extreme_ratio)) %>%
  arrange(model_display)

# Display the RL metrics table - simplified for Word
make_word_table(rl_comparison, 
      caption_text = "RL Metrics: Mean PPP Values and Extreme Ratios by Model", 
      digits = 3)

# Create a visualization of RL metrics
ggplot(rl_metrics, aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for RL Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Visualize extreme ratios for RL statistics
ggplot(rl_metrics, aes(x = statistic, y = extreme_ratio, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Proportion of Subjects with Extreme PPP Values for RL Statistics",
       subtitle = "Lower values indicate better fit (fewer extreme PPP values)",
       x = "Statistic", y = "Proportion of Subjects")

# Create a heatmap for RL metrics
rl_metrics %>%
  ggplot(aes(x = statistic, y = model_display, fill = mean_ppp)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), color = "black", size = 3) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.5, limits = c(0, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "RL Metrics Heatmap: Mean PPP Values",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Model",
       fill = "Mean PPP")
```

## Deck Selection Metrics Analysis

Now let's analyze the different deck selection metrics, comparing the original good deck ratio with the new metrics focusing on specific decks.

```{r deck-selection-metrics, fig.height=7, fig.width=9}
# Get deck selection statistics from configuration
deck_selection_stats <- model_config$key_statistics$deck_selection

# Filter for deck selection statistics across all models with RL components
deck_selection_metrics <- rl_summaries %>%
  filter(statistic %in% deck_selection_stats)

# Create a comparison table
deck_metrics_comparison <- deck_selection_metrics %>%
  select(model_display, statistic, mean_ppp, extreme_ratio) %>%
  pivot_wider(names_from = statistic, 
              values_from = c(mean_ppp, extreme_ratio)) %>%
  arrange(model_display)

# Display the table with Word-compatible formatting
make_word_table(deck_metrics_comparison, 
      caption_text = "Deck Selection Metrics: Mean PPP Values and Extreme Ratios by Model",
      digits = 3)

# Create labels for metrics in the visualization
deck_metric_labels <- c(
  "good_deck_ratio" = "Original Good Decks (3+4) / All Selections",
  "new_good_deck_ratio" = "New Good Decks (3+4) / Decks 1,3,4",
  "new_bad_deck_ratio" = "Bad Deck (1) / Decks 1,3,4"
)

# Visualize deck selection metrics
deck_selection_metrics %>%
  mutate(metric_label = deck_metric_labels[statistic]) %>%
  ggplot(aes(x = metric_label, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for Deck Selection Metrics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Metric", y = "Mean PPP Value")

# Visualize extreme ratios for deck selection metrics
deck_selection_metrics %>%
  mutate(metric_label = deck_metric_labels[statistic]) %>%
  ggplot(aes(x = metric_label, y = extreme_ratio, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Proportion of Subjects with Extreme PPP Values for Deck Selection Metrics",
       subtitle = "Lower values indicate better fit (fewer extreme PPP values)",
       x = "Metric", y = "Proportion of Subjects")

# Compare deck selection metrics within each model
deck_selection_metrics %>%
  mutate(metric_label = deck_metric_labels[statistic]) %>%
  ggplot(aes(x = model_display, y = mean_ppp, fill = metric_label)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Deck Selection Metrics Within Each Model",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Model", y = "Mean PPP Value")

# Create a heatmap specifically for deck selection metrics
deck_selection_metrics %>%
  ggplot(aes(x = statistic, y = model_display, fill = mean_ppp)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), color = "black", size = 3) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.5, limits = c(0, 1)) +
  theme_minimal() +
  labs(title = "Deck Selection Metrics: Mean PPP Values Heatmap",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Deck Selection Metric", y = "Model",
       fill = "Mean PPP")
```

## Comparison: RL-Only vs. Hybrid Models (RL Component)

Let's directly compare how the RL components perform in RL-only models versus their hybrid counterparts.

```{r rl-hybrid-comparison, fig.height=10, fig.width=9}
# Function to extract base model name
extract_base_model <- function(model_name) {
  if (grepl("_ddm$", model_name)) {
    return(gsub("_ddm$", "", model_name))
  } else {
    return(model_name)
  }
}

# Create a dataset for RL model comparison (RL-only vs. hybrid)
rl_model_comparison <- rl_metrics %>%
  mutate(
    model_type = case_when(
      model %in% rl_only_models ~ "RL-Only",
      model %in% hybrid_models ~ "Hybrid (RL+DDM)",
      TRUE ~ "Other"
    ),
    # Extract base model name for pairing
    base_model = sapply(model, extract_base_model)
  )

# Calculate average metrics by base model and model type
rl_comparison_summary <- rl_model_comparison %>%
  group_by(base_model, model_type) %>%
  summarize(
    mean_ppp_overall = mean(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(base_model, model_type)

# Display the comparison table
make_word_table(rl_comparison_summary, digits = 3,
      caption_text = "RL Component: RL-Only vs. Hybrid Models",
      col.names = c("Base Model", "Model Type", "Mean PPP", "Mean Extreme Ratio"))

# Visualize the comparison for each RL statistic by base model
rl_stat_comparison <- rl_model_comparison %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  facet_wrap(~ base_model, ncol = 2) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("RL-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "RL Component Performance: RL-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Visualize the comparison specifically for deck selection metrics
deck_selection_comparison <- rl_model_comparison %>%
  filter(statistic %in% deck_selection_stats) %>%
  mutate(metric_label = deck_metric_labels[statistic]) %>%
  ggplot(aes(x = metric_label, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  facet_wrap(~ base_model, ncol = 2) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("RL-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Deck Selection Metrics: RL-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Metric", y = "Mean PPP Value")

# Create a direct comparison of RL-only vs. Hybrid model pairs
rl_paired_comparison <- rl_comparison_summary %>%
  # Rename the model_type values to avoid problematic characters in column names
  mutate(model_type = case_when(
    model_type == "RL-Only" ~ "RL_Only",
    model_type == "Hybrid (RL+DDM)" ~ "Hybrid_RLDDM",
    TRUE ~ model_type
  )) %>%
  pivot_wider(names_from = model_type, values_from = c(mean_ppp_overall, mean_extreme_ratio)) %>%
  mutate(
    ppp_difference = mean_ppp_overall_Hybrid_RLDDM - mean_ppp_overall_RL_Only,
    extreme_difference = mean_extreme_ratio_Hybrid_RLDDM - mean_extreme_ratio_RL_Only
  )

# Visualize the paired comparison
ggplot(rl_paired_comparison, 
       aes(x = base_model, 
           y = ppp_difference, 
           fill = extreme_difference)) +
  geom_col() +
  geom_text(aes(label = sprintf("%.3f", ppp_difference)), 
            vjust = ifelse(rl_paired_comparison$ppp_difference >= 0, -0.5, 1.5)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_gradient2(
    low = "green", 
    mid = "gray", 
    high = "red", 
    midpoint = 0,
    limits = c(-0.2, 0.2)
  ) +
  theme_minimal() +
  labs(title = "Impact of Adding DDM to RL Models",
       subtitle = "Positive values indicate hybrid models have higher (worse) Mean PPP deviation from 0.5",
       x = "Base RL Model", 
       y = "Difference in Mean PPP (Hybrid - RL-Only)",
       fill = "Difference in\nExtreme Ratio\n(Hybrid - RL-Only)")
```

# Sequential Sampling Model (SSM) Component Analysis

## SSM Metrics Across All Models with DDM Components

Now let's analyze how well each model with a DDM component captures key sequential sampling statistics, including both play and pass reaction times.

```{r ssm-metrics, fig.height=8, fig.width=10}
# Get SSM statistics from the configuration
play_rt_stats <- model_config$key_statistics$play_rt
skip_rt_stats <- model_config$key_statistics$skip_rt
choice_stats <- model_config$key_statistics$choice
ssm_key_stats <- c(choice_stats, play_rt_stats, skip_rt_stats)

# Filter for key SSM statistics across all models with DDM components
ssm_metrics <- ssm_summaries %>%
  filter(statistic %in% ssm_key_stats)

# Create a comparison table
ssm_comparison <- ssm_metrics %>%
  select(model_display, statistic, mean_ppp, extreme_ratio) %>%
  pivot_wider(names_from = statistic, 
              values_from = c(mean_ppp, extreme_ratio)) %>%
  arrange(model_display)

# Display the table with Word-compatible formatting
make_word_table(ssm_comparison, 
      caption_text = "SSM Metrics: Mean PPP Values and Extreme Ratios by Model",
      digits = 3)

# Visualize Play RT metrics
ssm_metrics %>%
  filter(statistic %in% play_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for PLAY Reaction Time Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Visualize Skip/Pass RT metrics
ssm_metrics %>%
  filter(statistic %in% skip_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for SKIP/PASS Reaction Time Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Visualize Choice Probability metrics
ssm_metrics %>%
  filter(statistic %in% choice_stats) %>%
  ggplot(aes(x = model_display, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  labs(title = "Mean PPP Values for Choice Probability",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Model", y = "Mean PPP Value")

# Create a heatmap for SSM metrics
ssm_metrics %>%
  ggplot(aes(x = statistic, y = model_display, fill = mean_ppp)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), color = "black", size = 3) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                      midpoint = 0.5, limits = c(0, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "SSM Metrics Heatmap: Mean PPP Values",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Model",
       fill = "Mean PPP")
```

## Comparison: DDM-Only vs. Hybrid Models (SSM Component)

Let's directly compare how the SSM components perform in the DDM-only model versus the hybrid models.

```{r ddm-hybrid-comparison, fig.height=8, fig.width=9}
# Create a dataset for SSM model comparison (DDM-only vs. hybrid)
ssm_model_comparison <- ssm_metrics %>%
  mutate(
    model_type = case_when(
      model %in% ddm_only_models ~ "DDM-Only",
      model %in% hybrid_models ~ "Hybrid (RL+DDM)",
      TRUE ~ "Other"
    ),
    # For hybrid models, extract the RL component
    rl_component = case_when(
      grepl("^ev_", model) ~ "EV",
      grepl("^pvldecay_", model) ~ "PVLdecay",
      grepl("^pvldelta_", model) ~ "PVLdelta",
      grepl("^pvlboth_", model) ~ "PVLboth",
      grepl("^pvlbothsd_", model) ~ "PVLbothsd",
      grepl("^vppdelta_", model) ~ "VPPdelta",
      grepl("^vppdecay_", model) ~ "VPPdecay",
      grepl("^vppboth_", model) ~ "VPPboth",
      TRUE ~ NA_character_
    )
  )

# Calculate average metrics by model type and statistic
ssm_stat_summary <- ssm_model_comparison %>%
  group_by(model_type, statistic) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

# Create separate summaries for different RT types
play_rt_summary <- ssm_stat_summary %>%
  filter(statistic %in% play_rt_stats) %>%
  group_by(model_type) %>%
  summarize(
    play_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    play_mean_extreme = mean(mean_extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

skip_rt_summary <- ssm_stat_summary %>%
  filter(statistic %in% skip_rt_stats) %>%
  group_by(model_type) %>%
  summarize(
    skip_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    skip_mean_extreme = mean(mean_extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

# Combine the summaries
rt_type_summary <- full_join(play_rt_summary, skip_rt_summary, by = "model_type")

# Display the summary table
make_word_table(rt_type_summary, digits = 3,
      caption_text = "SSM Component: Play vs. Skip RT Performance",
      col.names = c("Model Type", "Play Mean PPP", "Play Mean Extreme Ratio", 
                    "Skip Mean PPP", "Skip Mean Extreme Ratio"))

# Visualize the comparison for play RTs
ssm_model_comparison %>%
  filter(statistic %in% play_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("DDM-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "PLAY RT Performance: DDM-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Visualize the comparison for skip RTs
ssm_model_comparison %>%
  filter(statistic %in% skip_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("DDM-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "SKIP RT Performance: DDM-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

# Detailed hybrid model comparison for SSM
ssm_metrics %>%
  filter(model %in% hybrid_models) %>%
  # Group models by family
  mutate(
    model_family = case_when(
      grepl("^ev_", model) ~ "EV+DDM",
      grepl("^pvldecay_", model) ~ "PVLdecay+DDM",
      grepl("^pvldelta_", model) ~ "PVLdelta+DDM",
      grepl("^pvlboth_ddm", model) ~ "PVLboth+DDM",
      grepl("^pvlbothsd_", model) ~ "PVLbothsd+DDM",
      grepl("^vppdecay_", model) ~ "VPPdecay+DDM",
      grepl("^vppdelta_", model) ~ "VPPdelta+DDM",
      grepl("^vppboth_ddm", model) ~ "VPPboth+DDM",
      TRUE ~ model
    )
  ) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_family)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  facet_wrap(~ factor(grepl("play", statistic), labels = c("Skip/Pass RT", "Play RT")), scales = "free_x") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "SSM Component Performance Across Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")
```

# Cross-Model Comparison

Let's examine key metrics across all models to identify the strengths and weaknesses of each approach.

```{r cross-model-comparison, fig.height=10, fig.width=10}
# Function to create component-specific performance summaries
create_component_performance <- function(data, component_type) {
  data %>%
    filter(component == component_type) %>%
    group_by(model, model_display) %>%
    summarize(
      mean_ppp = mean(mean_ppp, na.rm = TRUE),
      extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
      problematic_stats = sum(extreme_ratio > 0.3, na.rm = TRUE),
      total_stats = n(),
      pct_problematic = problematic_stats / total_stats * 100,
      .groups = "drop"
    ) %>%
    rename_with(~ paste0(component_type, "_", .), .cols = c(mean_ppp, extreme_ratio, problematic_stats, total_stats, pct_problematic))
}

# Create data frames for component-specific model performance
rl_component_performance <- create_component_performance(all_summaries, "RL")
ssm_component_performance <- create_component_performance(all_summaries, "SSM")

# Create a base dataframe with all model information
all_models_df <- tibble(
  model = available_all_models,
  model_display = unlist(model_display_names[available_all_models])
)

# Ensure consistent data types for joining
rl_component_performance <- rl_component_performance %>%
  mutate(model_display = as.character(model_display))

ssm_component_performance <- ssm_component_performance %>%
  mutate(model_display = as.character(model_display))

# Join the component performances
model_performance <- all_models_df %>%
  left_join(rl_component_performance, by = c("model", "model_display")) %>%
  left_join(ssm_component_performance, by = c("model", "model_display")) %>%
  mutate(
    # Add model type
    model_type = case_when(
      model %in% rl_only_models ~ "RL Only",
      model %in% ddm_only_models ~ "DDM Only",
      model %in% hybrid_models ~ "Hybrid (RL+DDM)",
      TRUE ~ "Unknown"
    ),
    
    # Calculate overall metrics for all models
    overall_mean_ppp = case_when(
      model %in% rl_only_models ~ RL_mean_ppp,
      model %in% ddm_only_models ~ SSM_mean_ppp,
      model %in% hybrid_models ~ (RL_mean_ppp + SSM_mean_ppp) / 2,
      TRUE ~ NA_real_
    ),
    overall_extreme_ratio = case_when(
      model %in% rl_only_models ~ RL_extreme_ratio,
      model %in% ddm_only_models ~ SSM_extreme_ratio,
      model %in% hybrid_models ~ (RL_extreme_ratio + SSM_extreme_ratio) / 2,
      TRUE ~ NA_real_
    )
  ) %>%
  arrange(desc(overall_mean_ppp))

# Display the combined performance table
make_word_table(model_performance %>% 
        select(model_display, model_type, RL_mean_ppp, RL_extreme_ratio, 
               SSM_mean_ppp, SSM_extreme_ratio, 
               overall_mean_ppp, overall_extreme_ratio),
      digits = 3,
      caption_text = "Component-Specific and Overall Model Performance",
      col.names = c("Model", "Type", "RL Mean PPP", "RL Extreme Ratio", 
                   "SSM Mean PPP", "SSM Extreme Ratio", 
                   "Overall Mean PPP", "Overall Extreme Ratio"))

# Create a visualization of model performance by component
all_summaries %>%
  group_by(model_display, component) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = model_display, y = mean_extreme_ratio, fill = component)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5,
            size = 3) +
  scale_y_continuous(limits = c(0, max(overall_metrics$mean_extreme_ratio) * 1.2),
                    labels = scales::percent) +
  scale_fill_manual(values = c("RL" = "#1B9E77", "SSM" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Model Performance by Component",
       subtitle = "Lower extreme ratio values indicate better fit; PPP values shown above bars",
       x = "Model", y = "Mean Proportion of Extreme PPP Values",
       fill = "Component")

# Create a heatmap for key statistics across all models
# Get all key statistics across components
key_stats_groups <- model_config$key_statistics
key_stats_all <- unlist(key_stats_groups)

# Function to create a statistic group label
assign_metric_group <- function(stat) {
  for (group_name in names(key_stats_groups)) {
    if (stat %in% key_stats_groups[[group_name]]) {
      return(group_name)
    }
  }
  return("Other")
}

# Create more descriptive group names
metric_group_labels <- c(
  "deck_selection" = "Deck Selection",
  "rl_performance" = "Other RL Metrics",
  "play_rt" = "Play RT",
  "skip_rt" = "Skip RT",
  "choice" = "Choice"
)

# Filter for key statistics and assign groups
key_stats_data <- all_summaries %>%
  filter(statistic %in% key_stats_all) %>%
  mutate(
    # Assign each statistic to its metric group
    metric_group_raw = sapply(statistic, assign_metric_group),
    # Convert to user-friendly labels
    metric_group = metric_group_labels[metric_group_raw]
  )

# Create heatmap for PPP values
key_stats_data %>%
  ggplot(aes(x = statistic, y = model_display, fill = mean_ppp)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), color = "black", size = 3) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.5, limits = c(0, 1)) +
  facet_grid(. ~ metric_group, scales = "free", space = "free_x") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "PPP Values for Key Statistics Across All Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Model",
       fill = "Mean PPP Value")

# Create heatmap for extreme ratios
key_stats_data %>%
  ggplot(aes(x = statistic, y = model_display, fill = extreme_ratio)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.0f%%", extreme_ratio*100)), color = "black", size = 3) +
  scale_fill_gradient(low = "green", high = "red", limits = c(0, 1)) +
  facet_grid(. ~ metric_group, scales = "free", space = "free_x") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Proportion of Subjects with Extreme PPP Values",
       subtitle = "Lower values indicate better fit",
       x = "Statistic", y = "Model",
       fill = "Extreme Ratio")
```

# Additional Analysis of New Deck Selection Metrics

Let's dig deeper into the new deck selection metrics to see how models differ in their ability to capture deck selection patterns focusing on specific decks.

```{r new-deck-analysis, fig.height=9, fig.width=10}
# Function to extract block-level learning curve data
extract_block_data <- function(ppc_obj, model_name, metric) {
  # Check if the model has the required plots
  if (is.null(ppc_obj) || 
      !("plots" %in% names(ppc_obj)) || 
      !(metric %in% names(ppc_obj$plots))) {
    return(NULL)
  }
  
  # Try to extract data from the plot
  tryCatch({
    plot_data <- ggplot_build(ppc_obj$plots[[metric]])$data[[2]]
    plot_data$metric <- metric
    plot_data$model <- model_name
    return(plot_data)
  }, error = function(e) {
    warning(paste("Could not extract block data for model:", model_name, "metric:", metric))
    return(NULL)
  })
}

# Define metrics to extract
block_metrics <- c(
  "learning_curve", 
  "new_good_learning_curve", 
  "new_bad_learning_curve"
)

# Initialize empty dataframe for block data
block_data_all <- data.frame()

# Extract block data for each model and metric
for (model_name in names(ppc_data)) {
  for (metric in block_metrics) {
    metric_data <- extract_block_data(ppc_data[[model_name]], model_name, metric)
    if (!is.null(metric_data)) {
      block_data_all <- bind_rows(block_data_all, metric_data)
    }
  }
}

# Check if we have block data to analyze
if (nrow(block_data_all) > 0) {
  # Clean up the dataset
  block_data_clean <- block_data_all %>%
    rename(block = x, value = y) %>%
    mutate(
      model_display = model_display_names[model],
      metric_label = case_when(
        metric == "learning_curve" ~ "Original Good Decks (3+4) / All Selections",
        metric == "new_good_learning_curve" ~ "New Good Decks (3+4) / Decks 1,3,4",
        metric == "new_bad_learning_curve" ~ "Bad Deck (1) / Decks 1,3,4",
        TRUE ~ metric
      ),
      model_type = case_when(
        model %in% rl_only_models ~ "RL Only",
        model %in% ddm_only_models ~ "DDM Only",
        model %in% hybrid_models ~ "Hybrid (RL+DDM)",
        TRUE ~ "Unknown"
      )
    )
  
  # Create learning curve visualization for different metrics
  block_data_clean %>%
    ggplot(aes(x = block, y = value, color = metric_label)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    facet_wrap(~ model_display, scales = "free_y") +
    scale_color_viridis_d() +
    theme_minimal() +
    labs(title = "Learning Curves for Different Deck Selection Metrics",
         subtitle = "Observed data across blocks",
         x = "Block", y = "Proportion",
         color = "Metric")
  
  # Create a comparison of each metric across models
  block_data_clean %>%
    ggplot(aes(x = block, y = value, color = model_display)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    facet_wrap(~ metric_label, scales = "free_y") +
    scale_color_viridis_d() +
    theme_minimal() +
    labs(title = "Deck Selection Metrics Across Models",
         subtitle = "Observed data across blocks",
         x = "Block", y = "Proportion",
         color = "Model")
  
  # Extract base model name for pairings
  block_data_clean <- block_data_clean %>%
    mutate(
      base_model = case_when(
        grepl("_ddm$", model) ~ gsub("_ddm$", "", model),
        TRUE ~ model
      ),
      model_category = case_when(
        model %in% rl_only_models ~ "RL Only",
        model %in% hybrid_models ~ "Hybrid",
        TRUE ~ "Other"
      )
    )
  
  # Plot comparison within each base model
  block_data_clean %>%
    filter(base_model %in% rl_only_models) %>%  # Only include base models that have both versions
    ggplot(aes(x = block, y = value, color = model_category, linetype = model_category)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    facet_grid(metric_label ~ base_model) +
    scale_color_brewer(palette = "Set1") +
    theme_minimal() +
    labs(title = "RL-Only vs. Hybrid Model Comparison",
         subtitle = "Learning curves by base model and metric",
         x = "Block", y = "Proportion",
         color = "Model Type", linetype = "Model Type")
  
  # Create a slope analysis to see learning rate differences
  block_data_clean %>%
    group_by(model, model_display, model_type, metric, metric_label) %>%
    # Calculate slope between first and last block
    summarize(
      first_block = first(value),
      last_block = last(value),
      slope = (last_block - first_block) / (max(block) - min(block)),
      .groups = "drop"
    ) %>%
    ggplot(aes(x = slope, y = reorder(model_display, slope), fill = model_type)) +
    geom_col() +
    facet_wrap(~ metric_label) +
    theme_minimal() +
    labs(title = "Learning Slope by Model and Metric",
         subtitle = "Higher slopes indicate stronger learning effects",
         x = "Slope (Change per Block)",
         y = "Model",
         fill = "Model Type")
} else {
  cat("No block-level data available for analysis\n")
}
```

# Integration with Parameter Recovery Results

```{r param-recovery-integration, fig.height=8, fig.width=10}
# Function to load recovery results
load_recovery_results <- function(model_names) {
  # Paths to recovery data files
  REC_SIM_DIR <- file.path(PROJ_DIR, "Data", "sim", "recovery")
  
  # Initialize empty list for recovery data
  recovery_data <- list()
  
  # Try to load recovery data for each model
  for (model_name in model_names) {
    file_path <- file.path(REC_SIM_DIR, 
                          paste0("recovery_igt_mod_batch_001_", model_name, "_desc-sim_params.rds"))
    
    if (file.exists(file_path)) {
      recovery_data[[model_name]] <- readRDS(file_path)
    } else {
      warning(paste("Recovery file not found for model:", model_name))
    }
  }
  
  return(recovery_data)
}

# Function to extract overall metrics from recovery objects
extract_overall_from_recovery <- function(recovery_obj, model_name) {
  if (is.null(recovery_obj)) {
    return(NULL)
  }
  
  overall <- recovery_obj$overall
  overall$model <- model_name
  return(overall)
}

# Load recovery data for models in our analysis
recovery_data <- load_recovery_results(available_all_models)

# Combine all overall metrics
overall_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_overall_from_recovery(recovery_data[[name]], name)
  })
)

# Create recovery performance data frame
recovery_performance <- overall_df %>%
  pivot_wider(names_from = metric, values_from = value) %>%
  select(model, correlation, rmse, bias, relative_bias)

# Combine with PPC performance
combined_performance <- recovery_performance %>%
  left_join(model_performance, by = "model") %>%
  select(model_display, model_type, correlation, rmse, relative_bias, 
         RL_mean_ppp, RL_extreme_ratio, 
         SSM_mean_ppp, SSM_extreme_ratio,
         overall_mean_ppp, overall_extreme_ratio)

# Create a formatted table
make_word_table(combined_performance, digits = 3,
      caption_text = "Combined Parameter Recovery and PPC Performance",
      col.names = c("Model", "Type", "Param Correlation", "Param RMSE", "Param Rel Bias", 
                   "RL Mean PPP", "RL Extreme Ratio", 
                   "SSM Mean PPP", "SSM Extreme Ratio",
                   "Overall Mean PPP", "Overall Extreme Ratio"))

# Create a scatter plot of parameter recovery vs PPC performance
combined_performance %>%
  ggplot(aes(x = correlation, y = 1 - overall_extreme_ratio, 
             color = model_display, size = 1/rmse)) +
  geom_point(alpha = 0.8) +
  geom_text_repel(aes(label = model_display), size = 3, box.padding = 0.5) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_size_continuous(name = "Inverse RMSE\n(Larger is better)") +
  theme_minimal() +
  labs(title = "Parameter Recovery vs PPC Performance",
       subtitle = "Better models appear in the upper-right (high recovery correlation, low extreme PPP ratios)",
       x = "Parameter Recovery Correlation", 
       y = "PPC Goodness (1 - Mean Extreme Ratio)",
       color = "Model")

# Create component-specific scatter plots
combined_performance %>%
  filter(!is.na(RL_extreme_ratio)) %>%
  ggplot(aes(x = correlation, y = 1 - RL_extreme_ratio, 
             color = model_display, size = 1/rmse)) +
  geom_point(alpha = 0.8) +
  geom_text_repel(aes(label = model_display), size = 3, box.padding = 0.5) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_size_continuous(name = "Inverse RMSE\n(Larger is better)") +
  theme_minimal() +
  labs(title = "Parameter Recovery vs RL Component PPC Performance",
       subtitle = "Better models appear in the upper-right",
       x = "Parameter Recovery Correlation", 
       y = "RL Component PPC Goodness (1 - Extreme Ratio)",
       color = "Model")

combined_performance %>%
  filter(!is.na(SSM_extreme_ratio)) %>%
  ggplot(aes(x = correlation, y = 1 - SSM_extreme_ratio, 
             color = model_display, size = 1/rmse)) +
  geom_point(alpha = 0.8) +
  geom_text_repel(aes(label = model_display), size = 3, box.padding = 0.5) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_size_continuous(name = "Inverse RMSE\n(Larger is better)") +
  theme_minimal() +
  labs(title = "Parameter Recovery vs SSM Component PPC Performance",
       subtitle = "Better models appear in the upper-right",
       x = "Parameter Recovery Correlation", 
       y = "SSM Component PPC Goodness (1 - Extreme Ratio)",
       color = "Model")

# Create a comprehensive plot that combines recovery and PPC metrics
combined_performance %>%
  mutate(
    ppp_deviation = abs(overall_mean_ppp - 0.5),
    extreme_goodness = 1 - overall_extreme_ratio
  ) %>%
  ggplot(aes(x = correlation, y = extreme_goodness, 
             color = model_type, size = 1/ppp_deviation)) +
  geom_point(alpha = 0.8) +
  geom_text_repel(aes(label = model_display), size = 3, box.padding = 0.5) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_size_continuous(name = "PPP Accuracy\n(Larger is better)") +
  scale_color_brewer(palette = "Set1") +
  theme_minimal() +
  labs(title = "Combined Model Performance: Recovery & PPC",
       subtitle = "Better models appear in the upper-right corner",
       x = "Parameter Recovery Correlation", 
       y = "PPC Goodness (1 - Extreme Ratio)",
       color = "Model Type")
```