---
title: "PPC Subject-Level Scatter Plots"
author: "Felix Pichardo"
date: "2025-03-21"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.show = 'all', fig.keep = 'all', dev = 'png', dpi = 300)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(viridis)
library(scales)
library(gridExtra)
library(ggrepel)
library(grid)
library(boot) # For bootstrap confidence intervals
```

# Setup and Configuration

```{r model-config}
# Simplified Model Configuration
model_config <- list(
  # Define model families (the core algorithms)
  families = list(
    ev = list(
      display_name = "Expected Value",
      models = c("ev", "ev_ddm")
    ),
    pvl = list(
      display_name = "Prospect Valence Learning",
      # Group all PVL variants
      variants = list(
        delta = list(
          display_name = "PVLdelta",
          models = c("pvldelta", "pvldelta_ddm")
        ),
        decay = list(
          display_name = "PVLdecay",
          models = c("pvldecay", "pvldecay_ddm") 
        ),
        both = list(
          display_name = "PVLboth",
          models = c("pvlboth", "pvlboth_ddm")
        ),
        bothsd = list(
          display_name = "PVLbothsd",
          models = c("pvlbothsd", "pvlbothsd_ddm")
        ),
        puldelta = list(
          display_name = "PULdelta",
          models = c("puldelta", "puldelta_ddm")
        ),
        puldecay = list(
          display_name = "PULdecay",
          models = c("puldecay", "puldecay_ddm")
        ),
        pulboth = list(
          display_name = "PULboth",
          models = c("pulboth", "pulboth_ddm")
        ),
        pvsdelta = list(
          display_name = "PVSdelta",
          models = c("pvsdelta", "pvsdelta_ddm")
        ),
        pvsdecay = list(
          display_name = "PVSdecay",
          models = c("pvsdecay", "pvsdecay_ddm")
        ),
        pvsboth = list(
          display_name = "PVSboth",
          models = c("pvsboth", "pvsboth_ddm")
        )
      )
    ),
    vpp = list(
      display_name = "Value-Plus-Perseverance",
      # Group all VPP variants
      variants = list(
        delta = list(
          display_name = "VPPdeltag",
          models = c("vppdeltag", "vppdeltag_ddm")
        ),
        decay = list(
          display_name = "VPPdecayg",
          models = c("vppdecayg", "vppdecayg_ddm") 
        ),
        both = list(
          display_name = "VPPbothg",
          models = c("vppbothg", "vppbothg_ddm")
        ),
        delta = list(
          display_name = "VPPdeltagd",
          models = c("vppdeltagd", "vppdeltagd_ddm")
        ),
        decay = list(
          display_name = "VPPdecaygd",
          models = c("vppdecaygd", "vppdecaygd_ddm") 
        ),
        both = list(
          display_name = "VPPbothgd",
          models = c("vppbothgd", "vppbothgd_ddm")
        ),
        puldelta = list(
          display_name = "PULVPPdeltag",
          models = c("pulvppdeltag", "pulvppdeltag_ddm")
        ),
        puldecay = list(
          display_name = "PULVPPdecayg",
          models = c("pulvppdecayg", "pulvppdecayg_ddm")
        ),
        pulboth = list(
          display_name = "PULVPPbothg",
          models = c("pulvppbothg", "pulvppbothg_ddm")
        ),
        pvsdelta = list(
          display_name = "PVSVPPdeltag",
          models = c("pvsvppdeltag", "pvsvppdeltag_ddm")
        ),
        pvsdecay = list(
          display_name = "PVSVPPdecayg",
          models = c("pvsvppdecayg", "pvsvppdecayg_ddm")
        ),
        pvsboth = list(
          display_name = "PVSVPPbothg",
          models = c("pvsvppbothg", "pvsvppbothg_ddm")
        )
      )
    ),
    ddm = list(
      display_name = "DDM Only",
      models = c("ddm")
    )
  ),
  
  # Define model types (for categorization)
  types = list(
    rl_only = "Reinforcement Learning", 
    ddm_only = "Sequential Sampling",
    hybrid = "Hybrid (RL+DDM)"
  ),
  
  # Define key statistics for PPC analysis
  key_statistics = list(
    deck_selection = c("good_deck_ratio", "new_good_deck_ratio", "new_bad_deck_ratio"),
    rl_performance = c("skip_ratio", "total_money", "avg_outcome"),
    play_rt = c("rt_play_mean", "rt_play_median", "rt_play_quantiles_10%", "rt_play_quantiles_30%", 
                "rt_play_quantiles_50%", "rt_play_quantiles_70%", "rt_play_quantiles_90%"),
    skip_rt = c("rt_skip_mean", "rt_skip_median", "rt_skip_quantiles_10%", "rt_skip_quantiles_30%", 
                "rt_skip_quantiles_50%", "rt_skip_quantiles_70%", "rt_skip_quantiles_90%"),
    choice = c("choice_prob")
  )
)

# Build derived model lists
build_model_lists <- function(config) {
  # Initialize lists
  all_models <- character()
  display_names <- list()
  rl_only_models <- character()
  ddm_only_models <- character()
  hybrid_models <- character()
  all_model_families <- list()
  
  # Process all model families
  for (family_name in names(config$families)) {
    family <- config$families[[family_name]]
    
    # Handle families with variants
    if ("variants" %in% names(family)) {
      for (variant_name in names(family$variants)) {
        variant <- family$variants[[variant_name]]
        
        # Process each model in the variant
        for (model in variant$models) {
          # Create display name
          display_name <- paste(variant$display_name, ifelse(grepl("_ddm$", model), "+DDM", "Only"))
          display_names[[model]] <- display_name
          
          # Determine model type and store in appropriate list
          if (grepl("_ddm$", model)) {
            hybrid_models <- c(hybrid_models, model)
          } else if (model == "ddm") {
            ddm_only_models <- c(ddm_only_models, model)
          } else {
            rl_only_models <- c(rl_only_models, model)
          }
          
          # Add to all models list
          all_models <- c(all_models, model)
          
          # Add to model families
          base_family <- ifelse(family_name == "ddm", "ddm", 
                                paste0(family_name, variant_name))
          
          if (is.null(all_model_families[[base_family]])) {
            all_model_families[[base_family]] <- character()
          }
          all_model_families[[base_family]] <- c(all_model_families[[base_family]], model)
        }
      }
    } else {
      # Simple family without variants (like EV or DDM)
      for (model in family$models) {
        # Create display name
        display_name <- paste(family$display_name, ifelse(grepl("_ddm$", model), "+DDM", ""))
        display_names[[model]] <- display_name
        
        # Determine model type and store in appropriate list
        if (grepl("_ddm$", model)) {
          hybrid_models <- c(hybrid_models, model)
        } else if (model == "ddm") {
          ddm_only_models <- c(ddm_only_models, model)
        } else {
          rl_only_models <- c(rl_only_models, model)
        }
        
        # Add to all models list
        all_models <- c(all_models, model)
        
        # Add to model families
        base_family <- ifelse(family_name == "ddm", "ddm", family_name)
        if (is.null(all_model_families[[base_family]])) {
          all_model_families[[base_family]] <- character()
        }
        all_model_families[[base_family]] <- c(all_model_families[[base_family]], model)
      }
    }
  }
  
  # Return all derived lists
  return(list(
    all_models = unique(all_models),
    rl_only_models = unique(rl_only_models),
    ddm_only_models = unique(ddm_only_models),
    hybrid_models = unique(hybrid_models),
    model_display_names = display_names,
    model_families = all_model_families
  ))
}

# Generate all the model lists from configuration
derived_lists <- build_model_lists(model_config)
all_models <- derived_lists$all_models
rl_only_models <- derived_lists$rl_only_models
ddm_only_models <- derived_lists$ddm_only_models
hybrid_models <- derived_lists$hybrid_models
model_display_names <- derived_lists$model_display_names
model_families <- derived_lists$model_families

# Function to calculate bootstrap confidence intervals
calc_boot_ci <- function(data, indices, fun) {
  return(fun(data[indices]))
}

# Print model lists for verification
cat("All models:", length(all_models), "\n")
cat("RL-only models:", length(rl_only_models), "\n")
cat("DDM-only models:", length(ddm_only_models), "\n")
cat("Hybrid models:", length(hybrid_models), "\n")
cat("Model families:", length(model_families), "\n")
```

```{r data-loading}
# Function to load PPC result files
load_ppc_results <- function(model_name, base_dir = NULL) {
  if (is.null(base_dir)) {
    PROJ_DIR <- here::here()
    base_dir <- file.path(PROJ_DIR, "Data", "sim", "ppc")
  }
  
  file_path <- file.path(base_dir, paste0("ppc_results_igt_mod_", model_name, "_batch_001.rds"))
  
  if (file.exists(file_path)) {
    return(readRDS(file_path))
  } else {
    warning(paste("File not found for model:", model_name))
    return(NULL)
  }
}

# Paths to data files
PROJ_DIR <- here::here()
PPC_DIR <- file.path(PROJ_DIR, "Data", "sim", "ppc")

# Automatically discover available PPC models
available_ppc_files <- list.files(PPC_DIR, pattern = "ppc_results_igt_mod_.*_batch_001.rds", full.names = FALSE)
available_ppc_models <- available_ppc_files %>% 
  str_remove("ppc_results_igt_mod_") %>%
  str_remove("_batch_001.rds")

# Display discovered models
cat("Discovered PPC models:", length(available_ppc_models), "\n")
print(available_ppc_models)
```

# Subject-Level Prediction Scatter Plots

In this section, we will generate scatter plots showing the relationship between observed and predicted values at the subject level for various metrics and models.

```{r metrics-definition}
# Define metrics of interest
rl_metrics <- c(
  "good_deck_ratio",   # Proportion of good deck selections
  "new_good_deck_ratio", # Newer metric for deck performance
  "total_money",       # Total amount won
  "avg_outcome",       # Average per-trial outcome
  "skip_ratio"         # Proportion of skipped trials
)

rt_metrics <- c(
  "rt_play_mean",      # Mean reaction time for play decisions
  "rt_skip_mean",      # Mean reaction time for skip decisions
  "choice_prob"        # Probability of choice
)

# Create nicer display names for metrics
metric_display_names <- c(
  "good_deck_ratio" = "Good Deck Ratio",
  "new_good_deck_ratio" = "New Good Deck Ratio",
  "total_money" = "Total Money Won",
  "avg_outcome" = "Average Outcome",
  "skip_ratio" = "Skip Ratio",
  "rt_play_mean" = "Play RT (Mean)",
  "rt_skip_mean" = "Skip RT (Mean)",
  "choice_prob" = "Choice Probability"
)
```

```{r load-ppc-data, results='hide'}
# Load PPC data for all available models
ppc_data <- list()
for (model_name in available_ppc_models) {
  ppc_data[[model_name]] <- load_ppc_results(model_name, PPC_DIR)
}

# Update available models list based on what was successfully loaded
available_ppc_models <- names(ppc_data)
available_rl_models <- intersect(rl_only_models, available_ppc_models)
available_hybrid_models <- intersect(hybrid_models, available_ppc_models)
available_ddm_models <- intersect(ddm_only_models, available_ppc_models)

cat("Successfully loaded PPC data for", length(available_ppc_models), "models\n")
```

## Subject-Level Scatter Plots for RL and Hybrid Models

The following plots display how well each model predicts individual subject performance on key behavioral metrics. Each point represents a subject, with observed (actual) values on the x-axis and model-predicted values on the y-axis. Correlation and RMSE values, along with 95% confidence intervals, indicate prediction accuracy.

```{r create-subject-scatter-functions}
# Function to create a subject-level scatter plot with 95% CI
create_subject_scatter <- function(model_name, metric_name, component = "rl") {
  if (!model_name %in% names(ppc_data)) {
    return(NULL)
  }
  
  # Get all subjects
  subject_ids <- names(ppc_data[[model_name]]$subjects)
  
  # Initialize empty dataframe for observed and predicted values
  scatter_data <- data.frame()
  
  # Iterate through subjects
  for (subject_id in subject_ids) {
    subject_data <- ppc_data[[model_name]]$subjects[[subject_id]]
    
    # Check access path based on component
    if (component == "rl") {
      # For RL-only models or RL component of hybrid models
      if ("summary" %in% names(subject_data) && 
          (is.data.frame(subject_data$summary) || 
           (is.list(subject_data$summary) && "rl" %in% names(subject_data$summary)))) {
        
        # Get the summary data
        if (is.data.frame(subject_data$summary)) {
          summary_df <- subject_data$summary
        } else {
          summary_df <- subject_data$summary$rl
        }
        
        # Find the row for this metric
        metric_row <- summary_df[summary_df$statistic == metric_name, ]
        
        if (nrow(metric_row) > 0) {
          # Extract observed and predicted values
          observed <- metric_row$observed
          predicted <- metric_row$predicted_mean
          
          # Add to dataframe
          scatter_data <- bind_rows(scatter_data, 
                                   data.frame(
                                     subject_id = subject_id,
                                     observed = observed,
                                     predicted = predicted
                                   ))
        }
      }
    } else if (component == "ssm") {
      # For DDM-only models or SSM component of hybrid models
      if ("summary" %in% names(subject_data) && 
          (is.data.frame(subject_data$summary) || 
           (is.list(subject_data$summary) && "ssm" %in% names(subject_data$summary)))) {
        
        # Get the summary data
        if (is.data.frame(subject_data$summary)) {
          summary_df <- subject_data$summary
        } else {
          summary_df <- subject_data$summary$ssm
        }
        
        # Find the row for this metric
        metric_row <- summary_df[summary_df$statistic == metric_name, ]
        
        if (nrow(metric_row) > 0) {
          # Extract observed and predicted values
          observed <- metric_row$observed
          predicted <- metric_row$predicted_mean
          
          # Add to dataframe
          scatter_data <- bind_rows(scatter_data, 
                                   data.frame(
                                     subject_id = subject_id,
                                     observed = observed,
                                     predicted = predicted
                                   ))
        }
      }
    }
  }
  
  # If we have data, create the scatter plot
  if (nrow(scatter_data) > 0) {
    # Calculate correlation
    correlation <- cor(scatter_data$observed, scatter_data$predicted, use = "pairwise.complete.obs")
    
    # Calculate RMSE
    rmse <- sqrt(mean((scatter_data$observed - scatter_data$predicted)^2, na.rm = TRUE))
    
    # Calculate bootstrap CI for correlation
    boot_correlation <- function(data, indices) {
      cor(data$observed[indices], data$predicted[indices], use = "pairwise.complete.obs")
    }
    
    # Run bootstrap if we have enough data points
    if (nrow(scatter_data) >= 10) {
      set.seed(123) # For reproducibility
      boot_result <- boot(scatter_data, boot_correlation, R = 1000)
      ci <- boot.ci(boot_result, type = "perc")
      ci_lower <- ci$percent[4]
      ci_upper <- ci$percent[5]
      ci_text <- sprintf("\n95%% CI: [%.3f, %.3f]", ci_lower, ci_upper)
    } else {
      ci_text <- ""
      ci_lower <- NA
      ci_upper <- NA
    }
    
    # Get display name for the model
    model_display <- model_display_names[[model_name]]
    
    # Create the scatter plot with 95% CI
    result_plot <- ggplot(scatter_data, aes(x = observed, y = predicted)) +
      geom_point(alpha = 0.7) +
      geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red") +
      geom_smooth(method = "lm", formula = y ~ x, color = "blue", fill = "lightblue", alpha = 0.3) +
      annotate("text", x = min(scatter_data$observed), y = max(scatter_data$predicted),
              label = paste("r =", round(correlation, 3), ci_text, "\nRMSE =", round(rmse, 3)),
              hjust = 0, vjust = 1) +
      labs(
        title = paste(model_display, "-", metric_display_names[metric_name]),
        x = "Observed Value",
        y = "Predicted Value"
      ) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 11)
      )
    
    # Return plot along with statistics
    return(list(
      plot = result_plot,
      stats = data.frame(
        model = model_name,
        model_display = as.character(model_display),
        metric = metric_name,
        metric_display = metric_display_names[metric_name],
        correlation = correlation,
        ci_lower = ci_lower,
        ci_upper = ci_upper,
        rmse = rmse,
        n_subjects = nrow(scatter_data)
      )
    ))
  } else {
    return(NULL)
  }
}

# Function to create multi-model comparison for a specific metric
create_metric_comparison <- function(metric_name, model_list, component = "rl") {
  # Filter available models
  available_models <- intersect(model_list, available_ppc_models)
  
  # Initialize empty list to store results
  all_results <- list(
    scatter_data = data.frame(),
    model_stats = data.frame()
  )
  
  # Process each model
  for (model_name in available_models) {
    result <- create_subject_scatter(model_name, metric_name, component)
    
    if (!is.null(result)) {
      # Extract data from the plot for combined comparison
      plot_data <- ggplot_build(result$plot)$data[[1]]
      
      # Create combined dataset
      model_data <- data.frame(
        model = model_name,
        model_display = as.character(model_display_names[[model_name]]),
        observed = plot_data$x,
        predicted = plot_data$y
      )
      
      # Add to combined results
      all_results$scatter_data <- bind_rows(all_results$scatter_data, model_data)
      all_results$model_stats <- bind_rows(all_results$model_stats, result$stats)
    }
  }
  
  # If we have data, create comparison plot
  if (nrow(all_results$scatter_data) > 0 && nrow(all_results$model_stats) > 0) {
    # Order models by correlation
    model_order <- all_results$model_stats %>%
      arrange(desc(correlation)) %>%
      pull(model_display)
    
    # Convert model display to factor with ordered levels
    all_results$scatter_data$model_display <- factor(
      all_results$scatter_data$model_display,
      levels = model_order
    )
    
    # Create faceted scatter plot
    comparison_plot <- ggplot(all_results$scatter_data, aes(x = observed, y = predicted)) +
      geom_point(alpha = 0.5) +
      geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red") +
      geom_smooth(method = "lm", formula = y ~ x, color = "blue", se = TRUE) +
      facet_wrap(~ model_display) +
      labs(
        title = paste("Model Comparison for", metric_display_names[metric_name]),
        subtitle = "Models ordered by correlation (higher is better)",
        x = "Observed Value",
        y = "Predicted Value"
      ) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        strip.text = element_text(size = 10, face = "bold"),
        axis.title = element_text(size = 11)
      )
    
    # Add correlation text to each facet
    for (i in 1:nrow(all_results$model_stats)) {
      stat_row <- all_results$model_stats[i, ]
      x_pos <- min(all_results$scatter_data$observed[all_results$scatter_data$model_display == stat_row$model_display])
      y_pos <- max(all_results$scatter_data$predicted[all_results$scatter_data$model_display == stat_row$model_display])
      
      # Create label with correlation and 95% CI
      if (!is.na(stat_row$ci_lower) && !is.na(stat_row$ci_upper)) {
        label_text <- sprintf("r = %.3f [%.3f, %.3f]\nRMSE = %.3f", 
                            stat_row$correlation, stat_row$ci_lower, stat_row$ci_upper, stat_row$rmse)
      } else {
        label_text <- sprintf("r = %.3f\nRMSE = %.3f", stat_row$correlation, stat_row$rmse)
      }
      
      comparison_plot <- comparison_plot +
        annotate("text", x = x_pos, y = y_pos, label = label_text,
                hjust = 0, vjust = 1, size = 3)
    }
    
    # Create a bar plot showing correlations
    correlation_plot <- all_results$model_stats %>%
      mutate(model_display = factor(model_display, levels = model_order)) %>%
      ggplot(aes(x = reorder(model_display, correlation), y = correlation)) +
      geom_bar(stat = "identity", fill = "steelblue") +
      geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +
      geom_text(aes(label = sprintf("%.3f", correlation)),
                hjust = -0.1, size = 3) +
      coord_flip() +
      labs(
        title = paste("Model Prediction Accuracy for", metric_display_names[metric_name]),
        subtitle = "Subject-level correlation with 95% confidence intervals",
        x = "Model",
        y = "Correlation"
      ) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 11)
      )
    
    # Return both plots along with statistics
    return(list(
      scatter_plot = comparison_plot,
      correlation_plot = correlation_plot,
      stats = all_results$model_stats
    ))
  } else {
    return(NULL)
  }
}
```

### RL Metrics Scatter Plots

Each plot shows how well the model predicts individual differences in RL-related metrics.

```{r rl-scatter-plots, fig.height=10, fig.width=14, results='hide'}
# Generate scatter plots for RL metrics across models
# This includes both RL-only models and hybrid models with RL components
rl_model_list <- c(available_rl_models, available_hybrid_models)

# Process each RL metric
rl_results <- list()
for (metric in rl_metrics) {
  cat(paste("\n### Comparing Models on", metric_display_names[metric], "\n"))
  result <- create_metric_comparison(metric, rl_model_list, "rl")
  if (!is.null(result)) {
    rl_results[[metric]] <- result
    print(result$correlation_plot)
    print(result$scatter_plot)
    
    # Display statistics table
    kable(result$stats %>% 
            select(model_display, correlation, ci_lower, ci_upper, rmse, n_subjects) %>%
            arrange(desc(correlation)), 
          digits = 3,
          col.names = c("Model", "Correlation", "95% CI Lower", "95% CI Upper", "RMSE", "# Subjects"),
          caption = paste("Model Prediction Accuracy for", metric_display_names[metric])) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                   full_width = FALSE) %>%
      print()
  } else {
    cat("No valid data for this metric\n")
  }
}
```

### RT Metrics Scatter Plots

These plots show how well hybrid and DDM models predict individual differences in reaction time metrics.

```{r rt-scatter-plots, fig.height=10, fig.width=14, results='hide'}
# Generate scatter plots for RT metrics across models
# This includes both hybrid models and DDM-only models
rt_model_list <- c(available_hybrid_models, available_ddm_models)

# Process each RT metric
rt_results <- list()
for (metric in rt_metrics) {
  cat(paste("\n### Comparing Models on", metric_display_names[metric], "\n"))
  result <- create_metric_comparison(metric, rt_model_list, "ssm")
  if (!is.null(result)) {
    rt_results[[metric]] <- result
    print(result$correlation_plot)
    print(result$scatter_plot)
    
    # Display statistics table
    kable(result$stats %>% 
            select(model_display, correlation, ci_lower, ci_upper, rmse, n_subjects) %>%
            arrange(desc(correlation)), 
          digits = 3,
          col.names = c("Model", "Correlation", "95% CI Lower", "95% CI Upper", "RMSE", "# Subjects"),
          caption = paste("Model Prediction Accuracy for", metric_display_names[metric])) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                   full_width = FALSE) %>%
      print()
  } else {
    cat("No valid data for this metric\n")
  }
}
```

## Individual Differences Analysis

```{r individual-diff-analysis, fig.height=10, fig.width=14}
# Function to calculate individual difference correlations across all models
calculate_individual_correlations <- function(component_type, metrics) {
  # Initialize results dataframe
  results <- data.frame()
  
  # Process by model type
  if (component_type == "rl") {
    model_list <- c(available_rl_models, available_hybrid_models)
  } else {
    model_list <- c(available_hybrid_models, available_ddm_models)
  }
  
  # Process all models for each metric
  for (model_name in model_list) {
    for (metric_name in metrics) {
      result <- create_subject_scatter(model_name, metric_name, component_type)
      if (!is.null(result)) {
        results <- bind_rows(results, result$stats)
      }
    }
  }
  
  return(results)
}

# Calculate for RL metrics
rl_correlations <- calculate_individual_correlations("rl", rl_metrics)

# Calculate for RT metrics
rt_correlations <- calculate_individual_correlations("ssm", rt_metrics)

# Combine all correlations
all_correlations <- bind_rows(
  rl_correlations %>% mutate(component = "RL"),
  rt_correlations %>% mutate(component = "SSM")
)

# Display combined statistics
kable(all_correlations %>% 
        select(model_display, component, metric_display, correlation, ci_lower, ci_upper, rmse, n_subjects) %>%
        arrange(component, metric_display, desc(correlation)), 
      digits = 3,
      col.names = c("Model", "Component", "Metric", "Correlation", "95% CI Lower", "95% CI Upper", "RMSE", "# Subjects"),
      caption = "Subject-Level Prediction Performance Across All Models and Metrics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
               full_width = FALSE)

# Visualize performance by component type (RL vs SSM)
component_plot <- ggplot(all_correlations, 
       aes(x = reorder(paste(metric_display, "-", model_display), correlation), 
           y = correlation, fill = component)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +
  facet_wrap(~ component, scales = "free_y") +
  coord_flip() +
  labs(title = "Subject-Level Prediction Performance",
       subtitle = "By model and metric with 95% confidence intervals",
       x = "Model and Metric",
       y = "Correlation",
       fill = "Component") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text.y = element_text(size = 7),
    legend.title = element_text(size = 10)
  )
print(component_plot)

# Find best performing models for each metric
best_models <- all_correlations %>%
  group_by(component, metric, metric_display) %>%
  slice_max(order_by = correlation, n = 1) %>%
  ungroup() %>%
  select(component, metric_display, model_display, correlation, ci_lower, ci_upper, rmse) %>%
  arrange(component, metric_display)

# Display best models table
kable(best_models, digits = 3,
      col.names = c("Component", "Metric", "Best Model", "Correlation", 
                   "95% CI Lower", "95% CI Upper", "RMSE"),
      caption = "Best Performing Models for Each Metric") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
               full_width = FALSE)

# Create a heatmap of correlations
heatmap_data <- all_correlations %>%
  select(model_display, component, metric_display, correlation) %>%
  mutate(
    model_component = paste(model_display, "-", component)
  )

# Create heatmap
correlation_heatmap <- ggplot(heatmap_data, 
       aes(x = metric_display, y = model_component, fill = correlation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", correlation)), color = "black", size = 2.5) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.5, limits = c(0, 1)) +
  labs(title = "Subject-Level Prediction Correlations",
       subtitle = "By model and metric (higher values indicate better prediction)",
       x = "Metric",
       y = "Model",
       fill = "Correlation") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(correlation_heatmap)

# Analyze performance of hybrid models vs. non-hybrid models
hybrid_comparison <- all_correlations %>%
  mutate(
    is_hybrid = grepl("\\+DDM", model_display)
  ) %>%
  group_by(component, metric_display, is_hybrid) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    sd_correlation = sd(correlation, na.rm = TRUE),
    n_models = n(),
    se_correlation = sd_correlation / sqrt(n_models),
    ci_lower = mean_correlation - qt(0.975, n_models - 1) * se_correlation,
    ci_upper = mean_correlation + qt(0.975, n_models - 1) * se_correlation,
    .groups = "drop"
  )

# Display hybrid vs non-hybrid comparison
kable(hybrid_comparison, digits = 3,
      col.names = c("Component", "Metric", "Is Hybrid", "Mean Correlation", 
                   "SD Correlation", "# Models", "SE", "95% CI Lower", "95% CI Upper"),
      caption = "Hybrid vs. Non-Hybrid Models Performance Comparison") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
               full_width = FALSE)

# Visualize hybrid vs non-hybrid comparison
hybrid_plot <- ggplot(hybrid_comparison, 
       aes(x = metric_display, y = mean_correlation, fill = is_hybrid)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                position = position_dodge(width = 0.9),
                width = 0.25) +
  facet_wrap(~ component) +
  scale_fill_manual(values = c("FALSE" = "#1B9E77", "TRUE" = "#7570B3"),
                  labels = c("FALSE" = "Non-Hybrid", "TRUE" = "Hybrid")) +
  labs(title = "Hybrid vs. Non-Hybrid Models Performance",
       subtitle = "Mean correlations with 95% confidence intervals",
       x = "Metric",
       y = "Mean Correlation",
       fill = "Model Type") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.title = element_text(size = 10)
  )
print(hybrid_plot)
```

# Model Selection Summary

This section provides a summary of the best-performing models based on their ability to predict individual differences in key behavioral metrics.

```{r model-selection-summary, fig.height=8, fig.width=14}
# Create a comprehensive ranking of models based on correlation across metrics
model_ranking <- all_correlations %>%
  group_by(model, model_display, component) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    sd_correlation = sd(correlation, na.rm = TRUE),
    n_metrics = n(),
    se_correlation = sd_correlation / sqrt(n_metrics),
    ci_lower = mean_correlation - qt(0.975, n_metrics - 1) * se_correlation,
    ci_upper = mean_correlation + qt(0.975, n_metrics - 1) * se_correlation,
    min_correlation = min(correlation, na.rm = TRUE),
    max_correlation = max(correlation, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(component, desc(mean_correlation))

# Display model ranking
kable(model_ranking, digits = 3,
      col.names = c("Model", "Display Name", "Component", "Mean Correlation", 
                   "SD Correlation", "# Metrics", "SE", "95% CI Lower", "95% CI Upper",
                   "Min Correlation", "Max Correlation"),
      caption = "Model Rankings by Subject-Level Prediction Performance") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
               full_width = FALSE)

# Create a visualization of model rankings
ranking_plot <- ggplot(model_ranking, 
       aes(x = reorder(model_display, mean_correlation), y = mean_correlation, fill = component)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.25) +
  geom_text(aes(label = sprintf("%.3f", mean_correlation)),
            position = position_stack(vjust = 0.5),
            color = "white", fontface = "bold") +
  facet_wrap(~ component, scales = "free_y") +
  coord_flip() +
  labs(title = "Model Rankings by Subject-Level Prediction Performance",
       subtitle = "Mean correlation across metrics with 95% confidence intervals",
       x = "Model",
       y = "Mean Correlation",
       fill = "Component") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(ranking_plot)

# Create a combined ranking for hybrid models (combining RL and SSM performance)
hybrid_models_ranking <- all_correlations %>%
  filter(grepl("\\+DDM", model_display)) %>%
  group_by(model, model_display) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    sd_correlation = sd(correlation, na.rm = TRUE),
    n_metrics = n(),
    se_correlation = sd_correlation / sqrt(n_metrics),
    ci_lower = mean_correlation - qt(0.975, n_metrics - 1) * se_correlation,
    ci_upper = mean_correlation + qt(0.975, n_metrics - 1) * se_correlation,
    min_correlation = min(correlation, na.rm = TRUE),
    max_correlation = max(correlation, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(mean_correlation))

# Display hybrid models ranking
kable(hybrid_models_ranking, digits = 3,
      col.names = c("Model", "Display Name", "Mean Correlation", 
                   "SD Correlation", "# Metrics", "SE", "95% CI Lower", "95% CI Upper",
                   "Min Correlation", "Max Correlation"),
      caption = "Hybrid Models Ranking (Combining RL and SSM Metrics)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
               full_width = FALSE)

# Create a visualization of hybrid models ranking
hybrid_ranking_plot <- ggplot(hybrid_models_ranking, 
       aes(x = reorder(model_display, mean_correlation), y = mean_correlation)) +
  geom_bar(stat = "identity", fill = "#7570B3") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.25) +
  geom_text(aes(label = sprintf("%.3f", mean_correlation)),
            position = position_stack(vjust = 0.5),
            color = "white", fontface = "bold") +
  coord_flip() +
  labs(title = "Hybrid Models Ranking",
       subtitle = "Mean correlation across all metrics with 95% confidence intervals",
       x = "Model",
       y = "Mean Correlation") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11)
  )
print(hybrid_ranking_plot)

# Create a scatterplot showing correlation range by model
range_plot <- ggplot(model_ranking, 
       aes(x = reorder(model_display, mean_correlation), y = mean_correlation, color = component)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = min_correlation, ymax = max_correlation), width = 0.2) +
  coord_flip() +
  labs(title = "Model Performance Range",
       subtitle = "Mean correlation with range from min to max",
       x = "Model",
       y = "Correlation",
       color = "Component") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    legend.title = element_text(size = 10)
  )
print(range_plot)
```
