---
title: "Posterior Predictive Check Analysis"
author: "Felix Pichardo"
date: "2025-03-07"
output: 
  word_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(viridis)
library(scales)
library(gridExtra)
```

# Introduction

This document analyzes the posterior predictive checks (PPCs) performed on several computational models of decision-making in the modified Iowa Gambling Task (mIGT). PPCs evaluate a model's ability to reproduce patterns observed in the empirical data by comparing statistics derived from observed data to statistics calculated from simulated data generated using posterior parameter estimates.

## Models Evaluated

We evaluate several types of models:

1. **Reinforcement Learning (RL) Models**
   - Expected Value (EV)
   - Prospect Valence Learning with Delta rule (PVLdelta)
   - Prospect Valence Learning with Decay rule (PVLdecay)

2. **Sequential Sampling Model (SSM)**
   - Drift Diffusion Model (DDM)

3. **Hybrid Models (RL+SSM)**
   - EV+DDM
   - PVLdelta+DDM
   - PVLdecay+DDM

## Posterior Predictive Checks (PPC)

For each model, we assess how well it captures key behavioral patterns by calculating posterior predictive p-values (PPP values). These values represent the probability that the simulated data are more extreme than the observed data. Values close to 0.5 indicate good fit, while values close to 0 or 1 indicate poor fit. We consider PPP values below 0.05 or above 0.95 as "extreme" and potentially problematic.

```{r load-data, include=FALSE}
# Function to load PPC result files
load_ppc_results <- function(file_path) {
  readRDS(file_path)
}

# Paths to data files
PROJ_DIR <- here::here()
PPC_DIR <- file.path(PROJ_DIR, "Data", "sim", "ppc")

# List of files to process - all models
ppc_files <- list.files(PPC_DIR, pattern = "ppc_results_igt_mod_.*_batch_001.rds", full.names = TRUE)

# Load all PPC objects
ppc_data <- list()
for (file in ppc_files) {
  model_name <- basename(file) %>% 
    str_remove("ppc_results_igt_mod_") %>%
    str_remove("_batch_001.rds")
  
  ppc_data[[model_name]] <- load_ppc_results(file)
}

# Create a list of model names with proper formatting for display
model_display_names <- c(
  "ddm" = "DDM Only",
  "ev" = "EV Only",
  "pvldecay" = "PVLdecay Only",
  "pvldelta" = "PVLdelta Only",
  "ev_ddm" = "EV+DDM",
  "pvldecay_ddm" = "PVLdecay+DDM",
  "pvldelta_ddm" = "PVLdelta+DDM"
)

# Group models by type
rl_only_models <- c("ev", "pvldecay", "pvldelta")
ddm_only_models <- c("ddm") 
hybrid_models <- c("ev_ddm", "pvldecay_ddm", "pvldelta_ddm")
```

```{r extract-summary-stats, include=FALSE}
# Function to extract summary statistics
extract_summary_stats <- function(ppc_obj, model_name) {
  # Check if the model has RL and SSM components or just one component
  if (is.list(ppc_obj$model$summary) && "rl" %in% names(ppc_obj$model$summary)) {
    # Hybrid model with both components
    rl_summary <- ppc_obj$model$summary$rl %>%
      mutate(component = "RL", model = model_name)
    
    ssm_summary <- ppc_obj$model$summary$ssm %>%
      mutate(component = "SSM", model = model_name)
    
    return(bind_rows(rl_summary, ssm_summary))
  } else {
    # Single component model
    summary_df <- ppc_obj$model$summary
    
    # For individual models, determine component type based on model name
    # rather than using statistics which have misleading prefixes
    component_type <- case_when(
      model_name %in% c("ev", "pvldecay", "pvldelta") ~ "RL",
      model_name == "ddm" ~ "SSM",
      TRUE ~ "Unknown"
    )
    
    # Clean up statistic names by removing misleading prefixes if present
    summary_df <- summary_df %>%
      mutate(statistic = str_remove(statistic, "^(rl_|ssm_)"))
    
    return(summary_df %>% mutate(component = component_type, model = model_name))
  }
}

# Combine all summary statistics
all_summaries <- bind_rows(
  lapply(names(ppc_data), function(name) {
    extract_summary_stats(ppc_data[[name]], name)
  })
)

# Replace model names with display names
all_summaries <- all_summaries %>%
  mutate(model_display = model_display_names[model])

# Reorder factor levels for consistent ordering in plots
all_summaries$model_display <- factor(all_summaries$model_display,
                                      levels = c("DDM Only", "EV Only", "PVLdecay Only", "PVLdelta Only",
                                                "EV+DDM", "PVLdecay+DDM", "PVLdelta+DDM"))

# Create separate datasets for RL and SSM components
rl_summaries <- all_summaries %>% filter(component == "RL")
ssm_summaries <- all_summaries %>% filter(component == "SSM")
```

# Overall PPC Performance

```{r overall-performance}
# Calculate overall fit metrics for each model and component
overall_metrics <- all_summaries %>%
  group_by(model, model_display, component) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    median_ppp = median(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    extreme_stats_count = sum(extreme_ratio > 0.3, na.rm = TRUE),
    total_stats = n(),
    pct_problematic = extreme_stats_count / total_stats * 100,
    .groups = "drop"
  ) %>%
  arrange(component, mean_extreme_ratio)

# Display the overall metrics table
kable(overall_metrics, digits = 3,
      col.names = c("Model", "Display Name", "Component", "Mean PPP", "Median PPP", 
                    "Mean Extreme Ratio", "# Problematic Stats", "Total Stats", "% Problematic"),
      caption = "Overall PPC Performance by Model and Component")
```

**Table Explanation**: This table summarizes the posterior predictive check (PPC) performance for each model and component. "Mean PPP" values closer to 0.5 indicate better model fit. "Mean Extreme Ratio" shows the proportion of subjects with extreme PPP values (lower is better). "% Problematic" indicates the percentage of statistics that exceed a threshold of concern (lower is better).

```{r overall-plot}
# Visualize overall model performance by component
ggplot(overall_metrics, 
       aes(x = reorder(model_display, mean_extreme_ratio), 
           y = mean_extreme_ratio, 
           fill = mean_ppp)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", pct_problematic)), 
            position = position_stack(vjust = 0.5), 
            color = "white", fontface = "bold") +
  facet_wrap(~ component, scales = "free_y") +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.4, limits = c(0, 0.5),
                     name = "Mean PPP\n(closer to 0.5 is better)") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Model Performance by Component",
       subtitle = "Percentage of problematic statistics shown in bars (lower is better)",
       x = NULL, 
       y = "Mean Proportion of Extreme PPP Values")
```

**Figure Explanation**: This figure shows the performance of each model by component type (RL and SSM). The bars represent the mean proportion of extreme PPP values (lower is better), with the percentage of problematic statistics displayed inside each bar. The color indicates the mean PPP value, with greener colors representing values closer to the ideal 0.5.

# Reinforcement Learning (RL) Component Analysis

## RL Metrics Across Models

```{r rl-metrics}
# Define key RL statistics to focus on
rl_key_stats <- c("good_deck_ratio", "skip_ratio", "total_money", "avg_outcome")

# Filter for key RL statistics across all models with RL components
rl_metrics <- rl_summaries %>%
  filter(statistic %in% rl_key_stats)

# Create a comparison table
rl_comparison <- rl_metrics %>%
  select(model_display, statistic, mean_ppp, extreme_ratio) %>%
  pivot_wider(names_from = statistic, 
              values_from = c(mean_ppp, extreme_ratio)) %>%
  arrange(model_display)

# Display the table with better formatting
kable(rl_comparison, digits = 3,
      caption = "RL Metrics: Mean PPP Values and Extreme Ratios by Model")
```

**Table Explanation**: This table shows how well each model captures key reinforcement learning metrics. For each statistic, we provide both the mean PPP value (closer to 0.5 is better) and the extreme ratio (proportion of subjects with extreme PPP values, lower is better).

```{r rl-metrics-plot}
# Create a visualization of RL metrics
ggplot(rl_metrics, aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for RL Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")
```

**Figure Explanation**: This bar chart shows the mean PPP values for key reinforcement learning statistics across models. The dashed black line represents the ideal PPP value of 0.5, while the dotted red lines indicate the boundaries for extreme values (0.05 and 0.95). Bars closer to the dashed black line indicate better model fit for that statistic.

## RL-Only vs. Hybrid Models Comparison

```{r rl-hybrid-comparison}
# Create a dataset for RL model comparison (RL-only vs. hybrid)
rl_model_comparison <- rl_metrics %>%
  mutate(model_type = case_when(
    model %in% rl_only_models ~ "RL-Only",
    model %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Other"
  )) %>%
  # Extract base model name for pairing
  mutate(base_model = case_when(
    model == "ev" | model == "ev_ddm" ~ "EV",
    model == "pvldecay" | model == "pvldecay_ddm" ~ "PVLdecay",
    model == "pvldelta" | model == "pvldelta_ddm" ~ "PVLdelta",
    TRUE ~ "Other"
  ))

# Calculate average metrics by base model and model type
rl_comparison_summary <- rl_model_comparison %>%
  group_by(base_model, model_type) %>%
  summarize(
    mean_ppp_overall = mean(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(base_model, model_type)

# Display the comparison table
kable(rl_comparison_summary, digits = 3,
      col.names = c("Base Model", "Model Type", "Mean PPP", "Mean Extreme Ratio"),
      caption = "RL Component: RL-Only vs. Hybrid Models")
```

**Table Explanation**: This table compares the performance of RL components between RL-only models and their hybrid counterparts. We can see how adding a DDM component affects the fit of the RL component. Mean PPP values closer to 0.5 and lower mean extreme ratios indicate better fit.

```{r rl-stat-comparison}
# Visualize the comparison for each RL statistic
rl_stat_comparison <- rl_model_comparison %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  facet_wrap(~ base_model, ncol = 3) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("RL-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "RL Component Performance: RL-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

rl_stat_comparison
```

**Figure Explanation**: This figure compares the mean PPP values for RL statistics between RL-only models and their hybrid counterparts. Each facet shows a different base model (EV, PVLdecay, PVLdelta), allowing us to see how adding a DDM component affects the fit of each RL statistic. The dashed line represents the ideal PPP value of 0.5.

# Sequential Sampling Model (SSM) Component Analysis

## SSM Metrics Across Models

```{r ssm-metrics}
# Define key SSM statistics to focus on, ensuring both play and pass metrics are included
ssm_key_stats <- c(
  # Choice probabilities
  "choice_prob", 
  # Play reaction times
  "rt_play_mean", "rt_play_median", 
  "rt_play_quantiles_10%", "rt_play_quantiles_90%",
  # Skip/Pass reaction times
  "rt_skip_mean", "rt_skip_median", 
  "rt_skip_quantiles_10%", "rt_skip_quantiles_90%"
)

# Filter for key SSM statistics across all models with DDM components
ssm_metrics <- ssm_summaries %>%
  filter(statistic %in% ssm_key_stats)

# Create a comparison table
ssm_comparison <- ssm_metrics %>%
  select(model_display, statistic, mean_ppp, extreme_ratio) %>%
  pivot_wider(names_from = statistic, 
              values_from = c(mean_ppp, extreme_ratio)) %>%
  arrange(model_display)

# Display the table with better formatting
kable(ssm_comparison, digits = 3,
      caption = "SSM Metrics: Mean PPP Values and Extreme Ratios by Model")
```

**Table Explanation**: This table shows how well each model captures key sequential sampling metrics, including choice probabilities and reaction times for both play and skip decisions. For each statistic, we provide both the mean PPP value (closer to 0.5 is better) and the extreme ratio (proportion of subjects with extreme PPP values, lower is better).

```{r play-rt-plot}
# Group reaction time metrics for clearer visualization
play_rt_stats <- c("rt_play_mean", "rt_play_median", "rt_play_quantiles_10%", "rt_play_quantiles_90%")
skip_rt_stats <- c("rt_skip_mean", "rt_skip_median", "rt_skip_quantiles_10%", "rt_skip_quantiles_90%")

# Visualize Play RT metrics
play_rt_plot <- ssm_metrics %>%
  filter(statistic %in% play_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for PLAY Reaction Time Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

play_rt_plot
```

**Figure Explanation**: This bar chart shows the mean PPP values for play reaction time statistics across models. The dashed black line represents the ideal PPP value of 0.5, while the dotted red lines indicate the boundaries for extreme values (0.05 and 0.95). Bars closer to the dashed black line indicate better model fit for that statistic.

```{r skip-rt-plot}
# Visualize Skip/Pass RT metrics
skip_rt_plot <- ssm_metrics %>%
  filter(statistic %in% skip_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "Mean PPP Values for SKIP/PASS Reaction Time Statistics",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

skip_rt_plot
```

**Figure Explanation**: This bar chart shows the mean PPP values for skip/pass reaction time statistics across models. The dashed black line represents the ideal PPP value of 0.5, while the dotted red lines indicate the boundaries for extreme values (0.05 and 0.95). Bars closer to the dashed black line indicate better model fit for that statistic.

```{r choice-prob-plot}
# Visualize Choice Probability metrics
choice_prob_plot <- ssm_metrics %>%
  filter(statistic == "choice_prob") %>%
  ggplot(aes(x = model_display, y = mean_ppp, fill = model_display)) +
  geom_bar(stat = "identity") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Mean PPP Values for Choice Probability",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Model", y = "Mean PPP Value")

choice_prob_plot
```

**Figure Explanation**: This bar chart shows the mean PPP values for choice probability across models. The dashed black line represents the ideal PPP value of 0.5, while the dotted red lines indicate the boundaries for extreme values (0.05 and 0.95). Bars closer to the dashed black line indicate better model fit for choice probability.

## DDM-Only vs. Hybrid Models Comparison

```{r ddm-hybrid-comparison}
# Create a dataset for SSM model comparison (DDM-only vs. hybrid)
ssm_model_comparison <- ssm_metrics %>%
  mutate(model_type = case_when(
    model %in% ddm_only_models ~ "DDM-Only",
    model %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Other"
  ))

# Group reaction time metrics for clearer visualization
play_rt_stats <- c("rt_play_mean", "rt_play_median", "rt_play_quantiles_10%", "rt_play_quantiles_90%")
skip_rt_stats <- c("rt_skip_mean", "rt_skip_median", "rt_skip_quantiles_10%", "rt_skip_quantiles_90%")

# Calculate average metrics by model type and statistic
ssm_stat_summary <- ssm_model_comparison %>%
  group_by(model_type, statistic) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

# Create separate summaries for different RT types
play_rt_summary <- ssm_stat_summary %>%
  filter(statistic %in% play_rt_stats) %>%
  group_by(model_type) %>%
  summarize(
    play_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    play_mean_extreme = mean(mean_extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

skip_rt_summary <- ssm_stat_summary %>%
  filter(statistic %in% skip_rt_stats) %>%
  group_by(model_type) %>%
  summarize(
    skip_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    skip_mean_extreme = mean(mean_extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  )

# Combine the summaries
rt_type_summary <- full_join(play_rt_summary, skip_rt_summary, by = "model_type")

# Display the summary table
kable(rt_type_summary, digits = 3,
      col.names = c("Model Type", "Play Mean PPP", "Play Mean Extreme Ratio", 
                    "Skip Mean PPP", "Skip Mean Extreme Ratio"),
      caption = "SSM Component: Play vs. Skip RT Performance")
```

**Table Explanation**: This table compares the performance of reaction time modeling between DDM-only and hybrid models, separating play and skip reaction times. Mean PPP values closer to 0.5 and lower mean extreme ratios indicate better fit. We can see how well each model type captures the different types of reaction times.

```{r play-rt-comparison}
# Visualize the comparison for play RTs
play_rt_comparison <- ssm_model_comparison %>%
  filter(statistic %in% play_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("DDM-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "PLAY RT Performance: DDM-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

play_rt_comparison
```

**Figure Explanation**: This figure compares the mean PPP values for play reaction time statistics between DDM-only and hybrid models. The dashed black line represents the ideal PPP value of 0.5, while the dotted red lines indicate the boundaries for extreme values (0.05 and 0.95). This visualization helps us understand if adding RL components improves the fit of play reaction time metrics.

```{r skip-rt-comparison}
# Visualize the comparison for skip RTs
skip_rt_comparison <- ssm_model_comparison %>%
  filter(statistic %in% skip_rt_stats) %>%
  ggplot(aes(x = statistic, y = mean_ppp, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(0.05, 0.95), linetype = "dotted", color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("DDM-Only" = "#1B9E77", "Hybrid (RL+DDM)" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(title = "SKIP RT Performance: DDM-Only vs. Hybrid Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Mean PPP Value")

skip_rt_comparison
```

**Figure Explanation**: This figure compares the mean PPP values for skip reaction time statistics between DDM-only and hybrid models. The dashed black line represents the ideal PPP value of 0.5, while the dotted red lines indicate the boundaries for extreme values (0.05 and 0.95). This visualization helps us understand if adding RL components improves the fit of skip reaction time metrics.

# Cross-Model Comparison

```{r component-performance}
# Create data frames for component-specific model performance
rl_component_performance <- all_summaries %>%
  filter(component == "RL") %>%
  group_by(model, model_display) %>%
  summarize(
    rl_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    rl_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    rl_problematic_stats = sum(extreme_ratio > 0.3, na.rm = TRUE),
    rl_total_stats = n(),
    rl_pct_problematic = rl_problematic_stats / rl_total_stats * 100,
    .groups = "drop"
  )

ssm_component_performance <- all_summaries %>%
  filter(component == "SSM") %>%
  group_by(model, model_display) %>%
  summarize(
    ssm_mean_ppp = mean(mean_ppp, na.rm = TRUE),
    ssm_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    ssm_problematic_stats = sum(extreme_ratio > 0.3, na.rm = TRUE),
    ssm_total_stats = n(),
    ssm_pct_problematic = ssm_problematic_stats / ssm_total_stats * 100,
    .groups = "drop"
  )

# Combine all models and fill in missing values appropriately
all_models <- tibble(
  model = c(rl_only_models, ddm_only_models, hybrid_models),
  model_display = model_display_names[c(rl_only_models, ddm_only_models, hybrid_models)]
)

model_performance <- all_models %>%
  left_join(rl_component_performance, by = c("model", "model_display")) %>%
  left_join(ssm_component_performance, by = c("model", "model_display")) %>%
  mutate(
    # Fill in missing values with NA for models without certain components
    rl_mean_ppp = ifelse(model %in% rl_only_models | model %in% hybrid_models, rl_mean_ppp, NA),
    rl_extreme_ratio = ifelse(model %in% rl_only_models | model %in% hybrid_models, rl_extreme_ratio, NA),
    ssm_mean_ppp = ifelse(model %in% ddm_only_models | model %in% hybrid_models, ssm_mean_ppp, NA),
    ssm_extreme_ratio = ifelse(model %in% ddm_only_models | model %in% hybrid_models, ssm_extreme_ratio, NA),
    
    # Calculate overall metrics for hybrid models
    overall_mean_ppp = case_when(
      model %in% rl_only_models ~ rl_mean_ppp,
      model %in% ddm_only_models ~ ssm_mean_ppp,
      model %in% hybrid_models ~ (rl_mean_ppp + ssm_mean_ppp) / 2,
      TRUE ~ NA_real_
    ),
    overall_extreme_ratio = case_when(
      model %in% rl_only_models ~ rl_extreme_ratio,
      model %in% ddm_only_models ~ ssm_extreme_ratio,
      model %in% hybrid_models ~ (rl_extreme_ratio + ssm_extreme_ratio) / 2,
      TRUE ~ NA_real_
    )
  ) %>%
  arrange(desc(overall_mean_ppp))

# Display the combined performance table
kable(model_performance %>%
        select(model_display, rl_mean_ppp, rl_extreme_ratio, 
               ssm_mean_ppp, ssm_extreme_ratio, 
               overall_mean_ppp, overall_extreme_ratio),
      digits = 3,
      col.names = c("Model", "RL Mean PPP", "RL Extreme Ratio", 
                   "SSM Mean PPP", "SSM Extreme Ratio", 
                   "Overall Mean PPP", "Overall Extreme Ratio"),
      caption = "Component-Specific and Overall Model Performance")
```

**Table Explanation**: This table provides a comprehensive overview of model performance by component. For each model, we show the mean PPP values and extreme ratios for both RL and SSM components (where applicable), as well as the overall performance metrics. Mean PPP values closer to 0.5 and lower extreme ratios indicate better model fit.

```{r component-performance-plot}
# Create a visualization of model performance by component
component_performance_plot <- all_summaries %>%
  group_by(model_display, component) %>%
  summarize(
    mean_ppp = mean(mean_ppp, na.rm = TRUE),
    mean_extreme_ratio = mean(extreme_ratio, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = model_display, y = mean_extreme_ratio, fill = component)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5,
            size = 3) +
  scale_y_continuous(limits = c(0, max(overall_metrics$mean_extreme_ratio) * 1.2),
                    labels = scales::percent) +
  scale_fill_manual(values = c("RL" = "#1B9E77", "SSM" = "#D95F02")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Model Performance by Component",
       subtitle = "Lower extreme ratio values indicate better fit; PPP values shown above bars",
       x = "Model", y = "Mean Proportion of Extreme PPP Values",
       fill = "Component")

component_performance_plot
```

**Figure Explanation**: This bar chart compares the performance of RL and SSM components across all models. The bars represent the mean proportion of extreme PPP values (lower is better), with the actual mean PPP values displayed above each bar. This visualization helps us understand the relative strengths of each component within each model.

```{r key-stats-heatmap}
# Select key statistics for the heatmap
key_rl_stats <- c("good_deck_ratio", "skip_ratio", "avg_outcome", "total_money")
key_play_stats <- c("rt_play_mean", "rt_play_median")
key_skip_stats <- c("rt_skip_mean", "rt_skip_median")
key_choice_stats <- c("choice_prob")

# Gather all key stats
key_stats_all <- c(key_rl_stats, key_play_stats, key_skip_stats, key_choice_stats)

# Filter for key statistics
key_stats_data <- all_summaries %>%
  filter(statistic %in% key_stats_all) %>%
  mutate(metric_group = case_when(
    statistic %in% key_rl_stats ~ "RL Metrics",
    statistic %in% key_play_stats ~ "Play RT",
    statistic %in% key_skip_stats ~ "Skip RT",
    statistic %in% key_choice_stats ~ "Choice",
    TRUE ~ "Other"
  ))

# Create heatmap for PPP values
key_stats_heatmap <- key_stats_data %>%
  ggplot(aes(x = statistic, y = model_display, fill = mean_ppp)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.2f", mean_ppp)), color = "black", size = 3) +
  scale_fill_gradient2(low = "red", mid = "yellow", high = "green", 
                     midpoint = 0.5, limits = c(0, 1)) +
  facet_grid(. ~ metric_group, scales = "free", space = "free_x") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "PPP Values for Key Statistics Across All Models",
       subtitle = "Values closer to 0.5 indicate better fit",
       x = "Statistic", y = "Model",
       fill = "Mean PPP Value")

key_stats_heatmap
```

**Figure Explanation**: This heatmap shows the mean PPP values for key statistics across all models, grouped into four categories: RL Metrics, Play RT, Skip RT, and Choice. The color scale ranges from red (poor fit) through yellow to green (good fit), with the actual PPP values displayed in each cell. This visualization allows us to quickly identify strengths and weaknesses across models and statistics.

```{r extreme-ratio-heatmap}
# Create heatmap for extreme ratios
extreme_ratio_heatmap <- key_stats_data %>%
  ggplot(aes(x = statistic, y = model_display, fill = extreme_ratio)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.0f%%", extreme_ratio*100)), color = "black", size = 3) +
  scale_fill_gradient(low = "green", high = "red", limits = c(0, 1)) +
  facet_grid(. ~ metric_group, scales = "free", space = "free_x") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Proportion of Subjects with Extreme PPP Values",
       subtitle = "Lower values indicate better fit",
       x = "Statistic", y = "Model",
       fill = "Extreme Ratio")

extreme_ratio_heatmap
```

**Figure Explanation**: This heatmap shows the proportion of subjects with extreme PPP values for key statistics across all models. The color scale ranges from green (good fit, low proportion of subjects with extreme values) to red (poor fit, high proportion), with the actual percentages displayed in each cell. This visualization helps us identify which models and statistics have problematic fits at the subject level.

```{r param-recovery-integration, include=FALSE}
# Extract overall metrics from the recovery RMD file
# Create a function to extract overall metrics
extract_overall <- function(recovery_obj, model_name) {
  overall <- recovery_obj$overall
  overall$model <- model_name
  return(overall)
}

# Paths to recovery data files
REC_SIM_DIR <- file.path(PROJ_DIR, "Data", "sim", "recovery")

# List of files to process
recovery_files = list.files(REC_SIM_DIR, 
                            pattern = "recovery_igt_mod_batch_001_.*_desc-sim_params.rds", 
                            full.names = TRUE)

# Load all recovery objects
recovery_data <- list()
for (file in recovery_files) {
  model_name <- basename(file) %>% 
    str_remove("recovery_igt_mod_batch_001_") %>%
    str_remove("_desc-sim_params.rds")
  
  recovery_data[[model_name]] <- readRDS(file)
}

# Combine all overall metrics
overall_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_overall(recovery_data[[name]], name)
  })
)

# Create recovery performance data frame
recovery_performance <- overall_df %>%
  pivot_wider(names_from = metric, values_from = value) %>%
  select(model, correlation, rmse, bias, relative_bias)

# Combine with PPC performance
combined_performance <- recovery_performance %>%
  left_join(model_performance, by = "model") %>%
  select(model_display, correlation, rmse, relative_bias, 
         rl_mean_ppp, rl_extreme_ratio, 
         ssm_mean_ppp, ssm_extreme_ratio,
         overall_mean_ppp, overall_extreme_ratio)
```

```{r combined-performance}
# Create a formatted table
kable(combined_performance, digits = 3,
      col.names = c("Model", "Param Correlation", "Param RMSE", "Param Rel Bias", 
                   "RL Mean PPP", "RL Extreme Ratio", 
                   "SSM Mean PPP", "SSM Extreme Ratio",
                   "Overall Mean PPP", "Overall Extreme Ratio"),
      caption = "Combined Parameter Recovery and PPC Performance")
```

**Table Explanation**: This table integrates parameter recovery metrics with PPC performance measures. Parameter recovery is assessed using correlation (higher is better), RMSE (lower is better), and relative bias (closer to zero is better). This allows us to see the relationship between a model's ability to recover its parameters and its ability to fit empirical data patterns.

```{r scatter-plot}
# Create a scatter plot of parameter recovery vs PPC performance
scatter_plot <- combined_performance %>%
  ggplot(aes(x = correlation, y = 1 - overall_extreme_ratio, 
             color = model_display, size = 1/rmse)) +
  geom_point(alpha = 0.8) +
  geom_text(aes(label = model_display), hjust = -0.2, vjust = 0, size = 3) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_size_continuous(name = "Inverse RMSE\n(Larger is better)") +
  theme_minimal() +
  labs(title = "Parameter Recovery vs PPC Performance",
       subtitle = "Better models appear in the upper-right (high recovery correlation, low extreme PPP ratios)",
       x = "Parameter Recovery Correlation", 
       y = "PPC Goodness (1 - Mean Extreme Ratio)",
       color = "Model")

scatter_plot
```

**Figure Explanation**: This scatter plot shows the relationship between parameter recovery (x-axis, correlation) and PPC performance (y-axis, percentage of good fits). The size of each point represents the inverse of RMSE, so larger points indicate better parameter recovery precision. Models in the upper-right corner exhibit both good parameter recovery and good empirical fit, representing the most reliable models overall.

```{r component-scatter}
# Create component-specific scatter plots
rl_scatter <- combined_performance %>%
  filter(!is.na(rl_extreme_ratio)) %>%
  ggplot(aes(x = correlation, y = 1 - rl_extreme_ratio, 
             color = model_display, size = 1/rmse)) +
  geom_point(alpha = 0.8) +
  geom_text(aes(label = model_display), hjust = -0.2, vjust = 0, size = 3) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_size_continuous(name = "Inverse RMSE\n(Larger is better)") +
  theme_minimal() +
  labs(title = "Parameter Recovery vs RL Component PPC Performance",
       subtitle = "Better models appear in the upper-right",
       x = "Parameter Recovery Correlation", 
       y = "RL Component PPC Goodness (1 - Extreme Ratio)",
       color = "Model")

rl_scatter
```

**Figure Explanation**: This scatter plot focuses specifically on the relationship between parameter recovery and RL component performance. As with the previous plot, models in the upper-right corner represent the best balance between parameter recovery and empirical fit of the RL component.

```{r ssm-scatter}
ssm_scatter <- combined_performance %>%
  filter(!is.na(ssm_extreme_ratio)) %>%
  ggplot(aes(x = correlation, y = 1 - ssm_extreme_ratio, 
             color = model_display, size = 1/rmse)) +
  geom_point(alpha = 0.8) +
  geom_text(aes(label = model_display), hjust = -0.2, vjust = 0, size = 3) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_size_continuous(name = "Inverse RMSE\n(Larger is better)") +
  theme_minimal() +
  labs(title = "Parameter Recovery vs SSM Component PPC Performance",
       subtitle = "Better models appear in the upper-right",
       x = "Parameter Recovery Correlation", 
       y = "SSM Component PPC Goodness (1 - Extreme Ratio)",
       color = "Model")

ssm_scatter
```

**Figure Explanation**: This scatter plot focuses specifically on the relationship between parameter recovery and SSM component performance. Similar to the previous plots, models in the upper-right corner represent the best balance between parameter recovery and empirical fit of the SSM component.