---
title: "Parameter Recovery Results"
author: "Felix Pichardo"
date: "2025-02-28"
output: 
  word_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(ggrepel)  # For label repulsion in plots
```

# Introduction

This document presents the parameter recovery analysis for several computational models of decision-making in the modified Iowa Gambling Task (mIGT). Parameter recovery evaluates how reliably a model's parameters can be estimated from data generated by that model. Good parameter recovery is essential for meaningful interpretation of model parameters in empirical applications.

## Models Evaluated

We evaluate several types of models:

1. **Reinforcement Learning (RL) Models**
   - Expected Value (EV)
   - Prospect Valence Learning with Delta rule (PVLdelta)
   - Prospect Valence Learning with Decay rule (PVLdecay)
   - Prospect Valence Learning with Both rules (PVLboth)

2. **Sequential Sampling Model (SSM)**
   - Drift Diffusion Model (DDM)

3. **Hybrid Models (RL+SSM)**
   - EV+DDM
   - PVLdelta+DDM
   - PVLdecay+DDM
   - PVLboth+DDM

```{r model-config, include=FALSE}
# Model Configuration - Single source of truth for model definitions
model_config <- list(
  # Define model groups for easier reference
  groups = list(
    rl_only = c("ev", "pvldecay", "pvldelta", "pvlboth"),
    ddm_only = c("ddm"),
    hybrid = c("ev_ddm", "pvldecay_ddm", "pvldelta_ddm", "pvlboth_ddm")
  ),
  
  # Display names for each model
  display_names = c(
    "ddm" = "DDM Only",
    "ev" = "EV Only",
    "pvldecay" = "PVLdecay Only",
    "pvldelta" = "PVLdelta Only",
    "pvlboth" = "PVLboth Only",
    "ev_ddm" = "EV+DDM",
    "pvldecay_ddm" = "PVLdecay+DDM",
    "pvldelta_ddm" = "PVLdelta+DDM",
    "pvlboth_ddm" = "PVLboth+DDM"
  ),
  
  # Define model families for comparison
  families = list(
    ev = c("ev", "ev_ddm"),
    pvldecay = c("pvldecay", "pvldecay_ddm"),
    pvldelta = c("pvldelta", "pvldelta_ddm"),
    pvlboth = c("pvlboth", "pvlboth_ddm")
  ),
  
  # Define parameter groups for analysis
  parameter_groups = list(
    "DDM Process" = c("boundary", "tau", "beta"),
    "Consistency/Drift" = c("drift", "drift_con", "con"),
    "Valuation" = c("wgt_pun", "wgt_rew", "gain", "loss"),
    "Learning Rate" = c("update", "retend")
  )
)

# Derived lists for convenience
all_models <- c(
  model_config$groups$rl_only, 
  model_config$groups$ddm_only, 
  model_config$groups$hybrid
)
rl_only_models <- model_config$groups$rl_only
ddm_only_models <- model_config$groups$ddm_only
hybrid_models <- model_config$groups$hybrid
model_display_names <- model_config$display_names
model_families <- model_config$families
```

```{r data-loading, include=FALSE}
# Function to load recovery data with error handling
load_recovery_data <- function(model_name, base_dir = NULL) {
  if (is.null(base_dir)) {
    PROJ_DIR <- here::here()
    base_dir <- file.path(PROJ_DIR, "Data", "sim", "recovery")
  }
  
  file_path <- file.path(base_dir, paste0("recovery_igt_mod_batch_001_", model_name, "_desc-sim_params.rds"))
  
  if (file.exists(file_path)) {
    return(readRDS(file_path))
  } else {
    warning(paste("Recovery file not found for model:", model_name))
    return(NULL)
  }
}

# Paths to data files
PROJ_DIR <- here::here()
REC_SIM_DIR <- file.path(PROJ_DIR, "Data", "sim", "recovery")

# Automatically discover available models in the directory
available_files <- list.files(REC_SIM_DIR, pattern = "recovery_igt_mod_batch_001_.*_desc-sim_params.rds", full.names = FALSE)
available_models <- available_files %>% 
  str_remove("recovery_igt_mod_batch_001_") %>%
  str_remove("_desc-sim_params.rds")

# Load data for all configured models that are available
recovery_data <- list()
for (model_name in all_models) {
  if (model_name %in% available_models) {
    recovery_data[[model_name]] <- load_recovery_data(model_name, REC_SIM_DIR)
  }
}

# Update model lists based on what's actually available
available_rl_models <- intersect(rl_only_models, names(recovery_data))
available_ddm_models <- intersect(ddm_only_models, names(recovery_data))
available_hybrid_models <- intersect(hybrid_models, names(recovery_data))
available_all_models <- names(recovery_data)
```

# Overall Recovery Performance

```{r overall-performance}
# Create a function to extract overall metrics with error handling
extract_overall <- function(recovery_obj, model_name) {
  if (is.null(recovery_obj)) {
    return(NULL)
  }
  
  overall <- recovery_obj$overall
  overall$model <- model_name
  overall$model_display <- model_display_names[model_name]
  
  # Add model type classification
  overall$model_type <- case_when(
    model_name %in% rl_only_models ~ "RL Only",
    model_name %in% ddm_only_models ~ "DDM Only",
    model_name %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Unknown"
  )
  
  return(overall)
}

# Combine all overall metrics
overall_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_overall(recovery_data[[name]], name)
  })
)

# Create a wider format for easier comparison
overall_wide <- overall_df %>%
  pivot_wider(names_from = metric, values_from = value) %>%
  select(model, model_display, model_type, correlation, rmse, bias, relative_bias) %>%
  arrange(model_type, model)

# Display nice table
kable(overall_wide, digits = 3, 
      col.names = c("Model", "Display Name", "Type", "Correlation", "RMSE", "Bias", "Relative Bias"),
      caption = "Overall Recovery Performance Metrics")
```

This table presents the overall parameter recovery performance for each model. The "Correlation" column shows how well the recovered parameters correlate with the true generating parameters (higher values indicate better recovery). "RMSE" (Root Mean Square Error) measures the precision of parameter estimates (lower values indicate better precision). "Bias" and "Relative Bias" indicate systematic deviation from true values (values closer to zero indicate less bias). Models are grouped by type (RL Only, DDM Only, or Hybrid).

```{r correlation-plot}
# Function to visualize overall performance
plot_overall_performance <- function(data, metric = "correlation") {
  # Define plot labels based on metric
  y_label <- case_when(
    metric == "correlation" ~ "Parameter Recovery Correlation (higher is better)",
    metric == "rmse" ~ "Parameter Recovery RMSE (lower is better)",
    metric == "relative_bias" ~ "Parameter Relative Bias (closer to 0 is better)",
    TRUE ~ metric
  )
  
  # Set up color direction based on metric (higher better for correlation, lower better for others)
  color_direction <- if(metric == "correlation") "high" else "low"
  midpoint <- if(metric == "correlation") 0.7 else 0.3
  limits <- if(metric == "correlation") c(0, 1) else NULL
  
  # Create plot
  ggplot(data, aes(x = reorder(model_display, !!sym(metric), FUN = if(metric == "correlation") max else min), 
                   y = !!sym(metric), fill = !!sym(metric))) +
    geom_bar(stat = "identity") +
    scale_fill_gradient2(
      low = if(color_direction == "low") "green" else "red", 
      mid = "yellow", 
      high = if(color_direction == "low") "red" else "green",
      midpoint = midpoint,
      limits = limits
    ) +
    coord_flip() +
    facet_wrap(~ model_type, scales = "free_y") +
    theme_minimal() +
    labs(
      title = paste("Model Recovery Performance -", toupper(metric)),
      x = NULL,
      y = y_label,
      fill = metric
    )
}

# Create overall performance visualizations
plot_overall_performance(overall_wide, "correlation")
```

This figure shows parameter recovery correlation across all models, grouped by model type. Each bar represents a different model, with the length and color intensity indicating correlation strength. Higher correlation values (greener colors, longer bars) indicate better recovery performance. Models are ordered from best to worst within each panel. This visualization helps identify which models most reliably recover their parameters.

```{r rmse-plot}
# Plot RMSE performance
plot_overall_performance(overall_wide, "rmse")
```

This figure shows parameter recovery RMSE (Root Mean Square Error) across all models, grouped by model type. Each bar represents a different model, with shorter bars and greener colors indicating better precision (lower RMSE). Models are ordered from best (lowest RMSE) to worst within each panel. This visualization helps identify which models recover their parameters with the greatest precision.

# Parameter-Specific Recovery

```{r parameter-functions, include=FALSE}
# Function to extract parameter-specific data with error handling
extract_params <- function(recovery_obj, model_name) {
  if (is.null(recovery_obj) || !("by_parameter" %in% names(recovery_obj))) {
    return(NULL)
  }
  
  params <- recovery_obj$by_parameter
  params$model <- model_name
  params$model_display <- model_display_names[model_name]
  
  # Add model type classification
  params$model_type <- case_when(
    model_name %in% rl_only_models ~ "RL Only",
    model_name %in% ddm_only_models ~ "DDM Only",
    model_name %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Unknown"
  )
  
  # Add parameter type based on config
  params$param_type <- NA_character_
  for (type_name in names(model_config$parameter_groups)) {
    type_params <- model_config$parameter_groups[[type_name]]
    params$param_type[params$parameter %in% type_params] <- type_name
  }
  params$param_type[is.na(params$param_type)] <- "Other"
  
  # For hybrid models, extract the RL component
  params$rl_component <- NA_character_
  if (model_name %in% hybrid_models) {
    for (family_name in names(model_families)) {
      if (model_name %in% model_families[[family_name]]) {
        params$rl_component <- family_name
        break
      }
    }
  } else if (model_name %in% rl_only_models) {
    params$rl_component <- model_name
  }
  
  return(params)
}

# Function to create parameter tables for a specific model
create_param_table <- function(model_name) {
  if (!model_name %in% names(recovery_data) || is.null(recovery_data[[model_name]])) {
    return(cat(paste("Model", model_name, "data not available.\n")))
  }
  
  param_df <- recovery_data[[model_name]]$by_parameter

  kable(param_df, digits = 3, 
        caption = paste("Parameter Recovery for", model_display_names[model_name]))
}

# Combine all parameter data
params_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_params(recovery_data[[name]], name)
  })
)
```

## DDM Only Model

```{r ddm-parameter-table}
# Create parameter table for DDM model
for (model_name in available_ddm_models) {
  create_param_table(model_name)
}
```

This table shows recovery metrics for each parameter in the DDM Only model. The parameters include boundary (decision threshold), non-decision time (tau), and bias (beta). "Correlation" indicates how strongly the recovered parameter values correlate with the true values (higher is better). "RMSE" measures the precision of the estimates (lower is better). "Bias" and "Relative Bias" indicate systematic deviation (values closer to 0 are better).

## RL Models

```{r rl-parameter-tables}
# Create parameter tables for RL models
for (model_name in available_rl_models) {
  cat("\n### ", model_display_names[model_name], "\n")
  create_param_table(model_name)
}
```

These tables show recovery metrics for each parameter in the different RL models. Parameters include valuation components (like gain and loss sensitivity) and learning rates. For each parameter, "Correlation" indicates how strongly the recovered values correlate with the true values, while "RMSE" measures estimation precision. Higher correlations and lower RMSE values indicate better parameter recovery.

## Hybrid Models (RL+DDM)

```{r hybrid-parameter-tables}
# Create parameter tables for hybrid models
for (model_name in available_hybrid_models) {
  cat("\n### ", model_display_names[model_name], "\n")
  create_param_table(model_name)
}
```

These tables show recovery metrics for each parameter in the hybrid models that combine reinforcement learning (RL) and drift diffusion model (DDM) components. The parameters include both RL parameters (like valuation and learning rate parameters) and DDM parameters (boundary, non-decision time, bias). The recovery metrics help evaluate how reliably each parameter can be estimated from data generated by the model.

# Cross-Model Parameter Recovery Analysis

```{r cross-model-analysis}
# Create a comparison of correlation by parameter type and model type
correlation_by_param_type <- params_df %>%
  group_by(model_type, param_type) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    mean_rmse = mean(rmse, na.rm = TRUE),
    parameter_count = n(),
    .groups = "drop"
  ) %>%
  arrange(param_type, desc(mean_correlation))

# Display the summary table
kable(correlation_by_param_type, digits = 3,
      col.names = c("Model Type", "Parameter Type", "Mean Correlation", "Mean RMSE", "# Parameters"),
      caption = "Parameter Recovery by Model Type and Parameter Type")
```

This table summarizes parameter recovery performance by model type and parameter category. For each combination, it shows the mean correlation (higher is better), mean RMSE (lower is better), and the number of parameters in that category. This provides insight into which model types best recover different categories of parameters, helping identify strengths and weaknesses in parameter recovery across model structures.

```{r param-type-bar}
# We'll use a more structured approach to visualize this data
ggplot(correlation_by_param_type, 
       aes(x = param_type, y = mean_correlation, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = sprintf("%.3f", mean_correlation)),
            position = position_dodge(width = 0.9),
            vjust = -0.3, size = 3) +
  scale_y_continuous(limits = c(0, max(correlation_by_param_type$mean_correlation) * 1.2)) +
  scale_fill_brewer(palette = "Set2") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Parameter Recovery by Type",
       x = "Parameter Type",
       y = "Mean Correlation",
       fill = "Model Type")
```

This figure compares parameter recovery across different parameter types and model types. Each group of bars represents a parameter category (DDM Process, Consistency/Drift, Learning Rate, Valuation), with different colors showing how well each model type recovers those parameters. The height of each bar shows the mean correlation, with actual values displayed above the bars. This visualization helps identify which model types best recover different parameter categories.

```{r correlation-by-parameter}
# Create better visualization functions
plot_parameter_recovery <- function(data, metric = "correlation", facet_var = "param_type") {
  # Define y-axis label based on metric
  y_label <- if(metric == "correlation") {
    "Correlation (higher is better)"
  } else {
    "RMSE (lower is better)"
  }
  
  # Set plot limits and direction based on metric
  y_limits <- if(metric == "correlation") {
    c(0, 1)
  } else {
    c(0, max(data[[metric]], na.rm = TRUE) * 1.1)
  }
  
  # Choose color palette based on model_type or other variable
  if (length(unique(data$model_type)) > 1) {
    fill_var <- "model_type"
    fill_scale <- scale_fill_brewer(palette = "Set2")
  } else {
    fill_var <- "model_display"
    fill_scale <- scale_fill_viridis_d()
  }
  
  # Create the plot with improved aesthetics
  p <- ggplot(data, aes(x = parameter, y = .data[[metric]], fill = .data[[fill_var]])) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    facet_wrap(as.formula(paste("~", facet_var)), scales = "free_x", ncol = 2) +
    fill_scale +
    scale_y_continuous(limits = y_limits) +
    labs(
      title = paste("Parameter Recovery (", toupper(metric), ")"),
      y = y_label,
      x = "Parameter",
      fill = if(fill_var == "model_type") "Model Type" else "Model"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
      strip.text = element_text(size = 11, face = "bold"),
      panel.grid.major.x = element_blank(),
      panel.grid.minor = element_blank(),
      panel.spacing = unit(1, "lines"),
      strip.background = element_rect(fill = "gray95", color = NA)
    )
  
  return(p)
}

# Plot correlation by parameter and model type
plot_parameter_recovery(params_df, "correlation", "param_type")
```

This detailed visualization shows recovery correlations for individual parameters, grouped by parameter type. Within each panel, different colors represent different model types (RL Only, DDM Only, Hybrid). The height of each bar indicates the correlation between true and recovered parameter values, with higher bars indicating better recovery. This helps identify which specific parameters are recovered well across different model types.

```{r rmse-by-parameter}
# Plot RMSE by parameter and model type
plot_parameter_recovery(params_df, "rmse", "param_type")
```

This visualization shows RMSE (Root Mean Square Error) for individual parameters, grouped by parameter type. Lower bars indicate better precision in parameter recovery. Different colors represent different model types (RL Only, DDM Only, Hybrid). This figure complements the correlation plot by showing the precision of parameter estimates rather than just their relationship with true values.

# Parameter Recovery by Model Family

```{r ev-family, results='asis'}
# Function to plot parameter recovery by family
plot_model_family <- function(family_name, metric = "correlation") {
  # Get models in this family
  family_models <- c(
    family_name,  # RL-only
    paste0(family_name, "_ddm")  # Hybrid
  )
  
  # Filter data for this family
  family_data <- params_df %>% 
    filter(model %in% intersect(family_models, available_all_models))
  
  # Return NULL if no data
  if (nrow(family_data) == 0) {
    return(NULL)
  }
  
  # Create plot
  plot_parameter_recovery(family_data, metric)
}

# Create family-specific plot for EV if available
if (sum(model_families[["ev"]] %in% available_all_models) > 0) {
  ev_corr_plot <- plot_model_family("ev", "correlation")
  ev_rmse_plot <- plot_model_family("ev", "rmse")
  if (!is.null(ev_corr_plot)) {
    print(ev_corr_plot + labs(title = "EV Family: Parameter Recovery (Correlation)"))
  }
  if (!is.null(ev_rmse_plot)) {
    print(ev_rmse_plot + labs(title = "EV Family: Parameter Recovery (RMSE)"))
  }
}
```

These figures compare parameter recovery within the EV (Expected Value) model family, showing both the standalone EV model and the hybrid EV+DDM model. The correlation plot (top) shows how strongly recovered parameters correlate with true values, while the RMSE plot (bottom) shows estimation precision. Parameters are grouped by type (DDM Process, Consistency/Drift, etc.). This comparison reveals how adding a DDM component affects parameter recovery in the EV framework.

```{r pvldecay-family, results='asis'}
# Create family-specific plot for PVLdecay if available
if (sum(model_families[["pvldecay"]] %in% available_all_models) > 0) {
  pvldecay_corr_plot <- plot_model_family("pvldecay", "correlation")
  pvldecay_rmse_plot <- plot_model_family("pvldecay", "rmse")
  if (!is.null(pvldecay_corr_plot)) {
    print(pvldecay_corr_plot + labs(title = "PVLDECAY Family: Parameter Recovery (Correlation)"))
  }
  if (!is.null(pvldecay_rmse_plot)) {
    print(pvldecay_rmse_plot + labs(title = "PVLDECAY Family: Parameter Recovery (RMSE)"))
  }
}
```

These figures compare parameter recovery within the PVLdecay model family, showing both the standalone PVLdecay model and the hybrid PVLdecay+DDM model. The correlation plot shows how strongly recovered parameters correlate with true values, while the RMSE plot shows estimation precision. Parameters are grouped by type. This comparison helps understand how adding a DDM component affects parameter recovery in the PVLdecay framework.

```{r pvldelta-family, results='asis'}
# Create family-specific plot for PVLdelta if available
if (sum(model_families[["pvldelta"]] %in% available_all_models) > 0) {
  pvldelta_corr_plot <- plot_model_family("pvldelta", "correlation")
  pvldelta_rmse_plot <- plot_model_family("pvldelta", "rmse")
  if (!is.null(pvldelta_corr_plot)) {
    print(pvldelta_corr_plot + labs(title = "PVLDELTA Family: Parameter Recovery (Correlation)"))
  }
  if (!is.null(pvldelta_rmse_plot)) {
    print(pvldelta_rmse_plot + labs(title = "PVLDELTA Family: Parameter Recovery (RMSE)"))
  }
}
```

These figures compare parameter recovery within the PVLdelta model family, showing both the standalone PVLdelta model and the hybrid PVLdelta+DDM model. The correlation plot shows how strongly recovered parameters correlate with true values, while the RMSE plot shows estimation precision. Parameters are grouped by type. This comparison reveals how adding a DDM component affects parameter recovery in the PVLdelta framework.

```{r pvlboth-family, results='asis'}
# Create family-specific plot for PVLboth if available
if (sum(model_families[["pvlboth"]] %in% available_all_models) > 0) {
  pvlboth_corr_plot <- plot_model_family("pvlboth", "correlation")
  pvlboth_rmse_plot <- plot_model_family("pvlboth", "rmse")
  if (!is.null(pvlboth_corr_plot)) {
    print(pvlboth_corr_plot + labs(title = "PVLBOTH Family: Parameter Recovery (Correlation)"))
  }
  if (!is.null(pvlboth_rmse_plot)) {
    print(pvlboth_rmse_plot + labs(title = "PVLBOTH Family: Parameter Recovery (RMSE)"))
  }
}
```

These figures compare parameter recovery within the PVLboth model family, showing both the standalone PVLboth model and the hybrid PVLboth+DDM model. The correlation plot shows how strongly recovered parameters correlate with true values, while the RMSE plot shows estimation precision. Parameters are grouped by type. This comparison helps understand how adding a DDM component affects parameter recovery in this more complex RL framework.

# Parameter-Focused Analysis

```{r ddm-process-parameters, results='asis'}
# Function to create parameter-focused plots
plot_by_parameter_type <- function(param_type_focus) {
  # Filter data for this parameter type
  param_data <- params_df %>% 
    filter(param_type == param_type_focus)
  
  # If no data, return NULL
  if (nrow(param_data) == 0) {
    return(NULL)
  }
  
  # Create a cleaner model family grouping for side-by-side plots
  param_data <- param_data %>%
    mutate(
      model_group = case_when(
        model_type == "DDM Only" ~ "DDM Only",
        model_type == "RL Only" ~ "RL Only",
        model_type == "Hybrid (RL+DDM)" ~ "Hybrid (RL+DDM)",
        TRUE ~ "Other"
      ),
      model_family = case_when(
        grepl("^ev", model) | grepl("_ev_", model) ~ "EV",
        grepl("^pvldecay", model) | grepl("_pvldecay_", model) ~ "PVLdecay",
        grepl("^pvldelta", model) | grepl("_pvldelta_", model) ~ "PVLdelta",
        grepl("^pvlboth", model) | grepl("_pvlboth_", model) ~ "PVLboth",
        TRUE ~ "DDM"
      )
    )
  
  # Plot correlation
  p_corr <- ggplot(param_data, aes(x = model_family, y = correlation, fill = model_group)) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    facet_wrap(~ parameter, scales = "free_x", ncol = 3) +
    scale_fill_brewer(palette = "Set2") +
    scale_y_continuous(limits = c(0, 1)) +
    labs(
      title = paste("Parameter Recovery (Correlation) for", param_type_focus, "Parameters"),
      y = "Correlation (higher is better)",
      x = "Model Family",
      fill = "Model Type"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
      strip.text = element_text(size = 11, face = "bold"),
      panel.grid.major.x = element_blank(),
      panel.grid.minor = element_blank(),
      panel.spacing = unit(1, "lines"),
      strip.background = element_rect(fill = "gray95", color = NA)
    )
  
  # Plot RMSE
  p_rmse <- ggplot(param_data, aes(x = model_family, y = rmse, fill = model_group)) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    facet_wrap(~ parameter, scales = "free_y", ncol = 3) +
    scale_fill_brewer(palette = "Set2") +
    labs(
      title = paste("Parameter Recovery (RMSE) for", param_type_focus, "Parameters"),
      y = "RMSE (lower is better)",
      x = "Model Family",
      fill = "Model Type"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
      strip.text = element_text(size = 11, face = "bold"),
      panel.grid.major.x = element_blank(),
      panel.grid.minor = element_blank(),
      panel.spacing = unit(1, "lines"),
      strip.background = element_rect(fill = "gray95", color = NA)
    )
  
  return(list(correlation = p_corr, rmse = p_rmse))
}

# Generate plots for DDM Process parameters
ddm_plots <- plot_by_parameter_type("DDM Process")
if (!is.null(ddm_plots)) {
  print(ddm_plots$correlation)
  print(ddm_plots$rmse)
}
```

These figures focus specifically on DDM Process parameters (boundary, tau, beta). The correlation plot (top) shows how well these parameters are recovered in different model families and types, with higher bars indicating better recovery. The RMSE plot (bottom) shows the precision of parameter estimates, with lower bars indicating better precision. Parameters are organized by model family (DDM, EV, PVLdecay, PVLdelta, PVLboth) and model type (DDM Only, RL Only, Hybrid). This focused view helps identify which models best recover decision process parameters.

```{r consistency-drift-parameters, results='asis'}
# Generate plots for Consistency/Drift parameters
consistency_plots <- plot_by_parameter_type("Consistency/Drift")
if (!is.null(consistency_plots)) {
  print(consistency_plots$correlation)
  print(consistency_plots$rmse)
}
```

These figures focus specifically on Consistency/Drift parameters (con, drift, drift_con). The correlation plot (top) shows how well these parameters are recovered in different model families and types, with higher bars indicating better recovery. The RMSE plot (bottom) shows the precision of parameter estimates, with lower bars indicating better precision. This focused view helps identify which models best recover parameters related to decision consistency and drift rates.

```{r valuation-parameters, results='asis'}
# Generate plots for Valuation parameters
valuation_plots <- plot_by_parameter_type("Valuation")
if (!is.null(valuation_plots)) {
  print(valuation_plots$correlation)
  print(valuation_plots$rmse)
}
```

These figures focus specifically on Valuation parameters (gain, loss, wgt_pun, wgt_rew). The correlation plot (top) shows how well these parameters are recovered in different model families and types, with higher bars indicating better recovery. The RMSE plot (bottom) shows the precision of parameter estimates, with lower bars indicating better precision. This focused view helps identify which models best recover parameters related to outcome valuation and reward/punishment sensitivity.

```{r learning-rate-parameters, results='asis'}
# Generate plots for Learning Rate parameters
learning_plots <- plot_by_parameter_type("Learning Rate")
if (!is.null(learning_plots)) {
  print(learning_plots$correlation)
  print(learning_plots$rmse)
}
```

These figures focus specifically on Learning Rate parameters (update, retend). The correlation plot (top) shows how well these parameters are recovered in different model families and types, with higher bars indicating better recovery. The RMSE plot (bottom) shows the precision of parameter estimates, with lower bars indicating better precision. This focused view helps identify which models best recover parameters related to learning and value updating.

# Best Performing Models by Parameter

```{r best-models}
# Create a summary visualization of best-performing models by parameter
param_summary <- params_df %>%
  group_by(parameter, param_type) %>%
  # For each parameter, find which model performs best
  summarize(
    best_corr_model = model_display[which.max(correlation)],
    best_corr_value = max(correlation),
    best_rmse_model = model_display[which.min(rmse)],
    best_rmse_value = min(rmse),
    .groups = "drop"
  )

# Plot best models by parameter (Correlation)
ggplot(param_summary, aes(x = parameter, y = best_corr_value, fill = best_corr_model)) +
  geom_col() +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  scale_fill_brewer(palette = "Set3") +
  scale_y_continuous(limits = c(0, 1)) +
  labs(
    title = "Best Performing Models by Parameter (Correlation)",
    y = "Maximum Correlation",
    x = "Parameter",
    fill = "Best Model"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.text = element_text(size = 11, face = "bold")
  )
```

This figure identifies the best-performing model for each parameter in terms of correlation. Each bar represents a different parameter, with the height showing the maximum correlation achieved by any model. The color indicates which specific model achieved this best performance. Parameters are grouped by type (DDM Process, Consistency/Drift, Learning Rate, Valuation). This visualization helps identify which models excel at recovering specific parameters.

```{r best-models-rmse}
# Plot best models by parameter (RMSE)
ggplot(param_summary, aes(x = parameter, y = best_rmse_value, fill = best_rmse_model)) +
  geom_col() +
  facet_wrap(~ param_type, scales = "free", ncol = 2) +
  scale_fill_brewer(palette = "Set3") +
  labs(
    title = "Best Performing Models by Parameter (RMSE)",
    y = "Minimum RMSE",
    x = "Parameter",
    fill = "Best Model"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.text = element_text(size = 11, face = "bold")
  )
```

This figure identifies the best-performing model for each parameter in terms of RMSE (precision). Each bar represents a different parameter, with the height showing the RMSE achieved by the best model (shorter bars indicate better precision). The color indicates which specific model achieved this best performance. Parameters are grouped by type. This visualization complements the correlation plot by showing which models recover parameters with the greatest precision.

# Model Performance Summary

```{r model-recommendation}
# Aggregate model performance across parameter types
model_recommendation <- params_df %>%
  group_by(model, model_display, model_type, param_type) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    mean_rmse = mean(rmse, na.rm = TRUE),
    parameter_count = n(),
    .groups = "drop"
  ) %>%
  group_by(model, model_display, model_type) %>%
  summarize(
    overall_correlation = mean(mean_correlation, na.rm = TRUE),
    overall_rmse = mean(mean_rmse, na.rm = TRUE),
    best_param_type = param_type[which.max(mean_correlation)],
    best_param_correlation = max(mean_correlation, na.rm = TRUE),
    worst_param_type = param_type[which.min(mean_correlation)],
    worst_param_correlation = min(mean_correlation, na.rm = TRUE),
    param_type_count = n(),
    .groups = "drop"
  ) %>%
  arrange(desc(overall_correlation))

# Display the recommendation table
kable(model_recommendation, digits = 3,
      col.names = c("Model", "Display Name", "Type", "Overall Correlation", "Overall RMSE", 
                     "Best Parameter Type", "Best Param Correlation", 
                     "Worst Parameter Type", "Worst Param Correlation", "# Param Types"),
      caption = "Model Recovery Performance Summary")
```

This table provides a comprehensive summary of parameter recovery performance for each model. It shows overall correlation and RMSE values, along with the best and worst recovered parameter types for each model. The "Best Parameter Type" column indicates which category of parameters the model recovers most reliably, while the "Worst Parameter Type" shows where improvements might be needed. Models are ordered by overall correlation, with better performing models at the top.

```{r overall-model-performance}
# Create a bar chart of overall model performance
ggplot(model_recommendation, 
       aes(x = reorder(model_display, overall_correlation), 
           y = overall_correlation, 
           fill = model_type)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.3f", overall_correlation)),
            position = position_stack(vjust = 0.5),
            color = "white") +
  coord_flip() +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  labs(title = "Overall Model Recovery Performance",
       subtitle = "Based on parameter recovery correlation",
       x = NULL,
       y = "Mean Correlation",
       fill = "Model Type")
```

This figure presents the overall parameter recovery performance for each model, ordered from highest to lowest correlation. The length of each bar represents the mean correlation across all parameters, with the actual value displayed inside the bar. Colors indicate model type (RL Only, DDM Only, Hybrid). This visualization provides a quick comparison of overall parameter recovery quality across all models.

```{r tradeoff-plot}
# Create a visualization that shows both correlation and RMSE
ggplot(model_recommendation, 
       aes(x = overall_correlation, y = 1/overall_rmse, 
           color = model_type, label = model_display)) +
  geom_point(size = 4, alpha = 0.7) +
  geom_text_repel(box.padding = 0.5, point.padding = 0.5) +
  scale_color_brewer(palette = "Set2") +
  theme_minimal() +
  labs(title = "Model Recovery Performance Tradeoff",
       subtitle = "Better models are in the upper-right (high correlation, low RMSE)",
       x = "Correlation (higher is better)",
       y = "1/RMSE (higher is better)",
       color = "Model Type")
```

This scatter plot reveals the tradeoff between correlation (x-axis) and precision (y-axis, shown as 1/RMSE so higher values are better). Each point represents a different model, with colors indicating model type. Models in the upper-right corner perform best, with both high correlation and high precision (low RMSE). This visualization helps identify models that achieve the best balance between these two important aspects of parameter recovery.

```{r parameter-type-by-model}
# Visualize parameter type performance by model
param_type_by_model <- params_df %>%
  group_by(model_display, param_type) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    .groups = "drop"
  )

ggplot(param_type_by_model, 
       aes(x = model_display, y = mean_correlation, fill = param_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_brewer(palette = "Set3") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Parameter Type Recovery by Model",
       x = "Model",
       y = "Mean Correlation",
       fill = "Parameter Type")
```

This figure shows how well each model recovers different types of parameters. Each group of bars represents a different model, with colors indicating parameter types (DDM Process, Consistency/Drift, Learning Rate, Valuation). The height of each bar shows the mean correlation for that parameter type. This visualization helps identify each model's strengths and weaknesses in recovering different parameter categories.