---
title: "Parameter Recovery Results"
author: "Felix Pichardo"
date: "2025-02-28"
output: 
  word_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(patchwork)
```

# Introduction

This document presents the parameter recovery analysis for several computational models of decision-making in the modified Iowa Gambling Task (mIGT). Parameter recovery evaluates how reliably a model's parameters can be estimated from data generated by that model. Good parameter recovery is essential for meaningful interpretation of model parameters in empirical applications.

## Models Evaluated

We evaluate several types of models:

1. **Reinforcement Learning (RL) Models**
   - Expected Value (EV)
   - Prospect Valence Learning with Delta rule (PVLdelta)
   - Prospect Valence Learning with Decay rule (PVLdecay)

2. **Sequential Sampling Model (SSM)**
   - Drift Diffusion Model (DDM)

3. **Hybrid Models (RL+SSM)**
   - EV+DDM
   - PVLdelta+DDM
   - PVLdecay+DDM

```{r load-data, include=FALSE}
# Function to read recovery data files
load_recovery_data <- function(file_path) {
  readRDS(file_path)
}

# Paths to data files
PROJ_DIR <- here::here()
REC_SIM_DIR <- file.path(PROJ_DIR, "Data", "sim", "recovery")

# List of files to process
recovery_files <- list.files(REC_SIM_DIR, pattern = "*.rds", full.names = TRUE)

# Load all recovery objects
recovery_data <- list()
for (file in recovery_files) {
  model_name <- basename(file) %>% 
    str_remove("recovery_igt_mod_batch_001_") %>%
    str_remove("_desc-sim_params.rds")
  
  recovery_data[[model_name]] <- load_recovery_data(file)
}
```

# Overall Recovery Performance

```{r overall-metrics, include=TRUE}
# Create a function to extract overall metrics
extract_overall <- function(recovery_obj, model_name) {
  overall <- recovery_obj$overall
  overall$model <- model_name
  return(overall)
}

# Combine all overall metrics
overall_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_overall(recovery_data[[name]], name)
  })
)

# Reorder rows for better comparison
model_order <- c("ddm", "ev", "pvldecay", "pvldelta", 
                "ev_ddm", "pvldecay_ddm", "pvldelta_ddm")

overall_df <- overall_df %>%
  mutate(model = factor(model, levels = model_order)) %>%
  arrange(model) %>%
  select(model, metric, value)

# Create a wider format for easier comparison
overall_wide <- overall_df %>%
  pivot_wider(names_from = metric, values_from = value) %>%
  rename(Model = model, Correlation = correlation, RMSE = rmse, 
         Bias = bias, `Relative Bias` = relative_bias)

# Add model type grouping
overall_wide <- overall_wide %>%
  mutate(Type = case_when(
    Model == "ddm" ~ "DDM Only",
    Model %in% c("ev", "pvldecay", "pvldelta") ~ "RL Only",
    TRUE ~ "Hybrid (RL+DDM)"
  )) %>%
  select(Type, everything())

# Display nice table
kable(overall_wide, digits = 3, caption = "Overall Recovery Performance Metrics")
```

**Table Explanation**: This table summarizes the overall parameter recovery performance for each model. Higher correlation values indicate better recovery of parameter relationships. Lower RMSE (Root Mean Square Error) values indicate more precise recovery. Bias measures indicate systematic errors in recovery, with values closer to zero being better. The models are grouped by type: DDM Only, RL Only, and Hybrid (RL+DDM).

# Parameter-Specific Recovery

For each model, we examine how well individual parameters are recovered. The tables below show recovery metrics for each parameter in the different models.

```{r parameter-extraction, include=FALSE}
# Extract parameter-specific data
extract_params <- function(recovery_obj, model_name) {
  params <- recovery_obj$by_parameter
  params$model <- model_name
  return(params)
}

# Combine all parameter data
params_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_params(recovery_data[[name]], name)
  })
)

# Add parameter type
params_df <- params_df %>%
  mutate(param_type = case_when(
    parameter %in% c("boundary", "tau", "beta") ~ "DDM Process",
    parameter %in% c("drift", "drift_con", "con") ~ "Consistency/Drift",
    parameter %in% c("wgt_pun", "wgt_rew", "gain", "loss") ~ "Valuation",
    parameter %in% c("update", "retend") ~ "Learning Rate",
    TRUE ~ "Other"
  ))

# Create grouped model type
params_df <- params_df %>%
  mutate(model_type = case_when(
    model == "ddm" ~ "DDM Only",
    model %in% c("ev", "pvldecay", "pvldelta") ~ "RL Only",
    TRUE ~ "Hybrid (RL+DDM)"
  ))

# Create more readable model names
params_df <- params_df %>%
  mutate(
    model_display = case_when(
      model == "ddm" ~ "DDM Only",
      model == "ev" ~ "EV Only",
      model == "pvldecay" ~ "PVLdecay Only",
      model == "pvldelta" ~ "PVLdelta Only",
      model == "ev_ddm" ~ "EV+DDM",
      model == "pvldecay_ddm" ~ "PVLdecay+DDM",
      model == "pvldelta_ddm" ~ "PVLdelta+DDM"
    ),
    # Create model family grouping
    model_family = case_when(
      model %in% c("ddm", "ev", "ev_ddm") ~ "EV Models",
      model %in% c("ddm", "pvldecay", "pvldecay_ddm") ~ "PVLdecay Models",
      model %in% c("ddm", "pvldelta", "pvldelta_ddm") ~ "PVLdelta Models"
    )
  )
```

## DDM Only Model

```{r ddm-table}
# Create parameter table for DDM
param_table_ddm <- recovery_data[["ddm"]]$by_parameter
kable(param_table_ddm, digits = 3, caption = "Parameter Recovery for DDM Only")
```

**Table Explanation**: This table shows the recovery metrics for parameters in the DDM Only model. The key parameters include boundary (decision threshold), tau (non-decision time), and others related to drift rates. Higher correlation and lower RMSE values indicate better parameter recovery.

## RL Models

### Expected Value (EV) Model

```{r ev-table}
param_table_ev <- recovery_data[["ev"]]$by_parameter
kable(param_table_ev, digits = 3, caption = "Parameter Recovery for EV Only")
```

**Table Explanation**: This table shows the recovery metrics for parameters in the Expected Value (EV) model. The parameters include learning rates and value sensitivity parameters. Higher correlation and lower RMSE values indicate better parameter recovery.

### PVLdecay Model

```{r pvldecay-table}
param_table_pvldecay <- recovery_data[["pvldecay"]]$by_parameter
kable(param_table_pvldecay, digits = 3, caption = "Parameter Recovery for PVLdecay Only")
```

**Table Explanation**: This table shows the recovery metrics for parameters in the PVLdecay model. The parameters include valuation parameters (gain, loss) and the learning rate parameter. Higher correlation and lower RMSE values indicate better parameter recovery.

### PVLdelta Model

```{r pvldelta-table}
param_table_pvldelta <- recovery_data[["pvldelta"]]$by_parameter
kable(param_table_pvldelta, digits = 3, caption = "Parameter Recovery for PVLdelta Only")
```

**Table Explanation**: This table shows the recovery metrics for parameters in the PVLdelta model. The parameters include valuation parameters (gain, loss) and the learning rate parameter. Higher correlation and lower RMSE values indicate better parameter recovery.

## Hybrid Models (RL+DDM)

### EV+DDM Model

```{r ev-ddm-table}
param_table_ev_ddm <- recovery_data[["ev_ddm"]]$by_parameter
kable(param_table_ev_ddm, digits = 3, caption = "Parameter Recovery for EV+DDM")
```

**Table Explanation**: This table shows the recovery metrics for parameters in the hybrid EV+DDM model. The parameters include both RL components (learning rates, value sensitivity) and DDM components (boundary, non-decision time). Higher correlation and lower RMSE values indicate better parameter recovery.

### PVLdecay+DDM Model

```{r pvldecay-ddm-table}
param_table_pvldecay_ddm <- recovery_data[["pvldecay_ddm"]]$by_parameter
kable(param_table_pvldecay_ddm, digits = 3, caption = "Parameter Recovery for PVLdecay+DDM")
```

**Table Explanation**: This table shows the recovery metrics for parameters in the hybrid PVLdecay+DDM model. The parameters include both RL components (valuation, learning) and DDM components (boundary, non-decision time). Higher correlation and lower RMSE values indicate better parameter recovery.

### PVLdelta+DDM Model

```{r pvldelta-ddm-table}
param_table_pvldelta_ddm <- recovery_data[["pvldelta_ddm"]]$by_parameter
kable(param_table_pvldelta_ddm, digits = 3, caption = "Parameter Recovery for PVLdelta+DDM")
```

**Table Explanation**: This table shows the recovery metrics for parameters in the hybrid PVLdelta+DDM model. The parameters include both RL components (valuation, learning) and DDM components (boundary, non-decision time). Higher correlation and lower RMSE values indicate better parameter recovery.

# Correlation Comparison by Parameter Type

```{r correlation-comparison}
# Plot correlation by parameter type
ggplot(params_df, aes(x = parameter, y = correlation, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ param_type, scales = "free_x") +
  theme_minimal() +
  labs(title = "Parameter Recovery (Correlation) by Parameter Type",
       y = "Correlation",
       x = "Parameter",
       fill = "Model Type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure shows the correlation values for parameter recovery, grouped by parameter type. Parameters are categorized into DDM Process, Consistency/Drift, Valuation, and Learning Rate types. Different colors represent different model types (DDM Only, RL Only, Hybrid). Higher bars indicate better recovery of parameter relationships.

# RMSE Comparison by Parameter Type

```{r rmse-comparison}
# Plot RMSE by parameter type
ggplot(params_df, aes(x = parameter, y = rmse, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ param_type, scales = "free_x") +
  theme_minimal() +
  labs(title = "Parameter Recovery (RMSE) by Parameter Type",
       y = "RMSE",
       x = "Parameter",
       fill = "Model Type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure shows the RMSE values for parameter recovery, grouped by parameter type. Lower bars indicate more precise parameter estimates. The parameters are categorized into DDM Process, Consistency/Drift, Valuation, and Learning Rate types, with different colors representing different model types.

# Model Family Comparisons

The following visualizations compare parameter recovery within model families to examine how adding components affects recovery.

## EV Model Family (Correlation)

```{r ev-correlation}
# Define custom color palettes - distinct for each model family
model_colors <- c(
  "DDM Only" = "#4575b4",
  "EV Only" = "#74add1", 
  "PVLdecay Only" = "#74add1",
  "PVLdelta Only" = "#74add1",
  "EV+DDM" = "#f46d43",
  "PVLdecay+DDM" = "#f46d43", 
  "PVLdelta+DDM" = "#f46d43"
)

# Filter for EV family models
ev_data <- params_df %>% filter(model %in% c("ddm", "ev", "ev_ddm"))

# Plot correlation for EV family
ggplot(ev_data, aes(x = parameter, y = correlation, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  scale_fill_manual(values = model_colors) +
  scale_y_continuous(limits = c(0, 1)) +
  labs(title = "Parameter Recovery (Correlation) for EV Model Family",
       y = "Correlation (higher is better)",
       x = "Parameter",
       fill = "Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure compares the correlation values for parameter recovery within the EV model family (DDM Only, EV Only, and EV+DDM). Parameters are grouped by type, and higher bars indicate better recovery of parameter relationships. This visualization helps us understand how combining models affects parameter recovery.

## PVLdecay Model Family (Correlation)

```{r pvldecay-correlation}
# Filter for PVLdecay family models
pvldecay_data <- params_df %>% filter(model %in% c("ddm", "pvldecay", "pvldecay_ddm"))

# Plot correlation for PVLdecay family
ggplot(pvldecay_data, aes(x = parameter, y = correlation, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  scale_fill_manual(values = model_colors) +
  scale_y_continuous(limits = c(0, 1)) +
  labs(title = "Parameter Recovery (Correlation) for PVLdecay Model Family",
       y = "Correlation (higher is better)",
       x = "Parameter",
       fill = "Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure compares the correlation values for parameter recovery within the PVLdecay model family (DDM Only, PVLdecay Only, and PVLdecay+DDM). Parameters are grouped by type, and higher bars indicate better recovery of parameter relationships. This helps us understand how combining PVLdecay with DDM affects parameter recovery.

## PVLdelta Model Family (Correlation)

```{r pvldelta-correlation}
# Filter for PVLdelta family models
pvldelta_data <- params_df %>% filter(model %in% c("ddm", "pvldelta", "pvldelta_ddm"))

# Plot correlation for PVLdelta family
ggplot(pvldelta_data, aes(x = parameter, y = correlation, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  scale_fill_manual(values = model_colors) +
  scale_y_continuous(limits = c(0, 1)) +
  labs(title = "Parameter Recovery (Correlation) for PVLdelta Model Family",
       y = "Correlation (higher is better)",
       x = "Parameter",
       fill = "Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure compares the correlation values for parameter recovery within the PVLdelta model family (DDM Only, PVLdelta Only, and PVLdelta+DDM). Parameters are grouped by type, and higher bars indicate better recovery of parameter relationships. This helps us understand how combining PVLdelta with DDM affects parameter recovery.

## EV Model Family (RMSE)

```{r ev-rmse}
# Plot RMSE for EV family
ggplot(ev_data, aes(x = parameter, y = rmse, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  scale_fill_manual(values = model_colors) +
  labs(title = "Parameter Recovery (RMSE) for EV Model Family",
       y = "RMSE (lower is better)",
       x = "Parameter",
       fill = "Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure compares the RMSE values for parameter recovery within the EV model family. Lower bars indicate more precise parameter recovery. This visualization helps us understand how the precision of parameter estimates changes when combining EV with DDM.

## PVLdecay Model Family (RMSE)

```{r pvldecay-rmse}
# Plot RMSE for PVLdecay family
ggplot(pvldecay_data, aes(x = parameter, y = rmse, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  scale_fill_manual(values = model_colors) +
  labs(title = "Parameter Recovery (RMSE) for PVLdecay Model Family",
       y = "RMSE (lower is better)",
       x = "Parameter",
       fill = "Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure compares the RMSE values for parameter recovery within the PVLdecay model family. Lower bars indicate more precise parameter recovery. This visualization helps us understand how the precision of parameter estimates changes when combining PVLdecay with DDM.

## PVLdelta Model Family (RMSE)

```{r pvldelta-rmse}
# Plot RMSE for PVLdelta family
ggplot(pvldelta_data, aes(x = parameter, y = rmse, fill = model_display)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  scale_fill_manual(values = model_colors) +
  labs(title = "Parameter Recovery (RMSE) for PVLdelta Model Family",
       y = "RMSE (lower is better)",
       x = "Parameter",
       fill = "Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure compares the RMSE values for parameter recovery within the PVLdelta model family. Lower bars indicate more precise parameter recovery. This visualization helps us understand how the precision of parameter estimates changes when combining PVLdelta with DDM.

# Parameter Type Analysis

The following visualizations examine parameter recovery by focusing on specific parameter types across models.

## DDM Process Parameters

```{r ddm-process-correlation}
# Filter data for DDM Process parameters
ddm_process_data <- params_df %>% filter(param_type == "DDM Process")

# Create a cleaner model family grouping for side-by-side plots
ddm_process_data <- ddm_process_data %>%
  mutate(
    model_group = case_when(
      model == "ddm" ~ "DDM Only",
      model %in% c("ev", "pvldecay", "pvldelta") ~ "RL Only",
      TRUE ~ "Hybrid (RL+DDM)"
    ),
    model_specific = case_when(
      model == "ev" | model == "ev_ddm" ~ "EV",
      model == "pvldecay" | model == "pvldecay_ddm" ~ "PVLdecay",
      model == "pvldelta" | model == "pvldelta_ddm" ~ "PVLdelta",
      TRUE ~ "DDM"
    )
  )

# Plot correlation for DDM Process parameters
ggplot(ddm_process_data, aes(x = model_specific, y = correlation, fill = model_group)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ parameter, scales = "free_x", ncol = 3) +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(limits = c(0, 1)) +
  labs(title = "Parameter Recovery (Correlation) for DDM Process Parameters",
       y = "Correlation (higher is better)",
       x = "Model Family",
       fill = "Model Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure focuses on DDM Process parameters (boundary, tau, beta) and compares their correlation values across different model families. The bars are grouped by parameter and colored by model type. Higher bars indicate better recovery of parameter relationships.

```{r ddm-process-rmse}
# Plot RMSE for DDM Process parameters
ggplot(ddm_process_data, aes(x = model_specific, y = rmse, fill = model_group)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ parameter, scales = "free_y", ncol = 3) +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Parameter Recovery (RMSE) for DDM Process Parameters",
       y = "RMSE (lower is better)",
       x = "Model Family",
       fill = "Model Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure shows the RMSE values for DDM Process parameters across different model families. Lower bars indicate more precise parameter recovery. This visualization helps us understand which models provide the most precise estimates for decision process parameters.

## Valuation Parameters

```{r valuation-correlation}
# Filter data for Valuation parameters
valuation_data <- params_df %>% filter(param_type == "Valuation")

# Create a cleaner model family grouping for side-by-side plots
valuation_data <- valuation_data %>%
  mutate(
    model_group = case_when(
      model == "ddm" ~ "DDM Only",
      model %in% c("ev", "pvldecay", "pvldelta") ~ "RL Only",
      TRUE ~ "Hybrid (RL+DDM)"
    ),
    model_specific = case_when(
      model == "ev" | model == "ev_ddm" ~ "EV",
      model == "pvldecay" | model == "pvldecay_ddm" ~ "PVLdecay",
      model == "pvldelta" | model == "pvldelta_ddm" ~ "PVLdelta",
      TRUE ~ "DDM"
    )
  )

# Plot correlation for Valuation parameters
ggplot(valuation_data, aes(x = model_specific, y = correlation, fill = model_group)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ parameter, scales = "free_x", ncol = 3) +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(limits = c(0, 1)) +
  labs(title = "Parameter Recovery (Correlation) for Valuation Parameters",
       y = "Correlation (higher is better)",
       x = "Model Family",
       fill = "Model Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure focuses on Valuation parameters (gain, loss, weights) and compares their correlation values across different model families. The bars are grouped by parameter and colored by model type. Higher bars indicate better recovery of parameter relationships.

```{r valuation-rmse}
# Plot RMSE for Valuation parameters
ggplot(valuation_data, aes(x = model_specific, y = rmse, fill = model_group)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ parameter, scales = "free_y", ncol = 3) +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Parameter Recovery (RMSE) for Valuation Parameters",
       y = "RMSE (lower is better)",
       x = "Model Family",
       fill = "Model Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

**Figure Explanation**: This figure shows the RMSE values for Valuation parameters across different model families. Lower bars indicate more precise parameter recovery. This visualization helps us understand which models provide the most precise estimates for valuation parameters.

# Best Performing Models by Parameter

```{r best-models}
# Create summary dataset
param_summary <- params_df %>%
  group_by(parameter, param_type) %>%
  # For each parameter, find which model performs best
  summarize(
    best_corr_model = model_display[which.max(correlation)],
    best_corr_value = max(correlation),
    best_rmse_model = model_display[which.min(rmse)],
    best_rmse_value = min(rmse),
    .groups = "drop"
  )

# Plot best models by parameter
ggplot(param_summary, aes(x = parameter, y = best_corr_value, fill = best_corr_model)) +
  geom_col() +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  scale_fill_brewer(palette = "Set3") +
  scale_y_continuous(limits = c(0, 1)) +
  labs(
    title = "Best Performing Models by Parameter (Correlation)",
    y = "Maximum Correlation",
    x = "Parameter",
    fill = "Best Model"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.text = element_text(size = 11, face = "bold")
  )
```

**Figure Explanation**: This figure identifies the best-performing model for each parameter based on correlation values. For each parameter, the bar shows the maximum correlation achieved, and the color indicates which model achieved it. This provides a quick overview of which models excel at recovering specific parameters, organized by parameter type.