---
title: "Recovery Results"
author: "Felix Pichardo"
date: "2025-02-28"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(ggrepel)  # For label repulsion in plots
```

# Model Configuration

First, we define the model configuration to make this analysis more extensible:

```{r model-config}
# Enhanced Model Configuration
model_config <- list(
  # Define model families (the core algorithms)
  families = list(
    ev = list(
      display_name = "Expected Value",
      models = c("ev", "ev_ddm")
    ),
    pvl = list(
      display_name = "Prospect Valence Learning",
      # Group all PVL variants
      variants = list(
        delta = list(
          display_name = "PVLdelta",
          models = c("pvldelta", "pvldelta_ddm")
        ),
        decay = list(
          display_name = "PVLdecay",
          models = c("pvldecay", "pvldecay_ddm") 
        ),
        both = list(
          display_name = "PVLboth",
          models = c("pvlboth", "pvlboth_ddm")
        ),
        bothsd = list(
          display_name = "PVLbothsd",
          models = c("pvlbothsd", "pvlbothsd_ddm")
        ),
        puldelta = list(
          display_name = "PULdelta",
          models = c("puldelta", "puldelta_ddm")
        ),
        puldecay = list(
          display_name = "PULdecay",
          models = c("puldecay", "puldecay_ddm")
        ),
        pulboth = list(
          display_name = "PULboth",
          models = c("pulboth", "pulboth_ddm")
        ),
        pvsdelta = list(
          display_name = "PVSdelta",
          models = c("pvsdelta", "pvsdelta_ddm")
        ),
        pvsdecay = list(
          display_name = "PVSdecay",
          models = c("pvsdecay", "pvsdecay_ddm")
        ),
        pvsboth = list(
          display_name = "PVSboth",
          models = c("pvsboth", "pvsboth_ddm")
        )
      )
    ),
    vpp = list(
      display_name = "Value-Plus-Perseverance",
      # Group all VPP variants
      variants = list(
        delta = list(
          display_name = "VPPdeltag",
          models = c("vppdeltag", "vppdeltag_ddm")
        ),
        decay = list(
          display_name = "VPPdecayg",
          models = c("vppdecayg", "vppdecayg_ddm") 
        ),
        both = list(
          display_name = "VPPbothg",
          models = c("vppbothg", "vppbothg_ddm")
        ),
        delta = list(
          display_name = "VPPdeltagd",
          models = c("vppdeltagd", "vppdeltagd_ddm")
        ),
        decay = list(
          display_name = "VPPdecaygd",
          models = c("vppdecaygd", "vppdecaygd_ddm") 
        ),
        both = list(
          display_name = "VPPbothgd",
          models = c("vppbothgd", "vppbothgd_ddm")
        ),
        puldelta = list(
          display_name = "PULVPPdeltag",
          models = c("pulvppdeltag", "pulvppdeltag_ddm")
        ),
        puldecay = list(
          display_name = "PULVPPdecayg",
          models = c("pulvppdecayg", "pulvppdecayg_ddm")
        ),
        pulboth = list(
          display_name = "PULVPPbothg",
          models = c("pulvppbothg", "pulvppbothg_ddm")
        ),
        pvsdelta = list(
          display_name = "PVSVPPdeltag",
          models = c("pvsvppdeltag", "pvsvppdeltag_ddm")
        ),
        pvsdecay = list(
          display_name = "PVSVPPdecayg",
          models = c("pvsvppdecayg", "pvsvppdecayg_ddm")
        ),
        pvsboth = list(
          display_name = "PVSVPPbothg",
          models = c("pvsvppbothg", "pvsvppbothg_ddm")
        )
      )
    ),
    ddm = list(
      display_name = "DDM Only",
      models = c("ddm")
    )
  ),
  
  # Define model types (for categorization)
  types = list(
    rl_only = "Reinforcement Learning", 
    ddm_only = "Sequential Sampling",
    hybrid = "Hybrid (RL+DDM)"
  ),
  
  # Define parameter groups
  parameter_groups = list(
    "DDM Process" = c("boundary", "tau", "beta"),
    "Consistency/Drift" = c("drift", "drift_con", "con"),
    "Valuation" = c("wgt_pun", "wgt_rew", "gain", "loss", "gain_shape", "loss_shape"),
    "Learning Rate" = c("update", "retend", "decay"),
    "Perseveration" = c("k", "w", "ep"),
    "Other" = c("mag")
  )
)

# Build derived model lists automatically
build_model_lists <- function(config) {
  # Initialize lists
  all_models <- character()
  display_names <- list()
  rl_only_models <- character()
  ddm_only_models <- character()
  hybrid_models <- character()
  all_model_families <- list()
  
  # Process all model families
  for (family_name in names(config$families)) {
    family <- config$families[[family_name]]
    
    # Handle families with variants
    if ("variants" %in% names(family)) {
      for (variant_name in names(family$variants)) {
        variant <- family$variants[[variant_name]]
        
        # Process each model in the variant
        for (model in variant$models) {
          # Create display name
          display_name <- paste(variant$display_name, ifelse(grepl("_ddm$", model), "+DDM", "Only"))
          display_names[[model]] <- display_name
          
          # Determine model type and store in appropriate list
          if (grepl("_ddm$", model)) {
            hybrid_models <- c(hybrid_models, model)
          } else if (model == "ddm") {
            ddm_only_models <- c(ddm_only_models, model)
          } else {
            rl_only_models <- c(rl_only_models, model)
          }
          
          # Add to all models list
          all_models <- c(all_models, model)
          
          # Add to model families - group by base algorithm
          base_family <- ifelse(family_name == "ddm", "ddm", 
                                paste0(family_name, variant_name))
          
          if (is.null(all_model_families[[base_family]])) {
            all_model_families[[base_family]] <- character()
          }
          all_model_families[[base_family]] <- c(all_model_families[[base_family]], model)
        }
      }
    } else {
      # Simple family without variants (like EV or DDM)
      for (model in family$models) {
        # Create display name
        display_name <- paste(family$display_name, ifelse(grepl("_ddm$", model), "+DDM", ""))
        display_names[[model]] <- display_name
        
        # Determine model type and store in appropriate list
        if (grepl("_ddm$", model)) {
          hybrid_models <- c(hybrid_models, model)
        } else if (model == "ddm") {
          ddm_only_models <- c(ddm_only_models, model)
        } else {
          rl_only_models <- c(rl_only_models, model)
        }
        
        # Add to all models list
        all_models <- c(all_models, model)
        
        # Add to model families
        base_family <- ifelse(family_name == "ddm", "ddm", family_name)
        if (is.null(all_model_families[[base_family]])) {
          all_model_families[[base_family]] <- character()
        }
        all_model_families[[base_family]] <- c(all_model_families[[base_family]], model)
      }
    }
  }
  
  # Return all derived lists
  return(list(
    all_models = unique(all_models),
    rl_only_models = unique(rl_only_models),
    ddm_only_models = unique(ddm_only_models),
    hybrid_models = unique(hybrid_models),
    model_display_names = display_names,
    model_families = all_model_families
  ))
}

# Generate all the model lists from configuration
derived_lists <- build_model_lists(model_config)
all_models <- derived_lists$all_models
rl_only_models <- derived_lists$rl_only_models
ddm_only_models <- derived_lists$ddm_only_models
hybrid_models <- derived_lists$hybrid_models
model_display_names <- derived_lists$model_display_names
model_families <- derived_lists$model_families

# Print model lists for verification
cat("All models:", length(all_models), "\n")
cat("RL-only models:", length(rl_only_models), "\n")
cat("DDM-only models:", length(ddm_only_models), "\n")
cat("Hybrid models:", length(hybrid_models), "\n")
cat("Model families:", length(model_families), "\n")
```

```{r data-loading}
# Function to load recovery data with error handling
load_recovery_data <- function(model_name, base_dir = NULL) {
  if (is.null(base_dir)) {
    PROJ_DIR <- here::here()
    base_dir <- file.path(PROJ_DIR, "Data", "sim", "recovery")
  }
  
  file_path <- file.path(base_dir, paste0("recovery_igt_mod_batch_001_", model_name, "_desc-sim_params.rds"))
  
  if (file.exists(file_path)) {
    return(readRDS(file_path))
  } else {
    warning(paste("Recovery file not found for model:", model_name))
    return(NULL)
  }
}

# Paths to data files
task = "igt_mod"
PROJ_DIR <- here::here()
REC_SIM_DIR <- file.path(PROJ_DIR, "Data", "sim", "recovery")
#REC_SIM_DIR <- file.path(PROJ_DIR, "Data", task, "sim", "recovery")

# Automatically discover available models in the directory
available_files <- list.files(REC_SIM_DIR, pattern = "recovery_igt_mod_batch_001_(.*)_desc-sim_params.rds", full.names = FALSE)
available_models <- available_files %>% 
  str_remove("recovery_igt_mod_batch_001_") %>%
  str_remove("_desc-sim_params.rds")

# Load data for all configured models that are available
recovery_data <- list()
for (model_name in all_models) {
  if (model_name %in% available_models) {
    recovery_data[[model_name]] <- load_recovery_data(model_name, REC_SIM_DIR)
  }
}

# Update model lists based on what's actually available
available_all_models <- names(recovery_data)
available_rl_models <- intersect(rl_only_models, available_all_models)
available_ddm_models <- intersect(ddm_only_models, available_all_models)
available_hybrid_models <- intersect(hybrid_models, available_all_models)

# Print availability stats
cat("Available models:", length(available_all_models), "out of", length(all_models), "\n")
```

# Overall Recovery Performance

```{r overall-performance}
# Create a function to extract overall metrics with error handling
extract_overall <- function(recovery_obj, model_name) {
  if (is.null(recovery_obj)) {
    return(NULL)
  }
  
  overall <- recovery_obj$overall
  overall$model <- model_name
  overall$model_display <- model_display_names[model_name]
  
  # Add model type classification
  overall$model_type <- case_when(
    model_name %in% rl_only_models ~ "RL Only",
    model_name %in% ddm_only_models ~ "DDM Only",
    model_name %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Unknown"
  )
  
  return(overall)
}

# Combine all overall metrics
overall_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_overall(recovery_data[[name]], name)
  })
)

# Create a wider format for easier comparison
overall_wide <- overall_df %>%
  pivot_wider(names_from = metric, values_from = value) %>%
  select(model, model_display, model_type, correlation, rmse, bias, relative_bias) %>%
  arrange(model_type, model)

# Display nice table
kable(overall_wide, digits = 3, 
      col.names = c("Model", "Display Name", "Type", "Correlation", "RMSE", "Bias", "Relative Bias"),
      caption = "Overall Recovery Performance Metrics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Function to visualize overall performance - Fixed to avoid reorder issues
plot_overall_performance <- function(data, metric = "correlation") {
  # Define plot labels based on metric
  y_label <- case_when(
    metric == "correlation" ~ "Parameter Recovery Correlation (higher is better)",
    metric == "rmse" ~ "Parameter Recovery RMSE (lower is better)",
    metric == "relative_bias" ~ "Parameter Relative Bias (closer to 0 is better)",
    TRUE ~ metric
  )
  
  # Set up color direction based on metric (higher better for correlation, lower better for others)
  color_direction <- if(metric == "correlation") "high" else "low"
  midpoint <- if(metric == "correlation") 0.7 else 0.3
  limits <- if(metric == "correlation") c(0, 1) else NULL
  
  # Pre-sort the data by the metric value
  if (metric == "correlation") {
    sorted_data <- data %>% 
      arrange(model_type, desc(!!sym(metric))) %>%
      mutate(model_display = factor(model_display, levels = unique(model_display)))
  } else {
    sorted_data <- data %>% 
      arrange(model_type, !!sym(metric)) %>%
      mutate(model_display = factor(model_display, levels = unique(model_display)))
  }
  
  # Create plot without using reorder()
  ggplot(sorted_data, aes(x = model_display, y = !!sym(metric), fill = !!sym(metric))) +
    geom_bar(stat = "identity") +
    scale_fill_gradient2(
      low = if(color_direction == "low") "green" else "red", 
      mid = "yellow", 
      high = if(color_direction == "low") "red" else "green",
      midpoint = midpoint,
      limits = limits
    ) +
    coord_flip() +
    facet_wrap(~ model_type, scales = "free_y") +
    theme_minimal() +
    labs(
      title = paste("Model Recovery Performance -", toupper(metric)),
      x = NULL,
      y = y_label,
      fill = metric
    )
}

# Create overall performance visualizations
plot_overall_performance(overall_wide, "correlation")
plot_overall_performance(overall_wide, "rmse")
```

# Parameter-Specific Recovery

```{r parameter-functions}
# Function to extract parameter-specific data with error handling
extract_params <- function(recovery_obj, model_name) {
  if (is.null(recovery_obj) || !("by_parameter" %in% names(recovery_obj))) {
    return(NULL)
  }
  
  params <- recovery_obj$by_parameter
  params$model <- model_name
  params$model_display <- as.character(model_display_names[model_name])  # Convert to character
  
  # Add model type classification
  params$model_type <- case_when(
    model_name %in% rl_only_models ~ "RL Only",
    model_name %in% ddm_only_models ~ "DDM Only",
    model_name %in% hybrid_models ~ "Hybrid (RL+DDM)",
    TRUE ~ "Unknown"
  )
  
  # Add parameter type based on config
  params$param_type <- NA_character_
  for (type_name in names(model_config$parameter_groups)) {
    type_params <- model_config$parameter_groups[[type_name]]
    params$param_type[params$parameter %in% type_params] <- type_name
  }
  params$param_type[is.na(params$param_type)] <- "Other"
  
  # Extract family and variant information
  for (family_name in names(model_config$families)) {
    family <- model_config$families[[family_name]]
    
    # Check if this model belongs to this family
    if ("variants" %in% names(family)) {
      # Check each variant in this family
      for (variant_name in names(family$variants)) {
        variant <- family$variants[[variant_name]]
        if (model_name %in% variant$models) {
          params$family_name <- family_name
          params$variant_name <- variant_name
          break
        }
      }
    } else {
      # Simple family without variants
      if (model_name %in% family$models) {
        params$family_name <- family_name
        params$variant_name <- NA
      }
    }
  }
  
  return(params)
}

# Function to create parameter tables for a specific model
create_param_table <- function(model_name) {
  if (!model_name %in% names(recovery_data) || is.null(recovery_data[[model_name]])) {
    return(NULL)
  }
  
  param_df <- recovery_data[[model_name]]$by_parameter

  kable(param_df, digits = 3, 
        caption = paste("Parameter Recovery for", model_display_names[model_name])) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                  full_width = FALSE)
}

# Improved function to display parameter tables by model type
display_model_tables <- function(model_type) {
  if (model_type == "ddm_only") {
    model_list <- available_ddm_models
  } else if (model_type == "rl_only") {
    model_list <- available_rl_models
  } else if (model_type == "hybrid") {
    model_list <- available_hybrid_models
  } else {
    model_list <- character(0)
  }
  
  if (length(model_list) == 0) {
    return("No models available for this type.")
  }
  
  # Process each model sequentially for proper HTML output
  for (model_name in model_list) {
    cat(paste0("\n### Model: ", model_display_names[model_name], "\n\n"))
    
    if (!model_name %in% names(recovery_data) || is.null(recovery_data[[model_name]])) {
      cat(paste("Model", model_name, "data not available.\n\n"))
    } else {
      param_df <- recovery_data[[model_name]]$by_parameter
      print(
        kable(param_df, digits = 3, 
              caption = paste("Parameter Recovery for", model_display_names[model_name])) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                      full_width = FALSE)
      )
      cat("\n\n") # Add some spacing between tables
    }
  }
}
```

## DDM Only Models
```{r, results='asis'}
display_model_tables("ddm_only")
```

## RL Models
```{r, results='asis'}
display_model_tables("rl_only")
```

## Hybrid Models (RL+DDM)
```{r, results='asis'}
display_model_tables("hybrid")
```

# Cross-Model Parameter Recovery Analysis

Now let's analyze parameter recovery performance across different models and model types:

```{r cross-model-analysis}
# Combine all parameter data
params_df <- bind_rows(
  lapply(names(recovery_data), function(name) {
    extract_params(recovery_data[[name]], name)
  })
)

# Create a comparison of correlation by parameter type and model type
correlation_by_param_type <- params_df %>%
  group_by(model_type, param_type) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    mean_rmse = mean(rmse, na.rm = TRUE),
    parameter_count = n(),
    .groups = "drop"
  ) %>%
  arrange(param_type, desc(mean_correlation))

# Display the summary table
kable(correlation_by_param_type, digits = 3,
      col.names = c("Model Type", "Parameter Type", "Mean Correlation", "Mean RMSE", "# Parameters"),
      caption = "Parameter Recovery by Model Type and Parameter Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Visualize the comparison
ggplot(correlation_by_param_type, 
       aes(x = param_type, y = mean_correlation, fill = model_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = sprintf("%.3f", mean_correlation)),
            position = position_dodge(width = 0.9),
            vjust = -0.3, size = 3) +
  scale_y_continuous(limits = c(0, max(correlation_by_param_type$mean_correlation) * 1.2)) +
  scale_fill_brewer(palette = "Set2") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Parameter Recovery by Type",
       x = "Parameter Type",
       y = "Mean Correlation",
       fill = "Model Type")

# Create better visualization functions
plot_parameter_recovery <- function(data, metric = "correlation", facet_var = "param_type") {
  # Define y-axis label based on metric
  y_label <- if(metric == "correlation") {
    "Correlation (higher is better)"
  } else {
    "RMSE (lower is better)"
  }
  
  # Set plot limits and direction based on metric
  y_limits <- if(metric == "correlation") {
    c(0, 1)
  } else {
    c(0, max(data[[metric]], na.rm = TRUE) * 1.1)
  }
  
  # Choose color palette based on model_type or other variable
  if (length(unique(data$model_type)) > 1) {
    fill_var <- "model_type"
    fill_scale <- scale_fill_brewer(palette = "Set2")
  } else {
    fill_var <- "model_display"
    fill_scale <- scale_fill_viridis_d()
  }
  
  # Create the plot with improved aesthetics
  p <- ggplot(data, aes(x = parameter, y = .data[[metric]], fill = .data[[fill_var]])) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    facet_wrap(as.formula(paste("~", facet_var)), scales = "free_x", ncol = 2) +
    fill_scale +
    scale_y_continuous(limits = y_limits) +
    labs(
      title = paste("Parameter Recovery (", toupper(metric), ")"),
      y = y_label,
      x = "Parameter",
      fill = if(fill_var == "model_type") "Model Type" else "Model"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      strip.text = element_text(size = 11, face = "bold")
    )
  
  return(p)
}

# Plot correlation by parameter and model type
plot_parameter_recovery(params_df, "correlation", "param_type")

# Plot RMSE by parameter and model type
plot_parameter_recovery(params_df, "rmse", "param_type")
```

# Parameter Recovery by Model Family

Let's examine how parameters are recovered in each model family:

```{r model-family-analysis}
# Add a more informative family label for grouping
params_df <- params_df %>%
  mutate(
    model_family_label = case_when(
      grepl("^ev", model) ~ "EV",
      grepl("^pvldelta", model) ~ "PVLdelta",
      grepl("^puldelta", model) ~ "PULdelta",
      grepl("^pvldecay", model) ~ "PVLdecay",
      grepl("^pvlboth$|^pvlboth_", model) ~ "PVLboth",
      grepl("^pvlbothsd", model) ~ "PVLbothsd",
      grepl("^vppdelta", model) ~ "VPPdelta",
      grepl("^vppdecay", model) ~ "VPPdecay",
      grepl("^vppboth$|^vppboth_", model) ~ "VPPboth",
      model == "ddm" ~ "DDM",
      TRUE ~ "Other"
    ),
    is_hybrid = grepl("_ddm$", model)
  )

# Group parameters by model family and type
family_parameter_performance <- params_df %>%
  group_by(model_family_label, is_hybrid, param_type, parameter) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    mean_rmse = mean(rmse, na.rm = TRUE),
    model_count = n(),
    .groups = "drop"
  )

# Plot performance by model family and parameter type
ggplot(family_parameter_performance, 
       aes(x = parameter, y = mean_correlation, 
           fill = interaction(model_family_label, is_hybrid))) +
  geom_col(position = position_dodge(width = 0.8)) +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  scale_fill_brewer(palette = "Paired") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    strip.text = element_text(size = 11, face = "bold")
  ) +
  labs(
    title = "Parameter Recovery by Model Family and Parameter Type",
    y = "Mean Correlation",
    x = "Parameter",
    fill = "Model Family"
  )

# Create a focused comparison within each model family that has both RL-only and hybrid versions
# First, identify families with both versions
family_has_both <- family_parameter_performance %>%
  group_by(model_family_label) %>%
  summarize(
    has_rl_only = any(!is_hybrid),
    has_hybrid = any(is_hybrid),
    has_both = has_rl_only & has_hybrid,
    .groups = "drop"
  ) %>%
  filter(has_both) %>%
  pull(model_family_label)

# Plot comparison within families that have both versions
if (length(family_has_both) > 0) {
  family_parameter_performance %>%
    filter(model_family_label %in% family_has_both) %>%
    ggplot(aes(x = parameter, y = mean_correlation, fill = is_hybrid)) +
    geom_col(position = position_dodge(width = 0.8)) +
    facet_grid(param_type ~ model_family_label, scales = "free_x") +
    scale_fill_manual(
      values = c("FALSE" = "#1B9E77", "TRUE" = "#D95F02"),
      labels = c("FALSE" = "RL-Only", "TRUE" = "Hybrid (RL+DDM)"),
      name = "Model Type"
    ) +
    scale_y_continuous(limits = c(0, 1)) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "bottom",
      strip.text = element_text(size = 9, face = "bold")
    ) +
    labs(
      title = "RL-Only vs. Hybrid: Parameter Recovery Within Model Families",
      y = "Mean Correlation",
      x = "Parameter"
    )
}
```

# Parameter-Focused Analysis

Let's examine how each parameter is recovered across different models:

```{r parameter-focused}
# Function to create parameter-focused plots
plot_by_parameter_type <- function(param_type_focus) {
  # Filter data for this parameter type
  param_data <- params_df %>% 
    filter(param_type == param_type_focus)
  
  # If no data, return NULL
  if (nrow(param_data) == 0) {
    return(NULL)
  }
  
  # Plot correlation
  p_corr <- ggplot(param_data, aes(x = model_family_label, y = correlation, fill = model_type)) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    facet_wrap(~ parameter, scales = "free_x", ncol = 3) +
    scale_fill_brewer(palette = "Set2") +
    scale_y_continuous(limits = c(0, 1)) +
    labs(
      title = paste("Parameter Recovery (Correlation) for", param_type_focus, "Parameters"),
      y = "Correlation (higher is better)",
      x = "Model Family",
      fill = "Model Type"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      strip.text = element_text(size = 11, face = "bold")
    )
  
  # Plot RMSE
  p_rmse <- ggplot(param_data, aes(x = model_family_label, y = rmse, fill = model_type)) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    facet_wrap(~ parameter, scales = "free_y", ncol = 3) +
    scale_fill_brewer(palette = "Set2") +
    labs(
      title = paste("Parameter Recovery (RMSE) for", param_type_focus, "Parameters"),
      y = "RMSE (lower is better)",
      x = "Model Family",
      fill = "Model Type"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      strip.text = element_text(size = 11, face = "bold")
    )
  
  return(list(correlation = p_corr, rmse = p_rmse))
}

# Loop through each parameter type to create focused plots
for (param_type in unique(params_df$param_type)) {
  cat(paste("\n##", param_type, "Parameters\n"))
  param_plots <- plot_by_parameter_type(param_type)
  if (!is.null(param_plots)) {
    print(param_plots$correlation)
    print(param_plots$rmse)
  }
}
```

# Best Performing Models by Parameter

Now let's identify which models perform best for each parameter:

```{r best-models}
# Create a summary visualization of best-performing models by parameter
param_summary <- params_df %>%
  group_by(parameter, param_type) %>%
  # For each parameter, find which model performs best
  summarize(
    best_corr_model = model_display[which.max(correlation)],
    best_corr_value = max(correlation, na.rm = TRUE),
    best_rmse_model = model_display[which.min(rmse)],
    best_rmse_value = min(rmse, na.rm = TRUE),
    .groups = "drop"
  )

# Plot best models by parameter (Correlation)
ggplot(param_summary, aes(x = parameter, y = best_corr_value, fill = best_corr_model)) +
  geom_col() +
  facet_wrap(~ param_type, scales = "free_x", ncol = 2) +
  scale_fill_viridis_d() +
  scale_y_continuous(limits = c(0, 1)) +
  labs(
    title = "Best Performing Models by Parameter (Correlation)",
    y = "Maximum Correlation",
    x = "Parameter",
    fill = "Best Model"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    strip.text = element_text(size = 11, face = "bold")
  )

# Plot best models by parameter (RMSE)
ggplot(param_summary, aes(x = parameter, y = best_rmse_value, fill = best_rmse_model)) +
  geom_col() +
  facet_wrap(~ param_type, scales = "free", ncol = 2) +
  scale_fill_viridis_d() +
  labs(
    title = "Best Performing Models by Parameter (RMSE)",
    y = "Minimum RMSE",
    x = "Parameter",
    fill = "Best Model"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    strip.text = element_text(size = 11, face = "bold")
  )
```

# Model Performance Summary

Let's create a summary of model performance based on parameter recovery:

```{r model-summary}
# Aggregate model performance across parameter types
model_performance <- params_df %>%
  group_by(model, model_display, model_type, param_type) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    mean_rmse = mean(rmse, na.rm = TRUE),
    parameter_count = n(),
    .groups = "drop"
  ) %>%
  group_by(model, model_display, model_type) %>%
  summarize(
    overall_correlation = mean(mean_correlation, na.rm = TRUE),
    overall_rmse = mean(mean_rmse, na.rm = TRUE),
    best_param_type = param_type[which.max(mean_correlation)],
    best_param_correlation = max(mean_correlation, na.rm = TRUE),
    worst_param_type = param_type[which.min(mean_correlation)],
    worst_param_correlation = min(mean_correlation, na.rm = TRUE),
    param_type_count = n(),
    .groups = "drop"
  ) %>%
  arrange(desc(overall_correlation))

# Display the model performance table
kable(model_performance, digits = 3,
      col.names = c("Model", "Display Name", "Type", "Overall Correlation", "Overall RMSE", 
                     "Best Parameter Type", "Best Param Correlation", 
                     "Worst Parameter Type", "Worst Param Correlation", "# Param Types"),
      caption = "Model Recovery Performance Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Create a bar chart of overall model performance
ggplot(model_performance, 
       aes(x = reorder(as.character(model_display), overall_correlation), 
           y = overall_correlation, 
           fill = model_type)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.3f", overall_correlation)),
            position = position_stack(vjust = 0.5),
            color = "white") +
  coord_flip() +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  labs(title = "Overall Model Recovery Performance",
       subtitle = "Based on parameter recovery correlation",
       x = NULL,
       y = "Mean Correlation",
       fill = "Model Type")

# Create a visualization that shows both correlation and RMSE
ggplot(model_performance, 
       aes(x = overall_correlation, y = 1/overall_rmse, 
           color = model_type, label = model_display)) +
  geom_point(size = 4, alpha = 0.7) +
  geom_text_repel(box.padding = 0.5, point.padding = 0.5) +
  scale_color_brewer(palette = "Set2") +
  theme_minimal() +
  labs(title = "Model Recovery Performance Tradeoff",
       subtitle = "Better models are in the upper-right (high correlation, low RMSE)",
       x = "Correlation (higher is better)",
       y = "1/RMSE (higher is better)",
       color = "Model Type")

# Visualize parameter type performance by model
param_type_by_model <- params_df %>%
  group_by(model_display, param_type) %>%
  summarize(
    mean_correlation = mean(correlation, na.rm = TRUE),
    .groups = "drop"
  )

ggplot(param_type_by_model, 
       aes(x = model_display, y = mean_correlation, fill = param_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Parameter Type Recovery by Model",
       x = "Model",
       y = "Mean Correlation",
       fill = "Parameter Type")
```