---
title: "Model Comparison Report: {{TASK}} - {{COHORT}}"
subtitle: "{{COMPARISON_NAME}}"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: hide
    df_print: paged
params:
  results_file: "{{RESULTS_FILE}}"
  task: "{{TASK}}"
  cohort: "{{COHORT}}"
  session: "{{SESSION}}"
  comparison_name: "{{COMPARISON_NAME}}"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 10, fig.height = 6, dpi = 300)

# Load required libraries
suppressPackageStartupMessages({
  library(dplyr)
  library(ggplot2)
  library(knitr)
  library(DT)
  library(plotly)
  library(here)
  library(rlang)
})

# Load results
results <- readRDS(params$results_file)
comparison_data <- results$comparison_data
analysis_results <- results$analysis_results
models_by_type <- results$models_by_type
config <- results$config

# Load helper functions
source(file.path(here::here(), "scripts", "model_comparison", "helpers", "model_comparison_helpers.R"))
source(file.path(here::here(), "scripts", "model_comparison", "visualization", "comparison_plots.R"))
source(file.path(here::here(), "scripts", "ppc", "helpers", "task_config.R"))
```

# Executive Summary

## Key Findings

```{r executive-summary}
# Create executive summary table
summary_table <- data.frame(
  Criterion = character(),
  Best_Model = character(), 
  Performance = character(),
  Notes = character(),
  stringsAsFactors = FALSE
)

# Information Criteria Winner
if ("ic" %in% names(analysis_results) && nrow(analysis_results$ic$overall_ranking) > 0) {
  best_ic_model <- analysis_results$ic$overall_ranking$model[1]
  ic_method <- analysis_results$ic$metadata$ic_method
  delta_col <- grep("^delta_", names(analysis_results$ic$overall_ranking), value = TRUE)[1]
  best_delta <- analysis_results$ic$overall_ranking[[delta_col]][1]
  
  summary_table <- rbind(summary_table, data.frame(
    Criterion = paste("Information Criteria (", toupper(ic_method), ")", sep = ""),
    Best_Model = best_ic_model,
    Performance = sprintf("Δ%s = %.2f", toupper(ic_method), best_delta),
    Notes = analysis_results$ic$overall_ranking$performance_tier[1]
  ))
}

# Parameter Recovery Winner
if ("recovery" %in% names(analysis_results) && nrow(analysis_results$recovery$model_summary) > 0) {
  best_recovery_model <- analysis_results$recovery$model_summary$model[1]
  best_recovery_score <- analysis_results$recovery$model_summary$mean_correlation[1]
  
  summary_table <- rbind(summary_table, data.frame(
    Criterion = "Parameter Recovery",
    Best_Model = best_recovery_model,
    Performance = sprintf("r = %.3f", best_recovery_score),
    Notes = analysis_results$recovery$model_summary$recovery_quality[1]
  ))
}

# PPC Winner
if ("ppc" %in% names(analysis_results) && nrow(analysis_results$ppc$model_summary) > 0) {
  best_ppc_model <- analysis_results$ppc$model_summary$model[1]
  best_ppc_score <- analysis_results$ppc$model_summary$overall_proportion_extreme[1]
  
  summary_table <- rbind(summary_table, data.frame(
    Criterion = "Posterior Predictive Checks",
    Best_Model = best_ppc_model,
    Performance = sprintf("%.1f%% extreme", best_ppc_score * 100),
    Notes = analysis_results$ppc$model_summary$model_quality[1]
  ))
}

kable(summary_table, caption = "Model Comparison Summary") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
```

## Models Analyzed

```{r models-analyzed}
models_table <- data.frame(
  Model = names(comparison_data),
  Type = sapply(names(comparison_data), classify_model_type),
  Has_Recovery = sapply(comparison_data, function(x) !is.null(x$recovery)),
  Has_PPC = sapply(comparison_data, function(x) !is.null(x$ppc)),
  Has_IC = sapply(comparison_data, function(x) !is.null(x$ic)),
  stringsAsFactors = FALSE
)

models_table$Complete <- models_table$Has_Recovery & models_table$Has_PPC & models_table$Has_IC

kable(models_table, caption = "Available Data by Model") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
  kableExtra::column_spec(6, background = ifelse(models_table$Complete, "#d4edda", "#f8d7da"))
```

# Information Criteria Analysis

{{IC_SECTION}}

# Parameter Recovery Analysis

{{RECOVERY_SECTION}}

# Posterior Predictive Checks

{{PPC_SECTION}}

# Model Type Comparisons

{{MODEL_TYPE_SECTION}}

# Task-Specific Analysis

{{TASK_SPECIFIC_SECTION}}

# Detailed Model Profiles

{{MODEL_PROFILES_SECTION}}

# Conclusions and Recommendations

## Overall Model Ranking

```{r overall-ranking}
if ("integrated_ranking" %in% names(analysis_results)) {
  # Use integrated ranking if available
  integrated_ranking <- analysis_results$integrated_ranking$consensus_ranking %>%
    select(consensus_rank, model, model_type, overall_quality, 
           ic_score, recovery_score, ppc_score, rank_stability) %>%
    mutate(across(c(ic_score, recovery_score, ppc_score, rank_stability), ~round(.x, 3)))
  
  DT::datatable(integrated_ranking, 
                caption = "Integrated Model Ranking (Consensus across all metrics)",
                options = list(pageLength = 15, scrollX = TRUE)) %>%
    DT::formatStyle("overall_quality",
                    backgroundColor = DT::styleEqual(
                      c("excellent_all_around", "strong_overall", "good_balanced", 
                        "strong_but_uneven", "adequate_performance", "needs_improvement"),
                      c("#d4edda", "#d1ecf1", "#fff3cd", "#ffeaa7", "#fdcb6e", "#f8d7da")
                    ))
  
  cat("\n\n### Methodology\n\n")
  cat("This integrated ranking combines:
")
  cat("- **Information Criteria (IC):** Model fit with complexity penalty\n")
  cat("- **Parameter Recovery:** Ability to recover true parameter values\n")
  cat("- **Posterior Predictive Checks (PPC):** Reproduction of behavioral patterns\n\n")
  
  cat("**Weighting schemes used:**\n")
  cat("- Equal: 33% each metric\n")
  cat("- IC-weighted: 50% IC, 25% recovery, 25% PPC\n")
  cat("- Balanced: 40% IC, 30% recovery, 30% PPC\n\n")
  
  cat("**Consensus rank:** Median rank across all weighting schemes\n")
  cat("**Rank stability:** Lower values indicate more consistent ranking across schemes\n\n")
  
} else if ("ic" %in% names(analysis_results) && nrow(analysis_results$ic$overall_ranking) > 0) {
  # Fall back to IC ranking only if integrated ranking not available
  ranking_display <- analysis_results$ic$overall_ranking %>%
    select(rank, model, model_type, matches("estimate$"), matches("^delta_"), 
           model_weight, performance_tier) %>%
    mutate(across(where(is.numeric), ~round(.x, 3)))
  
  DT::datatable(ranking_display, 
                caption = "Model Ranking (Information Criteria Only)",
                options = list(pageLength = 15, scrollX = TRUE)) %>%
    DT::formatStyle("performance_tier",
                    backgroundColor = DT::styleEqual(
                      c("top_tier", "competitive", "considerable_difference", "strong_difference", "decisive_difference"),
                      c("#d4edda", "#fff3cd", "#ffeaa7", "#fdcb6e", "#e17055")
                    ))
  
  cat("\n\n**Note:** This ranking is based on Information Criteria only. ",
      "For comprehensive evaluation, include parameter recovery and PPC analysis.\n\n")
  
} else {
  cat("No ranking data available.")
}
```

## Key Insights

```{r insights}
insights <- list()

# Integrated ranking insights (preferred)
if ("integrated_ranking" %in% names(analysis_results)) {
  consensus_ranking <- analysis_results$integrated_ranking$consensus_ranking
  best_model <- consensus_ranking$model[1]
  best_quality <- consensus_ranking$overall_quality[1]
  
  insights$integrated <- paste("**Best overall model (integrated ranking):**", best_model, 
                              "with", gsub("_", " ", best_quality), "performance")
  
  # Top tier models (consensus rank <= 3 or top 25%)
  top_threshold <- max(3, round(nrow(consensus_ranking) * 0.25))
  top_models <- consensus_ranking$model[consensus_ranking$consensus_rank <= top_threshold]
  
  if (length(top_models) > 1) {
    insights$top_models <- paste("**Top-performing models:**", paste(top_models, collapse = ", "))
  }
  
  # Stability insights
  stable_models <- consensus_ranking %>%
    filter(rank_stability <= quantile(rank_stability, 0.25, na.rm = TRUE)) %>%
    pull(model)
  
  if (length(stable_models) > 0) {
    insights$stability <- paste("**Most stable rankings:**", paste(head(stable_models, 3), collapse = ", "),
                               "- consistent performance across weighting schemes")
  }
  
  # Quality distribution
  quality_summary <- table(consensus_ranking$overall_quality)
  excellent_count <- sum(quality_summary[grepl("excellent|strong", names(quality_summary))], na.rm = TRUE)
  
  if (excellent_count > 0) {
    insights$quality_dist <- paste("**High-quality models:**", excellent_count, "out of", 
                                  nrow(consensus_ranking), "models show excellent or strong overall performance")
  }
}

# IC insights (fallback or additional)
if ("ic" %in% names(analysis_results)) {
  ic_ranking <- analysis_results$ic$overall_ranking
  top_tier_models <- ic_ranking %>%
    filter(performance_tier == "top_tier") %>%
    pull(model)
  
  if (length(top_tier_models) == 1) {
    insights$ic <- paste("**Clear IC winner:**", top_tier_models[1])
  } else if (length(top_tier_models) > 1) {
    insights$ic <- paste("**Multiple competitive models (IC):**", paste(top_tier_models, collapse = ", "))
  }
}

# Recovery insights
if ("recovery" %in% names(analysis_results)) {
  best_groups <- head(analysis_results$recovery$group_summary$group, 3)
  worst_groups <- tail(analysis_results$recovery$group_summary$group, 3)
  
  insights$recovery <- paste("**Parameter Recovery:** Best recovered groups:", paste(best_groups, collapse = ", "),
                           ". Most challenging:", paste(worst_groups, collapse = ", "))
}

# PPC insights
if ("ppc" %in% names(analysis_results)) {
  difficult_domains <- analysis_results$ppc$domain_summary %>%
    arrange(desc(proportion_extreme)) %>%
    head(2) %>%
    pull(domain)
  
  insights$ppc <- paste("**PPC Performance:** Most challenging behavioral domains:", paste(difficult_domains, collapse = ", "))
}

for (i in seq_along(insights)) {
  cat("**", names(insights)[i], "**: ", insights[[i]], "\n\n")
}
```

## Recommendations

Based on the comprehensive analysis:

```{r recommendations}
# Generate data-driven recommendations
recommendations <- list()

if ("ic" %in% names(analysis_results)) {
  ic_ranking <- analysis_results$ic$overall_ranking
  
  # Top recommendation
  best_model <- ic_ranking$model[1]
  best_tier <- ic_ranking$performance_tier[1]
  
  if (best_tier == "top_tier") {
    recommendations$primary <- paste("**Primary recommendation:** Use", best_model, "as it shows the best overall fit to the data.")
  } else {
    recommendations$primary <- paste("**Primary recommendation:** Consider", best_model, "but note that model selection is less decisive.")
  }
  
  # Alternative recommendations
  competitive_models <- ic_ranking %>%
    filter(performance_tier %in% c("top_tier", "competitive")) %>%
    filter(row_number() > 1) %>%
    pull(model)
  
  if (length(competitive_models) > 0) {
    recommendations$alternatives <- paste("**Alternative options:** Consider", paste(competitive_models, collapse = ", "), "as competitive alternatives.")
  }
}

# Type-specific recommendations
if (length(models_by_type) > 1) {
  type_winners <- sapply(names(models_by_type), function(type) {
    type_models <- models_by_type[[type]]
    if ("ic" %in% names(analysis_results)) {
      type_ranking <- analysis_results$ic$overall_ranking %>%
        filter(model %in% type_models) %>%
        arrange(rank)
      if (nrow(type_ranking) > 0) {
        return(type_ranking$model[1])
      }
    }
    return(NA)
  })
  
  type_winners <- type_winners[!is.na(type_winners)]
  
  if (length(type_winners) > 0) {
    type_text <- paste(names(type_winners), ":", type_winners, collapse = "; ")
    recommendations$by_type <- paste("**Best by model type:** ", type_text)
  }
}

for (rec in recommendations) {
  cat(rec, "\n\n")
}
```

---

*Report generated on `r Sys.time()` using the model comparison pipeline.*

*Analysis included {{N_MODELS}} models with data from parameter recovery, posterior predictive checks, and information criteria.*
