---
title: "IGT ORL Model Parameter Analysis Across Adolescence"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 6)
```

```{r load-packages}
library(tidyverse)
library(here)
library(broom)
library(corrr)
library(ggcorrplot)
library(car)
library(emmeans)
library(patchwork)
library(knitr)
library(kableExtra)

# Set theme for plots
theme_set(theme_minimal(base_size = 12))
```

# Configuration

```{r config}
# Model configuration - easy to change
MODEL_TYPE <- "orl"  # Change to "vse" for VSE model
SESSION <- "00"

# Parameter names for each model
VSE_PARAMS <- c("con", "gain", "loss", "decay", "explore_alpha", "explore_bonus")
ORL_PARAMS <- c("Arew", "Apun", "K", "betaF", "betaP")

# Select current parameters
CURRENT_PARAMS <- if(MODEL_TYPE == "vse") VSE_PARAMS else ORL_PARAMS

# File paths
DATA_PATH <- file.path(here(), "Data/raw/luc/igt_luc_00.csv")
DEMO_PATH <- file.path(here(), "Data/raw/luc/igt_luc_00_demo.csv")
RDS_PATH <- file.path(here(), paste0("Data/igt/rds/fit/luc/task-igt_cohort-luc_ses-", SESSION, "_group-hier_model-", MODEL_TYPE, "_type-fit_desc-output.rds"))

print(paste("Analysis configuration:", MODEL_TYPE, "model"))
print(paste("Parameters:", paste(CURRENT_PARAMS, collapse = ", ")))
```

# Data Loading and Preprocessing

```{r load-data}
# Load behavioral data
raw_data <- read_csv(DATA_PATH)

# Load demographics data
demo_data <- read_csv(DEMO_PATH) %>%
  rename(subjID = ID) %>%  # Match column names - it's ID not subid!
  mutate(
    gender = factor(ifelse(Gender == 1, "Male", "Female")),
    age_continuous = Age,
    iq = FIQ  # It's FIQ not WASI!
  ) %>%
  select(subjID, gender, age_continuous, iq)

# Load model fit
model_fit <- readRDS(RDS_PATH)

# Extract summary statistics
fit_summary <- model_fit$summary_stats

print("Data loaded successfully")
print(paste("N trials:", nrow(raw_data)))
print(paste("N unique subjects in behavioral data:", n_distinct(raw_data$subjID)))
print(paste("N unique subjects in demographics:", n_distinct(demo_data$subjID)))
print(paste("N parameters in fit:", nrow(fit_summary)))
```

```{r extract-parameters}
# Create subject mapping (position to subjID)
subject_mapping <- raw_data %>%
  select(subjID) %>%
  distinct() %>%
  arrange(subjID) %>%
  mutate(sub_index = row_number())

print("Subject mapping created:")
print(paste("N subjects:", nrow(subject_mapping)))

# Extract individual parameter estimates (medians)
extract_param_estimates <- function(fit_summary, param_name, subject_mapping) {
  # Get parameter rows for this parameter
  param_rows <- fit_summary %>%
    filter(str_detect(variable, paste0("^", param_name, "\\["))) %>%
    mutate(sub_index = as.numeric(str_extract(variable, "(?<=\\[)\\d+(?=\\])"))) %>%
    select(sub_index, median) %>%
    rename(!!param_name := median)
  
  # Join with subject mapping
  subject_mapping %>%
    left_join(param_rows, by = "sub_index") %>%
    select(subjID, !!param_name)
}

# Extract all parameters
param_data <- subject_mapping %>% select(subjID)

for(param in CURRENT_PARAMS) {
  param_estimates <- extract_param_estimates(fit_summary, param, subject_mapping)
  param_data <- param_data %>%
    left_join(param_estimates, by = "subjID")
}

print("Parameter extraction completed")
print(paste("Parameters extracted:", paste(names(param_data)[-1], collapse = ", ")))
```

```{r create-performance-metrics}
# Calculate IGT performance metrics
igt_performance <- raw_data %>%
  group_by(subjID) %>%
  summarise(
    # Advantageous deck selections (assuming decks 3,4 are advantageous based on common IGT)
    adv_deck_selections = sum(choice %in% c(3, 4), na.rm = TRUE),
    total_trials = n(),
    prop_adv_selections = adv_deck_selections / total_trials,
    
    # Net score (total wins - total losses)
    total_wins = sum(wins, na.rm = TRUE),
    total_losses = sum(abs(losses), na.rm = TRUE),  # losses are typically negative
    net_score = total_wins - total_losses,
    
    .groups = 'drop'
  )

print("Performance metrics calculated")
head(igt_performance)
```

```{r merge-datasets}
# Get subject demographics from behavioral data
demographics <- raw_data %>%
  select(subjID, age_group) %>%
  distinct() %>%
  # Fix age group ordering for plots
  mutate(age_group = factor(age_group, levels = c("Early", "Middle", "Late")))

# Merge with demographics data
demographics <- demographics %>%
  left_join(demo_data, by = "subjID")

# Check data completeness
missing_demo <- demographics %>%
  summarise(
    missing_gender = sum(is.na(gender)),
    missing_age = sum(is.na(age_continuous)),
    missing_iq = sum(is.na(iq))
  )

print("Missing demographics data:")
print(missing_demo)

# Merge all data
analysis_data <- demographics %>%
  left_join(param_data, by = "subjID") %>%
  left_join(igt_performance, by = "subjID")

print("Final analysis dataset created")
print(paste("N subjects in final dataset:", nrow(analysis_data)))
print("Age group distribution:")
table(analysis_data$age_group)
print("Gender distribution:")
table(analysis_data$gender, useNA = "ifany")
```

```{r check-outliers}
# Function to identify outliers (99.9th percentile)
identify_outliers <- function(x, threshold = 0.999) {
  cutoff <- quantile(x, threshold, na.rm = TRUE)
  which(x > cutoff)
}

# Check for outliers in parameters and performance metrics
numeric_vars <- analysis_data %>% 
  select(all_of(CURRENT_PARAMS), adv_deck_selections, net_score) %>%
  names()

outlier_summary <- map_dfr(numeric_vars, function(var) {
  outliers <- identify_outliers(analysis_data[[var]])
  tibble(
    variable = var,
    n_outliers = length(outliers),
    outlier_threshold = quantile(analysis_data[[var]], 0.999, na.rm = TRUE),
    outlier_subjects = ifelse(length(outliers) > 0, 
                             paste(analysis_data$subjID[outliers], collapse = ", "), 
                             "None")
  )
})

print("Outlier summary (99.9th percentile):")
outlier_summary %>% kable() %>% kable_styling()
```

```{r normality-checks}
# Test normality for key variables
normality_tests <- map_dfr(numeric_vars, function(var) {
  shapiro_result <- shapiro.test(analysis_data[[var]])
  tibble(
    variable = var,
    shapiro_p = shapiro_result$p.value,
    normal = shapiro_p > 0.05
  )
})

print("Normality tests (Shapiro-Wilk):")
normality_tests %>% 
  mutate(shapiro_p = round(shapiro_p, 4)) %>%
  kable() %>% 
  kable_styling()
```

```{r transformations}
# Apply transformations to improve normality

# First, calculate Box-Cox lambda for betaP outside of mutate
betaP_shifted <- analysis_data$betaP + abs(min(analysis_data$betaP, na.rm = TRUE)) + 1
bc_result <- car::boxCox(lm(betaP_shifted ~ 1), plotit = FALSE)
optimal_lambda <- bc_result$x[which.max(bc_result$y)]

print(paste("Optimal Box-Cox lambda for betaP:", round(optimal_lambda, 3)))

transform_data <- analysis_data %>%
  mutate(
    # Log transforms for bounded parameters
    Arew_log = log(Arew),
    Apun_log = log(Apun),
    K_log = log(K),
    
    # Alternative transforms for still non-normal variables
    Apun_sqrt = sqrt(Apun),
    K_sqrt = sqrt(K),
    
    # Box-Cox transform for betaP
    betaP_shifted = betaP + abs(min(betaP, na.rm = TRUE)) + 1,
    betaP_bc = if(abs(optimal_lambda) < 0.1) {
      log(betaP_shifted)
    } else {
      (betaP_shifted^optimal_lambda - 1) / optimal_lambda
    },
    
    # Rank-based transforms as backup (convert to normal scores)
    Apun_rank = qnorm((rank(Apun) - 0.5) / n()),
    K_rank = qnorm((rank(K) - 0.5) / n()),
    betaP_rank = qnorm((rank(betaP) - 0.5) / n())
  )

# Test normality of transformed variables
transform_vars <- c("Arew_log", "Apun_log", "K_log", "Apun_sqrt", "K_sqrt", 
                   "betaP_bc", "Apun_rank", "K_rank", "betaP_rank")

transform_normality <- map_dfr(transform_vars, function(var) {
  if(var %in% names(transform_data)) {
    shapiro_result <- shapiro.test(transform_data[[var]])
    tibble(
      variable = var,
      shapiro_p = shapiro_result$p.value,
      normal = shapiro_p > 0.05,
      transform_type = case_when(
        str_ends(var, "_log") ~ "Log",
        str_ends(var, "_sqrt") ~ "Square root", 
        str_ends(var, "_bc") ~ "Box-Cox",
        str_ends(var, "_rank") ~ "Rank-based",
        TRUE ~ "Other"
      )
    )
  } else {
    tibble(variable = var, shapiro_p = NA, normal = NA, transform_type = "Missing")
  }
})

print("Normality tests for transformed variables:")
transform_normality %>% 
  mutate(shapiro_p = round(shapiro_p, 4)) %>%
  arrange(transform_type, variable) %>%
  kable() %>% 
  kable_styling()

# Summary of best transforms
best_transforms <- tibble(
  original = c("Arew", "Apun", "K", "betaF", "betaP"),
  original_normal = c(
    normality_tests$normal[normality_tests$variable == "Arew"],
    normality_tests$normal[normality_tests$variable == "Apun"], 
    normality_tests$normal[normality_tests$variable == "K"],
    normality_tests$normal[normality_tests$variable == "betaF"],
    normality_tests$normal[normality_tests$variable == "betaP"]
  )
) %>%
  mutate(
    recommended_transform = case_when(
      original == "Arew" ~ "Arew_log",
      original == "Apun" ~ {
        apun_sqrt_normal <- transform_normality$normal[transform_normality$variable == "Apun_sqrt"]
        if(length(apun_sqrt_normal) > 0 && !is.na(apun_sqrt_normal) && apun_sqrt_normal) {
          "Apun_sqrt"
        } else {
          "Apun_rank"
        }
      },
      original == "K" ~ {
        k_sqrt_normal <- transform_normality$normal[transform_normality$variable == "K_sqrt"]
        if(length(k_sqrt_normal) > 0 && !is.na(k_sqrt_normal) && k_sqrt_normal) {
          "K_sqrt"
        } else {
          "K_rank"
        }
      },
      original == "betaF" ~ "betaF (already normal)",
      original == "betaP" ~ "betaP_bc"
    )
  )

print("Recommended transformations:")
best_transforms %>% kable() %>% kable_styling()

# Note about proceeding with analyses
cat("\n=== ANALYSIS STRATEGY ===\n")
cat("Given that log transforms didn't achieve normality for all parameters:\n")
cat("1. Primary analyses use original parameters (more interpretable)\n") 
cat("2. Non-parametric alternatives provided for robustness\n")
cat("3. Transformed variables available if needed for specific analyses\n")
cat("4. Outlier sensitivity analyses included\n\n")

# Create transformed dataset without outliers  
transform_data_no_outliers <- transform_data %>%
  filter(!subjID %in% outlier_summary$outlier_subjects)
```

```{r outlier-handling}
# Create datasets with and without outliers
outlier_subjects <- outlier_summary %>%
  filter(n_outliers > 0) %>%
  pull(outlier_subjects) %>%
  str_split(", ") %>%
  unlist() %>%
  unique() %>%
  .[. != "None"] %>%
  as.numeric()

print(paste("Outlier subjects to be excluded:", paste(outlier_subjects, collapse = ", ")))

# Create analysis datasets
analysis_data_no_outliers <- analysis_data %>%
  filter(!subjID %in% outlier_subjects)

print(paste("N subjects after outlier removal:", nrow(analysis_data_no_outliers)))
```

# Descriptive Statistics

```{r descriptive-stats}
# Overall descriptive statistics
desc_stats <- analysis_data %>%
  select(all_of(CURRENT_PARAMS), adv_deck_selections, net_score) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarise(
    n = sum(!is.na(value)),
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    mad = mad(value, na.rm = TRUE),
    min = min(value, na.rm = TRUE),
    max = max(value, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(across(where(is.numeric), round, 3))

print("Descriptive statistics:")
desc_stats %>% kable() %>% kable_styling()
```

```{r descriptive-by-age-group}
# Descriptive statistics by age group
desc_by_age <- analysis_data %>%
  select(age_group, all_of(CURRENT_PARAMS), adv_deck_selections, net_score) %>%
  pivot_longer(-age_group, names_to = "variable", values_to = "value") %>%
  group_by(age_group, variable) %>%
  summarise(
    n = sum(!is.na(value)),
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(across(where(is.numeric), round, 3))

print("Descriptive statistics by age group:")
desc_by_age %>% 
  kable() %>% 
  kable_styling() %>%
  scroll_box(height = "400px")
```

# Analysis 1: Age-Related Differences in Parameters

## Age Group Comparisons

```{r age-group-comparisons}
# Function to run ANOVA and pairwise comparisons
run_age_group_analysis <- function(data, outcome_var) {
  # ANOVA
  formula_str <- paste(outcome_var, "~ age_group")
  aov_model <- aov(as.formula(formula_str), data = data)
  aov_summary <- summary(aov_model)
  
  # Pairwise comparisons
  emmeans_result <- emmeans(aov_model, "age_group")
  pairwise_result <- pairs(emmeans_result, adjust = "none")  # We'll do FDR later
  
  # Extract results
  tibble(
    variable = outcome_var,
    f_statistic = aov_summary[[1]][["F value"]][1],
    df_num = aov_summary[[1]][["Df"]][1],
    df_den = aov_summary[[1]][["Df"]][2],
    p_value = aov_summary[[1]][["Pr(>F)"]][1]
  )
}

# Run age group comparisons for all parameters
age_group_results <- map_dfr(CURRENT_PARAMS, ~run_age_group_analysis(analysis_data, .x))

# Add FDR correction
age_group_results <- age_group_results %>%
  mutate(
    p_fdr = p.adjust(p_value, method = "fdr"),
    sig_uncorrected = p_value < 0.05,
    sig_fdr = p_fdr < 0.05
  )

print("Age group comparison results:")
age_group_results %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  kable() %>%
  kable_styling()
```

```{r pairwise-comparisons}
# Function to get pairwise comparison details for significant results
get_pairwise_details <- function(data, outcome_var) {
  formula_str <- paste(outcome_var, "~ age_group")
  aov_model <- aov(as.formula(formula_str), data = data)
  emmeans_result <- emmeans(aov_model, "age_group")
  pairwise_result <- pairs(emmeans_result, adjust = "none")
  
  as_tibble(pairwise_result) %>%
    mutate(variable = outcome_var) %>%
    select(variable, contrast, estimate, SE, df, t.ratio, p.value)
}

# Get pairwise details for significant parameters (uncorrected)
sig_params <- age_group_results %>%
  filter(sig_uncorrected) %>%
  pull(variable)

if(length(sig_params) > 0) {
  pairwise_details <- map_dfr(sig_params, ~get_pairwise_details(analysis_data, .x))
  
  # Add FDR correction across all pairwise tests
  pairwise_details <- pairwise_details %>%
    mutate(
      p_fdr = p.adjust(p.value, method = "fdr"),
      sig_uncorrected = p.value < 0.05,
      sig_fdr = p_fdr < 0.05
    )
  
  print("Pairwise comparison details:")
  pairwise_details %>%
    mutate(across(where(is.numeric), round, 4)) %>%
    kable() %>%
    kable_styling()
} else {
  print("No significant age group effects found for parameters")
}
```

```{r nonparametric-age-comparisons}
# Non-parametric alternatives (Kruskal-Wallis tests)
kruskal_results <- map_dfr(CURRENT_PARAMS, function(param) {
  kw_test <- kruskal.test(analysis_data[[param]] ~ analysis_data$age_group)
  tibble(
    variable = param,
    chi_squared = kw_test$statistic,
    df = kw_test$parameter,
    p_value = kw_test$p.value
  )
})

# Add FDR correction
kruskal_results <- kruskal_results %>%
  mutate(
    p_fdr = p.adjust(p_value, method = "fdr"),
    sig_uncorrected = p_value < 0.05,
    sig_fdr = p_fdr < 0.05
  )

print("Non-parametric age group comparisons (Kruskal-Wallis):")
kruskal_results %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  kable() %>%
  kable_styling()

# Post-hoc tests for significant Kruskal-Wallis results
if(any(kruskal_results$sig_uncorrected)) {
  sig_kw_params <- kruskal_results %>%
    filter(sig_uncorrected) %>%
    pull(variable)
  
  print("Post-hoc pairwise comparisons (Dunn test) for significant Kruskal-Wallis results:")
  
  dunn_results <- map_dfr(sig_kw_params, function(param) {
    # Manual pairwise Mann-Whitney tests
    groups <- levels(analysis_data$age_group)
    comparisons <- combn(groups, 2, simplify = FALSE)
    
    map_dfr(comparisons, function(comp) {
      group1_data <- analysis_data %>% filter(age_group == comp[1]) %>% pull(!!sym(param))
      group2_data <- analysis_data %>% filter(age_group == comp[2]) %>% pull(!!sym(param))
      
      wt_result <- wilcox.test(group1_data, group2_data)
      
      tibble(
        variable = param,
        comparison = paste(comp[1], "vs", comp[2]),
        W = wt_result$statistic,
        p_value = wt_result$p.value
      )
    })
  })
  
  # Add FDR correction for post-hoc tests
  dunn_results <- dunn_results %>%
    mutate(
      p_fdr = p.adjust(p_value, method = "fdr"),
      sig_uncorrected = p_value < 0.05,
      sig_fdr = p_fdr < 0.05
    )
  
  dunn_results %>%
    mutate(across(where(is.numeric), round, 4)) %>%
    kable() %>%
    kable_styling()
}
```

```{r age-comparisons-no-outliers}
# Repeat age group comparisons without outliers
print("=== AGE GROUP COMPARISONS WITHOUT OUTLIERS ===")

age_group_results_no_outliers <- map_dfr(CURRENT_PARAMS, ~run_age_group_analysis(analysis_data_no_outliers, .x))

age_group_results_no_outliers <- age_group_results_no_outliers %>%
  mutate(
    p_fdr = p.adjust(p_value, method = "fdr"),
    sig_uncorrected = p_value < 0.05,
    sig_fdr = p_fdr < 0.05
  )

print("Age group comparison results (no outliers):")
age_group_results_no_outliers %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  kable() %>%
  kable_styling()

# Pairwise comparisons for significant results without outliers
sig_params_no_outliers <- age_group_results_no_outliers %>%
  filter(sig_uncorrected) %>%
  pull(variable)

if(length(sig_params_no_outliers) > 0) {
  pairwise_details_no_outliers <- map_dfr(sig_params_no_outliers, ~get_pairwise_details(analysis_data_no_outliers, .x))
  
  pairwise_details_no_outliers <- pairwise_details_no_outliers %>%
    mutate(
      p_fdr = p.adjust(p.value, method = "fdr"),
      sig_uncorrected = p.value < 0.05,
      sig_fdr = p_fdr < 0.05
    )
  
  print("Pairwise comparison details (no outliers):")
  pairwise_details_no_outliers %>%
    mutate(across(where(is.numeric), round, 4)) %>%
    kable() %>%
    kable_styling()
}
```

## Visualizations: Parameters by Age Group

```{r plot-params-by-age}
# Create violin plots for parameters by age group
param_plots <- map(CURRENT_PARAMS, function(param) {
  # Check if this parameter showed significant age effects
  is_significant <- param %in% (age_group_results %>% filter(sig_fdr) %>% pull(variable))
  
  p <- analysis_data %>%
    ggplot(aes(x = age_group, y = !!sym(param), fill = age_group)) +
    geom_violin(alpha = 0.7, trim = FALSE) +
    geom_boxplot(width = 0.1, alpha = 0.8, outlier.alpha = 0.3) +
    geom_jitter(width = 0.15, alpha = 0.4, size = 0.8) +
    scale_fill_viridis_d() +
    labs(
      title = paste0(param, ifelse(is_significant, " *", "")),
      x = "Age Group",
      y = param,
      subtitle = ifelse(is_significant, "Significant age group difference (FDR corrected)", "")
    ) +
    theme(legend.position = "none")
  
  return(p)
})

# Arrange plots
wrap_plots(param_plots, ncol = 3)
```

```{r plot-params-by-age-no-outliers}
# Same plots without outliers for comparison
param_plots_no_outliers <- map(CURRENT_PARAMS, function(param) {
  is_significant <- param %in% (age_group_results %>% filter(sig_fdr) %>% pull(variable))
  
  p <- analysis_data_no_outliers %>%
    ggplot(aes(x = age_group, y = !!sym(param), fill = age_group)) +
    geom_violin(alpha = 0.7, trim = FALSE) +
    geom_boxplot(width = 0.1, alpha = 0.8, outlier.alpha = 0.3) +
    geom_jitter(width = 0.15, alpha = 0.4, size = 0.8) +
    scale_fill_viridis_d() +
    labs(
      title = paste0(param, " (No Outliers)", ifelse(is_significant, " *", "")),
      x = "Age Group",
      y = param
    ) +
    theme(legend.position = "none")
  
  return(p)
})

print("Parameter distributions without outliers:")
wrap_plots(param_plots_no_outliers, ncol = 3)
```

# Analysis 2: Parameter-Performance Relationships

## Correlations

```{r parameter-performance-correlations}
# Calculate correlations between parameters and performance
perf_vars <- c("adv_deck_selections", "net_score")

correlation_results <- expand_grid(
  parameter = CURRENT_PARAMS,
  performance = perf_vars
) %>%
  rowwise() %>%
  mutate(
    cor_test = list(cor.test(analysis_data[[parameter]], analysis_data[[performance]])),
    correlation = cor_test$estimate,
    p_value = cor_test$p.value,
    ci_lower = cor_test$conf.int[1],
    ci_upper = cor_test$conf.int[2]
  ) %>%
  select(-cor_test) %>%
  ungroup()

# Add FDR correction
correlation_results <- correlation_results %>%
  mutate(
    p_fdr = p.adjust(p_value, method = "fdr"),
    sig_uncorrected = p_value < 0.05,
    sig_fdr = p_fdr < 0.05
  )

print("Parameter-Performance Correlations (Pearson):")
correlation_results %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  kable() %>%
  kable_styling()
```

```{r nonparametric-correlations}
# Non-parametric correlations (Spearman)
spearman_results <- expand_grid(
  parameter = CURRENT_PARAMS,
  performance = perf_vars
) %>%
  rowwise() %>%
  mutate(
    cor_test = list(cor.test(analysis_data[[parameter]], analysis_data[[performance]], method = "spearman")),
    correlation = cor_test$estimate,
    p_value = cor_test$p.value
  ) %>%
  select(-cor_test) %>%
  ungroup()

# Add FDR correction
spearman_results <- spearman_results %>%
  mutate(
    p_fdr = p.adjust(p_value, method = "fdr"),
    sig_uncorrected = p_value < 0.05,
    sig_fdr = p_fdr < 0.05
  )

print("Parameter-Performance Correlations (Spearman):")
spearman_results %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  kable() %>%
  kable_styling()
```

```{r correlations-no-outliers}
# Repeat correlations without outliers
print("=== CORRELATIONS WITHOUT OUTLIERS ===")

correlation_results_no_outliers <- expand_grid(
  parameter = CURRENT_PARAMS,
  performance = perf_vars
) %>%
  rowwise() %>%
  mutate(
    cor_test = list(cor.test(analysis_data_no_outliers[[parameter]], analysis_data_no_outliers[[performance]])),
    correlation = cor_test$estimate,
    p_value = cor_test$p.value,
    ci_lower = cor_test$conf.int[1],
    ci_upper = cor_test$conf.int[2]
  ) %>%
  select(-cor_test) %>%
  ungroup() %>%
  mutate(
    p_fdr = p.adjust(p_value, method = "fdr"),
    sig_uncorrected = p_value < 0.05,
    sig_fdr = p_fdr < 0.05
  )

print("Parameter-Performance Correlations without outliers (Pearson):")
correlation_results_no_outliers %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  kable() %>%
  kable_styling()
```

```{r correlation-matrix-plot}
# Create correlation matrix plot
cor_data <- analysis_data %>%
  select(all_of(CURRENT_PARAMS), adv_deck_selections, net_score) %>%
  cor(use = "complete.obs")

# Plot correlation matrix
ggcorrplot(cor_data, 
           hc.order = TRUE, 
           type = "lower",
           lab = TRUE,
           lab_size = 3,
           colors = c("#6D9EC1", "white", "#E46726")) +
  labs(title = "Parameter-Performance Correlation Matrix")
```

## Scatter Plots for Significant Correlations

```{r scatter-plots-significant}
# Create scatter plots for significant correlations
sig_correlations <- correlation_results %>%
  filter(sig_fdr) %>%
  select(parameter, performance)

if(nrow(sig_correlations) > 0) {
  scatter_plots <- pmap(sig_correlations, function(parameter, performance) {
    analysis_data %>%
      ggplot(aes(x = !!sym(parameter), y = !!sym(performance))) +
      geom_point(alpha = 0.6) +
      geom_smooth(method = "lm", se = TRUE, color = "red") +
      labs(
        title = paste(parameter, "vs", performance),
        x = parameter,
        y = performance
      )
  })
  
  wrap_plots(scatter_plots, ncol = 2)
} else {
  print("No significant parameter-performance correlations found after FDR correction")
}
```

```{r scatter-plots-no-outliers}
# Create scatter plots without outliers for comparison
if(nrow(sig_correlations) > 0) {
  scatter_plots_no_outliers <- pmap(sig_correlations, function(parameter, performance) {
    analysis_data_no_outliers %>%
      ggplot(aes(x = !!sym(parameter), y = !!sym(performance))) +
      geom_point(alpha = 0.6) +
      geom_smooth(method = "lm", se = TRUE, color = "red") +
      labs(
        title = paste(parameter, "vs", performance, "(No Outliers)"),
        x = parameter,
        y = performance
      )
  })
  
  print("Scatter plots without outliers:")
  wrap_plots(scatter_plots_no_outliers, ncol = 2)
}
```

# Analysis 3: Linear Regression Models

```{r regression-models}
# Function to run regression model
run_regression_model <- function(outcome_var, data = analysis_data_no_outliers) {
  # Create formula
  predictors <- paste(CURRENT_PARAMS, collapse = " + ")
  formula_str <- paste(outcome_var, "~", predictors)
  
  # Fit model
  model <- lm(as.formula(formula_str), data = data)
  
  # Get model summary
  model_summary <- summary(model)
  
  # Check VIF
  vif_values <- car::vif(model)
  
  # Extract results
  coef_results <- tidy(model) %>%
    filter(term != "(Intercept)") %>%
    mutate(outcome = outcome_var)
  
  model_stats <- tibble(
    outcome = outcome_var,
    r_squared = model_summary$r.squared,
    adj_r_squared = model_summary$adj.r.squared,
    f_statistic = model_summary$fstatistic[1],
    f_p_value = pf(model_summary$fstatistic[1], 
                   model_summary$fstatistic[2], 
                   model_summary$fstatistic[3], 
                   lower.tail = FALSE),
    max_vif = max(vif_values)
  )
  
  list(
    coefficients = coef_results,
    model_stats = model_stats,
    vif = vif_values,
    model = model
  )
}

# Run regression models for both performance metrics
regression_results <- map(perf_vars, run_regression_model)
names(regression_results) <- perf_vars

# Combine coefficient results
all_coefficients <- map_dfr(regression_results, "coefficients")

# Add FDR correction to coefficients
all_coefficients <- all_coefficients %>%
  mutate(
    p_fdr = p.adjust(p.value, method = "fdr"),
    sig_uncorrected = p.value < 0.05,
    sig_fdr = p_fdr < 0.05
  )

print("Regression coefficients:")
all_coefficients %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  kable() %>%
  kable_styling()

# Model statistics
model_stats <- map_dfr(regression_results, "model_stats")
print("Model statistics:")
model_stats %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  kable() %>%
  kable_styling()
```

```{r vif-check}
# Check VIF values
print("Variance Inflation Factors:")
vif_results <- map_dfr(names(regression_results), function(outcome) {
  tibble(
    outcome = outcome,
    parameter = names(regression_results[[outcome]]$vif),
    vif = regression_results[[outcome]]$vif
  )
})

vif_results %>%
  mutate(vif = round(vif, 3)) %>%
  kable() %>%
  kable_styling()

# Flag high VIF values
high_vif <- vif_results %>% filter(vif > 5)
if(nrow(high_vif) > 0) {
  print("WARNING: High VIF values detected (>5):")
  print(high_vif)
} else {
  print("All VIF values are acceptable (<5)")
}
```

```{r residual-plots}
# Create residual plots for model diagnostics
residual_plots <- map2(regression_results, names(regression_results), function(reg_result, outcome) {
  model <- reg_result$model
  
  # Get residuals and fitted values
  plot_data <- tibble(
    fitted = fitted(model),
    residuals = residuals(model),
    standardized_residuals = rstandard(model)
  )
  
  # Residuals vs Fitted
  p1 <- plot_data %>%
    ggplot(aes(x = fitted, y = residuals)) +
    geom_point(alpha = 0.6) +
    geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
    geom_smooth(se = FALSE, color = "blue") +
    labs(title = paste("Residuals vs Fitted:", outcome),
         x = "Fitted Values", y = "Residuals")
  
  # Q-Q plot
  p2 <- plot_data %>%
    ggplot(aes(sample = standardized_residuals)) +
    stat_qq() +
    stat_qq_line(color = "red") +
    labs(title = paste("Q-Q Plot:", outcome),
         x = "Theoretical Quantiles", y = "Sample Quantiles")
  
  p1 + p2
})

# Display residual plots
walk(residual_plots, print)
```

# Analysis 4: Gender Comparisons

```{r gender-analysis}
# Gender differences in parameters
gender_results <- map_dfr(CURRENT_PARAMS, function(param) {
  # Remove any missing gender data
  analysis_subset <- analysis_data_no_outliers %>% 
    filter(!is.na(gender)) %>%
    filter(!is.na(!!sym(param)))
  
  if(nrow(analysis_subset) > 0 && length(unique(analysis_subset$gender)) == 2) {
    t_test <- t.test(analysis_subset[[param]] ~ analysis_subset$gender)
    tibble(
      parameter = param,
      mean_female = t_test$estimate[1],
      mean_male = t_test$estimate[2],
      t_statistic = t_test$statistic,
      df = t_test$parameter,
      p_value = t_test$p.value,
      ci_lower = t_test$conf.int[1],
      ci_upper = t_test$conf.int[2],
      n_female = sum(analysis_subset$gender == "Female", na.rm = TRUE),
      n_male = sum(analysis_subset$gender == "Male", na.rm = TRUE)
    )
  } else {
    tibble(
      parameter = param,
      mean_female = NA, mean_male = NA, t_statistic = NA,
      df = NA, p_value = NA, ci_lower = NA, ci_upper = NA,
      n_female = NA, n_male = NA
    )
  }
})

# Add FDR correction
gender_results <- gender_results %>%
  mutate(
    p_fdr = p.adjust(p_value, method = "fdr"),
    sig_uncorrected = p_value < 0.05,
    sig_fdr = p_fdr < 0.05
  )

print("Gender comparison results:")
gender_results %>%
  mutate(across(where(is.numeric), round, 4)) %>%
  kable() %>%
  kable_styling()

# Gender by age group interactions for significant gender effects
sig_gender_params <- gender_results %>%
  filter(sig_uncorrected & !is.na(p_value)) %>%
  pull(parameter)

if(length(sig_gender_params) > 0) {
  print("Testing gender by age group interactions for significant parameters:")
  
  interaction_results <- map_dfr(sig_gender_params, function(param) {
    analysis_subset <- analysis_data %>% 
      filter(!is.na(gender)) %>%
      filter(!is.na(!!sym(param)))
    formula_str <- paste(param, "~ gender * age_group")
    aov_model <- aov(as.formula(formula_str), data = analysis_subset)
    aov_summary <- summary(aov_model)
    
    tibble(
      parameter = param,
      gender_f = aov_summary[[1]][["F value"]][1],
      gender_p = aov_summary[[1]][["Pr(>F)"]][1],
      age_f = aov_summary[[1]][["F value"]][2],
      age_p = aov_summary[[1]][["Pr(>F)"]][2],
      interaction_f = aov_summary[[1]][["F value"]][3],
      interaction_p = aov_summary[[1]][["Pr(>F)"]][3]
    )
  })
  
  interaction_results %>%
    mutate(across(where(is.numeric), round, 4)) %>%
    kable() %>%
    kable_styling()
} else {
  print("No significant gender effects found to test for interactions")
}
```

```{r gender-visualization}
# Visualize gender differences for significant parameters
if(length(sig_gender_params) > 0) {
  gender_plots <- map(sig_gender_params, function(param) {
    analysis_data %>%
      filter(!is.na(gender)) %>%
      ggplot(aes(x = gender, y = !!sym(param), fill = gender)) +
      geom_violin(alpha = 0.7, trim = FALSE) +
      geom_boxplot(width = 0.1, alpha = 0.8) +
      geom_jitter(width = 0.15, alpha = 0.4, size = 0.8) +
      scale_fill_viridis_d() +
      labs(
        title = paste("Gender differences in", param),
        x = "Gender",
        y = param
      ) +
      theme(legend.position = "none")
  })
  
  wrap_plots(gender_plots, ncol = 2)
} else {
  print("No significant gender effects to visualize")
}
```

# Summary of Results

```{r results-summary}
# Create comprehensive summary of significant findings
summary_results <- list()

# Age group effects (parametric)
age_sig <- age_group_results %>% filter(sig_fdr) %>% pull(variable)
summary_results$age_effects_parametric <- if(length(age_sig) > 0) {
  paste("Significant age group effects (ANOVA, FDR corrected):", paste(age_sig, collapse = ", "))
} else {
  "No significant age group effects found (ANOVA, FDR corrected)"
}

# Age group effects (non-parametric)
age_sig_np <- kruskal_results %>% filter(sig_fdr) %>% pull(variable)
summary_results$age_effects_nonparametric <- if(length(age_sig_np) > 0) {
  paste("Significant age group effects (Kruskal-Wallis, FDR corrected):", paste(age_sig_np, collapse = ", "))
} else {
  "No significant age group effects found (Kruskal-Wallis, FDR corrected)"
}

# Outlier sensitivity for age effects
age_sig_no_outliers <- age_group_results_no_outliers %>% filter(sig_fdr) %>% pull(variable)
summary_results$age_effects_no_outliers <- if(length(age_sig_no_outliers) > 0) {
  paste("Significant age group effects without outliers:", paste(age_sig_no_outliers, collapse = ", "))
} else {
  "No significant age group effects found without outliers"
}

# Parameter-performance correlations (Pearson)
cor_sig <- correlation_results %>% filter(sig_fdr)
summary_results$correlations_pearson <- if(nrow(cor_sig) > 0) {
  paste("Significant parameter-performance correlations (Pearson, FDR corrected):", 
        paste(paste(cor_sig$parameter, cor_sig$performance, sep = "-"), collapse = ", "))
} else {
  "No significant parameter-performance correlations found (Pearson, FDR corrected)"
}

# Parameter-performance correlations (Spearman)
cor_sig_sp <- spearman_results %>% filter(sig_fdr)
summary_results$correlations_spearman <- if(nrow(cor_sig_sp) > 0) {
  paste("Significant parameter-performance correlations (Spearman, FDR corrected):", 
        paste(paste(cor_sig_sp$parameter, cor_sig_sp$performance, sep = "-"), collapse = ", "))
} else {
  "No significant parameter-performance correlations found (Spearman, FDR corrected)"
}

# Outlier sensitivity for correlations
cor_sig_no_outliers <- correlation_results_no_outliers %>% filter(sig_fdr)
summary_results$correlations_no_outliers <- if(nrow(cor_sig_no_outliers) > 0) {
  paste("Significant correlations without outliers:", 
        paste(paste(cor_sig_no_outliers$parameter, cor_sig_no_outliers$performance, sep = "-"), collapse = ", "))
} else {
  "No significant correlations found without outliers"
}

# Regression predictors (basic model)
reg_sig_basic <- all_coefficients %>% 
  filter(sig_fdr) 
summary_results$regression_basic <- if(nrow(reg_sig_basic) > 0) {
  paste("Significant regression predictors (basic model, FDR corrected):", 
        paste(paste(reg_sig_basic$term, reg_sig_basic$outcome, sep = " → "), collapse = ", "))
} else {
  "No significant regression predictors found (basic model, FDR corrected)"
}

# Gender effects
gender_sig <- gender_results %>% filter(sig_fdr & !is.na(p_value)) %>% pull(parameter)
summary_results$gender_effects <- if(length(gender_sig) > 0) {
  paste("Significant gender effects (FDR corrected):", paste(gender_sig, collapse = ", "))
} else {
  "No significant gender effects found (FDR corrected)"
}

# Data quality notes
outlier_count <- length(outlier_subjects)
summary_results$data_quality <- paste(
  "Data quality notes:",
  paste0("- ", outlier_count, " outlier subjects identified and analyzed separately"),
  paste0("- ", sum(!normality_tests$normal), "/", nrow(normality_tests), " parameters violated normality assumptions"),
  "- Non-parametric alternatives provided for robustness",
  sep = "\n"
)

print("=== COMPREHENSIVE ANALYSIS SUMMARY ===")
iwalk(summary_results, ~cat(.y, ":\n", .x, "\n\n"))
```

```{r session-info}
sessionInfo()
```
